### 2023-05-31 main.tex
Add files via upload

\documentclass[%
%anonym,
% times,
 %referee,
 %doublespacing,
 ]{lin}

\input{localpackages}
\input{localcommands}

\begin{document}

\leftrunning{Yanru Lu \& Stefan Müller}  % Short author list

\rightrunning{An HPSG account for verbal reduplication in Mandarin Chinese} % Short title

\title{An HPSG account for verbal reduplication in Mandarin Chinese}

\author[1]{\givenname{Yanru} \surname{Lu}}

\address[1]
{%
  \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
  \addr{Unter den Linden 6}, % Street 
  \addr{D-10099 Berlin}, % Postcode etc
  \cnty{Germany}  % Country
  \email{yanru.lu@hu-berlin.de} % email
}

\author[2]{\givenname{Stefan} \surname{Müller}}

\address[2]
{%
  \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
  \addr{Unter den Linden 6}, % Street 
  \addr{D-10099 Berlin}, % Postcode etc
  \cnty{Germany}  % Country
  \email{st.mueller@hu-berlin.de} % email
}

\maketitle

\begin{abstract}
The current study presents an HPSG analysis for verbal reduplication in Mandarin Chinese. We provide a detailed description of the phenomenon. After discussing reduplication’s interaction with \textit{Aktionsarten} and aspect markers, we argue that it is a morphological rather than a syntactic process. We put forward a lexical rule for verbal reduplication in Mandarin Chinese, and the different forms of reduplication are captured in an inheritance hierarchy. The interaction between verbal reduplication and aspect marking is handled by multiple inheritance. This analysis covers all forms of verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
\keywords{HPSG, MRS, Mandarin Chinese, verbal reduplication}
\end{abstract}

\input{chapters/ch01-Intro}

\input{chapters/ch02-Phenomenon}

%\input{chapters/ch03-Theory}

\input{chapters/ch04-Previous}

\input{chapters/ch05-Analysis}

\input{chapters/ch06-Conclusion}

\renewrobustcmd{\disambiguate}[3]{#1}
\bibliographystyle{lin}

\bibliography{Bib.bib}

\end{document}

### 2023-05-31 chapters/ch01-Intro.tex
Update 2023-05-31-17:44:51

\section{Introduction}\label{sec:intro}

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \citep[e.g.][]{Chao1968, LiThompson1981,  Li1996, Dai1997,  Zhu1998, Xing2000, Chen2001,  Tsao2001, Yang2003, XiaoMcEnery2004}. 
It means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

\ea\label{ex:redup-ex} 
	\ea
	\gll qing ni chang zhe dao cai.\\
	please you taste this \textsc{clf} dish\\
	\glt `Please taste this dish.'

	\ex
	\gll qing ni \textit{chang}-\textit{chang} zhe dao cai.\\
	please you taste-taste this \textsc{clf} dish\\
	\glt `Please taste this dish a little bit.' 
	\z
\z

The current study tries to determine a suitable formal and unified analysis for the structure of verbal reduplication in Mandarin Chinese.
It contributes more empirical evidence and 
offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG, \citealt{PollardSag1994}) to this phenomenon 
using Minimal Recursion Semantics (MRS, \citealt{Copestakeetal2005}) as the semantic representation formalism.
This new account avoids the problems of previous approaches and
explains more forms of verbal reduplication in Mandarin Chinese.

This paper is organized as follows: 
after this introduction, we will present in \sectref{sec:phen} the forms and syntactic distribution as well as the semantics of verbal reduplication in Mandarin Chinese. 
Importantly, we restrict the object of this study to the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
We will also discuss in this section, with the help of corpus data, the question of whether the reduplication is a morphological or a syntactic process.
In \sectref{sec:prev}, I will discuss the advantages and drawbacks of previous approaches. 
\sectref{sec:analysis} will present a new {HPSG} account for verbal reduplication in Mandarin Chinese.
Finally,  \sectref{sec:conclu} will conclude the paper.

The data in this paper was drawn from several sources.
In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} was also consulted. 
Other examples from novels and plays written by native speakers were also considered.

### 2023-05-31 chapters/ch02-Phenomenon.tex
Update 2023-05-31-17:44:51

\section{The phenomenon}\label{sec:phen}

This section introduces the fundamental grammatical behaviors of verbal reduplication in Mandarin Chinese.
 After illustrating its forms, syntactic distribution and semantics, 
 we discuss the questions of whether it is better analyzed as a morphological or a syntactic phenomenon.

%%%%%%%%%%%%%
\subsection{Forms}\label{sec:forms}

There is no general agreement on the forms of verbal reduplication in Mandarin Chinese.
We adopt a broad definition in terms of the forms of verbal reduplication in Mandarin Chinese 
and list in (\ref{ex:redup-forms}) all the forms commonly discussed in the literature.

\settowidth\jamwidth{AB-\textit{le}-AB}

\ea\label{ex:redup-forms}
	\ea for monosyllabic verbs: \textit{shuo} `say'
		\ea \gll shuo-shuo\\
		say-say\\\jambox{AA}
		\ex \gll shuo-yi-shuo\\
		say-one-say\\\jambox{A-\textit{yi}-A}
		\ex \gll shuo-le-shuo\\
		say-\textsc{pfv}-say\\\jambox{A-\textit{le}-A}
		\ex \gll shuo-le-yi-shuo\\
		say-\textsc{pfv}-one-say\\\jambox{A-\textit{le}-\textit{yi}-A}
		\ex \gll shuo-shuo-kan\\
		say-say-look\\\jambox{AA-\textit{kan}}
		\ex \gll shuo-kan-kan\\
		 say-look-look\\\jambox{A-\textit{kan}-\textit{kan}}
		\z
	\ex for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
		\ea \gll lai-wang-lai-wang\\
		come-go-come-go\\ \jambox{ABAB}
		\ex \gll lai-wang-le-lai-wang\\
		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
		\ex \gll lai-lai-wang-wang\\
		come-come-go-go\\ \jambox{AABB}
		\z
	\ex\label{ex:forms-VO} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
		\ea \gll shuo-shuo-huang\\
		tell-tell-lie\\ \jambox{AAB}
		\ex \gll shuo-yi-shuo-huang\\
		tell-one-tell-lie\\ \jambox{A-\textit{yi}-AB}
		\ex \gll shuo-le-shuo-huang\\
		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
		\z
	\z
\z

 \citet{Fan1964}, \citet{Arcodiaetal2014}, \citet{MelloniBasciano2018} and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
Specifically, \citet{Arcodiaetal2014}, \citet{MelloniBasciano2018} and \citet{Xie2020} identified that AA and ABAB have a diminishing meaning, 
namely that the event happens for a short duration or to a small extent. 
AABB, on the other hand, expresses an increasing meaning, which indicates a repetition or action in progress. 
\citet{Xie2020} also found that AA and ABAB have relatively high productivity, 
whereas the productivity of AABB is low. 
She further showed that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
\citet[277]{Fan1964} proposed that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
while AABB developed from the reiterative rhetoric from Old Chinese. 
These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 
The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
AA-\textit{kan}, A-\textit{kan}-\textit{kan}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}-\textit{yi}\hyp{}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.

%%%%%%%%%%%%
\subsection{Syntactic distribution}\label{sec:syn-dis}

The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:redup-syn}). 
The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see Section \ref{sec:aspM}). 
The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:redup-quan}) \citetext{\citealp[114--115]{Chen2005}; \citealp[83--84]{Li1998}}.
This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[114--115]{Chen2005}; \citealp[84]{Li1998}}, namely a short duration or a small extent.

\settowidth\jamwidth{(CCL)}

\ea\label{ex:redup-syn}
	\ea Intransitive verb:
		\ea \gll ta xiao-le.\\
		he laugh-\textsc{pfv}\\
		\glt `He laughed.'
		\ex \gll ta \textit{xiao}-\textit{le}-\textit{xiao}.\\
		he laugh-\textsc{pfv}-laugh\\
		\glt `He laughed a little bit.'
		\z
	\ex Transitive verb:
		\ea \gll ni wen ta.\\
		you ask him\\
		\glt `Ask him.'
		\ex \gll ni \textit{wen}-\textit{(yi)}-\textit{wen} ta.\\
		you ask-(one)-ask he\\
		\glt `Try to ask him.'
		\z
	\ex Under negation:
		\ea \gll weishenme wo bu kan ta qita fangmian de jinbu he quanfangwei de chengzhang\\
		why I not look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\
		\glt `Why don't I look at his progress in other aspects and all-round growth?'
		\ex \gll weishenme wo bu \textit{kan}-\textit{kan} ta qita fangmian de jinbu he quanfangwei de chengzhang\\
		why I not look-look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\ \jambox{({CCL})}
		\glt `Why don't I look a little bit at his progress in other aspects and all-round growth?'
		\z
	\ex In \textit{ba}-construction:
		\ea \gll gou-mai zhiqian zhen gai ba qingkuang mo qingchu.\\
		purchase-buy before really should \textsc{ba} situation touch clearly\\
		\glt `(I) should really check the situation clearly before I make the purchase.'
		\ex \gll gou-mai zhiqian zhen gai ba qingkuang \textit{mo}-\textit{mo} qingchu.\\
		purchase-buy before really should \textsc{ba} situation touch-touch clearly\\ \jambox{({CCL})}
		\glt `(I) should really quickly check the situation clearly before I make the purchase.'
		\z
	\ex With modal verb:
		\ea \gll you liang ben shu ni-men keyi kan \ldots\\
		there.be two \textsc{clf} book you-\textsc{pl} can read\\
		\glt `There are two books that you can read \ldots'
		\ex \gll you liang ben shu ni-men keyi \textit{kan}-\textit{kan} \ldots\\
		there.be two \textsc{clf} book you-\textsc{pl} can read-read\\ \jambox{({CCL})}
		\glt `There are two books that you can read a little bit \ldots'
		\z
	\ex In Serial Verb Construction (SVC):
		\ea \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang kan nali chu-le wenti.\\
		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look where come.out-\textsc{pfv} problem\\
		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a look at where went wrong.'
		\ex \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang \textit{kan}-\textit{kan} nali chu-le wenti.\\
		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a quick look at where went wrong.'
		\z
	\ex With an expression of quantity: \label{ex:redup-quan}
		\ea[]{\gll ta yi tian pao shi li.\\
		he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
		\glt `He runs ten miles a day.'}
		\ex[*]{\gll ta yi tian \textit{pao}-\textit{pao} shi li.\\
		he one day run-run ten mile\\}
		\z
	\z
\z

%%%%%%%%%%%%%
\subsection{Semantics}\label{sec:sem}

In this section, we will first discuss the core meaning of the reduplication as well as the meaning of its different forms (\sectref{sec:core-sem}).
We will then investigate the interaction of the reduplication with \textit{Aktionsarten} (\sectref{sec:Aktionsarten}) and aspect markers (\sectref{sec:aspM}).

\subsubsection{Core meaning}\label{sec:core-sem}

The reduplication has a \textit{delimitativeness} meaning \citep[e.g.][]{Chao1968, Chen2001, Dai1997, Li1996, LiThompson1981, Tsao2001, XiaoMcEnery2004, Xing2000, Yang2003, Zhu1998}. 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
 \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

In general, all of the above cited research agreed that the reduplication expresses a short duration and/or a low frequency, which fits the definition of delimitativeness.
\citet[152--154]{XiaoMcEnery2004} and \citet{Yang2003} argued that the core meaning of reduplication is delimitativeness, 
while all other meanings are merely pragmatic extensions  in specific contexts.
\citet[152--154]{XiaoMcEnery2004} pointed out that tentativeness and casualness are constrained by a number of contextual elements 
such as the reduplicated verb must be volitional and the subject of the sentence must be animate.
But these constraints are only necessary but not sufficient conditions for a tentative or casual meaning of reduplication.
Among all instances of verbal reduplication they found in a corpus, all of them have a delimitative reading, while only some of them convey tentativeness or casualness.
\citet{Yang2003} compared the sentence pairs with reduplicated verbs and their unreduplicated counterparts,
and showed that the reduplication itself does not add a tentative, frequentative, casualness or increased agency meaning to the sentence.
Rather, these additional meanings arise from the sentences or the contexts as a whole.
She concluded that these additional meanings are results of meaning extensions of delimitativeness in specific contexts.
We follow \citet{XiaoMcEnery2004} and \citet{Yang2003} and treat delimitativeness as the central meaning of reduplication,
and the other meanings as pragmatic extensions.

The semantics of the reduplication has the properties of transitoriness,  holisticity  and dynamicity \citetext{\citealp[70--79]{Dai1997}; \citealp[155--159]{XiaoMcEnery2004}}.
It presents the situation as a  transitory and non\hyp{}decomposable whole.
A situation expressed by a sentence with the reduplication involves changes not only in the initiation and termination of an event, but also in the transitory process itself.
Compared to (\ref{ex:le-dyn-look}), which could mean that the protagonist kept staring at the the footprint,
(\ref{ex:redup-dyn-look}) indicates that the protagonist took a brief look or several brief looks at the footprint and looked away in the end, which is a process full of changes.

\ea
  \ea\label{ex:le-dyn-look}
    \gll Wu Xumang kan-le zuo-an shi liuxia de jiaoyin \ldots\\
    Wu Xumang look-\textsc{pfv} commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
    \glt `Wu Xumang looked at the footprint left when the crime was committed.'
  \ex\label{ex:redup-dyn-look}
    \gll Wu Xumang \textit{kan-le-kan} zuo-an shi liuxia de jiaoyin \ldots\\
    Wu Xumang look-\textsc{pfv}-look commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
    \glt `Wu Xumang looked a little bit at the footprint left when the crime was committed.'
  \z
\z

The semantics of A-\textit{le}-A can be deduced compositionally from its structure. 
It is a hierarchical combination of the perfective aspect and delimitativeness, ``conveying a transitory event which has been actualized'' \citep[151]{XiaoMcEnery2004}.

As for A-\textit{yi}-A, \citet[273]{Fan1964} compared examples found in novels and plays and concluded that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
\citet{Xing2000} considered that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
The former conveys a casual attitude whereas the latter sounds more serious.
However, he stressed that there is no difference in the delimitative semantics of both forms,
and that the variance in meaning is a pragmatic one.
The difference is also not absolute and often only shows a tendency.
\citet{Xu2002} found out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
But he also stated that these differences are pragmatic rather than semantic, 
as he argued that AA and A-\textit{yi}-A can be used interchangeably in most cases,
and the specific differences in meaning only arise from specific contexts as a whole.
\citet[15]{Yang2003} suggested that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.

AA-\textit{kan} and A-\textit{kan}-\textit{kan} are described to express a ``try \ldots and find out'' meaning \citep[63]{Cheng2012}.
\citet[290]{Tsao2001} also observed that the tentative meaning is particularly prominent when the reduplication is followed by \textit{kan} `look'.
We still consider the tentativeness implied by these two forms to be a pragmatic extension of delimitativeness.
The tentative meaning is made prominent by the verb \textit{kan} `look',
and the whole structure can be understood as ``do A a little bit and see''.

%%%%%%%%
\subsubsection{Interaction with \textit{Aktionsarten}}\label{sec:Aktionsarten}

Previous research often claimed that the reduplication can only be used for verb classes of certain \textit{Aktionsarten}, while it is infelicitous for other ones.
\citet[277--278]{Hong1999} and \citet[234--235]{LiThompson1981} suggested that reduplication is only possible for volitional activity verbs.
\citet[70--71]{Dai1997} und \citet[290]{Tsao2001} both considered that reduplication can only be used in dynamic situations.
The former further claimed that achievement verbs cannot be reduplicated.
 \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet{BascianoMelloni2017} proposed that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
This means that the reduplication can only interact with dynamic situations which encode no results and is consequently only compatible with activities and semelfactives, but not with states and achievements.

\citet[53]{Chen2001} and \citet[10--11]{Yang2003} acknowledged that the reduplication of non\hyp{}vo\-li\-tion\-al verbs is more restricted than that of volitional ones.
But \citet[381--382]{Zhu1998} listed a number of non\hyp{}volitional predicates that can be reduplicated.
We found the examples shown in (\ref{ex:nonvol}) in {CCL} where non\nobreakdash-vo\-li\-tion\-al verbs \textit{weiqu} `feel wronged', \textit{ren-xing} `be willful' and \textit{diao} `drop' are reduplicated.

\ea\label{ex:nonvol}
\ea
\gll keshi xian mujin, dajia ye zhihao \textit{weiqu-weiqu} le.\\
but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
\glt `But now, everybody can only feel wronged a little bit.'

\ex
\gll ta-men neng zuo de buguo shi \textit{ren-ren-xing} shua dian'er xiao piqi \textit{diao-diao} yanlei shenme de.\\
she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \jambox{({CCL})}
\glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
\z
\z

It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
Compared to the questionable reduplication of the stative verb \textit{bing} `be sick' in (\ref{ex:redup-stat})
and that of the achievement verb \textit{ying} `win' in (\ref{ex:redup-achiV}), 
the reduplication of the activity verb \textit{kan} `watch' in (\ref{ex:redup-actV})
and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) is readily acceptable.

\ea
\ea[?]
{\gll ta \textit{bing-bing} jiu hao le.\\
he be.sick-be.sick then well \textsc{ptc}\\ \jambox{\citep[155]{XiaoMcEnery2004}}
Intended: `He was sick for a little while and then got well.'}\label{ex:redup-stat}

\ex[?]
{\gll ta \textit{ying}-\textit{le}-\textit{ying} na chang bisai.\\
he win-\textsc{pfv}-win that \textsc{clf} competition\\ \jambox{\citep[155]{XiaoMcEnery2004}}
\glt Intended: `He won that competition a little bit.'}\label{ex:redup-achiV}

\ex[]
{\gll ta \textit{kan}-\textit{le}-\textit{kan} na chang bisai.\\
he watch-\textsc{pfv}-watch that \textsc{clf} competition\\
\glt `He watched that competition for a little while.' \\}\label{ex:redup-actV}

\ex[]
{\gll ta \textit{kesou-kesou} jiu hao le.\\
he cough-cough then well \textsc{ptc}\\
\glt `He coughed a little bit and then got well.'}\label{ex:redup-semel}
\z
\z

However, examples such as those in (\ref{ex:redup-achi-stat1}) -- (\ref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.

\footnotetext[2]{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
\ea
\ea\label{ex:redup-achi-stat1}
\gll deng ren-men ba zhe jian shi \textit{wang}-\textit{wang} zai shuo ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\

\ex\label{ex:redup-achi-stat2}
\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
\glt `Let's take a bath later and be comfortable for a little while.'\\

\ex\label{ex:redup-achi-stat3}
\gll \textit{lian}-\textit{lian}-\textit{ai} shi keyi de, ban xishi dinghao chi yidian.\footnotemark\\
like-like-love \textsc{cop} ok \textsc{de} host wedding best late a.bit\\
\glt `It's ok to be in love a little bit, but it's better to get married a bit later.'\\

\ex\label{ex:redup-achi-stat4}
\gll wo zhen xiang \textit{bing-yi-bing}, xie ta ge shi tian ban yue.\\
I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
\glt `I really want to be sick for a little while and rest for ten days or half a month.'

\ex\label{ex:redup-achi-stat5}
\gll jiao ta \textit{sheng-sheng} xiaohai, jiu zhidao zuo muqin de gan-ku le.\\
let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
\glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
\z
\z
\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}

This shows that although the reduplication does have a tendency to interact with volitional verbs and with activities and semelfactives due to its dynamic meaning, 
this is by no means a rigid constraint, 
and non\hyp{}volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.

%%%%%%%%
\subsubsection{Interaction with aspect markers}\label{sec:aspM}

As mentioned in Section \ref{sec:forms}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
There is no consensus on which elements exactly are considered aspect markers in Mandarin Chinese. We only discuss the most commonly recognized ones here.
}
We believe this incompatibility to be for semantic reasons.

\citet[Ch. 4]{XiaoMcEnery2004} considered \textit{le}, \textit{guo} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
The perfective aspect marker \textit{le} is compatible with reduplication while the experiential aspect marker \textit{guo} is not.
\citet[128--131]{XiaoMcEnery2004} described that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).

\ea
  \ea\label{ex:cry}
    \gll Weici, Deng Lijun shangxin de ku-le san tian.\\
    for.this Deng Lijun sadly \textsc{de} cry-\textsc{pfv} three day\\ \jambox{\citep[129]{XiaoMcEnery2004}}
    \glt `For this reason, Deng Lijun cried sadly for three days.'
  \ex\label{ex:know}
    \gll Ta zhidao-le zhe shi de nei-qing.\\
    he know-\textsc{pfv} this matter \textsc{de} inside-information\\ \jambox{\citep[130]{XiaoMcEnery2004}}
    \glt `He got to know the inside information on this matter.'
  \z
\z
\textit{Le} is compatible with the reduplication, because its dynamicity can relate to not only the termination or instantiation of an event (a point of change), but also the process of the situation, just like that of the reduplication.

On the other hand, the experiential aspect marker \textit{guo} cannot co\hyp{}occur with a reduplicated verb, 
because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
namely that a situation has been experienced historically and that ``the final state of the situation no longer obtains'' at the reference time \citep[144]{XiaoMcEnery2004}. 
Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \textit{guo} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
whereas \textit{le} in (\ref{ex:le-dyn}) conveys a change into the state of being a soldier \citep[149]{XiaoMcEnery2004}.

\ea
  \ea\label{ex:guo-dyn}
    \gll ta dang-guo bing.\\
    he serve.as-\textsc{exp} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
    \glt `He once served as a soldier.'
  \ex\label{ex:le-dyn}
    \gll ta dang-le bing.\\
    he serve.as-\textsc{pfv} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
    \glt `He became a soldier.'
  \z
\z
It is clear that \textit{guo} only indicates a change at the termination of a situation and cannot express the dynamicity within a situation.
Hence, it is incompatible with the semantics of the reduplication.

Due to the holistic semantics of the reduplication, it is incompatible with imperfective aspect markers: the durative aspect marker \textit{zhe} and the progressive aspect marker \textit{zai}, as both only focus on  a part of the situation and do not view the situation as a whole \citep[Ch. 5]{XiaoMcEnery2004}.

From the illustration above, it seems that due to its semantics, reduplication can only be marked by \textit{le} but not the other aspect markers.

%%%%%%%%%%%%
\subsection{Word vs. phrase}\label{sec:word}

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet{Chao1968}, \citet{LiThompson1981} and \citet{Liao2014} listed reduplication under morphological processes. 
\citet{Arcodiaetal2014}, \citet{Xiong2016}, \citet{BascianoMelloni2017}, \citet{YangWei2017}, \citet{MelloniBasciano2018}, \citet{Xie2020},   on the other hand, claimed it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020}, applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results argue for a morphological status of reduplication.

\citet{Xie2020} compared the AA and the ABAB forms of reduplication with the AABB form and claimed that AA and ABAB are syntactic processes while AABB is morphological.
She pointed out that AA and ABAB behave differently from AABB in their productivity, possibility of \textit{le} insertion, categorial stability, transitivity, and input/output constraints.
While AA and ABAB are highly productive, AABB shows low productivity. 
\textit{Le} can be inserted freely into AA (\ref{ex:le-insertionAA}) and ABAB (\ref{ex:le-insertionABAB}) but not into AABB (\ref{ex:le-insertionAABB}).

\ea\label{ex:le-insertionAA}
  \ea \gll Yao Ming \textit{kan}-\textit{kan} ta de fanyi Ke Lin...\\
  Yao Ming look-look he \textsc{de} translator Ke Lin\\
  \glt `Yao Ming looked at his translator Ke Lin a little bit...'

  \ex \gll Yao Ming \textit{kan}-\textit{le}-\textit{kan} ta de fanyi Ke Lin...\\
  Yao Ming look-\textsc{pfv}-look he \textsc{de} translator Ke Lin\\ \jambox{({CCL})}
  \glt `Yao Ming looked at his translator Ke Lin a little bit...'
  \z
\z

\ea\label{ex:le-insertionABAB}
  \ea \gll ta \textit{heji}-\textit{heji}, dui Jiangqing shuo...\\
  he consider-consider to Jiangqing say\\
 \glt `He considered a little bit, and told Jiangqing...'

  \ex \gll ta \textit{heji}-\textit{le}-\textit{heji}, dui Jiangqing shuo...\\
  he consider-\textsc{pfv}-consider to Jiangqing say\\ \jambox{({CCL})}
  \glt `He considered a little bit, and told Jiangqing...'
  \z
\z

\ea\label{ex:le-insertionAABB}
  \ea[]{\gll \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} jiu ba chulai le.\\
  shake-shake-sway-sway then pull out \textsc{ptc}\\  \jambox{\citep[85]{Xie2020}}
  \glt `Shake it a little bit and then it will be pulled out.'}

  \ex[*]{\gll \textit{yao}-\textit{yao}-\textit{le}-\textit{huang}-\textit{huang} jiu ba chulai le.\\
  shake-shake-\textsc{pfv}-sway-sway then pull out \textsc{ptc}\\ \jambox{\citep[85]{Xie2020}}}
  \z
\z

The output of AA and ABAB does not change the grammatical category of the input (verb), but the output of AABB could have other categories such as adverb (\ref{ex:AABBadv}) or adjective (\ref{ex:AABBadj}).

\ea\label{ex:AABBadv}
  \ea[*]{\gll dian-che \textit{yao-huang}-\textit{yao-huang} kai zou...\\
  electric-car shake-sway-shake-sway drive away...\\ \jambox{\citep[86]{Xie2020}}}

  \ex[]{\gll dian-che \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} kai zou...\\
  electric-car shake-shake-sway-sway drive away...\\ \jambox{\citep[86]{Xie2020}}
  \glt `The tram drove away jiggly...'}
  \z
\z

\ea\label{ex:AABBadj}
  \ea[*]{\gll ...zuo zai  \textit{yao-huang}-\textit{yao-huang} de che shang\\
  sit on shake-sway-shake-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}}

  \ex[]{\gll ...zuo zai  \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} de che shang\\
  sit on shake-shake-sway-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}
  \glt `...sit on the jiggling car'}
  \z
\z

AA and ABAB do not change the valency of the input verb, but AABB makes a transitive verb intransitive (\ref{ex:trans}).

\ea\label{ex:trans}
  \ea[]{\gll qiao-da gan-jing shi huanjie gan-qi de hao banfa.\\
  knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}
  \glt `Beating the liver channel is a good method to relieve the stagnation of liver \textit{qi}.'}

  \ex[]{\gll \textit{qiao-da}-\textit{qiao-da} gan-jing shi huanjie gan-qi de hao banfa.\\
  knock-beat-knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}
   \glt `Beating the liver channel a little bit is a good method to relieve the stagnation of liver \textit{qi}.'}

   \ex[*]{\gll \textit{qiao}-\textit{qiao}-\textit{da}-\textit{da} gan-jing shi huanjie gan-qi de hao banfa.\\
  knock-knock-beat-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}}

  \ex[]{\gll \textit{qiao}-\textit{qiao}-\textit{da}-\textit{da} shi huanjie gan-qi de hao banfa.\\
   knock-knock-beat-beat \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\
  \glt `Knocking around is a good method to relieve the stagnation of liver \textit{qi}.'}
  \z
\z

The two groups also have different input and output constraints. \citet{Xie2020} claimed that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see Section~\ref{sec:Aktionsarten}).
On the other hand, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
Moreover, as can be seen in the translation in (\ref{ex:AABB-input}), the output of AABB has an increasing meaning, i.e. an event happens repeatedly or continuously, as opposed to the delimitative meaning of AA and ABAB.

\ea\label{ex:AABB-input}
  \ea \gll duo-shan $\rightarrow$ \textit{duo}-\textit{duo}-\textit{shan}-\textit{shan}\\
  hide-dodge {} hide-hide-dodge-dodge\\ \jambox{\citep[88]{Xie2020}}
  \glt `hide and dodge' `hide and dodge repeatedly'

  \ex \gll jin-chu $\rightarrow$ \textit{jin}-\textit{jin}-\textit{chu}-\textit{chu}\\
  enter-exit {} enter-enter-exit-exit\\ \jambox{\citep[88]{Xie2020}}
  \glt `enter and exit' `enter and exit repeatedly'

  \ex \gll shuo-xiao $\rightarrow$ \textit{shuo}-\textit{shuo}-\textit{xiao}-\textit{xiao}\\
  talk-laugh {} talk-talk-laugh-laugh\\ \jambox{\citep[88]{Xie2020}}
  \glt `talk and laugh' `talk and laugh continuously'
  \z
\z

However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
For instance, the \textit{-bar} derivation in German is a productive morphological process \citep[381]{Mueller2013}. 
The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
And inflections of tense in German do not change the valency of the input verb.
Further, if \textit{le} is considered to be a morphological element \citep[e.g.][]{Huangetal2009, MuellerLipenkova2013}, the insertion of \textit{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only showed that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.

It is, therefore, necessary to resort to other tests that are intended to distinguish words from phrases. 
Furthermore, we applied the same tests to Parallel Verb Compounds, which are inarguably words (because at least one element in the compound cannot appear in a sentence independently), 
and {SVC}s, which are by definition phrases. 
We then compared the test results of these three kinds of expressions to see whether the reduplication behaves in a more similar way to Parallel Verb Compounds or to {SVC}s.

\citet{Duanmu1998} and \citet{Schaefer2009} proposed the following four tests to
distinguish words from phrases in Mandarin Chinese: semantic compositionality, phrasal extension,
phrasal substitution and conjunction reduction.\footnote{It is important to note that none of these criteria are sufficient or necessary to determine the word or phrase status of an expression. Nevertheless, they together might suggest which of the two statuses is more likely.}

The semantic criterion is that the meaning of a phrase is usually built up in a compositional way while that of a word usually not \citetext{\citealp[140]{Duanmu1998}; \citealp[275]{Schaefer2009}}. 
The meaning of the reduplication is not compositional, as it does not mean that the event denoted by the verb happens twice or multiple times, but rather that the event happens for a short duration and/or for low frequency.
This non-compositionality suggests that a reduplication is more word-like.

The syntactic criteria are all based on the Lexical Integrity Hypothesis according to \citet[60]{Huang1984}, as shown in (\ref{lih}):

\ea\label{lih}The Lexical Integrity Hypothesis\\
No phrase-level rule may affect a proper subpart of a word.
\z

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:redup-forms}) in Section~\ref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet{Huangetal2009} and \citet{MuellerLipenkova2013} considered aspect markers in Mandarin Chinese to be morphological elements. E.g. \citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

\ea
  \ea[]{\label{ex:ext-redup1}
  \gll ta dui ziji qingsheng de \textit{xiao-le-xiao}.\\
  he to \textsc{refl} quietly \textsc{de} laugh-\textsc{le}-laugh\\
  \glt `He quietly laughed a little bit to himself.'}

  \ex[*]{\label{ex:ext-redup2}
  \gll ta dui ziji \textit{xiao}-\textit{le} qingsheng de \textit{xiao}.\\
  he to \textsc{refl} laugh-\textsc{pfv} quietly \textsc{de} laugh\\}

  \ex[]{\label{ex:ext-redup3}
  \gll ta qingsheng de dui ziji \textit{xiao-le-xiao}.\\
  he quietly \textsc{de} to \textsc{refl} laugh-\textsc{pfv}-laugh\\
  \glt `He quietly laughed a little bit to himself.'}
  \z
\z

On the other hand, nothing can intervene in between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).

\ea\label{ex:ext-pvc}
  \ea[]{
  \gll ta gou-mai-le yi jian dayi.\\
  he purchase-buy-\textsc{pfv} one \textsc{clf} coat\\
  \glt `He bought a coat.'}

  \ex[*]{
  \gll ta gou-le-mai yi jian dayi.\\
  he purchase-\textsc{pfv}-buy one \textsc{clf} coat\\}

  \ex[*]{
  \gll ta gou-le-yi-mai yi jian dayi.\\
  he purchase-\textsc{pfv}-one-buy one \textsc{clf} coat\\}

  \ex[]{
  \gll ta kaixin de gou-mai-le yi jian dayi.\\
  he happily \textsc{de} purchase-buy-\textsc{pfv} one \textsc{clf} coat\\
  \glt `He bought a coat happily.'}

  \ex[*]{
  \gll ta gou kaixin de mai-le yi jian dayi.\\
  he purchase happily \textsc{de} buy-\textsc{pfv} one \textsc{clf} coat\\}
  \z
\z

But an {SVC} readily allows other elements to appear between the two verbs (in (\ref{ex:ext-svc1}), the direct object of the first verb) and each verb can be modified separately (\ref{ex:ext-svc2}), as well.

\ea
  \ea\label{ex:ext-svc1}
  \gll ta zhong cai mai.\\
  he plant vegetables sell\\
  \glt `He plants vegetables and sells them.

  \ex\label{ex:ext-svc2}
  \gll ta xinku de zhong cai qinfen de mai.\\
  he hard-workingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
  \glt `He plants vegetables hard-workingly and sells them diligently.'
  \z
\z
All in all, by the test of phrasal extension, reduplications behave more like words than like phrases.

The second syntactic test is phrasal substitution, namely the substitution of smaller exemplars of a specific category with a full blown XP \citetext{\citealp[152]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
If a part of an expression is actually an XP that only contains one element, a full realization of this XP should be possible as well.
Otherwise, this expression is considered to be a word.
In a reduplication structure, it is ungrammatical to substitute each element with a full {VP} (\ref{ex:sub-redup}).

\ea\label{ex:sub-redup}
  \ea[]{\label{ex-he-tasted-the-soup-a-little-bit}
  \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'}

    \ex[*]{
    \gll ta \textit{chang} \textit{tang} \textit{le} \textit{chang} \textit{tang}.\\
    he taste soup \textsc{pfv} taste soup\\}
  \z
\z

It is the same case with Parallel Verb Compounds (\ref{ex:sub-pvc}).

\ea[*]{
\gll ta gou yi jian dayi mai le yi tiao kuzi.\\
he purchase one \textsc{clf} coat buy \textsc{pfv} one \textsc{clf} pants\\}
\label{ex:sub-pvc}
\z

However, it is grammatical to replace a reduced part of a {SVC} with a full VP (\ref{ex:sub-svc}).

\ea\label{ex:sub-svc}
\gll ta zhong cai mai (cai).\\
 he plant vegetables sell vegetables\\
\glt `He plants vegetables and sells vegetables.'
 \z
Again, reduplications look more word-like than phrase-like.

The third syntactic criterion is conjunction reduction. It should only be possible for coordinated phrases (\ref{ex:co-phrase}) and not for coordinated words (\ref{ex:co-word}) \citetext{\citealp[137]{Duanmu1998}; \citealp[283]{Schaefer2009}}.

\ea\label{ex:co-phrase}
  \ea \gll [jiu de shu] gen [xin de shu]\\
  old \textsc{de} book and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
  \glt `old books and new books'

  \ex \gll [jiu de gen xin de] shu\\
  old \textsc{de} and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
  \glt `old and new books'
   \z
\z

\ea\label{ex:co-word}
  \ea[]{
  \gll [huo-che] gen [qi-che]\\
  fire-car and gas-car\\ \jambox{\citep[137]{Duanmu1998}}
  \glt `train and automobile'}

  \ex[*]{
  \gll [huo gen qi] che\\
  fire and gas car\\ \jambox{\citep[137]{Duanmu1998}}}
  \z
\z

For the reduplication, conjunction reduction does not seem to be possible. 
In (\ref{ex:co-redup1}), the reduplication \textit{jiao-jiao} `chew a little bit' is coordinated with a simple verb \textit{mo} `apply' together with the adverbial \textit{yidian} `a little bit'.
Without the adverbial \textit{yidian} `a little bit', \textit{mo} `apply' by itself cannot express the additional `a little bit' meaning even when it is coordinated with a reduplicated verb.
Similarly, in (\ref{ex:co-redup2}), the reduplication \textit{kan-le-kan} `look a little bit' is coordinated with the predicate \textit{zou-le chulai} `walked out'. The verb in the latter case is not reduplicated and it cannot express the delimitative meaning either.

\ea
  \ea\label{ex:co-redup1}
  \gll wujian gong-xiu mo dian bohe-gao huo \textit{jiao}-\textit{jiao} kouxiangtang.\\
    midday work-break apply a.little mint-cream or chew-chew chewing.gum\\ \jambox{({CCL})}
    \glt `During the working break in the midday, apply a little bit of mint cream or chew some chewing gum a little bit.'

   \ex\label{ex:co-redup2}
   \gll Song Ailing \textit{kan}-\textit{le}-\textit{kan} yupen you zou-le chulai.\\
   Song Ailing look-\textsc{pfv}-look bath.tub again walk-\textsc{pfv} out\\  \jambox{({CCL})}
   \glt `Song Ailing looked at the bath tub a little bit and walked out again.'
   \z
\z

Conjunction reduction is not possible for Parallel Verb Compounds as well.
We can see in (\ref{ex:co-pvc}) that for the Parallel Verb Compounds \textit{gou-mai} `purchase-buy, buy' and \textit{gou\hyp{}zhi} `purchase\hyp{}place, purchase', it is neither possible to delete the first verb nor the second.

\ea\label{ex:co-pvc}
     \ea[*]{
     \gll ta gou-mai-le yi jian dayi hai gou-le yi tiao kuzi.\\
    he purchase-buy-\textsc{pfv} one \textsc{clf} coat and purchase-\textsc{pfv} one \textsc{clf} pants\\
    \glt Intended: `He bought a coat and purchased a pair of pants.'}

    \ex[*]{
    \gll ta gou-mai-le yi jian dayi hai -zhi-le yi tiao kuzi.\\
    he purchase-buy-\textsc{pfv} one \textsc{clf} coat and place-\textsc{pfv} one \textsc{clf} pants\\
   \glt  Intended: `He bought a coat and purchased a pair of pants.'}
    \z
\z

By contrast, it is grammatical to delete a repeated part in a coordinated {SVC}. 
In (\ref{ex:co-svc1}), while it is possible for the object of selling to be only cows, it is equally acceptable to interpret it as the person sells both vegetables and cows. With the second interpretation, (\ref{ex:co-svc1}) can be understood as a reduced version of (\ref{ex:co-svc2}).

\ea
  \ea\label{ex:co-svc1}
  \gll ta zhong cai hai yang niu mai.\\
  he plant vegetables and farm cow sell\\
  \glt `He plants vegetables and farms cows and sells them.'

  \ex\label{ex:co-svc2}
  \gll ta zhong cai mai hai yang niu mai.\\
  he plant vegetables sell and farm cow sell\\
  \glt `He plants vegetables and sells them and farms cows and sells them.'
   \z
\z
Once again, this criterion suggests that reduplications do not have this expected property of phrases.

Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. 
In comparison, Parallel Verb Compounds failed all the tests as well, whereas {SVC}s passed all of them.
This makes the behavior of the reduplication seems more similar to that of a Parallel Verb Compound than that of an {SVC}.
Therefore, it seems more likely to assume the reduplication to be a morphological process rather than a syntactic one.

### 2023-05-31 chapters/ch04-Previous.tex
Update 2023-05-31-17:44:51

\section{Previous analyses}\label{sec:prev}

Previous analyses on the reduplication in Mandarin Chinese and in other languages can be classified
into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect marker (\sectref{sec:asp}), and
as a special reduplication construction (\sectref{sec:construc}).\footnote{The term \textit{construction} is used here in its general sense, not in the sense of Construction Grammar.} 
This section will review these analyses and will discuss their advantages and shortcomings.

%%%%%%%%%%%
\subsection{The reduplicant as a verbal classifier}\label{sec:clf}

\citet{Chao1968}, \citet{Fan1964} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet{Chao1968} or \textit{cognate object} in \citet{Chao1968, Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet{LiThompson1981} or \textit{frequency phrase} in \citet{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).

%\settowidth\jamwidth{(Chomsky, 1957: 15)}
\ea\label{ex:clf}
\gll mei che guo yi ci huang\\
not tell \textsc{exp} one \textsc{clf} lie\\ \jambox{\citep[616]{Chao1968}}
\glt `haven't told lie once'
\z

In this analysis, the first element in the reduplication is the actual verb, 
the second element is a verbal classifier borrowed from a verb, 
and \textit{yi} `one' is an optional pseudo-numeral that only has an abstract `a little bit' meaning.
The analysis is syntactic.

The parallel between the reduplication and a verbal classifier phrase is obvious. 
Both the reduplication and the verbal classifier phrase serve to quantify the duration or the extent of a situation. 
A reduplication structure can often be paraphrased into a verbal classifier phrase such as \textit{yi xia} ‘once, a while’, \textit{yi hui} ‘a while’, as illustrated in (\ref{ex:redup-clf}).

\ea\label{ex:redup-clf}
	\ea \gll \textit{deng}-\textit{deng} wo.\\
		wait-wait I\\
		\glt `Wait for me a little bit.'
	\ex \gll deng wo yi xia.\\
	wait I one \textsc{clf}\\
	\glt `Wait for me a little while.'
	\z
\z

However, there are several arguments suggesting that the reduplication cannot be analyzed the same way as a verbal classifier phrase. First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.

\ea\label{ex:clf-sep}
  \ea \gll ni deng yi xia Zhangsan!\\
   you wait one \textsc{clf} Zhangsan\\
   \glt `Wait for Zhangsan for a while!'
  \ex \gll ni deng Zhangsan yi xia!\\
   you wait Zhangsan one \textsc{clf}\\
   \glt `Wait for Zhangsan for a while!'
\z
\z

\ea\label{ex:redup-sep}
  \ea[]{\gll ni \textit{deng}-\textit{yi}-\textit{deng} Zhangsan!\\
   you wait-one-wait Zhangsan\\
   \glt `Wait for Zhangsan a little bit!'}
  \ex[*]{\gll ni \textit{deng} Zhangsan \textit{yi} \textit{deng}!\\
  you wait Zhangsan one wait\\}
\z
\z

Second, unlike verbal classifiers (\ref{ex:clf-num}), the \textit{yi} ‘one’ in A-\textit{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.

\ea\label{ex:clf-num}
  \ea \gll ta pai-le wo yi xia.\\
   he pat-\textsc{pfv} I one \textsc{clf}\\
   \glt `He patted me once.'
   \ex \gll ta pai-le wo liang xia.\\
    he pat-\textsc{pfv} I two \textsc{clf}\\
    \glt `He patted me twice.'
\z
\z

\ea\label{ex:redup-num}
  \ea[]{\gll ta \textit{pai}-\textit{le}-\textit{yi}-\textit{pai} wo.\\
   he pat-\textsc{pfv}-one-pat I\\
   \glt `He patted me a little bit.'}
   \ex[*]{\gll ta \textit{pai}-\textit{le}-\textit{liang}-\textit{pai} wo.\\
   he pat-\textsc{pfv}-two-pat I\\}
\z
\z

Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.

\ea
  \ea\label{ex:idiom}
  \gll bao fo-jiao\\
  clasp Buddha-foot\\
   \glt Literal: `clasp the Buddha's foot'\\
   Idiomatic: `make a last-minute effort'

   \ex\label{ex:clf-idiom}
   \gll ta kaoshi qian bao-le san xia fo-jiao.\\
   he exam before clasp-\textsc{pfv} three \textsc{clf} Buddha-foot\\
   \glt `He clasped the Buddha's foot three times before the exam.' (idiomatic reading unavailable)

   \ex\label{ex:redup-idiom}
   \gll ta kaoshi qian \textit{bao}-\textit{le}-\textit{bao} fo-jiao.\\
   he exam before clasp-\textsc{pfv}-clasp Buddha-foot\\
   \glt Literal: `He clasped the Buddha's foot a little bit before the exam.'\\
   Idiomatic: `He made a bit of a last-minute effort before the exam.'
\z
\z

Based on these observations, it seems inappropriate to view the reduplication as a kind of verbal classifier phrase.

%%%%%%%%%%%
\subsection{The reduplicant as an aspect marker}\label{sec:asp}

A number of studies consider the reduplication to be a delimitative aspect marker \citep{Arcodiaetal2014, BascianoMelloni2017, YangWei2017} 
due to its delimitative aspectual meaning. 
\citet{Travis1999, Travis2000} also analyzed the reduplication in Tagalog as an imperfective aspect marker.

 %%%%%%
%Arcodiaetal2014, BascianoMelloni2017

 \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} analyzed the reduplication within the
framework of First Phase Syntax \citep{Ramchand2008}.

\citet{Ramchand2008} proposed that an event is comprised of the following phrases: 
the causative subevent (\textit{init}P), the process subevent (\textit{proc}P) and the result subevent (\textit{res}P), which are ordered hierarchically, as illustrated in \figref{tree:ramchand}.\footnote{
The present study does not argue for a {NP} or a {DP} analysis and simply takes over the illustration provided in the cited papers.}
Dynamic and volitional verbs have the features [init proc] and are therefore located unter \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.  
Achievement verbs possess the feature [res] and reside under \textit{res}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}. 
Stative verbs do not contain a \textit{proc}P \citep[152]{BascianoMelloni2017}.

\begin{figure}
 \centering
\begin{forest}
[\textit{init}P (causing projection) [DP$_3$\\subject of `cause']
  [ [init]
    [\textit{proc}P (process projection)
      [DP$_2$\\subject of `process']
      [[\textit{proc}]
        [\textit{res}P (result projection)
        [DP$_1$\\subject of `result']
          [[\textit{res}] [XP]
          ]
        ]
      ] ]
    ]
  ]
\end{forest} 
\caption{Event structure according to \citet[193]{Ramchand2008}}
\label{tree:ramchand}
\end{figure}

\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
and that the second element is an aspect marker, which resides in the complement position of \textit{proc}, as it delimits the process of the event. 
Since the second element occupies the same syntactic position as \textit{res}P, it should have complementary distribution with \textit{res}P
and should thus be incompatible with achievement verbs because of their [res] feature.
Furthermore, if \textit{proc}P does not exist in the event, as in the case of states, there should be no place for the reduplication either.

This analysis correctly predicts that the reduplication of achievement verbs and stative verbs is not as easily acceptable as that of dynamic and volitional verbs (marked by [init, proc] features).

However, as shown in \sectref{sec:Aktionsarten}, the reduplication of states and achievements is unusual but not impossible.
This suggests that the reduced acceptability of reduplicated achievement and stative verbs is semantic rather than structural. 
Their use is possible in specific contexts and should not be ruled out syntactically.
Consequently, this proposal does not seem to offer an appropriate account for the reduplication.

 %%%%%%
 %YangWei2017, Tsai2008

 \citet{YangWei2017} endorsed the analysis of the reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.

\citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).

\ea\label{ex:incomplete}
 \gll Xiaoli chi-zhe/le/wan fan *(le).\\
 Xiaoli eat-\textsc{prog}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
 \glt `Xiaoli is eating/ate/finished eating the meal.'
\z

\ea\label{ex:complete}
\gll Xiaoli (gangcai) zai ku/ku-guo.\\
Xiaoli just.now \textsc{dur} cry/cry-\textsc{exp}\\
\glt `Xiaoli was crying/cried just now.'
\z
He thus proposed three aspect positions under TP. \textit{zai} and \textit{guo} reside under Asp$_1$, while \textit{zhe} and \textit{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \textit{wan} can only occur with certain types of predicate. This differentiation does not play a role for our purpose and will not be further discussed here.}

\begin{figure}
\centering
\begin{forest}
[TP [T]
  [...
    [AspP$_1$ (outer aspect) [Asp$_1$\\zai/guo]
      [\textit{v}P [\textit{v}]
        [AspP$_2$ (middle aspect) [Asp$_2$\\zhe/le]
          [VP [V-Asp$_3$ (inner aspect)\\wan]
          ]
        ]
      ]
    ]
  ]
]
\end{forest}
\caption{Structure of the aspectual system in Mandarin Chinese according to \citet[683]{Tsai2008}}
\label{tree:tsai}
\end{figure}

Turning to reduplication, it cannot occur without additional information as well (\ref{ex:redup-tsai}).
Based on this, the reduplicant should reside under Asp$_2$.

\ea\label{ex:redup-tsai}
\ea[*] {\gll ta \textit{xiao}-\textit{xiao}\\
he laugh-laugh\\}
\ex[] {\gll ta \textit{xiao}-\textit{le}-\textit{xiao}\\
he laugh-\textsc{pfv}-laugh\\
\glt `He laughed a little.'}
\ex[] {\gll ta \textit{xiao}-\textit{xiao}, bu shuohua\\
he laugh-laugh not speak\\
\glt `He laughed a little, didn't speak.'}\label{ex:redup-tsai-co}
\z
\z

This analysis would result in a mismatch between syntax and semantics. 
Even though reduplication, \textit{le} and \textit{guo} all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
\textit{guo} is situated under Asp$_1$ while \textit{le} and the reduplication are under Asp$_2$.

In sum, both analyses of the reduplicant as an aspect marker do not seem to be convincing.

%%%%%%%%%%%%
\subsection{Reduplication construction}\label{sec:construc}

The following section discusses previous literature which proposed a special construction for the reduplication.

 %%%%%%%
%Ghomeshietal2004

\citet{Ghomeshietal2004} provided an analysis within the theoretical framework of Parallel Architecture \citep{Jackendoff1997, Jackendoff2002} for Contrastive Reduplication (CRs) in English like (\ref{ex:salad}),\footnote{Capitalization indicates contrastive intonation.} 
as shown in Figure~\ref{ghomeshi-cr}.\footnote{{P} = phonological unit, {P/E/S CTR} = prototypical/extreme/salient contrast, XP$^{min}$ = XP without its specifier} 
%They postulated a new syntactic category {CR}$^{syn}$ to incorporate the reduplicant.
%It has the semantics of {P/E/S CTR} and an empty phonological content that copies from the phonology of the base it applies to.
%According to their observations, the base can be an X (e.g. \textit{SALAD-salad}) or an XP$^{min}$ (e.g. \textit{OVER-THE-HILL-over-the-hill}).
%In Figure~\ref{ghomeshi-cr}, {CR}$^{syn}$ is coindexed with the first {P}, 
%which is in turn coindexed with the phonology of X/XP$^{min}$ (P$_k$). 
%{CR}$^{syn}$ is coindexed with the semantics of {P/E/S CTR}, 
%which modifies the semantics of  X/XP$^{min}$ (Z$_k$).
\ea\label{ex:salad}
I make the tuna salad, and you make the \textit{SALAD-salad}.
\z
\begin{figure}[h!]
\centering
%\begin{multicols}{3}
\begin{minipage}[t]{.3\linewidth}
\begin{center}
Phonology\\
%\vspace{15pt}
P$_{j, k}$ P$_k$
\end{center}
\end{minipage}
%\columnbreak
\begin{minipage}[t]{.3\linewidth}
\begin{center}
Syntax\\
\begin{forest}
for tree = {inner sep = 0pt,
	s sep = 1pt,
	anchor=children last,
    	align=center}
[X/XP$^{min}$
 [CR$^{syn}$$_j$]
 [X/XP$^{min}$$_k$]
]
\end{forest}
\end{center}
\end{minipage}
%\columnbreak
\begin{minipage}[t]{.3\linewidth}
\begin{center}
Semantics
\[
\begin{bmatrix}
Z_{k}\\
\begin{bmatrix}
P/E/S\\
CTR
\end{bmatrix}_{\!j}
\end{bmatrix}
\]
\end{center}
\end{minipage}
%\end{multicols}
\caption{Analysis for {CR}s in English according to \citet[344]{Ghomeshietal2004}}
\label{ghomeshi-cr}
\end{figure}

Applying this to the reduplication in Mandarin Chinese, the structure should be something like \figref{ghomeshi-cn}.\footnote{{DELIM} = delimitative}\textsuperscript{,}\footnote{
Although the reduplication in Mandarin Chinese does not have a contrastive meaning, 
we preserve the notation of CR$^{syn}$ in \citet{Ghomeshietal2004} here to simply refer to the reduplicant.}
The base verb is coindexed with its phonology and its semantics `look'. 
The phonology of the reduplicant is coindexed with the phonology of the verb.
The reduplicant is coindexed with the delimiative semantics
and modifies the semantics of the base verb.
The base verb and the reduplicant combine to a V.\footnote{In English, it makes sense to assume CR$^{syn}$ to be a syntactic unit, because the base can be XP$^{min}$ (e.g. \textit{OVER-THE-HILL-over-the-hill}). 
But for Mandarin Chinese, the base can only be V.
As \citet[353]{Ghomeshietal2004} wrote: ``when applying to its smallest scope, X inside of a word, it has the feel of other things that attach there, i.e., morphological affixes''.
It seems that it suffices to assume the reduplication in Mandarin Chinese to be a morphological phenomenon (cf. \sectref{sec:word}).
We continue to call the second column ``syntax'' to preserve the consistency of the notations.
}
We draw the head on the left because all analyses mentioned above considered the first element in the reduplication to be the actual verb and the second element the reduplicant, 
but this analysis itself does not forbid the head to be on the right side.

\begin{figure}[h!]
\centering
\begin{minipage}[t]{.3\linewidth}
\begin{center}
Phonology\\
\begin{forest}
[P$_{j}$ [kan]] 
\end{forest}
\begin{forest}
[P$_{j, k}$ [kan]]
\end{forest}
\end{center}
\end{minipage}
%\columnbreak
\begin{minipage}[t]{.3\linewidth}
\begin{center}
Syntax\\
\begin{forest}
[V
 [V$_j$]
 [CR$^{syn}$$_k$]
]
\end{forest}
\end{center}
\end{minipage}
%\columnbreak
\begin{minipage}[t]{.3\linewidth}
\begin{center}
Semantics
\[
\begin{bmatrix}
\begin{bmatrix}
DELIM\\([LOOK]_{j})
\end{bmatrix}_{\!k}\\
\end{bmatrix}
\]
\end{center}
\end{minipage}
\caption{Analysis for AA following \citet{Ghomeshietal2004}}
\label{ghomeshi-cn}
\end{figure}

As for the other forms of reduplication, A-\textit{le}-A can be viewed as two compositional processes \mbox{[[[A] -\textit{le}] -A]}.
Furthermore, the \textit{yi} in A-\textit{yi}-A and A-\textit{le}-\textit{yi}-A can simply be viewed as a dangling phonological unit. 
In this case, \phonliste{ yi } is neither coindexed with a syntactic unit nor with a semantic one.

This analysis correctly captures the fact that the addition of \textit{yi} does not change the syntactic and semantic behaviors of the reduplication.
It also provides a formal account for the phonology of the reduplication.
On the other hand, by assuming a construction specially for the reduplication, this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese, unlike the affixation analyses described in \sectref{sec:asp}.

 %%%%%%%%%%%%%%
 %FanSongBond2015

\citet{FanSongBond2015} provided a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
They considered reduplication to be a morphological process and modeled it via lexical rules.
They provided the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
and further proposed \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.
For them, the reduplication functions as an intensifier predicate, as represented in the \textsc{predicate (pred)} in the \textsc{constructional-content (c-cont)}.
The \type{intensifier\_x\_rel} has two subtypes: \type{redup\_up\_x\_rel} for the amplifiying meaning of adjectival reduplication and \type{redup\_down\_x\_rel} for the delimitative meaning of verbal reduplication.
The orthography is handled separately.
The AABB form for adjectives and the ABAB form for verbs, as well as the AAB form for V-O compounds, are handled as irregular derivation forms.

\ea\label{avm:fsb-redup}
\avm{
[\type*{redup-type}\\
cat\textbar head & \1\\
val & \2\\
cont & \3 \normalfont \textsc{hook} [ltop & \4\\
			ind & \5]\\
c-cont & <[\type*{event-rel}\\
		pred & intensifier\_x\_rel\\
		lbl & \4\\
		arg1 & \5]>
]
}
$\to$
\avm{
[cat\textbar head & \1\\
val & \2\\
cont & \3
]
}
\z

\ea\label{avm:fsb-redup-a}
\avm{
[\type*{redup-a-lr $\subset$ redup-type}\\
cat\textbar head & adjective\\
val & [spr <>]\\
c-cont & <[pred & redup\_up\_x\_rel]>
]
}\\
\textsc{orthography}: A $\to$ AA; (irregular AB $\to$ AABB)
\z

\ea\label{avm:fsb-redup-v}
\avm{
[\type*{redup-v-lr $\subset$ redup-type}\\
cat\textbar head & verb\\
cont\textbar hook & [aspect & non-aspect]\\
c-cont & <[pred & redup\_down\_x\_rel]>
]
}\\
\textsc{orthography}: A $\to$ AA; A $\to$ A-\textit{yi}-A; (irregular AB $\to$ ABAB)
\z

This approach provided a unified account for adjectival and verbal reduplication.
Their commonalities are captured by inheritance hierarchies of the intensifier predicates and the lexical rules.
In the case of verbal reduplication, A-\textit{yi}-A is analyzed as an alternative orthographical form of AA.
This correctly captured the intuition that AA and A-\textit{yi}-A express the same meaning and only differ from each other phonologically/orthographically (see \sectref{sec:core-sem}).

Nevertheless, this analysis has some shortcomings.
To begin with, since the combination with aspect markers is completely forbidden, it is impossible for this approach to account for A\hyp{}\textit{le}\hyp{}A.
Moreover, as verbal reduplication is  considered to express a delimitative aspectual meaning,
it seems unconvincing to assume that there is no aspect information in its semantics.
We consider a semantic explanation as described in  \sectref{sec:aspM} to be more reasonable for ruling out aspect markers other than \textit{le}.
Furthermore, this account can only deal with monosyllabic reduplication and handles ABAB and AAB as irregular forms, for the reason that ABAB and AAB reduplication of AB verbs ``are not very productive in Chinese'' \citep[102]{FanSongBond2015}.
This is not true. 
\citet{BascianoMelloni2017}, \citet{MelloniBasciano2018},  \citet{Xing2000stat} and  \citet{Xie2020}  all considered both AA and ABAB to be productive,
and \citet{Xing2000stat} concluded that AAB is productive as well.
Thus, these forms should not be handled as  irregular forms, but should be derivable from lexical rules.

The shortcomings of previous analyses lead us to propose a new analysis on verbal reduplication with {HPSG}, 
that formalizes the phonology of the reduplication, resolves the problem of \textit{yi} and preserves the generalization on aspect marking, 
as we will elaborate in \sectref{sec:analysis}.

### 2023-05-31 chapters/ch05-Analysis.tex
Update 2023-05-31-17:44:51

\section{A new HPSG analysis}\label{sec:analysis}

In what follows, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
using MRS, as proposed in \citet{LuMueller2021}.

The implicational constraint in  (\ref{avm:redup}) shows the constraints on all structures of type
\textit{verbal-reduplication-lr} for Mandarin Chinese. 
Such structures take a verb as \textsc{lexical-daughter (lex-dtr)}.  
The output reduplicates the \textsc{phonology (phon)} of the input verb with the possibility to have further phonological material in between.
\etag{} indicates an underspecified list which could be empty or not. 
A delimitative relation is appended to the \textsc{rels} value of the input verb, 
and it takes the event index of the input verb as argument. 
The label of the output \iboxb{2} is identified with the label of the input and with the label of the delimitative relation, 
hence \type{delimitative-rel} is treated as a modifier.
 Further relations can be added at the beginning of the \textsc{relations (rels)} list to allow for
the additional perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A. 
The combination with the perfective will be elaborated on in the following paragraphs.

\ea
\type{verbal-reduplication-lr} \impl\\
\scalebox{.9}{%
    \avm{
        [
        phon & \1 $\oplus$ \etag $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \etag $\oplus$ \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] > \smallskip\\
        lex-dtr & [phon \1\\
        synsem\textbar loc & [cat  & [ head & verb ] \\
        cont & [ ltop & \2\\
        ind  & \3 ]]\\
        rels \4 ] ]
}}
\label{avm:redup}
\z

To account for the variations in the phonology of the reduplication as well as 
the combination with the phonology and semantics of the perfective aspect marker \textit{le}, 
the type hierarchy of lexical rules in \figref{fig:typehi} is put forward. 
\begin{figure}
    \centering
    \scalebox{.9}{\begin{forest}
        type hierarchy
        [,phantom
        [,phantom
        [verbal-reduplication-lr,name=verbal-reduplicaiton-lr
        [non-perfective-reduplicaiton-lr
        [a-a-lr]
        [a-yi-a-lr]]
        [,identify=!r211]]]
        [aspect-marking-lr
        [perfective-lr
        [perfective-reduplicaiton-lr%,edge to=verbal-reduplicaiton-lr
        [a-le-yi-a-lr]
        [a-le-a-lr]]
        [v-le-lr]]
        [durative-lr]
        [\ldots]]]
    \end{forest}
}
    \caption{Type hierarchy for lexical rules of verbal reduplication and \textit{le}}
    \label{fig:typehi}
\end{figure}
Apart from the type \type{perfective-reduplication-lr}, 
which adds the inherited perfective relation, 
there is a subtype \type{non-perfective-reduplication-lr}, 
which does not add further relations. 
Hence, what is \etag in the \textsc{rels} list in (\ref{avm:redup}) is the empty list in (\ref{avm:nonperf}):
\ea\label{avm:nonperf}
\type{non-perfective-verbal-reduplication-lr} \impl\\
\scalebox{.9}{%
    \avm{
        [
        rels & \1 $\oplus$ < [ ] > \smallskip\\
        lex-dtr & [ rels \1 ] ]
    }
}
\z
The \textsc{rels} list of the output of the lexical rule \iboxb{1} is the \textsc{rels} list of
the daughter plus one element. 
Since the element is specified in the supertype, it has not been specified in (\ref{avm:nonperf}) again.

\type{non-perfective-verbal-reduplication-lr} has \type{aa-lr} and \type{a-yi-a-lr} as direct subtypes.
(\ref{avm:AA}) and (\ref{avm:AyiA}) show \type{aa-lr} and \type{a-yi-a-lr}, respectively.
As subtypes of \type{ver\-bal\hyp{}re\-dup\-li\-ca\-tion\hyp{}lr} illustrated in (\ref{avm:redup}), 
both inherit the constraints on the \textsc{lex-dtr} and on the semantics of the output, 
and because of (\ref{avm:nonperf}), no extra material is appended to the \textsc{rels} value of the input verb
and the list containing the \type{delimitative-rel}.
 In addition to the inherited constraints,
\type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is empty, 
whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:

\ea\label{avm:constr-AA}
Constraints on lexical rules of type \type{aa-lr} and \type{a-yi-a-lr}:
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
 \ea   \type{aa-lr} \impl \\%& 
    \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }} %& 
\ex	\type{a-yi-a-lr} \impl\\
     \scalebox{.9}{%
        \avm{
            [phon & \1 $\oplus$ \phonliste{ yi } $\oplus$ \1\\
            lex-dtr & [phon & \1] ]
    }}
%\end{tabular}
\z
\z

\noindent
The lexical rules with all inherited constraints are given in (\ref{avm:AA}) and (\ref{avm:AyiA}):

\ea\label{avm:AA}
The AA lexical rule with all constraints inherited from the supertypes:
\scalebox{.9}{%
    \avm{
        [\type*{aa-lr}\\
        phon & \1 $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels & \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}}
\z

\ea\label{avm:AyiA}
The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:
\scalebox{.9}{%
    \avm{
        [\type*{a-yi-a-lr}\\
        phon & \1  $\oplus$ \phonliste{ yi } $\oplus$ \1\\
        synsem & [ loc\textbar cont [ ltop & \2 \\
        ind  & \3 ] ]\\
        rels &  \4 $\oplus$ < [\type*{delimitative-rel}\\
        lbl & \2\\
        arg0 & \3 ] >\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
            cont & [ ltop & \2\\
            ind  & \3 ]]}\\
        rels & \4]
        ]
}}
\z

\type{v-le-lr} is a direct subtype of the \type{perfective-lr}.
\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}
and has two subtypes, \type{a-le-yi-a-lr} and \type{a-le-a-lr} itself.
\type{verbal-reduplication-lr} is already presented in (\ref{avm:redup}). 
We now turn to the constraints on \type{perfective-lr} and its subtypes.

\citet[246]{MuellerLipenkova2013} proposed the perfective lexical rule given in (\ref{avm:pfv-old}), 
adapted to the formalization adopted in the current paper.
It takes a verb as \textsc{lex-dtr}
and appends \phonliste{ le } to its phonology.
Further, it accounts for the change in semantics by appending the \textsc{rels} value of the input verb to a \type{perfective-rel}.

\ea\label{avm:pfv-old}
Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \1 \+ \phonliste{ le }\\
        \punk{synsem\textbar cont}{ [ ltop & \2\\
            ind & \3 ]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> \+ \5\smallskip\\
        lex-dtr & [phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb]\\
            cont & [ ltop & \4\\
            ind & \3]]}\\
        rels & \5]
        ]
}}
\z
The event variables \iboxb{3} of the input and the output verb are shared. 
The \textsc{ltop} of the output of the lexical rule \iboxb{2} is the label of the perfective relation, 
and this relation scopes over the embedded verb. 
The handle of the embedded verb \iboxb{4} is the argument of the \type{perfective-rel}.

The lexical rule suggested in (\ref{avm:pfv-old}) only explains simple perfective aspect marking with \textit{le}, 
where \textit{le} immediately follows the verb.
But it cannot account for the perfective aspect marking of a reduplicated verb,
 as \textit{le} does not occur after the reduplication, 
nor can \textit{le} be reduplicated together with the verb.
It can only appear between the verb and the reduplicant.
In order to accommodate \textit{le} marking for both simple and reduplicated verbs, 
a general perfective lexical rule as in (\ref{avm:pfv-new}) and 
a subtype \type{v-le-lr} as in (\ref{avm:vle}) are posited here.
Besides adding a \type{perfective-rel} in the \textsc{rels} list of the output as in (\ref{avm:pfv-old}), 
the \type{perfective-lr} in (\ref{avm:pfv-new}) allows an underspecified list to be appended at the end of the \textsc{rels} list.
The \textsc{phon} value of the output makes it possible for further phonological material to occur both before and after \phonliste{ le }.

\ea\label{avm:pfv-new}
Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
\scalebox{.9}{%
    \avm{
        [\type*{perfective-lr}\\
        phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
        \punk{synsem\textbar cont}{ [ltop & \2\\
            ind  & \3]}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4 ]> $\oplus$ \5 $\oplus$ \etag\smallskip\\
        lex-dtr & [%phon & \1\\
        \punk{synsem\textbar loc}{[cat & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]}\\
        rels & \5]
        ]
}}
\z

\type{v-le-lr} as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
and that nothing else comes after \phonliste{ le }.
Furthermore, no other list can be appended at the end of the \textsc{rels} list of the output anymore.
This corresponds to the proposal of \citet[246]{MuellerLipenkova2013} shown in (\ref{avm:pfv-old}), 
which accounts for the simple perfective marking of verbs.

\ea\label{avm:vle}
Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
\scalebox{.9}{%
    \avm{
        [\type*{v-le-lr}\\
        phon & \1 $\oplus$ \phonliste{ le }\\
        \punk{synsem\textbar cont\textbar ltop}{ \2}\\ 
        rels & <[\type*{perfective-rel}\\
        lbl  & \2\\
        arg0 & \3\\
        arg1 & \4]> $\oplus$ \5\smallskip\\
        lex-dtr & [phon & \1\\
        cat  & [ head & verb\\
        cont & [ltop & \4\\
        ind & \3]]\\
        rels & \5]]
}}
\z

\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}.
The \textsc{phon} value of the output reduplicates the phonology of the input verb and states that there is \phonliste{ le } in between, 
as well as potentially further phonological material.
The \textsc{rels} list of the output appends the \type{delimitative-rel} to the \type{perfective-rel} and the \textsc{rels} value of the input verb.
The arguments of both \type{perfective-rel} and \type{delimitative-rel} share the event index of the
input verb \iboxb{3} to ensure that they apply to the same event denoted by the input verb. 
The label of the \type{delimitative-rel} and the input verb are identified (\type{delimitative-rel} is a modifier) 
and this shared label is embedded under the \type{perfective-rel}.

\ea\label{avm:pfv-redup}
Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
constraints inherited from \type{perfective-lr} and \type{verbal-reduplication-lr}:
%\resizebox{\linewidth}{!}{
    \scalebox{.9}{%
        \avm{
            [\type*{perfective-reduplication-lr}\\
            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
            \punk{synsem\textbar cont\textbar ltop}{ \2}\\ 
            rels & <[\type*{perfective-rel}\\
            lbl & \2\\
            arg0 & \3\\
            arg1 & \4]>
            $\oplus$ \5 $\oplus$
            <[\type*{delimitative-rel}\\
            lbl  & \4\\
            arg0 & \3]>\\
            lex-dtr & [phon & \1\\
            synsem\textbar loc & [cat  & [ head & verb ]\\
            cont & [ ltop & \4\\
            ind  & \3]]\\
            rels & \5]
            ]
    }}
    %}
\z
For example (\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
\ea\label{ex-he-tasted-the-soup-a-little-bit2}
    \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
    he taste-\textsc{pfv}-taste soup\\
    \glt `He tasted the soup a little bit.'
 \z
\ea\label{ex:mrs-soup}
h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
\z
So the delimitative relation is treated as an adjunct to the main relation of the verb, 
and the perfective relation scopes over both the main relation and the delimitative relation.

Two subtypes of \type{perfective-reduplication-lr} are posited:
\type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} %as in (\ref{avm:AleyiA}) 
and \type{a-le-a-lr}, as shown in (\ref{avm:AleA}). %(\ref{avm:AleA}).
They take over the semantic change to the input from \type{perfective\hyp{}reduplication\hyp{}lr}, but specify the \textsc{phon} value differently.
Specifically, \type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} specifies the middle phonological material as
\phonliste{ le, yi }, while \type{a-le-a} specifies it as \phonliste{ le } only.

\ea\label{avm:AleA}
%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
\ea    \scalebox{.9}{%
        \avm{
            [\type*{a-le-yi-a-lr}\\
            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }}%&
\ex    \scalebox{.9}{%
        \avm{
            [\type*{a-le-a-lr}\\
            phon & \1 \+ \phonliste{ le } \+ \1\\
            lex-dtr & [phon & \1
            ]
            ]
    }}
%\end{tabular}
\z
\z

Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
as long as the input verb is disyllabic.
Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
Although these forms are generally considered unacceptable \citetext{\citealp[160]{BascianoMelloni2017}, \citealp[275--276]{Hong1999}, \citealp[30]{LiThompson1981}, \citealp[239]{YangWei2017}}, 
\citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu})--(\ref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1})--(\ref{ex:ABleyiAB-ccl}) were found.

\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
\ea\label{ex:ABleyiAB}
\ea\label{ex:AByiAB-lu}
\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
you let me arrange-one-arrange\\
\glt `Let me arrange it a little bit!''

\ex\label{ex:AByiAB-pu}
\gll ni \textit{dating-yi-dating}.\footnotemark\\
you inquire-one-inquire\\
\glt `Inquire about it a little bit!''

\ex\label{ex:AByiAB-rou1}
\gll ge ge dian-tou \textit{weixiao-yi-weixiao}.\footnotemark\\
\textsc{clf} \textsc{clf} nod-head smile-one-smile\\
\glt `Each one nodded his head and smiled a little bit.'

\ex\label{ex:AByiAB-rou2}
\gll ta \textit{weixiao-le-yi-weixiao}, you \textit{mingxiang-le-yi-mingxiang}.\footnotemark\\
he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\
\glt `He smiled a little bit and meditated a little bit.'

\ex\label{ex:AByiAB-li}
\gll feichang yansu de ba jinshi yanjing \textit{duanzheng-le-yi-duanzheng}.\footnotemark\\
very seriously \textsc{de} \textsc{ba} nearsighted glasses straighten-\textsc{pfv}-one-straighten\\
\glt `[He] very seriously straightened the nearsighted glasses quickly.'

\ex\label{ex:ABleyiAB-ccl}
\gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
\z
\z

This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}, \citealp[143]{Sui2018}, \citealp[239]{YangWei2017}, \citealp[15]{Zhang2000}}, but we argue that it is not an issue of grammaticality.
Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.

AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\textit{kan} and A-\textit{kan}-\textit{kan} can also be accounted for by the lexical rules proposed in this section.
They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
    \citet{Huang1984} and \citet{Her1996, Her2010} argued that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
}
AA-\textit{kan} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \textit{kan} `look',
whereas A-\textit{kan}-\textit{kan} is the compound of a monosyllabic verb (A) and the reduplication of \textit{kan} `look'.
A-\textit{yi}-A-\textit{kan} is also possible, though rare, presumably also due to its length.
An inquiry in CCL found 55 hits of A-\textit{yi}-A-\textit{kan}.
A sample is listed in (\ref{ex:AyiAkan}).

\ea\label{ex:AyiAkan}
\ea
\gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
\glt `Researchers of special power may as well have a try as such as see \ldots'

\ex 
\gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'

\ex
\gll rang wo lai \textit{cai-yi-cai-kan}.\\
let I come guess-one-guess-look\\ \jambox{({CCL})}
\glt `Let me have a guess.'

\ex
\gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
\glt `Big bosses need to wait a little bit and see.'

\ex
\gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
\z
\z
Due to the prominent tentative, trying meaning of AA-\textit{kan} and A-\textit{kan}-\textit{kan}, they are not compatible with the perfective aspect marker \textit{le} semantically,
as one usually cannot try something that is already realized.
Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.

The current analysis provides a unified account for all forms of delimitative verbal reduplication in Mandarin Chinese.
Like in \citet{FanSongBond2015}, \textit{yi} is handled as a phonological element which does not make any contribution to the semantics,
and an inheritance hierarchy is used to capture the commonalities among different forms of reduplication.
But the present proposal also reflects the connection between the reduplication and aspect marking via multiple inheritance.
This account makes use of a semantic mechanism, which correctly rules out aspect marking with forms other than \textit{le}.
By providing a semantic explanation, this mechanism seems less \textit{ad hoc} than the one used in \citet{FanSongBond2015}, which simply assumed that the reduplication cannot combine with aspect information.
The present approach also has a broader coverage of the forms of verbal reduplication than the one in \citet{FanSongBond2015}.
Furthermore, all the forms are derivable from the lexical rules proposed here, so that there is no need to resort to irregular lexicon entries, and the productivity of these forms is correctly captured.
In sum, the analysis proposed in this paper possesses greater explanatory power and resolves the problems of previous studies.

### 2023-05-31 chapters/ch06-Conclusion.tex
Update 2023-05-31-17:44:51

\section{Conclusions}\label{sec:conclu}

The current study provides a new HPSG account for verbal reduplication in Mandarin Chinese.
We present empirical evidence that reduplication is possible with all \textit{Aktionsarten}.
We give a semantic explanation for the incompatibility of reduplication with aspect markers other than \textit{le}.
We argue that reduplication is a morphological rather than a syntactic process.
We model reduplication as a lexical rule,
and the different forms of reduplication are captured in an inheritance hierarchy using underspecified lists.
The interaction between verbal reduplication and aspect marking is handled by multiple inheritance.
This analysis is compatible with both mono- and disyllabic verbs, 
so that all productive forms of reduplication are derivable by lexical rules.
The analysis is implemented as part of the CoreGram project \citep{MuellerCoreGram} in a Chinese
grammar in the TRALE system \citep{MeurersEtAl2002, Penn2004}.

### 2023-06-03 chapters/ch01-Intro.tex
Update 2023-06-03-19:08:01

@@
 In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \citep[e.g.][]{Chao1968, LiThompson1981,  Li1996, Dai1997,  Zhu1998, Xing2000, Chen2001,  Tsao2001, Yang2003, XiaoMcEnery2004}.
-It means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
+This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
     in the example sentences will be set in italics.}
@@
 It contributes more empirical evidence and 
-offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG, \citealt{PollardSag1994}) to this phenomenon 
-using Minimal Recursion Semantics (MRS, \citealt{Copestakeetal2005}) as the semantic representation formalism.
+offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, Mueller2013}) to this phenomenon 
+using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}) as the semantic representation formalism.
 This new account avoids the problems of previous approaches and

### 2023-06-03 chapters/ch02-Phenomenon.tex
Update 2023-06-03-19:08:01

@@
 We adopt a broad definition in terms of the forms of verbal reduplication in Mandarin Chinese 
-and list in (\ref{ex:redup-forms}) all the forms commonly discussed in the literature.
+and list in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) all the forms commonly discussed in the literature.
 
-\settowidth\jamwidth{AB-\textit{le}-AB}
+%\settowidth\jamwidth{AB-\textit{le}-AB}
 
-\ea\label{ex:redup-forms}
-	\ea for monosyllabic verbs: \textit{shuo} `say'
+\ea\label{ex:forms-mono} for monosyllabic verbs: \textit{shuo} `say'
 	\ea \gll shuo-shuo\\ 
-		say-say\\\jambox{AA}
+		say-say\\ \hfill AA
 		\ex \gll shuo-yi-shuo\\
-		say-one-say\\\jambox{A-\textit{yi}-A}
+		say-one-say\\ \hfill A-\textit{yi}-A
 		\ex \gll shuo-le-shuo\\
-		say-\textsc{pfv}-say\\\jambox{A-\textit{le}-A}
+		say-\textsc{pfv}-say\\ \hfill A-\textit{le}-A
 		\ex \gll shuo-le-yi-shuo\\
-		say-\textsc{pfv}-one-say\\\jambox{A-\textit{le}-\textit{yi}-A}
+		say-\textsc{pfv}-one-say\\ \hfill A-\textit{le}-\textit{yi}-A
 		\ex \gll shuo-shuo-kan\\
-		say-say-look\\\jambox{AA-\textit{kan}}
+		say-say-look\\ \hfill AA-\textit{kan}
 		\ex \gll shuo-kan-kan\\
-		 say-look-look\\\jambox{A-\textit{kan}-\textit{kan}}
+		 say-look-look\\ \hfill A-\textit{kan}-\textit{kan}
 		\z
-	\ex for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
+
+\ex\label{ex:forms-di} for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
 		\ea \gll lai-wang-lai-wang\\
-		come-go-come-go\\ \jambox{ABAB}
+		come-go-come-go\\ \hfill ABAB
 		\ex \gll lai-wang-le-lai-wang\\
-		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
+		come-go-\textsc{pfv}-come-go\\ \hfill AB-\textit{le}-AB
 		\ex \gll lai-lai-wang-wang\\
-		come-come-go-go\\ \jambox{AABB}
+		come-come-go-go\\ \hfill AABB
 		\z
-	\ex\label{ex:forms-VO} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
+
+\ex\label{ex:forms-vo} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
 		\ea \gll shuo-shuo-huang\\
-		tell-tell-lie\\ \jambox{AAB}
+		tell-tell-lie\\ \hfill AAB
 		\ex \gll shuo-yi-shuo-huang\\
-		tell-one-tell-lie\\ \jambox{A-\textit{yi}-AB}
+		tell-one-tell-lie\\ \hfill A-\textit{yi}-AB
 		\ex \gll shuo-le-shuo-huang\\
-		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
-		\z
+		tell-\textsc{pfv}-tell-lie\\ \hfill A-\textit{le}-AB
 		\z
@@
 
-The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:redup-syn}). 
-The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see Section \ref{sec:aspM}). 
-The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:redup-quan}) \citetext{\citealp[114--115]{Chen2005}; \citealp[83--84]{Li1998}}.
-This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[114--115]{Chen2005}; \citealp[84]{Li1998}}, namely a short duration or a small extent.
+The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:syn-vi})--(\ref{ex:syn-svc}). 
+The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see \sectref{sec:aspM}). 
+The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
+This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent.
 
-\settowidth\jamwidth{(CCL)}
+%\settowidth\jamwidth{(CCL)}
 
-\ea\label{ex:redup-syn}
-	\ea Intransitive verb:
+\ea\label{ex:syn-vi} Intransitive verb:
 		\ea \gll ta xiao-le.\\
@@
 		\z
+
 \ex Transitive verb:
@@
 		\z
+
 \ex Under negation:
 		\ea \gll weishenme wo bu kan ta qita fangmian de jinbu he quanfangwei de chengzhang\\
-		why I not look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\
-		\glt `Why don't I look at his progress in other aspects and all-round growth?'
+		why I not look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\
+		\glt `Why don't I look at his progress in other aspects and comprehensive development?'
 		\ex \gll weishenme wo bu \textit{kan}-\textit{kan} ta qita fangmian de jinbu he quanfangwei de chengzhang\\
-		why I not look-look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\ \jambox{({CCL})}
-		\glt `Why don't I look a little bit at his progress in other aspects and all-round growth?'
+		why I not look-look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\ \hfill {({CCL})}
+		\glt `Why don't I look a little bit at his progress in other aspects and comprehensive development?'
 		\z
+
 \ex In \textit{ba}-construction:
@@
 		\ex \gll gou-mai zhiqian zhen gai ba qingkuang \textit{mo}-\textit{mo} qingchu.\\
-		purchase-buy before really should \textsc{ba} situation touch-touch clearly\\ \jambox{({CCL})}
+		purchase-buy before really should \textsc{ba} situation touch-touch clearly\\ \hfill {({CCL})}
 		\glt `(I) should really quickly check the situation clearly before I make the purchase.'
 		\z
+
 \ex With modal verb:
@@
 		\ex \gll you liang ben shu ni-men keyi \textit{kan}-\textit{kan} \ldots\\
-		there.be two \textsc{clf} book you-\textsc{pl} can read-read\\ \jambox{({CCL})}
+		there.be two \textsc{clf} book you-\textsc{pl} can read-read\\ \hfill {({CCL})}
 		\glt `There are two books that you can read a little bit \ldots'
 		\z
-	\ex In Serial Verb Construction (SVC):
+
+\ex\label{ex:syn-svc} In Serial Verb Construction (SVC):
 		\ea \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang kan nali chu-le wenti.\\
@@
 		\ex \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang \textit{kan}-\textit{kan} nali chu-le wenti.\\
-		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
+		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look-look where come.out-\textsc{pfv} problem\\ \hfill {({CCL})}
 		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a quick look at where went wrong.'
 		\z
-	\ex With an expression of quantity: \label{ex:redup-quan}
+
+\ex With an expression of quantity: \label{ex:syn-quan}
 		\ea[]{\gll ta yi tian pao shi li.\\
-		he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
+		he one day run ten mile\\ \hfill {\citep[83]{Li1998}}
 		\glt `He runs ten miles a day.'}
@@
 		he one day run-run ten mile\\}
-		\z
 		\z
@@
     \gll Wu Xumang kan-le zuo-an shi liuxia de jiaoyin \ldots\\ 
-    Wu Xumang look-\textsc{pfv} commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
+    Wu Xumang look-\textsc{pfv} commit-crime when leave \textsc{de} footprint\\ \hfill {\citep[158]{XiaoMcEnery2004}}
     \glt `Wu Xumang looked at the footprint left when the crime was committed.'
@@
     \gll Wu Xumang \textit{kan-le-kan} zuo-an shi liuxia de jiaoyin \ldots\\
-    Wu Xumang look-\textsc{pfv}-look commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
+    Wu Xumang look-\textsc{pfv}-look commit-crime when leave \textsc{de} footprint\\ \hfill {\citep[158]{XiaoMcEnery2004}}
     \glt `Wu Xumang looked a little bit at the footprint left when the crime was committed.'
@@
 \gll keshi xian mujin, dajia ye zhihao \textit{weiqu-weiqu} le.\\
-but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
+but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \hfill {({CCL})}
 \glt `But now, everybody can only feel wronged a little bit.'
@@
 \gll ta-men neng zuo de buguo shi \textit{ren-ren-xing} shua dian'er xiao piqi \textit{diao-diao} yanlei shenme de.\\
-she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \jambox{({CCL})}
+she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \hfill {({CCL})}
 \glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
@@
 {\gll ta \textit{bing-bing} jiu hao le.\\
-he be.sick-be.sick then well \textsc{ptc}\\ \jambox{\citep[155]{XiaoMcEnery2004}}
+he be.sick-be.sick then well \textsc{ptc}\\ \hfill {\citep[155]{XiaoMcEnery2004}}
 Intended: `He was sick for a little while and then got well.'}\label{ex:redup-stat}
@@
 {\gll ta \textit{ying}-\textit{le}-\textit{ying} na chang bisai.\\
-he win-\textsc{pfv}-win that \textsc{clf} competition\\ \jambox{\citep[155]{XiaoMcEnery2004}}
+he win-\textsc{pfv}-win that \textsc{clf} competition\\ \hfill {\citep[155]{XiaoMcEnery2004}}
 \glt Intended: `He won that competition a little bit.'}\label{ex:redup-achiV}
@@
 \gll wo zhen xiang \textit{bing-yi-bing}, xie ta ge shi tian ban yue.\\
-I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
+I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \hfill {\citep[54]{Chen2001}}
 \glt `I really want to be sick for a little while and rest for ten days or half a month.'
@@
 \gll jiao ta \textit{sheng-sheng} xiaohai, jiu zhidao zuo muqin de gan-ku le.\\
-let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
+let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \hfill {\citep[112]{Chen2005}}
 \glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
@@
 The perfective aspect marker \textit{le} is compatible with reduplication while the experiential aspect marker \textit{guo} is not.
-\citet[128--131]{XiaoMcEnery2004} described that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
+\citet[128--131]{XiaoMcEnery2004} stated that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
 It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
@@
     \gll Weici, Deng Lijun shangxin de ku-le san tian.\\
-    for.this Deng Lijun sadly \textsc{de} cry-\textsc{pfv} three day\\ \jambox{\citep[129]{XiaoMcEnery2004}}
+    for.this Deng Lijun sadly \textsc{de} cry-\textsc{pfv} three day\\ \hfill {\citep[129]{XiaoMcEnery2004}}
     \glt `For this reason, Deng Lijun cried sadly for three days.'
@@
     \gll Ta zhidao-le zhe shi de nei-qing.\\
-    he know-\textsc{pfv} this matter \textsc{de} inside-information\\ \jambox{\citep[130]{XiaoMcEnery2004}}
+    he know-\textsc{pfv} this matter \textsc{de} inside-information\\ \hfill {\citep[130]{XiaoMcEnery2004}}
     \glt `He got to know the inside information on this matter.'
@@
 
-On the other hand, the experiential aspect marker \textit{guo} cannot co\hyp{}occur with a reduplicated verb, 
+In comparison, the experiential aspect marker \textit{guo} cannot co\hyp{}occur with a reduplicated verb, 
 because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
@@
     \gll ta dang-guo bing.\\
-    he serve.as-\textsc{exp} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
+    he serve.as-\textsc{exp} soldier\\ \hfill {\citep[149]{XiaoMcEnery2004}}
     \glt `He once served as a soldier.'
@@
     \gll ta dang-le bing.\\
-    he serve.as-\textsc{pfv} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
+    he serve.as-\textsc{pfv} soldier\\ \hfill {\citep[149]{XiaoMcEnery2004}}
     \glt `He became a soldier.'
@@
   \ex \gll Yao Ming \textit{kan}-\textit{le}-\textit{kan} ta de fanyi Ke Lin...\\
-  Yao Ming look-\textsc{pfv}-look he \textsc{de} translator Ke Lin\\ \jambox{({CCL})}
+  Yao Ming look-\textsc{pfv}-look he \textsc{de} translator Ke Lin\\ \hfill {({CCL})}
   \glt `Yao Ming looked at his translator Ke Lin a little bit...'
@@
   \ex \gll ta \textit{heji}-\textit{le}-\textit{heji}, dui Jiangqing shuo...\\
-  he consider-\textsc{pfv}-consider to Jiangqing say\\ \jambox{({CCL})}
+  he consider-\textsc{pfv}-consider to Jiangqing say\\ \hfill {({CCL})}
   \glt `He considered a little bit, and told Jiangqing...'
@@
   \ea[]{\gll \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} jiu ba chulai le.\\
-  shake-shake-sway-sway then pull out \textsc{ptc}\\  \jambox{\citep[85]{Xie2020}}
+  shake-shake-sway-sway then pull out \textsc{ptc}\\  \hfill {\citep[85]{Xie2020}}
   \glt `Shake it a little bit and then it will be pulled out.'}
@@
   \ex[*]{\gll \textit{yao}-\textit{yao}-\textit{le}-\textit{huang}-\textit{huang} jiu ba chulai le.\\
-  shake-shake-\textsc{pfv}-sway-sway then pull out \textsc{ptc}\\ \jambox{\citep[85]{Xie2020}}}
+  shake-shake-\textsc{pfv}-sway-sway then pull out \textsc{ptc}\\ \hfill {\citep[85]{Xie2020}}}
   \z
@@
   \ea[*]{\gll dian-che \textit{yao-huang}-\textit{yao-huang} kai zou...\\
-  electric-car shake-sway-shake-sway drive away...\\ \jambox{\citep[86]{Xie2020}}}
+  electric-car shake-sway-shake-sway drive away...\\ \hfill {\citep[86]{Xie2020}}}
 
   \ex[]{\gll dian-che \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} kai zou...\\
-  electric-car shake-shake-sway-sway drive away...\\ \jambox{\citep[86]{Xie2020}}
+  electric-car shake-shake-sway-sway drive away...\\ \hfill {\citep[86]{Xie2020}}
   \glt `The tram drove away jiggly...'}
@@
   \ea[*]{\gll ...zuo zai  \textit{yao-huang}-\textit{yao-huang} de che shang\\
-  sit on shake-sway-shake-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}}
+  sit on shake-sway-shake-sway \textsc{de} car on\\ \hfill {\citep[86]{Xie2020}}}
 
   \ex[]{\gll ...zuo zai  \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} de che shang\\
-  sit on shake-shake-sway-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}
+  sit on shake-shake-sway-sway \textsc{de} car on\\ \hfill {\citep[86]{Xie2020}}
   \glt `...sit on the jiggling car'}
@@
   \ea[]{\gll qiao-da gan-jing shi huanjie gan-qi de hao banfa.\\
-  knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}
+  knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \hfill {\citep[88]{Xie2020}}
   \glt `Beating the liver channel is a good method to relieve the stagnation of liver \textit{qi}.'}
@@
   \ex[]{\gll \textit{qiao-da}-\textit{qiao-da} gan-jing shi huanjie gan-qi de hao banfa.\\
-  knock-beat-knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}
+  knock-beat-knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \hfill {\citep[88]{Xie2020}}
    \glt `Beating the liver channel a little bit is a good method to relieve the stagnation of liver \textit{qi}.'}
@@
    \ex[*]{\gll \textit{qiao}-\textit{qiao}-\textit{da}-\textit{da} gan-jing shi huanjie gan-qi de hao banfa.\\
-  knock-knock-beat-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}}
+  knock-knock-beat-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \hfill {\citep[88]{Xie2020}}}
 
@@
 The two groups also have different input and output constraints.
-\citet{Xie2020} claimed that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see Section~\ref{sec:Aktionsarten}).
-On the other hand, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
+\citet{Xie2020} claimed that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see \sectref{sec:Aktionsarten}).
+in comparison, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
 Moreover, as can be seen in the translation in (\ref{ex:AABB-input}), the output of AABB has an increasing meaning, i.e.
@@
   \ea \gll duo-shan $\rightarrow$ \textit{duo}-\textit{duo}-\textit{shan}-\textit{shan}\\
-  hide-dodge {} hide-hide-dodge-dodge\\ \jambox{\citep[88]{Xie2020}}
+  hide-dodge {} hide-hide-dodge-dodge\\ \hfill {\citep[88]{Xie2020}}
   \glt `hide and dodge' `hide and dodge repeatedly'
@@
   \ex \gll jin-chu $\rightarrow$ \textit{jin}-\textit{jin}-\textit{chu}-\textit{chu}\\
-  enter-exit {} enter-enter-exit-exit\\ \jambox{\citep[88]{Xie2020}}
+  enter-exit {} enter-enter-exit-exit\\ \hfill {\citep[88]{Xie2020}}
   \glt `enter and exit' `enter and exit repeatedly'
@@
   \ex \gll shuo-xiao $\rightarrow$ \textit{shuo}-\textit{shuo}-\textit{xiao}-\textit{xiao}\\
-  talk-laugh {} talk-talk-laugh-laugh\\ \jambox{\citep[88]{Xie2020}}
+  talk-laugh {} talk-talk-laugh-laugh\\ \hfill {\citep[88]{Xie2020}}
   \glt `talk and laugh' `talk and laugh continuously'
@@
 
-The semantic criterion is that the meaning of a phrase is usually built up in a compositional way while that of a word usually not \citetext{\citealp[140]{Duanmu1998}; \citealp[275]{Schaefer2009}}. 
+The semantic criterion is that the meaning of a phrase is usually built up in a compositional way while that of a is word usually not \citetext{\citealp[140]{Duanmu1998}; \citealp[275]{Schaefer2009}}.
 The meaning of the reduplication is not compositional, as it does not mean that the event denoted by the verb happens twice or multiple times, but rather that the event happens for a short duration and/or for low frequency.
@@
 And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
-Turning to separate modification,  element in the reduplication cannot be modified individually. 
+Turning to separate modification,  the element in the reduplication cannot be modified individually. 
 Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
@@
 
-On the other hand, nothing can intervene in between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).
+Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).
 
@@
   \gll ta xinku de zhong cai qinfen de mai.\\
-  he hard-workingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
+  he hardworkingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
   \glt `He plants vegetables hard-workingly and sells them diligently.'
@@
   \ea \gll [jiu de shu] gen [xin de shu]\\
-  old \textsc{de} book and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
+  old \textsc{de} book and new \textsc{de} book\\ \hfill {\citep[137]{Duanmu1998}}
   \glt `old books and new books'
@@
   \ex \gll [jiu de gen xin de] shu\\
-  old \textsc{de} and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
+  old \textsc{de} and new \textsc{de} book\\ \hfill {\citep[137]{Duanmu1998}}
   \glt `old and new books'
@@
   \gll [huo-che] gen [qi-che]\\
-  fire-car and gas-car\\ \jambox{\citep[137]{Duanmu1998}}
+  fire-car and gas-car\\ \hfill {\citep[137]{Duanmu1998}}
   \glt `train and automobile'}
@@
   \gll [huo gen qi] che\\
-  fire and gas car\\ \jambox{\citep[137]{Duanmu1998}}}
+  fire and gas car\\ \hfill {\citep[137]{Duanmu1998}}}
   \z
@@
   \gll wujian gong-xiu mo dian bohe-gao huo \textit{jiao}-\textit{jiao} kouxiangtang.\\
-    midday work-break apply a.little mint-cream or chew-chew chewing.gum\\ \jambox{({CCL})}
+    midday work-break apply a.little mint-cream or chew-chew chewing.gum\\ \hfill {({CCL})}
     \glt `During the working break in the midday, apply a little bit of mint cream or chew some chewing gum a little bit.'
@@
    \gll Song Ailing \textit{kan}-\textit{le}-\textit{kan} yupen you zou-le chulai.\\
-   Song Ailing look-\textsc{pfv}-look bath.tub again walk-\textsc{pfv} out\\  \jambox{({CCL})}
+   Song Ailing look-\textsc{pfv}-look bath.tub again walk-\textsc{pfv} out\\  \hfill {({CCL})}
    \glt `Song Ailing looked at the bath tub a little bit and walked out again.'
@@
 In comparison, Parallel Verb Compounds failed all the tests as well, whereas {SVC}s passed all of them.
-This makes the behavior of the reduplication seems more similar to that of a Parallel Verb Compound than that of an {SVC}.
-Therefore, it seems more likely to assume the reduplication to be a morphological process rather than a syntactic one.
+This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an {SVC}.
+Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.

### 2023-06-03 chapters/ch04-Previous.tex
Update 2023-06-03-19:08:01

@@
 %%%%%%%%%%%
-\subsection{The reduplicant as a verbal classifier}\label{sec:clf}
+\subsection{The reduplication as a verbal classifier phrase}\label{sec:clf}
 
-\citet{Chao1968}, \citet{Fan1964} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
+\citet{Fan1964}, \citet{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
 as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet{Chao1968} or \textit{cognate object} in \citet{Chao1968, Hong1999}.
@@
 \gll mei che guo yi ci huang\\
-not tell \textsc{exp} one \textsc{clf} lie\\ \jambox{\citep[616]{Chao1968}}
+not tell \textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
 \glt `haven't told lie once'
@@
 framework of First Phase Syntax \citep{Ramchand2008}.
-
 \citet{Ramchand2008} proposed that an event is comprised of the following phrases: 
@@
 The present study does not argue for a {NP} or a {DP} analysis and simply takes over the illustration provided in the cited papers.}
-Dynamic and volitional verbs have the features [init proc] and are therefore located unter \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.
+Dynamic and volitional verbs have the features [init proc] and are therefore located under \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.
 Achievement verbs possess the feature [res] and reside under \textit{res}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}. 
@@
 Their use is possible in specific contexts and should not be ruled out syntactically.
-Consequently, this proposal does not seem to offer an appropriate account for the reduplication.
+Consequently, this proposal does not seem to offer an appropriate account for  reduplication.
 
@@
 
- \citet{YangWei2017} endorsed the analysis of the reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+ \citet{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 
@@
 Turning to reduplication, it cannot occur without additional information as well (\ref{ex:redup-tsai}).
-Based on this, the reduplicant should reside under Asp$_2$.
+Based on this, the reduplicant should reside under Asp$_2$, as illustrated in \figref{tree:redupasp}.
 
@@
 he laugh-laugh not speak\\
-\glt `He laughed a little, didn't speak.'}\label{ex:redup-tsai-co}
+\glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
 \z
@@
 
+\begin{figure}
+    \centering
+    \begin{forest}
+        [TP [T]
+        [...
+        [AspP$_1$ (outer aspect) [Asp$_1$\\zai/guo]
+        [\textit{v}P [\textit{v}]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\zhe/le/reduplication]
+        [VP [V-Asp$_3$ (inner aspect)\\wan]
+        ]
+        ]
+        ]
+        ]
+        ]
+        ]
+    \end{forest}
+    \caption{Position of reduplication according to the aspectual system in \citet{Tsai2008}}
+    \label{tree:redupasp}
+\end{figure}
+
 This analysis would result in a mismatch between syntax and semantics. 
-Even though reduplication, \textit{le} and \textit{guo} all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
-\textit{guo} is situated under Asp$_1$ while \textit{le} and the reduplication are under Asp$_2$.
+Even though \textit{le}, \textit{guo} and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
+\textit{guo} is situated under Asp$_1$ while \textit{le} and the reduplication are under Asp$_2$, as can be seen from \figref{tree:redupasp}.
 
@@
 
-This analysis correctly captures the fact that the addition of \textit{yi} does not change the syntactic and semantic behaviors of the reduplication.
+This analysis correctly captures the fact that the addition of \textit{yi} does not change the syntactic and semantic behavior of the reduplication.
 It also provides a formal account for the phonology of the reduplication.
-On the other hand, by assuming a construction specially for the reduplication, this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese, unlike the affixation analyses described in \sectref{sec:asp}.
+Nevertheless, by assuming a construction specially for the reduplication, this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese, unlike the affixation analyses described in \sectref{sec:asp}.
 
@@
 and \citet{Xing2000stat} concluded that AAB is productive as well.
-Thus, these forms should not be handled as  irregular forms, but should be derivable from lexical rules.
+Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.
 

### 2023-06-03 chapters/ch05-Analysis.tex
Update 2023-06-03-19:08:01

@@
 In what follows, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
-using MRS, as proposed in \citet{LuMueller2021}.
+using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}).%, as proposed in \citet{LuMueller2021}.
 
@@
 \etag{} indicates an underspecified list which could be empty or not. 
-A delimitative relation is appended to the \textsc{rels} value of the input verb, 
+A delimitative relation is appended to the \textsc{relations (rels)} value of the input verb, 
 and it takes the event index of the input verb as argument. 
@@
 hence \type{delimitative-rel} is treated as a modifier.
- Further relations can be added at the beginning of the \textsc{relations (rels)} list to allow for
+ Further relations can be added at the beginning of the \textsc{rels} list to allow for
 the additional perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A. 
@@
 \type{verbal-reduplication-lr} \impl\\
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
         rels \4 ] ]
-}}
+}
+%}
 \label{avm:redup}
@@
 \type{non-perfective-verbal-reduplication-lr} \impl\\
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
     }
-}
+%}
 \z
-The \textsc{rels} list of the output of the lexical rule \iboxb{1} is the \textsc{rels} list of
-the daughter plus one element. 
-Since the element is specified in the supertype, it has not been specified in (\ref{avm:nonperf}) again.
+The \textsc{rels} list of the output of the lexical rule is the \textsc{rels} list of
+the daughter \iboxb{1} plus a list with one element. 
+Since this element is specified in the supertype, it is not specified in (\ref{avm:nonperf}) again.
 
@@
 \type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
-\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is empty, 
+\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is the empty list, 
 whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:
@@
  \ea   \type{aa-lr} \impl \\%& 
-    \scalebox{.9}{%
+  %  \scalebox{.9}{%
         \avm{
@@
             lex-dtr & [phon & \1] ]
-    }} %& 
+    }
+%} %& 
 \ex	\type{a-yi-a-lr} \impl\\
-     \scalebox{.9}{%
+ %    \scalebox{.9}{%
         \avm{
@@
             lex-dtr & [phon & \1] ]
-    }}
+    }
+%}
 %\end{tabular}
@@
 The AA lexical rule with all constraints inherited from the supertypes:
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
         ]
-}}
+}
+%}
 \z
@@
 The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
 Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
         phon & \1 \+ \phonliste{ le }\\
-        \punk{synsem\textbar cont}{ [ ltop & \2\\
+        \punk{synsem\textbar loc\textbar cont}{ [ ltop & \2\\
             ind & \3 ]}\\ 
@@
         arg0 & \3\\
-        arg1 & \4]> \+ \5\smallskip\\
+        arg1 & \4]> \,\+\, \5\smallskip\\
         lex-dtr & [phon & \1\\
@@
 Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
         phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
-        \punk{synsem\textbar cont}{ [ltop & \2\\
+        \punk{synsem\textbar loc \textbar cont}{ [ltop & \2\\
             ind  & \3]}\\ 
@@
         ]
-}}
+}
+%}
 \z
 
-\type{v-le-lr} as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
+\type{v-le-lr} with all inherited constraints as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
 and that nothing else comes after \phonliste{ le }.
@@
 Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
-\scalebox{.9}{%
+%\scalebox{.9}{%
     \avm{
@@
         phon & \1 $\oplus$ \phonliste{ le }\\
-        \punk{synsem\textbar cont\textbar ltop}{ \2}\\ 
+        \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
         rels & <[\type*{perfective-rel}\\
@@
         lex-dtr & [phon & \1\\
-        cat  & [ head & verb\\
+        synsem\textbar loc \textbar cat  & [ head & verb\\
         cont & [ltop & \4\\
@@
         rels & \5]]
-}}
+}
+%}
 \z
@@
 %\resizebox{\linewidth}{!}{
-    \scalebox{.9}{%
+ %   \scalebox{.9}{%
         \avm{
@@
             phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
-            \punk{synsem\textbar cont\textbar ltop}{ \2}\\ 
+            \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
             rels & <[\type*{perfective-rel}\\
@@
             ]
-    }}
+    }
+%}
     %}
@@
 %\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
-\ea    \scalebox{.9}{%
+\ea    %\scalebox{.9}{%
+        \type{a-le-yi-a-lr} \impl\\
         \avm{
-            [\type*{a-le-yi-a-lr}\\
+            [%\type*{a-le-yi-a-lr}\\
             phon & \1 \+ \phonliste{ le, yi } \+ \1\\
@@
             ]
-    }}%&
-\ex    \scalebox{.9}{%
+    }
+%}%&
+\ex   % \scalebox{.9}{%
+    \type{a-le-a-lr} \impl\\
         \avm{
-            [\type*{a-le-a-lr}\\
+            [%\type*{a-le-a-lr}\\
             phon & \1 \+ \phonliste{ le } \+ \1\\
@@
             ]
-    }}
+    }
+%}
 %\end{tabular}
@@
 \citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
-Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu})--(\ref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1})--(\ref{ex:ABleyiAB-ccl}) were found.
+Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.
 
@@
 \footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
-\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
+\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
 \ea\label{ex:ABleyiAB}
@@
 you let me arrange-one-arrange\\
-\glt `Let me arrange it a little bit!''
+\glt `Let me arrange it a little bit!'
 
@@
 you inquire-one-inquire\\
-\glt `Inquire about it a little bit!''
+\glt `Inquire about it a little bit!'
 
@@
 \gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
-many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
+many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \hfill {(CCL)}
 \glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
@@
 \gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
-special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
+special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \hfill {(CCL)}
 \glt `Researchers of special power may as well have a try as such as see \ldots'
@@
 \gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
-but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
+but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \hfill {(CCL)}
 \glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'
@@
 \gll rang wo lai \textit{cai-yi-cai-kan}.\\
-let I come guess-one-guess-look\\ \jambox{({CCL})}
+let I come guess-one-guess-look\\ \hfill {({CCL})}
 \glt `Let me have a guess.'
@@
 \gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
-big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
+big-boss-\textsc{pl} need wait-one-wait-look\\ \hfill {(CCL)}
 \glt `Big bosses need to wait a little bit and see.'
@@
 \gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
-madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
+madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \hfill {(CCL)}
 \glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'

### 2023-06-08 chapters/ch01-Intro.tex
Update 2023-06-08-15:59:49

@@
 
-In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \citep[e.g.][]{Chao1968, LiThompson1981,  Li1996, Dai1997,  Zhu1998, Xing2000, Chen2001,  Tsao2001, Yang2003, XiaoMcEnery2004}.
+In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g.
+\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[67]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+4.3]{XiaoMcEnery2004}).
 This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-15:59:49

--- 2023-05-31 chapters/ch02-Phenomenon.tex
@@
 We adopt a broad definition in terms of the forms of verbal reduplication in Mandarin Chinese 
-and list in (\ref{ex:redup-forms}) all the forms commonly discussed in the literature.
+and list in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) all the forms commonly discussed in the literature.
 
@@
 
-\ea\label{ex:redup-forms}
-	\ea for monosyllabic verbs: \textit{shuo} `say'
+\ea\label{ex:forms-mono} for monosyllabic verbs: \textit{shuo} `say'
 	\ea \gll shuo-shuo\\ 
-		say-say\\\jambox{AA}
+		say-say\\ \jambox{AA}
 		\ex \gll shuo-yi-shuo\\
-		say-one-say\\\jambox{A-\textit{yi}-A}
+		say-one-say\\ \jambox{A-\textit{yi}-A}
 		\ex \gll shuo-le-shuo\\
-		say-\textsc{pfv}-say\\\jambox{A-\textit{le}-A}
+		say-\textsc{pfv}-say\\ \jambox{A-\textit{le}-A}
 		\ex \gll shuo-le-yi-shuo\\
-		say-\textsc{pfv}-one-say\\\jambox{A-\textit{le}-\textit{yi}-A}
+		say-\textsc{pfv}-one-say\\ \jambox{A-\textit{le}-\textit{yi}-A}
 		\ex \gll shuo-shuo-kan\\
-		say-say-look\\\jambox{AA-\textit{kan}}
+		say-say-look\\ \jambox{AA-\textit{kan}}
 		\ex \gll shuo-kan-kan\\
-		 say-look-look\\\jambox{A-\textit{kan}-\textit{kan}}
+		 say-look-look\\ \jambox{A-\textit{kan}-\textit{kan}}
 		\z
-	\ex for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
+
+\ex\label{ex:forms-di} for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
 		\ea \gll lai-wang-lai-wang\\
@@
 		\z
-	\ex\label{ex:forms-VO} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
+
+\ex\label{ex:forms-vo} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
 		\ea \gll shuo-shuo-huang\\
@@
 		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
-		\z
 		\z
@@
 
-The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:redup-syn}). 
-The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see Section \ref{sec:aspM}). 
-The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:redup-quan}) \citetext{\citealp[114--115]{Chen2005}; \citealp[83--84]{Li1998}}.
-This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[114--115]{Chen2005}; \citealp[84]{Li1998}}, namely a short duration or a small extent.
+The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:syn-vi})--(\ref{ex:syn-svc}). 
+The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see \sectref{sec:aspM}). 
+The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
+This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent.
 
-\settowidth\jamwidth{(CCL)}
-
-\ea\label{ex:redup-syn}
-	\ea Intransitive verb:
+\settowidth\jamwidth{\citep[83]{Li1998}}
+\begin{sloppypar}
+\ea\label{ex:syn-vi} Intransitive verb:
 		\ea \gll ta xiao-le.\\
@@
 		\z
+
 \ex Under negation:
 		\ea \gll weishenme wo bu kan ta qita fangmian de jinbu he quanfangwei de chengzhang\\
-		why I not look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\
-		\glt `Why don't I look at his progress in other aspects and all-round growth?'
+		why I not look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\
+		\glt `Why don't I look at his progress in other aspects and comprehensive development?'
 		\ex \gll weishenme wo bu \textit{kan}-\textit{kan} ta qita fangmian de jinbu he quanfangwei de chengzhang\\
-		why I not look-look he other aspect \textsc{de} progress and all-round \textsc{de} growth\\ \jambox{({CCL})}
-		\glt `Why don't I look a little bit at his progress in other aspects and all-round growth?'
+		why I not look-look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\ \jambox{({CCL})}
+		\glt `Why don't I look a little bit at his progress in other aspects and comprehensive development?'
 		\z
+
 \ex In \textit{ba}-construction:
@@
 		\z
+
 \ex With modal verb:
@@
 		\z
-	\ex In Serial Verb Construction (SVC):
+
+\ex\label{ex:syn-svc} In Serial Verb Construction (SVC):
 		\ea \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang kan nali chu-le wenti.\\
@@
 		\z
-	\ex With an expression of quantity: \label{ex:redup-quan}
+
+\ex With an expression of quantity: \label{ex:syn-quan}
 		\ea[]{\gll ta yi tian pao shi li.\\
@@
 \z
-\z
+\end{sloppypar}
 
@@
 
-The reduplication has a \textit{delimitativeness} meaning \citep[e.g.][]{Chao1968, Chen2001, Dai1997, Li1996, LiThompson1981, Tsao2001, XiaoMcEnery2004, Xing2000, Yang2003, Zhu1998}. 
+The reduplication has a \textit{delimitativeness} meaning (e.g.
+\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[67]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+4.3]{XiaoMcEnery2004}).
 To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
@@
 (\ref{ex:redup-dyn-look}) indicates that the protagonist took a brief look or several brief looks at the footprint and looked away in the end, which is a process full of changes.
+
+\settowidth\jamwidth{\citep[158]{XiaoMcEnery2004}}
 
@@
 
+\settowidth\jamwidth{(CCL)}
+
+\begin{sloppypar}
 \ea\label{ex:nonvol}
@@
 \z
+\end{sloppypar}
 
@@
 and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) is readily acceptable.
+
+\settowidth\jamwidth{\citep[155]{XiaoMcEnery2004}}
 
@@
 Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.
+
+\settowidth\jamwidth{\citep[112]{Chen2005}}
 
@@
 The perfective aspect marker \textit{le} is compatible with reduplication while the experiential aspect marker \textit{guo} is not.
-\citet[128--131]{XiaoMcEnery2004} described that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
+\citet[128--131]{XiaoMcEnery2004} stated that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
 It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
 It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).
+
+\settowidth\jamwidth{\citep[129]{XiaoMcEnery2004}}
 
@@
 \textit{Le} can be inserted freely into AA (\ref{ex:le-insertionAA}) and ABAB (\ref{ex:le-insertionABAB}) but not into AABB (\ref{ex:le-insertionAABB}).
+
+\settowidth\jamwidth{\citep[85]{Xie2020}}
 
@@
 If the unit is a word, however, then neither of these should  be possible.
-As illustrated in (\ref{ex:redup-forms}) in Section~\ref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
+As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
 As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet{Huangetal2009} and \citet{MuellerLipenkova2013} considered aspect markers in Mandarin Chinese to be morphological elements.
@@
 
+\settowidth\jamwidth{\citep[137]{Duanmu1998}}
+
 \ea\label{ex:co-phrase}
@@
 The verb in the latter case is not reduplicated and it cannot express the delimitative meaning either.
+
+\settowidth\jamwidth{(CCL)}
 

### 2023-06-08 chapters/ch05-Analysis.tex
Update 2023-06-08-15:59:49

@@
 
+\settowidth\jamwidth{(CCL)}
+
 \footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
@@
 \footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
+\begin{sloppypar}
 \ea\label{ex:ABleyiAB}
@@
 \gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
-many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \hfill {(CCL)}
+many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
 \glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
@@
 
+\begin{sloppypar}
 \ea\label{ex:AyiAkan}
@@
 \gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
-special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \hfill {(CCL)}
+special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
 \glt `Researchers of special power may as well have a try as such as see \ldots'
@@
 \gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
-but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \hfill {(CCL)}
+but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
 \glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'
@@
 \gll rang wo lai \textit{cai-yi-cai-kan}.\\
-let I come guess-one-guess-look\\ \hfill {({CCL})}
+let I come guess-one-guess-look\\ \jambox{({CCL})}
 \glt `Let me have a guess.'
@@
 \gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
-big-boss-\textsc{pl} need wait-one-wait-look\\ \hfill {(CCL)}
+big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
 \glt `Big bosses need to wait a little bit and see.'
@@
 \gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
-madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \hfill {(CCL)}
+madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
 \glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
@@
 Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.
+\end{sloppypar}
 

### 2023-06-08 chapters/ch01-Intro.tex
Update 2023-06-08-16:29:37

@@
 In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[67]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
 4.3]{XiaoMcEnery2004}).

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-16:29:37

@@
 The reduplication has a \textit{delimitativeness} meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[67]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
 4.3]{XiaoMcEnery2004}).

### 2023-06-08 chapters/ch01-Intro.tex
Update 2023-06-08-18:56:45

@@
 In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
 4.3]{XiaoMcEnery2004}).

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-18:56:45

@@
 The reduplication has a \textit{delimitativeness} meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
 4.3]{XiaoMcEnery2004}).
@@
 The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
-\citet{Chao1968}, \citet{LiThompson1981} and \citet{Liao2014} listed reduplication under morphological processes. 
+\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981} and \citet[4--5]{Liao2014} listed reduplication under morphological processes. 
 \citet{Arcodiaetal2014}, \citet{Xiong2016}, \citet{BascianoMelloni2017}, \citet{YangWei2017}, \citet{MelloniBasciano2018}, \citet{Xie2020},   on the other hand, claimed it to be syntactic.
@@
 However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
-For instance, the \textit{-bar} derivation in German is a productive morphological process \citep[381]{Mueller2013}. 
+For instance, the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
 The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
 And inflections of tense in German do not change the valency of the input verb.
-Further, if \textit{le} is considered to be a morphological element \citep[e.g.][]{Huangetal2009, MuellerLipenkova2013}, the insertion of \textit{le} does not have to be viewed as a syntactic
+Further, if \textit{le} is considered to be a morphological element (e.g.
+\citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \textit{le} does not have to be viewed as a syntactic
 process either.
@@
 As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
-As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet{Huangetal2009} and \citet{MuellerLipenkova2013} considered aspect markers in Mandarin Chinese to be morphological elements.
+As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec.
+3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers (\textit{-le}, \textit{-zhe} and \textit{-guo}) in Mandarin Chinese to be morphological elements.
 E.g.
-\citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered aspect information to be syntactically encoded.}
+\citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered all aspect information to be syntactically encoded.}
 And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).

### 2023-06-08 chapters/ch04-Previous.tex
Update 2023-06-08-18:56:45

@@
 \citet{Fan1964}, \citet{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
-as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet{Chao1968} or \textit{cognate object} in \citet{Chao1968, Hong1999}.
-The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet{LiThompson1981} or \textit{frequency phrase} in \citet{Huangetal2009}.}.
+as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
+The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
 A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).
@@
  \citet{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
-
  \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-23:44:07

@@
 
- \citet{Fan1964}, \citet{Arcodiaetal2014}, \citet{MelloniBasciano2018} and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
+ \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
 and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
-Specifically, \citet{Arcodiaetal2014}, \citet{MelloniBasciano2018} and \citet{Xie2020} identified that AA and ABAB have a diminishing meaning, 
+Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identified that AA and ABAB have a diminishing meaning, 
 namely that the event happens for a short duration or to a small extent. 
-AABB, on the other hand, expresses an increasing meaning, which indicates a repetition or action in progress. 
-\citet{Xie2020} also found that AA and ABAB have relatively high productivity, 
+By contrast, AABB expresses an increasing meaning, which indicates a repetition or action in progress. 
+\citet[Sec. 3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
 whereas the productivity of AABB is low. 
@@
 AA-\textit{kan}, A-\textit{kan}-\textit{kan}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
-In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}-\textit{yi}\hyp{}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.
+In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.
 
@@
 and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
-Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
+Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
 ``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
-\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
- \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
- \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.
+\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication, as well.
+ \citet[276]{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
+ \citet[Sec. 3.1.3]{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.
 
@@
 She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
-\citet{Xing2000} considered that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
+\citet[Sec. 5]{Xing2000} considered that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
 The former conveys a casual attitude whereas the latter sounds more serious.
@@
 Previous research often claimed that the reduplication can only be used for verb classes of certain \textit{Aktionsarten}, while it is infelicitous for other ones.
-\citet[277--278]{Hong1999} and \citet[234--235]{LiThompson1981} suggested that reduplication is only possible for volitional activity verbs.
+ \citet[234--235]{LiThompson1981} and \citet[277--278]{Hong1999} suggested that reduplication is only possible for volitional activity verbs.
 \citet[70--71]{Dai1997} und \citet[290]{Tsao2001} both considered that reduplication can only be used in dynamic situations.
 The former further claimed that achievement verbs cannot be reduplicated.
- \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet{BascianoMelloni2017} proposed that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
+ \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet[145]{BascianoMelloni2017} proposed that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
 This means that the reduplication can only interact with dynamic situations which encode no results and is consequently only compatible with activities and semelfactives, but not with states and achievements.
@@
 
-However, examples such as those in (\ref{ex:redup-achi-stat1}) -- (\ref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
+However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
 Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.
@@
 \footnotetext[2]{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
+\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
+\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
+%\begin{sloppypar}
 \ea
@@
 \z
-\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
-\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
+%\end{sloppypar}
 
@@
 \citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981} and \citet[4--5]{Liao2014} listed reduplication under morphological processes. 
-\citet{Arcodiaetal2014}, \citet{Xiong2016}, \citet{BascianoMelloni2017}, \citet{YangWei2017}, \citet{MelloniBasciano2018}, \citet{Xie2020},   on the other hand, claimed it to be syntactic.
+By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claimed it to be syntactic.
 %And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
@@
 As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec.
-3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers (\textit{-le}, \textit{-zhe} and \textit{-guo}) in Mandarin Chinese to be morphological elements.
+3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers  in Mandarin Chinese (\textit{le}, \textit{zhe} and \textit{guo}) to be morphological elements.
 E.g.
-\citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered all aspect information to be syntactically encoded.}
+\citet{Travis2000}, \citet{Ramchand2008},  \citet[23]{Arcodiaetal2014}, \citet[146]{BascianoMelloni2017} considered all aspect information to be syntactically encoded.}
 And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).

### 2023-06-08 chapters/ch04-Previous.tex
Update 2023-06-08-23:44:07

@@
 
-\citet{Fan1964}, \citet{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
+\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
 as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
@@
 
- \citet{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+ \citet[229]{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
  \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
@@
 This is not true. 
-\citet{BascianoMelloni2017}, \citet{MelloniBasciano2018},  \citet{Xing2000stat} and  \citet{Xie2020}  all considered both AA and ABAB to be productive,
-and \citet{Xing2000stat} concluded that AAB is productive as well.
+\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec. 3.1]{Xie2020}  all considered both AA and ABAB to be productive,
+and \citet[36]{Xing2000stat} concluded that AAB is productive as well.
 Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.

### 2023-06-08 chapters/ch05-Analysis.tex
Update 2023-06-08-23:44:07

@@
 Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
-Although these forms are generally considered unacceptable \citetext{\citealp[160]{BascianoMelloni2017}, \citealp[275--276]{Hong1999}, \citealp[30]{LiThompson1981}, \citealp[239]{YangWei2017}}, 
+Although these forms are generally considered unacceptable \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}}, 
 \citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
@@
 
-\footnotetext[17]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
-\footnotetext[18]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
-\footnotetext[19]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
-\footnotetext[20]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, vol. 3, 171. Beijing: The Writers Publishing House.}
+\footnotetext[18]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
+\footnotetext[19]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
+\footnotetext[20]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
+\footnotetext[21]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
+\footnotetext[22]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
+
 \begin{sloppypar}
@@
 This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
-The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}, \citealp[143]{Sui2018}, \citealp[239]{YangWei2017}, \citealp[15]{Zhang2000}}, but we argue that it is not an issue of grammaticality.
+The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
 Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.
@@
 Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
-    \citet{Huang1984} and \citet{Her1996, Her2010} argued that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
+    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.
+2]{Her1996}; \citeyear[Sec.
+3.1]{Her2010}) argued that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
     Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.

### 2023-06-22 chapters/ch01-Intro.tex
Update 2023-06-08-23:44:07
added brief bit on mrs, added discussion of the lexical rule of Fan et al.

@@
     in the example sentences will be set in italics.}
-Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.
+Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while''.
 
@@
 In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} was also consulted.
-Other examples from novels and plays written by native speakers were also considered.
+Furtherm, examples from novels and plays written by native speakers were considered.

### 2023-06-22 chapters/ch04-Previous.tex
added brief bit on mrs, added discussion of the lexical rule of Fan et al.

@@
 
-\citet{FanSongBond2015} provided a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
+\citet*{FanSongBond2015} provided a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
 They considered reduplication to be a morphological process and modeled it via lexical rules.
@@
 and further proposed \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
-as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.
+as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.\footnote{%
+  Note that the format in which the lexical rule is given is not the input--output format usually
+  used for lexical rules in HPSG. Instead it is depicted as a unary branching phrase structure
+  rule: the input is the daughter on the right-hand side of the rule. The output is the mother on
+  the left-hand side. The view of lexical rules as unary branching rules is adopted in most current work on
+  lexical rules \citep{BC99a,Meurers2001a} despite the notation that is commonly assumed.  
+}
 For them, the reduplication functions as an intensifier predicate, as represented in the \textsc{predicate (pred)} in the \textsc{constructional-content (c-cont)}.

### 2023-06-22 chapters/ch05-Analysis.tex
added brief bit on mrs, added discussion of the lexical rule of Fan et al.

@@
 In what follows, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
-using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}).%, as proposed in \citet{LuMueller2021}.
+using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
+MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
+represented by statements of domination. This allows for elegant ways to underspecify scope. The
+details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005}. In
+what follows we will present the elementary predications with the features assumed in MRS, but leave
+out handle constraints to keep things simple.
 
-The implicational constraint in  (\ref{avm:redup}) shows the constraints on all structures of type
-\textit{verbal-reduplication-lr} for Mandarin Chinese. 
-Such structures take a verb as \textsc{lexical-daughter (lex-dtr)}.  
-The output reduplicates the \textsc{phonology (phon)} of the input verb with the possibility to have further phonological material in between.
-\etag{} indicates an underspecified list which could be empty or not. 
-A delimitative relation is appended to the \textsc{relations (rels)} value of the input verb, 
-and it takes the event index of the input verb as argument. 
-The label of the output \iboxb{2} is identified with the label of the input and with the label of the delimitative relation, 
-hence \type{delimitative-rel} is treated as a modifier.
- Further relations can be added at the beginning of the \textsc{rels} list to allow for
-the additional perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A. 
-The combination with the perfective will be elaborated on in the following paragraphs.
+Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
+organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
+reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
+structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
+\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
+input verb with the possibility to have further phonological material in between.  \etag{} indicates
+an underspecified list which could be empty or not.  A delimitative relation is appended to the
+\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb as
+argument.  The label of the output \iboxb{2} is identified with the label of the input and with the
+label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
+relations can be added at the beginning of the \textsc{rels} list to allow for the additional
+perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
+perfective will be elaborated on in the following paragraphs.
 
@@
 Furthermore, all the forms are derivable from the lexical rules proposed here, so that there is no need to resort to irregular lexicon entries, and the productivity of these forms is correctly captured.
-In sum, the analysis proposed in this paper possesses greater explanatory power and resolves the problems of previous studies.
+In sum, the analysis proposed in this paper possesses greater explanatory power and resolves the
+problems of previous studies.
+
+%      <!-- Local IspellDict: en_US-w_accents -->

### 2023-06-27 chapters/ch01-Intro.tex
Update 2023-06-27-21:39:49

@@
 We will also discuss in this section, with the help of corpus data, the question of whether the reduplication is a morphological or a syntactic process.
-In \sectref{sec:prev}, I will discuss the advantages and drawbacks of previous approaches. 
+In \sectref{sec:prev}, we will discuss the advantages and drawbacks of previous approaches. 
 \sectref{sec:analysis} will present a new {HPSG} account for verbal reduplication in Mandarin Chinese.
@@
 In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} was also consulted.
-Furtherm, examples from novels and plays written by native speakers were considered.
+Further, examples from novels and plays written by native speakers were considered.

### 2023-06-27 chapters/ch05-Analysis.tex
final analysis
Update 2023-06-27-21:39:49

@@
 
-In what follows, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
+In this section, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
 using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
@@
 details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005}. In
-what follows we will present the elementary predications with the features assumed in MRS, but leave
+what follows, we will present the elementary predications with the features assumed in MRS, but leave
 out handle constraints to keep things simple.
@@
 
-\ea
+\eas
 \type{verbal-reduplication-lr} \impl\\
@@
 \label{avm:redup}
-\z
+\zs
 
@@
 
+\newpage
 \ea\label{avm:AyiA}
@@
 
+\newpage
 \ea\label{avm:vle}
@@
 \citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
-Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin (12th to 20th centuries) (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.
+Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin %(12th to 20th centuries)
+ (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.
 

### 2024-02-07 replies-reviews.tex
Journal version + document for documenting changes

%% -*- coding:utf-8 -*-

%% -*- coding:utf-8 -*-
\documentclass[fleqn,twoside]{article}

\usepackage{fontspec}

\usepackage{hyperref}
\hypersetup{colorlinks=false, pdfborder={0 0 0}}

\usepackage{unified-biblatex}
\let\citew\citealp
\newcommand{\page}{}
\bibliography{bib-abbr,biblio}

\usepackage{langsci-forest-setup}

\usepackage{german}%

\selectlanguage{USenglish}

\usepackage{abbrev,merkmalstruktur,article-ex,makros.2e,mycommands,eng-date,my-xspace}
\usepackage{my-gb4e-article}

\usepackage{soul}

%\usepackage{forest}

\let\citew\cite

\newcommand{\is}[1]{}

\begin{document}
\noindent
{\large\bf Replies to reviews of \emph{An HPSG account for verbal reduplication in Mandarin Chinese}}

Dear editors,

Thank you very much for the positive reviews. The following text is a repetition of the points the
reviewers raised and an explanation of how we addressed open issues.

\section{Reviewer 1}

Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that “This shows
that although the reduplication does have a tendency to interact with volitional verbs and with
activities and semelfactives due to its dynamic meaning, this is by no means a rigid constraint, and
non-volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.”

Regarding volitionality, it should be noted that, as reported in various grammars, while it is generally true that verbs describing events not controlled by an agent cannot be reduplicated, some of them, under certain circumstances (e.g. in imperative or conditional sentences, or in causative rang/jiao/shi sentences, as in ex. (15¢e) provided by the author(s)), can reduplicate (it might be worthwhile to delve into why this occurs in such sentence structures). As for the possibility of reduplicating stative verbs, this is limited to specific verbs and circumstances. It has been observed that some stative verbs, e.g. bing ‘be sick’, are basically change of state predicates, which means that they are dynamic (see e.g. Tham 2013: 663; see also Sybesma 1997, Liu 2010, Peck, Lin \& Sun 2013; Basciano 2019). The same goes for those verbs expressing psychological states which can have a dynamic interpretation, as e.g. liaojié “understand’ (Basciano \& Melloni 2017, fn. 3). With regard to achievements, it is worth considering whether, in certain circumstances (the cases in which they are reduplicated), they assume a reading that cancels the felos. Anyway, since these cases are not the rule, I do not think they can be taken as an argument against the constraints on the action type of the base verb. Otherwise, if reduplication does not affect lexical aspect, how can the changes in the aspect properties of the verb after reduplication be explained? (e.g. \& (1) — AN/ kan (le ) san ge xidoshi ‘read for three hours’ vs. *\& (1) \& =AW kan (le ) kan san ge xicioshi (both reduplication and for X time expressions set a boundary to the event) / IE{ETS zhéngzai kan / *EAEG TG zhéngzai kan kan). In order to get a clearer picture and to find a semantic explanation for these facts, one should look at what these ‘special’ cases of reduplication have in common and try to draw generalizations: why can some stative and achievement verbs reduplicate under certain circumstances, while other cannot? What do these verbs have in common? Can we single out specific subclasses of these verbs which can reduplicate?

The author(s) argue(s) that verbal reduplication is a morphological phenomenon based on some tests (Sect. 2.4). However, the tests used have some shortcomings.

1) Compositionality: this test is not reliable. There are phrases whose meaning is not

compositional (see e.g. kick the bucket, shoot the breeze). Also, take verb-object constructions,
which are ambiguous between words and phrases: e.g. 1:0> dan-xin ‘take on-heart, worry” has a
non-compositional meaning, suggesting that it is a word, but is separable, suggesting that it is a
phrase (see Huang 1984). On p. 14, the author(s) state(s): “The meaning of the reduplication is not
compositional, as it does not mean that the event denoted by the verb happens twice or multiple
times, but rather that the event happens for a short duration and/or for low frequency. This non-
compositionality suggests that a reduplication is more word-like.”

If it were compositional, perhaps the meaning should be something like ‘look look” (do the action twice?) but not multiple times. However, I think it is a matter of iconicity rather than compositionality here. In addition, would this imply that the reduplicated verb is a compound? Its meaning and function, though, seem to be closer to inflection or derivation. If it is a derivational item, i.e. a suffix-like element, it can bear a fix aspectual meaning (delimitative aspect): in this sense, the meaning would be compositional.

2) Lexical integrity: if the reduplicated verb is a word, the position of the perfective aspect
marker le is unexpected. In fact, it is never found in between the two constituents of a compound
word, as the author(s) also show(s) in (27c). Her (2006: 1282), talking about V-4 géi sequences,
states that “The simple fact that the V-gei sequence cannot be separated, as in (19¢) indicates its
lexical integrity”, i.e. they form a single lexical item (745 T fih ji-géi-le ta vs. * 77 T 431 Ji-le géi ta).

Even if you assume that aspect markers are suffixes (morphological elements), they should not be placed in between the constituents of compounds, because this violates lexical integrity (as shown in ex. 27b by the author(s)): the suffix /e must be placed after the whole complex verb, which forms a single lexical unit, and not within it. In fact, in (non-separable) verb-object compounds, which are lexical units, | /e is never placed after the verbal constituent (F0» T guan-xin-le | *% T > guan-le xin vs. % | % gi-le md).

It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker /e can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern. Also, I do not understand the comparison with SVCs. Let’s say that reduplication is a syntactic phenomenon, but that does not mean that it is a SVC, i.e. a sequence of verbs or verb phrases in a relation of coordination or subordination, which are basically independent of each other. It could simply be another type of syntactic construction with its specific properties.

3) Phrasal substitution. The inclusion of this test is questionable since reduplication primarily targets verbs and not phrases. Therefore, syntactic objects should not be included in the reduplication; it is not repetition of phrases. Indeed, if the object is part of a non-separable verb-object compound (which is a lexical unit), it is included in the reduplication (F</0> 0> guan-xin guan-xin/*  K> guan-guan xin vs. WsBkE tico-tiao wii | * B FEBEE ticown tiaowii).

4) Conjunction reduction. This criterion can only be applied to set apart coordinated phrases from coordinate compound words with a head in common (e.g. ‘K huiché e ¥4 giché in (33) share the head  ché ‘vehicle’). But the examples provided by the author(s) to argue against conjunction reduction with reduplicated verbs are completely different: the verbs do not have the head in common (exx. 34). I believe that this is not a reasonable test to argue for the wordhood of reduplicated verbs.

In summary, the tests used to support the morphological status of reduplication appear
unconvincing. Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
author(s) say(s): “The following section discusses previous literature which proposed a special
construction for the reduplication”. However, it becomes evident that the phenomenon under
examination is entirely different from Mandarin verbal reduplication. Ghomeshi et al. (2004) analyze
a phenomenon which is well attested in world languages, even in those without productive
reduplication, i.e. contrastive focus reduplication/repetition, which involves the repetitions of
words and sometimes phrases (Oh, we re not LIVING-TOGETHER-living-together, Gomeshi et al. 2004: 308). Their function is “to focus the denotation of the reduplicated element on a more sharply delimited, more specialized, range” (Gomeshi etal. 2004: 308); for example, in ex. (47) cited by the author(s) SALAD-salad means green salad vs. salads in general. This has nothing to do with diminishing verbal reduplication in Mandarin. The authors’ endeavor to apply the analysis proposed for contrastive focus reduplication to Mandarin verbal reduplication raises questions about its rationale (why? These two phenomena are fundamentally distinct and serve different linguistic functions). Consequently, attempting to employ the same analytical framework for both is problematic, and, indeed, the author(s) conclude(s) that: “this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese”. This is precisely because contrastive focus repetition/reduplication is a different phenomenon with a different function, and Mandarin verbal reduplication cannot be analyzed in the same way. Furthermore, the author(s) suggest(s) that this approach “[...] also provides a formal account for the phonology of the reduplication”. However, contrastive focus reduplication/repetition generally does not involve morpho-phonological readjustment phenomena, which are typically found in reduplication. As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).

Pp. 26, lines 24-25: “The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. [] indicates an underspecified list which could be empty or not”. However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level. How can one determine which verbs are exempt from the proposed lexical rule? The proposed rule does not seem to provide a clear prediction of which verbs are allowed and which are excluded from reduplication. Why only some states and achievements are allowed? The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.

The proposed analysis appears to have a descriptive rather than an explanatory power.

I would add tones to the pinyin transcription.

Other comments:

p. 4: ex. (8b) is interesting, since it appears to involve the reduplication of V1 of a resultative compound. To the best of my knowledge, exiting literature on the subject consistently maintains that resultative compounds are not amenable to reduplication.

p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.

p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).

p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
element in the reduplication is the actual verb, which resides under init and proc, and that the
second element is an aspect marker, which resides in the complement position of proc, as it delimits
the process of the event”. Based on my understanding, these authors do not claim that the second
element serves as an aspect marker. They propose that the verb and the reduplicant are the spell-out
of two copies of the same lexical item within the vP domain: the reduplicant is the lower copy, in
complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.

p. 32, lines 28-34: “Although these forms are generally considered unacceptable (Li \& Thompson 1981: 30; Hong 1999: 275-276; Basciano \& Melloni 2017: 160; Yang \& Wei 2017: 239), Fan (1964: 269) and Sui (2018: 143) considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.” Given that these patterns were possible in previous stages of the language (see a.0. Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.

\section{Reviewer 2}

This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
Despite these strengths, certain questions warrant attention. The primary concern revolves around
treating verb reduplication as morphological. The authors compare it with Parallel Verb Compound
(PVC) and Serial Verb Construction (SVC), asserting that verb reduplication aligns more closely with
SVC than PVC in tests like phrase extension, substitution, and conjunction reduction. However, the
choice of SVC over regular verb phrases as a point of comparison with PVC and verb reduplication
lacks clarity. While SVC passes these tests, it is crucial to note that regular verb phrases may not pass
some, e.g., separate modification of subparts within a constituent.
In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.
For additional comments, please refer to the attached PDF file.

R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-kan, A-kan-kan,
AAB, A-yi-AB, A-le-AB will also be mentioned.

One of the key questions addressed in this paper pertains to whether verb reduplication is best understood as a morphological or a syntactic phenomenon. However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication (Xie, 2020).

To further enrich the ongoing debate, I wonder whether the authors will consider the inclusion of examples that previous studies have identified as morphological verb reduplications. This addition would help demonstrate the broader scope and applicability of your analysis. Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.

R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
not mean that the event denoted by the verb happens twice or multiple times, but
rather that the event happens for a short duration and/or for low frequency. This
non-compositionality suggests that a reduplication is more word-like.

Example (26) was employed to demonstrate that verb reduplication can be modified by an adverb as a whole but cannot have a part of it modified. The authors utilize this observation to bolster the argument that verb reduplication is a morphological, not a syntactic phenomenon.

However, the issue at hand is that even a standard verb phrase cannot be modified in this manner. Consider the following examples, in which the phrase 'dakai men' is a phrase rather than a word.

(1) ta qingsheng de dakai men. 
       he  quietly    DE open door 
      'He opened the door quietly.'

(2) * ta dakai qingsheng de men. 
         he open quietly       DE door
         'He opened the door quietly.'

The key consideration here is that the unacceptability of (26b) and examples such as (2) may not hinge solely on whether part of it can be modified. Instead, it could be associated with the post-verbal placement of the adverb.

Consequently, it becomes challenging to use these examples as support for the argument that verb reduplication should be classified as a morphological rather than a syntactic phenomenon. This is because even regular verb phrases cannot be partially modified in the same manner.

Answer: Yes, this is true.

Examples (27) and (28) serve as illustrations to demonstrate the application of the 'Lexical Integrity Hypothesis' in distinguishing PVC from SVC.

In reference to (25), it is explained that the Lexical Integrity Hypothesis posits that 'No
phrase-level rule may affect a proper subpart of a word.' However, it is noteworthy that the authors
employ le-insertion in (27) and (28), indicating that le- cannot be inserted into PVC but can be
inserted into SVC. This might suggest that the use of le-insertion in these examples could be
construed as a form of phrase-level operation, potentially conflicting with the author's perspective
of regarding 'le' as a morphological process.

Regarding example (34), the conjunctive structures do not exhibit conjunction reduction, a phenomenon that typically requires a degree of overlap between two elements, as shown in (32). Example (34) presents a scenario where there is no overlap between the verb structures.

Moreover, in Mandarin, conjunctions can only be employed with nouns and not with verbs phrases or
clauses (Schafer, 2009). If this holds true, it is less likely to observe conjunction reduction for
verb phrases. Consequently, it would be inappropriate to assert that verb reduplication is more
word-like and less phrase-like, as even regular verb phrases may encounter problems undergoing
conjunction reduction.

In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).

However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase. This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like 'Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)). Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate. This is because even a regular verb phrase faces limitations.

In light of this, it becomes essential to clarify why SVC, rather than regular verb phrases, was
chosen as a comparison to Parallel Verb Compounds. Such clarification would enhance the
persuasiveness of the tests presented in this section.

The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
presence of the number 'san' in (43b). If 'san xia' is replaced with 'yi xia,' which remains a
verbal classifier, the idiomatic meaning is perserved. In this case, there appears to be no
distinction between verbal classifier and reduplication.

It would enhance reader comprehension if the authors could provide a brief illustration of symbols
like HOOK, LTOP, IND, ARG, etc. This will aid readers in better grasping the authors' subsequent
proposals in Section 4.

Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).

PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
another constraint. A constraint that is a subtype in the hierarchy. The type
perfective-reduplication-lr in (51), which says that the PHON value of the daughter \ibox{1} appears
twice in the PHON value of the mother with some other material (\etag) between the two occurrences of \ibox{1}.

\section{Reviewer 3}

The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
conjunction reduction.

In Page 14, the draft makes use of a new terminology such as “word-like”. Of course, I can understand the meaning within the context. However, I think the author(s) might be better to use a more academic and formal terminology.

Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.
In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs. Is it what the author(s) invent only for modeling the verbal reduplication in this drat? If so, the author(s) want to account more for how it works in AVMs. Otherwise, the author(s) might be better to refer to the previous analysis about the notion.

In Section 4, I am expecting the author(s) provide a sample derivation (maybe a tree diagram). The draft provides the subsets about how verbal reduplication can be constrained within the AVMs. On top of them, a full derivation can be made for better understanding.

{\sloppy
\printbibliography[heading=subbibliography,notkeyword=this] 
}
\end{document}

%      <!-- Local IspellDict: en_US-w_accents -->

### 2024-02-07 chapters/ch01-Intro.tex
Journal version + document for documenting changes

@@
 It contributes more empirical evidence and 
-offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, Mueller2013}) to this phenomenon 
+offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, HPSGHandbook}) to this phenomenon 
 using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}) as the semantic representation formalism.

### 2024-02-07 main.tex
Update 2023-06-03-19:08:01
Update 2023-06-27-21:39:49
Journal version + document for documenting changes

@@
 
-\leftrunning{Yanru Lu \& Stefan Müller}  % Short author list
+%\leftrunning{Yanru Lu \& Stefan Müller}  % Short author list
 
@@
 
-\author[1]{\givenname{Yanru} \surname{Lu}}
+% \author[1]{\givenname{Yanru} \surname{Lu}}
+% \address[1]
+% {%
+%   \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
+%   \addr{Unter den Linden 6}, % Street 
+%   \addr{D-10099 Berlin}, % Postcode etc
+%   \cnty{Germany}  % Country
+%   \email{yanru.lu@hu-berlin.de} % email
+% }
 
-\address[1]
-{%
-  \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
-  \addr{Unter den Linden 6}, % Street 
-  \addr{D-10099 Berlin}, % Postcode etc
-  \cnty{Germany}  % Country
-  \email{yanru.lu@hu-berlin.de} % email
-}
-
-\author[2]{\givenname{Stefan} \surname{Müller}}
-
-\address[2]
-{%
-  \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
-  \addr{Unter den Linden 6}, % Street 
-  \addr{D-10099 Berlin}, % Postcode etc
-  \cnty{Germany}  % Country
-  \email{st.mueller@hu-berlin.de} % email
-}
+% \author[2]{\givenname{Stefan} \surname{Müller}}
+% \address[2]
+% {%
+%   \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
+%   \addr{Unter den Linden 6}, % Street 
+%   \addr{D-10099 Berlin}, % Postcode etc
+%   \cnty{Germany}  % Country
+%   \email{st.mueller@hu-berlin.de} % email
+% }
 
@@
 This analysis covers all forms of verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
-\keywords{HPSG, MRS, Mandarin Chinese, verbal reduplication}
+\keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}
 \end{abstract}

### 2024-04-04 replies-reviews.tex
Update 2024-04-04-21:31:49

@@
 \newcommand{\page}{}
-\bibliography{bib-abbr,biblio}
+\bibliography{Bib,bib-abbr,biblio}
 
@@
 
+%%%%% YL
 Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that “This shows
@@
 in imperative or conditional sentences, or in causative rang/jiao/shi sentences, as in ex.
-(15¢e) provided by the author(s)), can reduplicate (it might be worthwhile to delve into why this occurs in such sentence structures).
+(15e) provided by the author(s)), can reduplicate (it might be worthwhile to delve into why this occurs in such sentence structures).
 As for the possibility of reduplicating stative verbs, this is limited to specific verbs and circumstances.
@@
 Can we single out specific subclasses of these verbs which can reduplicate?
+%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
+Answer:
+First, the notion of ``aspect'' adopted in this article has to be explained in more detail.
+We adopt the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
+The general term ``aspect'' is considered to encompass the following two components:
+situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
+and viewpoint aspect, i.e. ``the aspectual information reflected bz the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
+Situation aspect can be further modeled as verb classes (dubbed ``Aktionsart'' in the previous version of this paper) at the lexical level
+and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
+The verb classes are determined with verbs in a neutral context, 
+where everything that might change the aspectual value of a verb is excluded
+and only the inherent features of the verb itself are considered
+(see \citealt[52]{XiaoMcEnery} for the detailed operationalization for Mandarin Chinese).
+This section is concerned with the interaction of the reduplication with verb classes,
+while the next section discusses the interaction with viewpoint aspect markers.
+The combination with other constituents such as adjuncts is briefly touched upon below,
+but a detailed discussion has to be left for future research.
 
+Second, there are more examples.
+Regarding volitionality, although (15e) is a causative sentence, (13a--b) are not imperative, conditional or causative (more on this below).
+Example () shows the same verb sheng1 `give birth to' as in (15e) reduplicated in a declarative sentence.
+我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
+
+As for stative verbs, \citet[Sec. 3.3]{Tham2013} uses xi3huan1 `like' and xiang1xin4 `believe' as examples of stative verbs
+to contrast adjectives
+and what she calls basic change of state verbs such as bing4 `sick'.
+\citet[680]{PeckEtAl2013} also list xi3huan1 `like' and xiang1xin4 `believe' as stative verbs.
+For these two verbs, examples such as () and () can be found.
+这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
+谁让我来相信相信 (CCL)
+However, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
+and indeed \citet[669--670]{Tham2013} herself noted,
+verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
+let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
+and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery} of individual-level states (ILSs) which only have stative interpretation,
+as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.
+The following examples contain the reduplication of xiang4 `look like' and zai4-chang3 `be present on the scene'.
+范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
+她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
+
+With regard to achievements, the reduplication does not seem to cancel the telos.
+Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (b) but not with ``for X-time'' (c).
+()a 一块... 到附近市场买买东西 (CCL)
+b 两天后到附近市场买买东西
+c *到附近市场买买东西两天
+The following continuation that cancels the telo is also infelicitous ().
+() 到附近市场买买东西 # 但什么也没买到
+
+All the examples above show that reduplication is applicable to all verb classes, contrary to common beliefs in the literature,
+and thus, a theoretical account of reduplication should not restrict its use to only a subset of verbs.
+With our account, we aim to explain as much language data as possible, regardless whether the reviewer considers some examples to be ``special'' or not.
+
+As we discussed in Sec. 2.3.1 in the previous version of the paper, the semantics of the reduplication has the properties of tansitoriness, holisticity and dynamicity.
+One might argue that examples such as () and () above convey dynamic meaning, even though stative verbs are used,
+i.e. they may be interpreted as `become similar to' and `become present' respectively.
+However, we argue that the dynamic interpretation does not come from the verb but from reduplication.
+These verbs are stative in a neutral context can can thus be classified as stative verbs.
+The point of our argument is that reduplication can be applied to verbs of all verb classes.
+The dynamicity also explains the general tendency for reduplication to appear in imperative contexts.
+
+Finally, as noted briefly in Sec. 2.2 in the previous version of the paper,
+the reduplication is incompatible with an expression that quantifies the duration or the extent of the event,
+ because the reduplication already contains a (abstract) quantity meaning, namely a short duration or a small extent.
+ This results from the properties of reduplication and does not change the verb class of the predicate.
+%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
+%%%%% YL
 The author(s) argue(s) that verbal reduplication is a morphological phenomenon based on some tests (Sect. 2.4). However, the tests used have some shortcomings.

### 2024-04-09 replies-reviews.tex
Update 2024-04-09-17:03:08

@@
 \usepackage{unified-biblatex}
+
 \let\citew\citealp
@@
 situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
-and viewpoint aspect, i.e. ``the aspectual information reflected bz the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
+and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
 Situation aspect can be further modeled as verb classes (dubbed ``Aktionsart'' in the previous version of this paper) at the lexical level
 and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
-The verb classes are determined with verbs in a neutral context, 
+The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory), 
 where everything that might change the aspectual value of a verb is excluded
 and only the inherent features of the verb itself are considered
-(see \citealt[52]{XiaoMcEnery} for the detailed operationalization for Mandarin Chinese).
+(see \citealt[52]{XiaoMcEnery} for more details).
+This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
+but its verb class remains the same,
+as the aspectual change can be attributable to other components at the sentential level.
 This section is concerned with the interaction of the reduplication with verb classes,
@@
 and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery} of individual-level states (ILSs) which only have stative interpretation,
-as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.
+as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
+Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery} are adjectives.
+Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. xxxxxxxxCitationsxxxxxx),
+and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013}, 
+these predicates are not included in our examples.}
 The following examples contain the reduplication of xiang4 `look like' and zai4-chang3 `be present on the scene'.
@@
 
-As we discussed in Sec. 2.3.1 in the previous version of the paper, the semantics of the reduplication has the properties of tansitoriness, holisticity and dynamicity.
-One might argue that examples such as () and () above convey dynamic meaning, even though stative verbs are used,
-i.e. they may be interpreted as `become similar to' and `become present' respectively.
+Finally, as we discussed in Sec. 2.3.1 in the previous version of the paper, the semantics of the reduplication has the properties of tansitoriness, holisticity and dynamicity.
+This means that the use of reduplication affects the situation aspect at the sentential level.
+One might argue that examples such as () and () above convey dynamic meaning, even though stative verbs are used.
+%i.e. they may be interpreted as `become similar to' and `become present' respectively.
 However, we argue that the dynamic interpretation does not come from the verb but from reduplication.
-These verbs are stative in a neutral context can can thus be classified as stative verbs.
-The point of our argument is that reduplication can be applied to verbs of all verb classes.
-The dynamicity also explains the general tendency for reduplication to appear in imperative contexts.
+These verbs are stative in a neutral context and can thus be classified as stative verbs.
+The dynamic interpretation only arises when they are reduplicated.
+The point of our examples is to show that reduplication can be applied to verbs of all verb classes.
 
-Finally, as noted briefly in Sec. 2.2 in the previous version of the paper,
+As noted briefly in Sec. 2.2 in the previous version of the paper,
 the reduplication is incompatible with an expression that quantifies the duration or the extent of the event,
- because the reduplication already contains a (abstract) quantity meaning, namely a short duration or a small extent.
+ because the reduplication already contains a (abstract) quantity meaning, namely a short duration or a small extent (transitoriness),
+ which cannot be measured on a concrete scale \citep[155]{XiaoMcEnery2004}.
  This results from the properties of reduplication and does not change the verb class of the predicate.
+
+Due to its unique features compared to the perfective aspect marker \textit{le} and the experiential aspect marker \textit{guo},
+the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery}.
+\textit{Le} expresses a situation being realized, 
+while \textit{guo} conveys a situation already experienced,
+and thus, both rarely occur in future situations.
+The use of reduplication does not have these constraints.
+This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts.
+
 %%%%%%%%%%%%%%%%%%%

### 2024-04-14 replies-reviews.tex
Update 2024-04-09-17:19:41
Update 2024-04-09-17:30:09
Update 2024-04-14-14:40:17

@@
 Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery} are adjectives.
-Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. xxxxxxxxCitationsxxxxxx),
+Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
 and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013}, 
@@
 However, we argue that the dynamic interpretation does not come from the verb but from reduplication.
-These verbs are stative in a neutral context and can thus be classified as stative verbs.
-The dynamic interpretation only arises when they are reduplicated.
+These verbs are stative in a neutral context and thus, we consider the intrinsic feature of these verbs to be stative.
+The dynamic interpretation only arises when they are used in specific contexts, in this case, when they are reduplicated.
 The point of our examples is to show that reduplication can be applied to verbs of all verb classes.
@@
  which cannot be measured on a concrete scale \citep[155]{XiaoMcEnery2004}.
+ The same can be argued for the incompatibility of reduplication and a quantified object () , as both serve to delimit the event expressed by the base verb \citep[]{}.
+ ()
  This results from the properties of reduplication and does not change the verb class of the predicate.
@@
 The use of reduplication does not have these constraints.
-This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts.
+This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts,
+which are frequently used to describe future situations.
 

### 2024-05-09 replies-reviews.tex
Update 2024-05-09-23:53:44

@@
 In summary, the tests used to support the morphological status of reduplication appear
-unconvincing. Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
+unconvincing. 
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+Answer:
+Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
+The tests of semantic compositionality and conjunction reduction are deemed unreliable.
+\citet[37--38]{Dai1992}, \citeyear[120--122]{Dai1998} explains the problems of conjunction reduction (he calls it ``coordination'').
+That leaves us with phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998}) 
+and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
+These tests have to be defined more clearly.
+
+First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
+This is possible for a VP (), as the NP inside of the VP can be modified by e.g. an AP.
+() 开红色的门
+In contrast, the individual verbs in reduplication cannot be modified by an e.g. AdvP.
+() is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
+()* 看偷偷地看
+
+Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
+This is possible for a verbal classifier phrase (), as the object can occur after or in-between.
+() 开两次门
+() 开门两次
+For reduplication, this is also not possible (), as the object cannot be inserted between the two verbs.
+() *开(了)门(了)开
+% If we analyze reduplication as a phrasal operation, we would expect the structure of
+% [VP [VP [V-le V]] O]
+% Since both phrases are VP, there should be nothing against the following strucutre:
+% [VP [VP [V-le O]] V]
+% However, this is not possible.
+
+Regarding the position of \textit{le}, there are counter-examples that show V-le-gei () as well as \textit{guan-le-xin} `close-\textsc{pfv}-heart, care for' () are possible.
+() 还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
+() 许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
+In any case, as reduplication is not compounding (\citealt[149--150]{Sui2008}; \citealt{GaoEtAl2021} provides empirical evidence.) 
+and the patterns discussed here constitute a different process as the AABB pattern,
+it is not surprising that \textit{le} occurs at a different position.
+
+The comparison with Parallel Verb Compounds and Serial Verb Constructions only serves to facilitate understanding
+but does not contribute to the arguments in any substantial way.
+Due to the critics from the reviewers, this comparison is removed.
+
+Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as reduplication) in other languages 
+than syntactic reduplication (below as repetition \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
+\citet[35--36]{Gil2005} considers non-iconicity and having only two copies as sufficient but not necessary conditions for reduplication.
+He further proposes building one intonational group as sufficient and necessary condition for reduplication (p. 36).
+All three conditions are true for verbal reduplication in Mandarin Chinese.
+\citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.
+This is also true for verbal reduplication in Mandarin Chinese.
+
+In sum, we maintain that verbal reduplication in Mandarin Chinese is better off analyzed as a morphological phenomenon.
+
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%
+%%%%YL
+Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
 author(s) say(s): “The following section discusses previous literature which proposed a special
@@
 As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).
+%%%%%%%%%%%%%%%%%%
+Answer:
+Since the reviewer deemed it irrelevant, the section concerning \citet{GomeshiEtAl2004} is removed.
 
+%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 Pp.

### 2024-05-09 replies-reviews.tex
Update 2024-05-10-00:02:31

@@
 () 许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
-In any case, as reduplication is not compounding (\citealt[149--150]{Sui2008}; \citealt{GaoEtAl2021} provides empirical evidence.) 
+In any case, as reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.) 
 and the patterns discussed here constitute a different process as the AABB pattern,
@@
 All three conditions are true for verbal reduplication in Mandarin Chinese.
+% one intonational group \citep[154]{Sui2018}
 \citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.

### 2024-05-12 replies-reviews.tex
Update 2024-05-12-22:51:24

@@
  because the reduplication already contains a (abstract) quantity meaning, namely a short duration or a small extent (transitoriness),
- which cannot be measured on a concrete scale \citep[155]{XiaoMcEnery2004}.
- The same can be argued for the incompatibility of reduplication and a quantified object () , as both serve to delimit the event expressed by the base verb \citep[]{}.
- ()
+ which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}, \citealt[333]{SuiHu2016}).
+% The same can be argued for the incompatibility of reduplication and a quantized object () , as both serve to delimit the event expressed by the base verb \citep[322]{SuiHu2016}.
+ %() *我看看三本书。
  This results from the properties of reduplication and does not change the verb class of the predicate.
@@
 and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
-These tests have to be defined more clearly.
+These tests requires further clarifications.
 
@@
 () 许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
-In any case, as reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.) 
-and the patterns discussed here constitute a different process as the AABB pattern,
+In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.), 
+and the patterns discussed here constitute a different process than the AABB pattern 
+(see the discussion on \citealt{Xie2020} in our paper, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
 it is not surprising that \textit{le} occurs at a different position.

### 2024-07-02 replies-reviews.tex
Update 2024-06-24-11:35:02
Update 2024-07-02-20:34:28

@@
 The comparison with Parallel Verb Compounds and Serial Verb Constructions only serves to facilitate understanding
-but does not contribute to the arguments in any substantial way.
+by contrasting the behaviors of different multi-verb constructions in Mandarin Chinese,
+but this does not contribute to the arguments in any substantial way.
 Due to the critics from the reviewers, this comparison is removed.
@@
 %%%%%%%%%%%%%%%%%%%%%%
+%% YL
 Pp.
@@
 This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
-
+%%%%%%%%%%%%%%%%%%%%
+Answer:
+historically not arbitrary but synchronically opac, similar to linking elements in compounds which are also arbitrary to a certain extent and can be only for phonological reasons.
+In Chinese, one form of intensifying reduplication is A-li-AB e.g. 糊里糊涂, where the li is fixed and also somewhat arbitrary. 
+\citet[137]{Sui2018} assumes that this syllable is filled with li because the open syllable li is a relatively unmarked phonological constituent \citep{Yip1992}
+and the second syllable in A-li-AB occupies an unstressed position. 
+We can see the similarities between li in A-li-AB and yi in A-yi-A: they are both relatively unmarked and occupies an unstressed position.
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+%% YL
 The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level.
@@
 The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
+%%%%%%%%%%%%%%%%%%%%%
+Answer:
+As explained above, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
+The incompatibility with the progressive aspect marker is explained in the Semantics section.
+%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+%% Stefan
 The proposed analysis appears to have a descriptive rather than an explanatory power.
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+%% YL
 I would add tones to the pinyin transcription.
-
+%%%%
+Answer: will add
+%%%%%
 Other comments:
@@
 To the best of my knowledge, exiting literature on the subject consistently maintains that resultative compounds are not amenable to reduplication.
+%%%%%%%%
+Answer: add footnote
+%%%%%%%%
+p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
+%%%%
+Answer: See above.
+%%%%
+p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
+%%%%%%%%%%%%%5
+Answer: 
+There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \textit{yixia}:
+她看了他的脸一下。(CCL)
+他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
+We think it has to do with the weight/length of the object, i.e. shorter objects can be placed before \textit{yixia} while longer ones cannot.
+%This is not necessarily a syntactic constraint.
 
-p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
-
-p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
-
+Even if we accept that the object can be only be placed before \textit{yixia} in limited cases, 
+the fact that the object can be placed before \textit{yixia} in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+%%%%%%%%%%%%%%
 p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
@@
 complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.
-
+%%%%%%%%%%%%%
+Answer: We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
+%%%%%%%%%%%%%
 p.
@@
 Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.
+%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%
+%% YL
 R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
@@
 Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.
-
+%%%%%%%%%%%%%%%%
+Answer: % need to think about this more
+Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
+we do agree that they are different grammatical processes and thus requires separate analyses.
+Also note that there are numerous scholars that do consider the forms above as morphological processes (cite xxxxxxxxxxxx).
+\citet[83--84]{Xie2020} also suggests that AABB is much less productive than ABAB.
+This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
+This is probably the case for those AABBs that have an idiomatic meaning, such as \textit{zhi-zhi-dian-dian} `point-point-gesture-gesture, gossip'.
+Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
+i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
+This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
+and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
+The current analysis has a broad scope in that it explains all forms of productively formed verbal reduplication, which previous analyses were not able to do.
+%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%
+%% YL
 R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
@@
 
-Answer: Yes, this is true.
+%Answer: Yes, this is true.
 
@@
 persuasiveness of the tests presented in this section. 
+%%%%%%%%%%%%%%%%%%%
+Answer: See above.
+%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
+%% YL
 The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
@@
 distinction between verbal classifier and reduplication. 
+%%%%%%%%%%%%%%%%%%%%
+Answer:
+It is not \textit{san xia} `three times' that is special, but it is \textit{yi xia} `once' that is special.
+We can replace \textit{san} `three' with any number above two,
+and the distinction still exist.
+But \textit{yi xia} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \textit{xia}, which only have the `for X times' interpretation \citep[77]{Deng2013}.
+We think \textit{liang xia} `twice' is following this tendency, too.
+In this case, \textit{yi xia} and \textit{liang xia} cannot be seen as verbal classifier phrases anymore, but as duration adverbials as a whole.
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+%% Stefan
 It would enhance reader comprehension if the authors could provide a brief illustration of symbols
@@
 
-PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
+Answer: PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
 another constraint. A constraint that is a subtype in the hierarchy. The type
@@
 twice in the PHON value of the mother with some other material (\etag) between the two occurrences of \ibox{1}. 
+%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%
+%% YL
 The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
@@
 However, I think the author(s) might be better to use a more academic and formal terminology.
-
+%%%%%%%%%%%%%%%%%%%%%%
+Answer: reformulate as ``behaves more similar to a word''.
+%%%%%%%%%%%%%%%%%%%%%%
 Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.
+%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
+%% YL
+Answer: Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Stefan
 In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs.
@@
 On top of them, a full derivation can be made for better understanding.
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
 

### 2024-07-03 replies-reviews.tex
Update 2024-07-03-14:16:59

@@
 
-\usepackage{fontspec}
+\usepackage[
+style = langsci-unified,
+backend = biber,
+natbib = true,
+]{biblatex}
+\addbibresource{Bib.bib}
 
-\usepackage{hyperref}
-\hypersetup{colorlinks=false, pdfborder={0 0 0}}
+\usepackage{xcolor}
+\definecolor{lsDOIGray}{cmyk}{0,0,0,0.45}
 
-\usepackage{unified-biblatex}
+\input{localpackages}
+\input{localcommands}
+%\usepackage{fontspec}
 
-\let\citew\citealp
-\newcommand{\page}{}
-\bibliography{Bib,bib-abbr,biblio}
+%\usepackage{hyperref}
+%\hypersetup{colorlinks=false, pdfborder={0 0 0}}
 
-\usepackage{langsci-forest-setup}
+%\usepackage{unified-biblatex}
 
-\usepackage{german}%
+%\let\citew\citealp
+%\newcommand{\page}{}
+%\bibliography{Bib,bib-abbr,biblio}
 
-\selectlanguage{USenglish}
+%\usepackage{langsci-forest-setup}
 
-\usepackage{abbrev,merkmalstruktur,article-ex,makros.2e,mycommands,eng-date,my-xspace}
-\usepackage{my-gb4e-article}
+%\usepackage{german}%
 
-\usepackage{soul}
+%\selectlanguage{USenglish}
+
+%\usepackage{abbrev,merkmalstruktur,article-ex,makros.2e,mycommands,eng-date,my-xspace}
+%\usepackage{my-gb4e-article}
+
+%\usepackage{soul}
 
@@
 and only the inherent features of the verb itself are considered
-(see \citealt[52]{XiaoMcEnery} for more details).
+(see \citealt[52]{XiaoMcEnery2004} for more details).
 This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
@@
 let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
-and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery} of individual-level states (ILSs) which only have stative interpretation,
+and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
 as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
-Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery} are adjectives.
+Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
 Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
@@
 The following continuation that cancels the telo is also infelicitous ().
-() 到附近市场买买东西 # 但什么也没买到
+() 到附近市场买买东西 \# 但什么也没买到
 
@@
 Due to its unique features compared to the perfective aspect marker \textit{le} and the experiential aspect marker \textit{guo},
-the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery}.
+the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
 \textit{Le} expresses a situation being realized, 
@@
 Answer:
-Since the reviewer deemed it irrelevant, the section concerning \citet{GomeshiEtAl2004} is removed.
+Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.
 
@@
 %%%%%%%%%%%%%%%%
-Answer: % need to think about this more
+Answer: 
+\citet{Xie2020} identifies the AABB form as morphological verb reduplication.
 Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
-we do agree that they are different grammatical processes and thus requires separate analyses.
-Also note that there are numerous scholars that do consider the forms above as morphological processes (cite xxxxxxxxxxxx).
-\citet[83--84]{Xie2020} also suggests that AABB is much less productive than ABAB.
+we do agree that they are different grammatical processes and thus requires separate analyses \citep[See also][]{Deng2013, Wang2023}.
+Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch.
+4]{Chao1968}, \citealt[Ch.
+3]{LiThompson1981}, \citealt[4--5]{Liao2014} and \citealt[Sec.
+4]{Sui2018}).
+\citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
 This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
 This is probably the case for those AABBs that have an idiomatic meaning, such as \textit{zhi-zhi-dian-dian} `point-point-gesture-gesture, gossip'.
-Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
-i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
-This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
-and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
-The current analysis has a broad scope in that it explains all forms of productively formed verbal reduplication, which previous analyses were not able to do.
+%Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
+%i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
+%This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
+%and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
+The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
 %%%%%%%%%%%%%%%%%

### 2024-07-04 replies-reviews.tex
Update 2024-07-04-17:39:18

@@
 Can we single out specific subclasses of these verbs which can reduplicate?
+
 %%%%%%%%%%%%%%%%%%%
@@
 unconvincing.
+
 %%%%%%%%%%%%%%%%%%%%
@@
 This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
+
 %%%%%%%%%%%%%%%%%%%%
 Answer:
-historically not arbitrary but synchronically opac, similar to linking elements in compounds which are also arbitrary to a certain extent and can be only for phonological reasons.
-In Chinese, one form of intensifying reduplication is A-li-AB e.g. 糊里糊涂, where the li is fixed and also somewhat arbitrary. 
-\citet[137]{Sui2018} assumes that this syllable is filled with li because the open syllable li is a relatively unmarked phonological constituent \citep{Yip1992}
-and the second syllable in A-li-AB occupies an unstressed position. 
-We can see the similarities between li in A-li-AB and yi in A-yi-A: they are both relatively unmarked and occupies an unstressed position.
+\obj{le} `\textsc{pfv}' marks the perfective aspect.
+The reason for \obj{le} `\textsc{pfv} being the only aspect marker compatible with reduplication is explained in the Semantics Section.
+
+As for \obj{yi} `one', its use stems from the historical development of delimitative verbal reduplication but is synchronically opac.
+\citet[13--15]{Zhang2000} shows that delimitative verbal reduplication originates from the ``V + numeral + verbal classifier'' phrase,
+where the verbal classifier is borrowed from a verb of the same form, as shown in (\ref{ex:hist1}).
+\ea\label{ex:hist1} 
+明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
+%\gll \obj{ming2} \obj{}
+\z
+Here the numeral refers to the actual number of the action taking place 
+and can be any number.
+This evolves into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
+but simply conveys that the action happens in a short period of time or for only few times (\ref{ex:hist2}).
+\ea\label{ex:hist2}
+且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
+\z
+In this case, \obj{yi1} `one' cannot be replaced by other numerals.
+Since V-\obj{yi}-V does not express the actual number of the action anymore, 
+it became possible to delete the \obj{yi1} `one',
+hence the use of the VV (or AA) form, too.
+
+Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
+This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure 
+and is only there as a historical remnant.
+In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds
+
+Besides the obvious conceptual reason that  \obj{yi1} `one' means `little, few', 
+there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
+In Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused', 
+where the \obj{li} is fixed and also does not bear any meaning. 
+\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
+and the second syllable in A-\obj{li}-AB occupies an unstressed position. 
+We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
+This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
+But a phonological account is out of the scope of this paper and has to be left for further research.
+
+The subtypes of \type{verbal-reduplication-lr} prevent phonological materials other than \phonliste{le} and \phonliste{yi} from appearing in between the reduplication by specifying what can appear in the list and what not.
+
 %%%%%%%%%%%%%%%%%%%%
@@
 The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
+
 %%%%%%%%%%%%%%%%%%%%%
@@
 Answer: will add
+
 %%%%%
@@
 Answer: add footnote
+
 %%%%%%%%
@@
 Answer: See above.
+
 %%%%
 p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
-%%%%%%%%%%%%%5
+
+%%%%%%%%%%%%%
 Answer: 
@@
 the fact that the object can be placed before \textit{yixia} in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+
 %%%%%%%%%%%%%%
@@
 complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.
+
 %%%%%%%%%%%%%
 Answer: We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
+
 %%%%%%%%%%%%%
@@
 Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.
+
 %%%%%%%%%%%%%%%%%%%%%%
+Answer: add a footnote
 %%%%%%%%%%%%%%%%%%%%%%
@@
 Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.
+
 %%%%%%%%%%%%%%%%
@@
 Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
-we do agree that they are different grammatical processes and thus requires separate analyses \citep[See also][]{Deng2013, Wang2023}.
+we do agree that they are different grammatical processes and thus requires separate analyses (See also \citealt[Sec. 4.3]{Deng2013}, \citealt{Wang2023}).
 Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch.
@@
 4]{Sui2018}).
+\citet[14--15]{Zhang2000} argues that the AABB form of reduplication develops from a completely separate historical origin from the AA and ABAB forms, 
+as the former has a intensifying rather than delimitative meaning.
 \citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
@@
 The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
+An analysis for the AABB form of reduplication has to be left for further research.
+
 %%%%%%%%%%%%%%%%%
@@
 persuasiveness of the tests presented in this section.
+
 %%%%%%%%%%%%%%%%%%%
@@
 distinction between verbal classifier and reduplication.
+
 %%%%%%%%%%%%%%%%%%%%
@@
 and the distinction still exist.
-But \textit{yi xia} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \textit{xia}, which only have the `for X times' interpretation \citep[77]{Deng2013}.
+But \textit{yi xia} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \textit{xia}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
 We think \textit{liang xia} `twice' is following this tendency, too.
-In this case, \textit{yi xia} and \textit{liang xia} cannot be seen as verbal classifier phrases anymore, but as duration adverbials as a whole.
+In this case, it is easy to interpret \textit{yi xia} and \textit{liang xia} not as referring to the actual number of action taking place, 
+but as duration adverbials as a whole,
+thus differing them from ``actual'' verbal classifier phrases with other numerals.
 %%%%%%%%%%%%%%%%%%%%
@@
 However, I think the author(s) might be better to use a more academic and formal terminology.
+
 %%%%%%%%%%%%%%%%%%%%%%
 Answer: reformulate as ``behaves more similar to a word''.
+
 %%%%%%%%%%%%%%%%%%%%%%
 Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.
+
 %%%%%%%%%%%%%%%%%%%%%%
@@
 Answer: Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
+
 %%%%%%%%%%%%%%%%%%%%%%%

### 2024-07-04 replies-reviews.tex
Update 2024-07-04-18:45:17

@@
 \definecolor{lsDOIGray}{cmyk}{0,0,0,0.45}
+
+\usepackage{csquotes}
 
@@
 
+\noindent
 Dear editors,
@@
 %%%%% YL
-Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that “This shows
+\begin{displayquote}
+Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that ``This shows
 that although the reduplication does have a tendency to interact with volitional verbs and with
 activities and semelfactives due to its dynamic meaning, this is by no means a rigid constraint, and
-non-volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.”
+non-volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.''
 
 Regarding volitionality, it should be noted that, as reported in various grammars, while it is generally true that verbs describing events not controlled by an agent cannot be reduplicated, some of them, under certain circumstances (e.g.
-in imperative or conditional sentences, or in causative rang/jiao/shi sentences, as in ex.
+in imperative or conditional sentences, or in causative \obj{rang/jiao/shi} sentences, as in ex.
 (15e) provided by the author(s)), can reduplicate (it might be worthwhile to delve into why this occurs in such sentence structures).
@@
 The same goes for those verbs expressing psychological states which can have a dynamic interpretation, as e.g.
-liaojié “understand’ (Basciano \& Melloni 2017, fn.
+liaojié `understand' (Basciano \& Melloni 2017, fn.
 3).
@@
 \& (1) — AN/ kan (le ) san ge xidoshi ‘read for three hours’ vs.
-*\& (1) \& =AW kan (le ) kan san ge xicioshi (both reduplication and for X time expressions set a boundary to the event) / IE{ETS zhéngzai kan / *EAEG TG zhéngzai kan kan).
+*\& (1) \& =AW kan (le ) kan san ge xicioshi (both reduplication and for X time expressions set a boundary to the event) / IEETS zhéngzai kan / *EAEG TG zhéngzai kan kan).
 In order to get a clearer picture and to find a semantic explanation for these facts, one should look at what these ‘special’ cases of reduplication have in common and try to draw generalizations: why can some stative and achievement verbs reduplicate under certain circumstances, while other cannot?
@@
 Can we single out specific subclasses of these verbs which can reduplicate?
+\end{displayquote}
 
@@
 %%%%%%%%%%%%%%%%%%%
+\noindent
 Answer:
@@
 Regarding volitionality, although (15e) is a causative sentence, (13a--b) are not imperative, conditional or causative (more on this below).
-Example () shows the same verb sheng1 `give birth to' as in (15e) reduplicated in a declarative sentence.
-我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
+Example (\ref{ex:sheng}) shows the same verb \obj{sheng1} `give birth to' as in (15e) reduplicated in a declarative sentence.
+\ea\label{ex:sheng}%我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
+\gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi} \ldots \\
+we women {} only can give.birth.to-give.birth.to children\\\jambox{(BCC)}
+\glt `We women can only give birth to children \ldots'
+\z
 
-As for stative verbs, \citet[Sec. 3.3]{Tham2013} uses xi3huan1 `like' and xiang1xin4 `believe' as examples of stative verbs
+As for stative verbs, \citet[Sec. 3.3]{Tham2013} uses \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as examples of stative verbs
 to contrast adjectives
-and what she calls basic change of state verbs such as bing4 `sick'.
-\citet[680]{PeckEtAl2013} also list xi3huan1 `like' and xiang1xin4 `believe' as stative verbs.
-For these two verbs, examples such as () and () can be found.
-这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
-谁让我来相信相信 (CCL)
+and what she calls basic change of state verbs such as \obj{bing4} `sick'.
+\citet[680]{PeckEtAl2013} also list \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as stative verbs.
+For these two verbs, examples such as (\ref{ex:xihuan}) and (\ref{ex:xiangxin}) can be found.
+\ea\label{ex:xihuan}%这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
+\gll \objex{zhe4} \objex{che1} \objex{hao3} \objex{xing2} \objex{a}! \objex{zen3me} \objex{le}, \objex{wo3} \objex{jiu4} \obj{xi3huan1-xi3huan4} \objex{bu4xing2} \objex{me}?\\
+this car so cool \textsc{ptc} what \textsc{ptc} I just like-like cannot \textsc{ptc}\\\jambox{(BCC)}
+\glt `This car is so cool! What? I can't just like it for a little bit?'
+
+\ex\label{ex:xiangxin}%谁让我来相信相信 (CCL)
+\gll \objex{shei2} \objex{rang4} \objex{wo3} \objex{lai2} \objex{xiang1xin4-xiang1xin4}\\
+who let I come believe-believe\\\jambox{(CCL)}
+\glt `Who lets me believe him/her?'
+\z
 However, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
 and indeed \citet[669--670]{Tham2013} herself noted,
-verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
+verbs expressing psychological states such as these can have a change of state (COS) interpretation (but not necessarily),
 let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
@@
 these predicates are not included in our examples.}
-The following examples contain the reduplication of xiang4 `look like' and zai4-chang3 `be present on the scene'.
-范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
-她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
+The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
+\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
+Context: \objex{Wang2} \objex{Sheng4di2} is the actor of \objex{Gu4} \objex{Miao3} in a TV series. \objex{Wang2} \objex{An1yu3} is another actor in the series.\\
+\\
+\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}.
+\objex{Wang2} \objex{An1yu3} \objex{ni3} \objex{kuai4dian} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
+Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
+\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'
+
+\ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
+\objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3} \ldots\\
+she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
+\glt `She \ldots\, really needs her mother to be present on scene for a little while \ldots'
+\z
+\footnotetext{\url{https://www.163.com/dy/article/FS1FKUC30534DZO1.html} (Accessed 26th  March 2024).}
 
@@
 This means that the use of reduplication affects the situation aspect at the sentential level.
-One might argue that examples such as () and () above convey dynamic meaning, even though stative verbs are used.
+One might argue that examples such as (\ref{ex:xiang}) and (\ref{ex:zaichang}) above convey dynamic meaning, even though stative verbs are used.
 %i.e. they may be interpreted as `become similar to' and `become present' respectively.
@@
 
-Due to its unique features compared to the perfective aspect marker \textit{le} and the experiential aspect marker \textit{guo},
+Due to its unique features compared to the perfective aspect marker \textit{le} and the experiential aspect marker \textit{guo4},
 the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
 \textit{Le} expresses a situation being realized, 
-while \textit{guo} conveys a situation already experienced,
+while \textit{guo4} conveys a situation already experienced,
 and thus, both rarely occur in future situations.
@@
 As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).
+
 %%%%%%%%%%%%%%%%%%

### 2024-07-12 replies-reviews.tex

@@
 \gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi} \ldots \\
-we women {} only can give.birth.to-give.birth.to children\\\jambox{(BCC)}
+we women {} only can give.birth.to-give.birth.to child\\\jambox{(BCC)}
 \glt `We women can only give birth to children \ldots'
@@
 \ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
-Context: \objex{Wang2} \objex{Sheng4di2} is the actor of \objex{Gu4} \objex{Miao3} in a TV series. \objex{Wang2} \objex{An1yu3} is another actor in the series.\\
+Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series. 
+\objex{Wang2} \objex{An1yu3} is another actor in the series.\\
 \\
@@
 With regard to achievements, the reduplication does not seem to cancel the telos.
-Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (b) but not with ``for X-time'' (c).
-()a 一块... 到附近市场买买东西 (CCL)
-b 两天后到附近市场买买东西
-c *到附近市场买买东西两天
-The following continuation that cancels the telo is also infelicitous ().
-() 到附近市场买买东西 \# 但什么也没买到
+Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
+\ea
+\ea[]{\label{ex:teloa}% 一块... 到附近市场买买东西 (CCL)
+\gll \objex{yi2kuai4} \ldots\, \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\\
+together {} arrive nearby market buy-buy thing\\\jambox{(CCL)}
+\glt `(We) together \ldots\, went to the market nearby to buy some things.'}
+
+\ex[]{\label{ex:telob}% 两天后到附近市场买买东西
+\gll \objex{liang3} \objex{tian1} \objex{hou4} \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\\
+two day later arrive nearby market buy-buy thing\\
+\glt `Two days later, (we) went to the market nearby to buy some things.}
+
+\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
+    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}\\
+    arrive nearby market buy-buy thing two day\\
+    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
+\z\z
+The following continuation that cancels the telo is also infelicitous (\ref{ex:telod}).
+\ea\label{ex:telod} 到附近市场买买东西 \# 但什么也没买到
+\z
 

### 2024-07-12 replies-reviews.tex
Update 2024-07-12-17:14:42

@@
 The following continuation that cancels the telo is also infelicitous (\ref{ex:telod}).
-\ea\label{ex:telod} 到附近市场买买东西 \# 但什么也没买到
+\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
+\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}\\
+arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
+\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
 \z
@@
 %%%%% YL
+\begin{displayquote}
 The author(s) argue(s) that verbal reduplication is a morphological phenomenon based on some tests (Sect. 2.4). However, the tests used have some shortcomings.
@@
 unconvincing. 
+\end{displayquote}
 
@@
 %%%%%%%%%%%%%%%%%%%%
+\noindent
 Answer:
@@
 First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
-This is possible for a VP (), as the NP inside of the VP can be modified by e.g. an AP.
-() 开红色的门
+This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g. an AP.
+\ea\label{ex:modVP} %开红色的门
+\gll \objex{kai1} \objex{hong2se4de} \objex{men2}\\
+open  red door\\
+\glt `open the red door'
+\z
 In contrast, the individual verbs in reduplication cannot be modified by an e.g. AdvP.
-() is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
-()* 看偷偷地看
+(\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
+\ea[*]{\label{ex:modVV} %看偷偷地看
+\gll \objex{kan4} \objex{tou1tou1de} \objex{kan4}\\
+look secretly look\\
+}
+\z
 
 Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
-This is possible for a verbal classifier phrase (), as the object can occur after or in-between.
-() 开两次门
-() 开门两次
-For reduplication, this is also not possible (), as the object cannot be inserted between the two verbs.
-() *开(了)门(了)开
+This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in-between.
+\ea\label{ex:inVCP}%开两次门
+%开门两次
+\ea \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
+open door three time\\
+\glt `open the door three times'
+
+\ex  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
+open three time door\\
+\glt `open the door three times'
+\z\z
+For reduplication, this is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
+\ea\label{ex:inVV}
+\ea[]{\gll \obj{kai1}-(\obj{le})-\obj{kai1} \objex{men2}\\
+open-\textsc{pfv}-open door\\
+\glt `open the door for a little while'}
+
+\ex[*]{%开(了)门(了)开
+\gll \obj{kai1}-(\obj{le})-\obj{men2}-\obj{kai1}\\
+open-\textsc{pfv}-door-open\\
+}
+\z\z
 % If we analyze reduplication as a phrasal operation, we would expect the structure of
@@
 
-Regarding the position of \textit{le}, there are counter-examples that show V-le-gei () as well as \textit{guan-le-xin} `close-\textsc{pfv}-heart, care for' () are possible.
-() 还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
-() 许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
+Regarding the position of \obj{le}, there are counter-examples that show V-\obj{le-gei3} (\ref{ex:Vgei}) as well as \obj{guan1-le-xin1} `close-\textsc{pfv}-heart, care for' (\ref{ex:guanxin}) are possible.
+\ea\label{ex:Vgei}%还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
+\gll \ldots\, \objex{xu3duo1} \objex{nv2zi3}, \objex{jiang1} \objex{zi4ji3de} \objex{xiang4pian1} \ldots\, \objex{ji4-le-gei3} \objex{ta1}.\\
+{} many women take own photo {} send-\textsc{pfv}-give he\\\jambox{(CCL)}
+\glt `Many women \ldots\, sent him photos of themselves.'
+\z
+
+\ea\label{ex:guanxin}%许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
+\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-xin1}.\\
+many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\
+\glt `Many comrades \ldots\, voluntarily cared for the patients.'
+\z
+
 In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.), 
@@
 %%%%YL
+\begin{displayquote}
 Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
@@
 As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).
+\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%
+\noindent
 Answer:
@@
 %% YL
+\begin{displayquote}
 Pp.
@@
 This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
+\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%%
+\noindent
 Answer:
 \obj{le} `\textsc{pfv}' marks the perfective aspect.
-The reason for \obj{le} `\textsc{pfv} being the only aspect marker compatible with reduplication is explained in the Semantics Section.
+The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Semantics Section.
 
@@
 \ea\label{ex:hist1} 
-明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
-%\gll \obj{ming2} \obj{}
+%明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
+\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{liang2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\footnotemark\\
+Ming agian call Qi also call Ming in.succession call two call Qi thus bow\\
+\glt `Ming called again. Qi called too. Ming called twice. Qi thus bowed.'
 \z
+\footnotetext{《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}}
 Here the numeral refers to the actual number of the action taking place 
@@
 %% YL
+\begin{displayquote}
 The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level.
@@
 The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
+\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%%%
+\noindent
 Answer:

### 2024-07-13 replies-reviews.tex
made replies more readable with enumerate

--- 2024-07-12 replies-reviews.tex
@@
-%% -*- coding:utf-8 -*-
-
 %% -*- coding:utf-8 -*-
@@
 %\usepackage{fontspec}
+
+%\newtoggle{draft}\togglefalse{draft}
+\newtoggle{draft}\toggletrue{draft}
 
@@
 
+\begin{enumerate}
 %%%%% YL
-\begin{displayquote}
+\item 
 Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that ``This shows
@@
 Can we single out specific subclasses of these verbs which can reduplicate?
-\end{displayquote}
 
@@
 \noindent
-Answer:
+\textbf{Answer:}
 First, the notion of ``aspect'' adopted in this article has to be explained in more detail.
@@
 %%%%% YL
+\item 
 The author(s) argue(s) that verbal reduplication is a morphological phenomenon based on some tests (Sect. 2.4). However, the tests used have some shortcomings.
@@
 lexical integrity”, i.e. they form a single lexical item (745 T fih ji-géi-le ta vs. * 77 T 431 Ji-le géi ta).
+\itdopt{St. Mü.: fix brackets and references to examples.}
 
@@
 %%%%%%%%%%%%%%%%%%%%
-Answer:
+\textbf{Answer:}
 Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
@@
 ()* 看偷偷地看
+
+\itdopt{Stmü: Fix examples and referecnes to them.}
 
@@
 %%%%YL
+\item 
 Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
@@
 %%%%%%%%%%%%%%%%%%
-Answer:
+\textbf{Answer:}
 Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.
@@
 %% YL
-Pp.
-26, lines 24-25: “The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
-[] indicates an underspecified list which could be empty or not”.
+\item Pp.
+26, lines 24-25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
+[] indicates an underspecified list which could be empty or not''.
 However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements.
@@
 %%%%%%%%%%%%%%%%%%%%
-Answer:
+\textbf{Answer:}
 \obj{le} `\textsc{pfv}' marks the perfective aspect.
@@
 %% YL
+\item 
 The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level.
@@
 %%%%%%%%%%%%%%%%%%%%%
-Answer:
+\textbf{Answer:}
 As explained above, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
@@
 %% Stefan
+\item
 The proposed analysis appears to have a descriptive rather than an explanatory power.
@@
 
+\textbf{Answer:} \itdopt{Stefan, say something.}
+
 %%%%%%%%%%%%%%%%%%%%
@@
 %% YL
+\item 
 I would add tones to the pinyin transcription.
 %%%%
-Answer: will add
+
+\textbf{Answer:} will add
+
+\end{enumerate}
 
 %%%%%
-Other comments:
+\subsection{Other comments}
 
+\begin{enumerate}
+\item
 p.
@@
 %%%%%%%%
-Answer: add footnote
+
+\textbf{Answer:} add footnote
 
 %%%%%%%%
+\item
 p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
 %%%%
-Answer: See above.
+
+\textbf{Answer:} See above.
 
 %%%%
+\item
 p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
@@
 %%%%%%%%%%%%%
-Answer: 
+\textbf{Answer:} 
 There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \textit{yixia}:
@@
 %%%%%%%%%%%%%%
+\item
 p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
@@
 %%%%%%%%%%%%%
-Answer: We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
+\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
 
 %%%%%%%%%%%%%
+\item
 p.
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Answer: add a footnote
+\textbf{Answer:} add a footnote
 %%%%%%%%%%%%%%%%%%%%%%
+\end{enumerate}
 
@@
 
-This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
+\begin{enumerate}
+\item This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
 clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
@@
 %%%%%%%%%%%%%%%%
-Answer: 
+\textbf{Answer:} 
 \citet{Xie2020} identifies the AABB form as morphological verb reduplication.
@@
 %% YL
+\item 
 R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
@@
 
-%Answer: Yes, this is true.
+\textbf{Answer:} %Yes, this is true.
 
-Examples (27) and (28) serve as illustrations to demonstrate the application of the 'Lexical Integrity Hypothesis' in distinguishing PVC from SVC.
+\item Examples (27) and (28) serve as illustrations to demonstrate the application of the 'Lexical Integrity Hypothesis' in distinguishing PVC from SVC.
 
@@
 
-In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).
+\item In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).
 
@@
 %%%%%%%%%%%%%%%%%%%
-Answer: See above.
+\textbf{Answer:} See above.
 %%%%%%%%%%%%%%%%%%%
@@
 %% YL
+\item 
 The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
@@
 %%%%%%%%%%%%%%%%%%%%
-Answer:
+\textbf{Answer:}
 It is not \textit{san xia} `three times' that is special, but it is \textit{yi xia} `once' that is special.
@@
 %% Stefan
+\item
 It would enhance reader comprehension if the authors could provide a brief illustration of symbols
@@
 
-Answer: PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
+\textbf{Answer:} PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
 another constraint. A constraint that is a subtype in the hierarchy. The type
@@
 
+\end{enumerate}
+
 \section{Reviewer 3}
@@
 %% YL
-The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
+\begin{enumerate}
+\item The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
 Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Answer: reformulate as ``behaves more similar to a word''.
+\textbf{Answer:} reformulate as ``behaves more similar to a word''.
 
 %%%%%%%%%%%%%%%%%%%%%%
+\item
 Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.
@@
 %% YL
-Answer: Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
+\textbf{Answer:} Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
 
@@
 %% Stefan
+\item
 In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs.
@@
 
+\itdopt{Stefan}
+\end{enumerate}
+
 {\sloppy

### 2024-07-13 replies-reviews.tex

@@
 First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
-This is possible for a VP (), as the NP inside of the VP can be modified by e.g. an AP.
-() 开红色的门
+This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g. an AP.
+\ea\label{ex:modVP} %开红色的门
+\gll \objex{kai1} \objex{hong2se4de} \objex{men2}\\
+open  red door\\
+\glt `open the red door'
+\z
 In contrast, the individual verbs in reduplication cannot be modified by an e.g. AdvP.
-() is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
-()* 看偷偷地看
+(\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
+\ea[*]{\label{ex:modVV} %看偷偷地看
+\gll \objex{kan4} \objex{tou1tou1de} \objex{kan4}\\
+look secretly look\\
+}
+\z
 
@@
 Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
-This is possible for a verbal classifier phrase (), as the object can occur after or in-between.
-() 开两次门
-() 开门两次
-For reduplication, this is also not possible (), as the object cannot be inserted between the two verbs.
-() *开(了)门(了)开
+This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in-between.
+\ea\label{ex:inVCP}%开两次门
+%开门两次
+\ea \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
+open door three time\\
+\glt `open the door three times'
+
+\ex  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
+open three time door\\
+\glt `open the door three times'
+\z\z
+For reduplication, this is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
+\ea\label{ex:inVV}
+\ea[]{\gll \obj{kai1}-(\obj{le})-\obj{kai1} \objex{men2}\\
+open-\textsc{pfv}-open door\\
+\glt `open the door for a little while'}
+
+\ex[*]{%开(了)门(了)开
+\gll \obj{kai1}-(\obj{le})-\obj{men2}-\obj{kai1}\\
+open-\textsc{pfv}-door-open\\
+}
+\z\z
 % If we analyze reduplication as a phrasal operation, we would expect the structure of
@@
 As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).
+\end{displayquote}
 
@@
 \obj{le} `\textsc{pfv}' marks the perfective aspect.
-The reason for \obj{le} `\textsc{pfv} being the only aspect marker compatible with reduplication is explained in the Semantics Section.
+The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Semantics Section.
 

### 2024-07-15 replies-reviews.tex
Update 2024-07-15-12:10:48

--- 2024-07-12 replies-reviews.tex
@@
 \gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-xin1}.\\
-many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\
+many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\\jambox{(CCL)}
 \glt `Many comrades \ldots\, voluntarily cared for the patients.'
@@
 \z
-\footnotetext{《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}}
+\footnotetext{\obj{Song4dai4} \obj{juan4}: \obj{Xu1tang2} \obj{He2shang} \obj{yu3lu4} \textit{[The Song dynasty volume: Quotations from Abbot Xutang]} p. 387 as cited in \citet[12]{Zhang2000}}
 Here the numeral refers to the actual number of the action taking place 
@@
 \ea\label{ex:hist2}
-且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
+%且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
+\gll \objex{qie3} \obj{xie1-yi-xie1} \objex{le}, \objex{qu4} \objex{zuo4} \objex{di4}.\footnotemark\\
+just rest-one-rest \textsc{ptc} go sit ground\\
+\glt `(Let me) just take a rest and go sit on the ground.'
 \z
+\footnotetext{\obj{Song4dai3} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p. 519 as cited in \citet[13]{Zhang2000}}
 In this case, \obj{yi1} `one' cannot be replaced by other numerals.
@@
 %% Stefan
+\begin{displayquote}
 The proposed analysis appears to have a descriptive rather than an explanatory power.
+\end{displayquote}
 %%%%%%%%%%%%%%%%%%%%
@@
 %% YL
+\begin{displayquote}
 I would add tones to the pinyin transcription.
+\end{displayquote}
+
 %%%%
-Answer: will add
+Answer: done
 
 %%%%%
-Other comments:
-
+%Other comments:
+\begin{displayquote}
 p.
@@
 To the best of my knowledge, exiting literature on the subject consistently maintains that resultative compounds are not amenable to reduplication.
+\end{displayquote}
+
 %%%%%%%%
@@
 %%%%%%%%
+\begin{displayquote}
 p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
+\end{displayquote}
 %%%%
+
 Answer: See above.
@@
 %%%%
+\begin{displayquote}
 p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
+\end{displayquote}
+%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%
+\noindent
 Answer: 
-There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \textit{yixia}:
-她看了他的脸一下。(CCL)
-他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
-We think it has to do with the weight/length of the object, i.e. shorter objects can be placed before \textit{yixia} while longer ones cannot.
-%This is not necessarily a syntactic constraint.
+There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
+\ea%她看了他的脸一下。(CCL)
+\gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
+she look-\textsc{pfv} his face one time\\\jambox{(CCL)}
+\glt `She took a look at his face.'
 
-Even if we accept that the object can be only be placed before \textit{yixia} in limited cases, 
-the fact that the object can be placed before \textit{yixia} in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
+\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
+he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
+\glt `He just took a look at the glass and the glass just broke.'
+\z
+We think it has to do with the weight/length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
+%This is not necessarily a syntactic constraint
+
+Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases, 
+the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
 
 %%%%%%%%%%%%%%
+\begin{displayquote}
 p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
@@
 complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.
+\end{displayquote}
 
 %%%%%%%%%%%%%
+\noindent
 Answer: We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
@@
 
+\begin{displayquote}
 This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
@@
 Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.
+\end{displayquote}
 
 %%%%%%%%%%%%%%%%
+\noindent
 Answer: 
@@
 This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
-This is probably the case for those AABBs that have an idiomatic meaning, such as \textit{zhi-zhi-dian-dian} `point-point-gesture-gesture, gossip'.
+This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi2-zhi3-dian2-dian3} `point-point-gesture-gesture, gossip'.
 %Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
@@
 %% YL
+\begin{displayquote}
 R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
@@
 persuasiveness of the tests presented in this section. 
+\end{displayquote}
 
@@
 %% YL
+\begin{displayquote}
 The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
@@
 distinction between verbal classifier and reduplication. 
+\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%%
+\noindent
 Answer:
-It is not \textit{san xia} `three times' that is special, but it is \textit{yi xia} `once' that is special.
-We can replace \textit{san} `three' with any number above two,
+It is not \obj{san1} \obj{xia4} `three times' that is special, but it is \obj{yi2} \obj{xia4} `once' that is special.
+We can replace \obj{san1} `three' with any number above two,
 and the distinction still exist.
-But \textit{yi xia} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \textit{xia}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
-We think \textit{liang xia} `twice' is following this tendency, too.
-In this case, it is easy to interpret \textit{yi xia} and \textit{liang xia} not as referring to the actual number of action taking place, 
+But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
+We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
+In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place, 
 but as duration adverbials as a whole,
@@
 %% Stefan
+\begin{displayquote}
 It would enhance reader comprehension if the authors could provide a brief illustration of symbols
@@
 Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57). 
+\end{displayquote}
 
+\noindent
 Answer: PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
@@
 %% YL
+\begin{displayquote}
 The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
@@
 However, I think the author(s) might be better to use a more academic and formal terminology.
+\end{displayquote}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
+\begin{displayquote}
 Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.
+\end{displayquote}
 
@@
 %% YL
+\noindent
 Answer: Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
@@
 %% Stefan
+\begin{displayquote}
 In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs.
@@
 On top of them, a full derivation can be made for better understanding.
+\end{displayquote}
 %%%%%%%%%%%%%%%%%%%%%%%

### 2024-07-15 chapters/ch05-Analysis.tex

@@
 \ea\label{avm:AA}
-The AA lexical rule with all constraints inherited from the supertypes:
+The AA lexical rule with all constraints inherited from the supertypes:\\
 %\scalebox{.9}{%
@@
 
-\newpage
+%\newpage
 \ea\label{avm:AyiA}
-The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:
+The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:\\
 %\scalebox{.9}{%

### 2024-07-15 replies-reviews.tex
Update 2024-07-15-12:30:26

@@
 
+\begin{enumerate}
 %%%%% YL
-\begin{displayquote}
+\item
 Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that ``This shows
@@
 %%%%% YL
-\begin{displayquote}
+\item
 The author(s) argue(s) that verbal reduplication is a morphological phenomenon based on some tests (Sect. 2.4). However, the tests used have some shortcomings.
@@
 unconvincing.
-\end{displayquote}
 
@@
 %%%%%%%%%%%%%%%%%%%%
-\noindent
-Answer:
+\textbf{Answer:}
 Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
@@
 \z
+
+\itdopt{Stmü: Fix examples and referecnes to them.}
 
@@
 %%%%YL
-\begin{displayquote}
+\item
 Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
@@
 As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).
-\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%
-\noindent
-Answer:
+\textbf{Answer:}
 Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.
@@
 %% YL
-\begin{displayquote}
-Pp.
-26, lines 24-25: “The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
-[] indicates an underspecified list which could be empty or not”.
+\item Pp.
+26, lines 24-25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
+[] indicates an underspecified list which could be empty or not''.
 However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements.
 This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
-\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%%
-\noindent
-Answer:
+\textbf{Answer:}
 \obj{le} `\textsc{pfv}' marks the perfective aspect.
@@
 %% YL
-\begin{displayquote}
+\item
 The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level.
@@
 The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
-\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%%%
-\noindent
-Answer:
+\textbf{Answer:}
 As explained above, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
@@
 %% Stefan
-\begin{displayquote}
+\item
 The proposed analysis appears to have a descriptive rather than an explanatory power.
-\end{displayquote}
 %%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%
+
+\textbf{Answer:} \itdopt{Stefan, say something.}
 
@@
 %% YL
-\begin{displayquote}
+\item
 I would add tones to the pinyin transcription.
-\end{displayquote}
 
 %%%%
-Answer: done
+\textbf{Answer:} done
 
@@
 %Other comments:
-\begin{displayquote}
+\item
 p.
@@
 To the best of my knowledge, exiting literature on the subject consistently maintains that resultative compounds are not amenable to reduplication.
-\end{displayquote}
 
 %%%%%%%%
-Answer: add footnote
+
+\textbf{Answer:} add footnote
 
 %%%%%%%%
-\begin{displayquote}
+\item
 p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
-\end{displayquote}
 %%%%
 
-Answer: See above.
+\textbf{Answer:} See above.
 
 %%%%
-\begin{displayquote}
+\item
 p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
-\end{displayquote}
 %%%%%%%%%%%%%
@@
 \noindent
-Answer: 
+\textbf{Answer:}
 There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
@@
 %%%%%%%%%%%%%%
-\begin{displayquote}
+\item
 p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
@@
 complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.
-\end{displayquote}
 
@@
 \noindent
-Answer: We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
+\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
 
 %%%%%%%%%%%%%
+\item
 p.
@@
 %%%%%%%%%%%%%%%%%%%%%%
-Answer: add a footnote
+\textbf{Answer:} add a footnote
 %%%%%%%%%%%%%%%%%%%%%%
+\end{enumerate}
 
 \section{Reviewer 2}
-
-\begin{displayquote}
+\begin{enumerate}
+\item
 This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
@@
 Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.
-\end{displayquote}
 
@@
 \noindent
-Answer: 
+\textbf{Answer:}
 \citet{Xie2020} identifies the AABB form as morphological verb reduplication.
@@
 %% YL
-\begin{displayquote}
+\item
 R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
@@
 
-%Answer: Yes, this is true.
+%\textbf{Answer:} %Yes, this is true.
 
@@
 persuasiveness of the tests presented in this section.
-\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%
-Answer: See above.
+\textbf{Answer:} See above.
 %%%%%%%%%%%%%%%%%%%
@@
 %% YL
-\begin{displayquote}
+\item
 The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
@@
 distinction between verbal classifier and reduplication.
-\end{displayquote}
 
@@
 \noindent
-Answer:
+\textbf{Answer}:
 It is not \obj{san1} \obj{xia4} `three times' that is special, but it is \obj{yi2} \obj{xia4} `once' that is special.
@@
 %% Stefan
-\begin{displayquote}
+\item
 It would enhance reader comprehension if the authors could provide a brief illustration of symbols
@@
 Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).
-\end{displayquote}
 
 \noindent
-Answer: PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
+\textbf{Answer:} PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
 another constraint. A constraint that is a subtype in the hierarchy. The type
@@
 
+\end{enumerate}
+
 \section{Reviewer 3}
 
+\begin{enumerate}
 %%%%%%%%%%%%%%%%%%%%%
@@
 %% YL
-\begin{displayquote}
+\item
 The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
@@
 However, I think the author(s) might be better to use a more academic and formal terminology.
-\end{displayquote}
 
 %%%%%%%%%%%%%%%%%%%%%%
-Answer: reformulate as ``behaves more similar to a word''.
+\textbf{Answer:} reformulate as ``behaves more similar to a word''.
 
 %%%%%%%%%%%%%%%%%%%%%%
-\begin{displayquote}
+\item
 Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.
-\end{displayquote}
 
@@
 %% Stefan
-\begin{displayquote}
+\item
 In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs.
@@
 On top of them, a full derivation can be made for better understanding.
-\end{displayquote}
 %%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%
+
+\itdopt{Stefan}
+\end{enumerate}
 

### 2024-07-20 replies-reviews.tex
Update 2024-07-20-20:23:56

@@
 %% YL
+\item
+R2 comments on the following passage: A-\obj{kan4-kan4}
+
+I am curious about the acceptability of this form 'A-kan-kan.' For instance, phrases like 'shuo-kan-kan' ('say-look-look') or 'ting-kan-kan' ('listen-look-look') do not seem acceptable to me.
+
+\textbf{Answer:}
+The acceptability of the A-\obj{kan4-kan4} form seems to vary among Mandarin Chinese speakers.
+\citet[73]{Cheng2012} suggests that unlike AA-\obj{kan4}, A-\obj{kan4-kan4} is an emerging construction that is still undergoing grammaticalization.
+He found in the Academia Sinica Balanced Corpus of Modern Chinese (Sinica Corpus, \citealt{sinica}) 23 tokens of A-\obj{kan4-kan4} but 141 tokens of AA-\obj{kan4} (p. 64).
+This shows that the former is less common than the latter.
+(\ref{ex:Akankan}) is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
+\ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
+\gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
+just follow-\textsc{prog} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
+\glt `Let's just follow the north wind, try and see if we can block the sand!'
+\z
+
+\citegen{Cheng2012} study is based on the Mandarin spoken in Taiwan.
+We might assume that A-\obj{kan4-kan4} is more widely used in Taiwan than in Mainland China.
+But we also found the following examples of A-\obj{kan4-kan4} in the BCC corpus \citep{BCC}, which includes mostly data from Mainland China.
+This suggests that A-\obj{kan4-kan4} is acceptable for and used by at least some Mainland Chinese Mandarin speakers as well.
+\ea %那么，你倒说看看 ，你会有什么样的改变\ldots \jambox{(BCC)}
+\gll \objex{na4me}, \objex{ni3} \objex{dao4} \obj{shuo1-kan4-kan4}, \objex{ni3} \objex{hui4} \objex{you3} \objex{shen2meyang4de} \objex{gai3bian4}\ldots\\
+then you just say-look-look you will have what.kind.of change\\\jambox{(BCC)}
+\glt `Then you just try and say what kind of changes you will have.'
+\z
+
+\ea %我得听看看你的条件再说\ldots \jambox{(BCC)}
+\gll \objex{wo3} \objex{dei3} \obj{ting1-kan4-kan4} \objex{ni3de} \objex{tiao2jian4} \objex{zai4} \objex{shuo1}\ldots\\
+I have.to listen-look-look your condition then say\\\jambox{(BCC)}
+\glt `I'll have to listen to your conditions first before talking about it/ deciding.'
+\z
+
+A statistical comparison of the acceptability and the productivity of A-\obj{kan4-kan4} among speakers of different varieties of Mandarin Chinese has to be left for future studies.
+
+\item
 R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and

### 2024-07-20 chapters/ch01-Intro.tex
Update 2024-07-20-20:23:56

@@
 	\ea
-	\gll qing ni chang zhe dao cai.\\
+	\gll \objex{qing3} \objex{ni3} \objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
 	please you taste this \textsc{clf} dish\\
@@
 	\ex
-	\gll qing ni \textit{chang}-\textit{chang} zhe dao cai.\\
+	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
 	please you taste-taste this \textsc{clf} dish\\
@@
 The data in this paper was drawn from several sources.
-In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} was also consulted.
+In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} and the BCC corpus \citep{BCC} was also consulted.
 Further, examples from novels and plays written by native speakers were considered.

### 2024-07-20 replies-reviews.tex
Update 2024-07-20-20:34:20

@@
 proposals in Section 4.
+\itdopt{Stefan}
 
+\item
 Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).
@@
 \item
+In Page 2, the draft says that CCL corpus was explored in addition to the author(s)’ intuition.
+I think this corpus-based method to bolster the acceptability judgments of the verbal reduplication expressions would be one of the merits in the current draft.
+The author(s) might be better to say more about why the corpus data was additionally explored and what was the findings from the corpus data (in comparison to the introspective judgments).
+
+\item
+From Pages 4 to 5, the draft provides thorough overview of the subtypes of verbal reduplication in Mandarin Chinese.
+Yet, I think the examples would be too heavy for now.
+I am not sure whether all the examples are connected to the analyses in the later sections.
+
+\textbf{Answer:} The examples are shortened to improve readability.
+
+\item 
+In Page 7 (section 2.3.2), the draft analyzes verbal reduplication with respect to Aktionsarten.
+Nonetheless, I am not well-aware of the concept.
+The author(s) might be better to account for the concept first in more detail.
+
+\textbf{Answer:} see above.
+
+\item
+In Page 13,
+there is a typo: ... (but see Section 2.3.2). in comparison, ...
+
+\textbf{Answer:} fixed.
+
+\item
+In the middle, the draft mentions the -bar derivation and be-prefixation in German.
+I understand the phenomenon has a similarity to verbal reduplication in Chinese.
+Yet, at a glance the German examples looked out-of-the-blue to me.
+
+\textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category of the input.
+To improve readability, English examples are used instead.
+
+\item
 The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
@@
 
+\item
 In Page 14, the draft makes use of a new terminology such as “word-like”.
@@
 \noindent
-Answer: Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
+\textbf{Answer: }Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.
 
@@
 Otherwise, the author(s) might be better to refer to the previous analysis about the notion.
+\itdopt{Stefan}
 
+\item
 In Section 4, I am expecting the author(s) provide a sample derivation (maybe a tree diagram).

### 2024-08-15 replies-reviews.tex
Update 2024-07-20-20:43:57
Update 2024-08-15-16:33:06

@@
 
+\textbf{Answer:}
+ Corpus data contains a variation of linguistic properties, which help us obtain a better picture of the phenomenon under study,
+ and discover relevant constraints that can otherwise go unnoticed through introspection.
+ Corpus data is generally natural and contextualized, which can be helpful when evaluating the examples through introspection \citep[921]{MM2009a}.
+ In the case of this study, the corpus data mainly shows that stative verbs and achievements can also be reduplicated in certain contexts, contrary to the claims in previous studies.
+Example sentences retrieved from the corpora are marked with their sources (``CCL'' or ``BCC'') behind them,
+as opposed to handcraft examples, which are not marked.
+
 \item
@@
 conjunction reduction.
+
+\textbf{Answer:} See above.
 

### 2024-08-18 chapters/ch01-Intro.tex
Update 2024-08-18-17:19:01

@@
 	\ex
-	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
+	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\objex{chang} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
 	please you taste-taste this \textsc{clf} dish\\
@@
 This new account avoids the problems of previous approaches and
-explains more forms of verbal reduplication in Mandarin Chinese.
+explains more forms of deliminative verbal reduplication in Mandarin Chinese.
 
@@
 Importantly, we restrict the object of this study to the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
-We will also discuss in this section, with the help of corpus data, the question of whether the reduplication is a morphological or a syntactic process.
+We will also discuss in this section, with the help of corpus data, the question of whether the reduplication is better analyzed as a morphological or a syntactic process.
 In \sectref{sec:prev}, we will discuss the advantages and drawbacks of previous approaches. 
@@
 Further, examples from novels and plays written by native speakers were considered.
+Corpus data provides natural and contextualized examples, and contains a variation of linguistic properties \citep[921]{MM2009a}.
+This can help us discover relevant constraints that can otherwise go unnoticed through introspection.

### 2024-08-18 chapters/ch02-Phenomenon.tex
Update 2023-06-27-21:39:49
Update 2024-08-18-17:19:01

@@
 
-\ea\label{ex:forms-mono} for monosyllabic verbs: \textit{shuo} `say'
-	\ea \gll shuo-shuo\\ 
+\ea\label{ex:forms-mono} for monosyllabic verbs: \obj{shuo1} `say'
+	\ea \gll \objex{shuo1-shuo}\\ 
 		say-say\\ \jambox{AA}
-		\ex \gll shuo-yi-shuo\\
+		\ex \gll \objex{shuo1-yi-shuo1}\\
 		say-one-say\\ \jambox{A-\textit{yi}-A}
-		\ex \gll shuo-le-shuo\\
+		\ex \gll \objex{shuo1-le-shuo1}\\
 		say-\textsc{pfv}-say\\ \jambox{A-\textit{le}-A}
-		\ex \gll shuo-le-yi-shuo\\
+		\ex \gll \objex{shuo1-le-yi-shuo1}\\
 		say-\textsc{pfv}-one-say\\ \jambox{A-\textit{le}-\textit{yi}-A}
-		\ex \gll shuo-shuo-kan\\
-		say-say-look\\ \jambox{AA-\textit{kan}}
-		\ex \gll shuo-kan-kan\\
-		 say-look-look\\ \jambox{A-\textit{kan}-\textit{kan}}
+		\ex \gll \objex{shuo1-shuo1-kan4}\\
+		say-say-look\\ \jambox{AA-\obj{kan4}}
+		\ex \gll \objex{shuo1-kan4-kan4}\footnotemark\\
+		 say-look-look\\ \jambox{A-\obj{kan4}-\obj{kan4}}
+		\z
+\footnotetext{One reviewer points out that this form is not acceptable for him/her.
+The acceptability of the A-\obj{kan4-kan4} form seems to vary among Mandarin Chinese speakers.
+\citet[73]{Cheng2012} suggests that unlike AA-\obj{kan4}, A-\obj{kan4-kan4} is an emerging construction that is still undergoing grammaticalization.
+He found in the Academia Sinica Balanced Corpus of Modern Chinese (Sinica Corpus; \citealt{sinica}) 23 tokens of A-\obj{kan4-kan4} but 141 tokens of AA-\obj{kan4} (p. 64).
+This shows that the former is less common than the latter.
+(\ref{ex:Akankan}) is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
+\ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
+\gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
+just follow-\textsc{prog} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
+\glt `Let's just follow the north wind, try and see if we can block the sand!'
 \z
 
-\ex\label{ex:forms-di} for disyllabic verbs: \textit{lai-wang} come-go `come and go/communicate'
-		\ea \gll lai-wang-lai-wang\\
+\citeauthor{Cheng2012}'s (\citeyear{Cheng2012}) study is based on the Mandarin spoken in Taiwan.
+We might assume that A-\obj{kan4-kan4} is more widely used in Taiwan than in Mainland China.
+But we also found the following examples of A-\obj{kan4-kan4} in the BCC corpus, which includes mostly data from Mainland China.
+This suggests that A-\obj{kan4-kan4} is acceptable for and used by at least some Mainland Chinese Mandarin speakers as well.
+\ea %那么，你倒说看看 ，你会有什么样的改变\ldots \jambox{(BCC)}
+\gll \objex{na4me}, \objex{ni3} \objex{dao4} \obj{shuo1-kan4-kan4}, \objex{ni3} \objex{hui4} \objex{you3} \objex{shen2meyang4de} \objex{gai3bian4}\ldots\\
+then you just say-look-look you will have what.kind.of change\\\jambox{(BCC)}
+\glt `Then you just try and say what kind of changes you will have.'
+%\z
+
+\ex %我得听看看你的条件再说\ldots \jambox{(BCC)}
+\gll \objex{wo3} \objex{dei3} \obj{ting1-kan4-kan4} \objex{ni3de} \objex{tiao2jian4} \objex{zai4} \objex{shuo1}\ldots\\
+I have.to listen-look-look your condition then say\\\jambox{(BCC)}
+\glt `I'll have to listen to your conditions first before talking about it/ deciding.'
+\z
+
+A statistical comparison of the acceptability and the productivity of A-\obj{kan4-kan4} among speakers of different varieties of Mandarin Chinese has to be left for future studies.
+}
+
+\ex\label{ex:forms-di} for disyllabic verbs: \obj{lai2-wang3} come-go `come and go/communicate'
+		\ea \gll \objex{lai2-wang3-lai2-wang3}\\
 		come-go-come-go\\ \jambox{ABAB}
-		\ex \gll lai-wang-le-lai-wang\\
+		\ex \gll \objex{lai2-wang3-le-lai2-wang3}\\
 		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
-		\ex \gll lai-lai-wang-wang\\
+		\ex \gll \objex{lai2-lai2-wang3-wang3}\\
 		come-come-go-go\\ \jambox{AABB}
@@
 
-\ex\label{ex:forms-vo} for V-O compounds: \textit{shuo-huang} tell-lie `lie'
-		\ea \gll shuo-shuo-huang\\
+\ex\label{ex:forms-vo} for V-O compounds: \obj{shuo1-huang3} tell-lie `lie'
+		\ea \gll \objex{shuo1-shuo1-huang3}\\
 		tell-tell-lie\\ \jambox{AAB}
-		\ex \gll shuo-yi-shuo-huang\\
+		\ex \gll \objex{shuo1-yi-shuo1-huang3}\\
 		tell-one-tell-lie\\ \jambox{A-\textit{yi}-AB}
-		\ex \gll shuo-le-shuo-huang\\
+		\ex \gll \objex{shuo1-le-shuo1-huang3}\\
 		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
@@
 namely that the event happens for a short duration or to a small extent. 
-By contrast, AABB expresses an increasing meaning, which indicates a repetition or action in progress. 
+By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
 \citet[Sec. 3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
@@
 The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see \sectref{sec:aspM}).
-The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
-This is probably because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent.
 
@@
 \ea\label{ex:syn-vi} Intransitive verb:
-		\ea \gll ta xiao-le.\\
+		\ea \gll \objex{ta1} \objex{xiao4-le}.\\
 		he laugh-\textsc{pfv}\\
 		\glt `He laughed.'
-		\ex \gll ta \textit{xiao}-\textit{le}-\textit{xiao}.\\
+		\ex \gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}.\\
 		he laugh-\textsc{pfv}-laugh\\
@@
 \ex Transitive verb:
-		\ea \gll ni wen ta.\\
+		\ea \gll \objex{ni3} \objex{wen4} \objex{ta1}.\\
 		you ask him\\
 		\glt `Ask him.'
-		\ex \gll ni \textit{wen}-\textit{(yi)}-\textit{wen} ta.\\
+		\ex \gll \objex{ni3} \obj{wen4}-\obj{(yi)}-\obj{wen4} \objex{ta1}.\\
 		you ask-(one)-ask he\\
@@
 \ex Under negation:
-		\ea \gll weishenme wo bu kan ta qita fangmian de jinbu he quanfangwei de chengzhang\\
-		why I not look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\
-		\glt `Why don't I look at his progress in other aspects and comprehensive development?'
-		\ex \gll weishenme wo bu \textit{kan}-\textit{kan} ta qita fangmian de jinbu he quanfangwei de chengzhang\\
-		why I not look-look he other aspect \textsc{de} progress and comprehensive \textsc{de} development\\ \jambox{({CCL})}
-		\glt `Why don't I look a little bit at his progress in other aspects and comprehensive development?'
+		\ea \gll \objex{wei4shen2me} \objex{wo3} \objex{bu4} \objex{kan4} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4} \ldots\\
+		why I not look he other aspect \textsc{de} progress\\
+		\glt `Why don't I look at his progress in other aspects?'
+		\ex \gll  \objex{wei4shen2me} \objex{wo3} \objex{bu4} \obj{kan4-kan} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4}\ldots\\
+		why I not look-look he other aspect \textsc{de} progress \\ \jambox{({CCL})}
+		\glt `Why don't I look a little bit at his progress in other aspects?'
 		\z
 
-\ex In \textit{ba}-construction:
-		\ea \gll gou-mai zhiqian zhen gai ba qingkuang mo qingchu.\\
-		purchase-buy before really should \textsc{ba} situation touch clearly\\
+\ex In a \textit{ba}-construction:
+		\ea \gll \objex{gou4-mai3} \objex{zhi1qian2} \objex{zhen1} \objex{gai1} \objex{ba3} \objex{qing2kuang4} \objex{mo1-qing1chu3}.\\
+		purchase-buy before really should \textsc{ba} situation touch-clearly\\
 		\glt `(I) should really check the situation clearly before I make the purchase.'
-		\ex \gll gou-mai zhiqian zhen gai ba qingkuang \textit{mo}-\textit{mo} qingchu.\\
-		purchase-buy before really should \textsc{ba} situation touch-touch clearly\\ \jambox{({CCL})}
+		\ex \gll \objex{gou4-mai3} \objex{zhi1qian2} \objex{zhen1} \objex{gai1} \objex{ba3} \objex{qing2kuang4} \obj{mo1-mo-qing1chu3}.\footnotemark\\
+		purchase-buy before really should \textsc{ba} situation touch-touch-clearly\\ \jambox{({CCL})}
 		\glt `(I) should really quickly check the situation clearly before I make the purchase.'
 		\z
+\footnotetext{As a reviewer comments, this example also involves the reduplication of V1 of a resultative compound.
+    This runs counter to exiting literature on this subject which consistently maintains that resultative compounds are not amenable to reduplication.}
 
 \ex With modal verb:
-		\ea \gll you liang ben shu ni-men keyi kan \ldots\\
+		\ea \gll \objex{you3} \objex{liang3} \objex{ben3} \objex{shu1} \objex{ni3-men} \objex{ke3yi3} \objex{kan4} \ldots\\
 		there.be two \textsc{clf} book you-\textsc{pl} can read\\
 		\glt `There are two books that you can read \ldots'
-		\ex \gll you liang ben shu ni-men keyi \textit{kan}-\textit{kan} \ldots\\
+		\ex \gll \objex{you3} \objex{liang3} \objex{ben3} \objex{shu1} \objex{ni3-men} \objex{ke3yi3} \obj{kan4-kan} \ldots\\
 		there.be two \textsc{clf} book you-\textsc{pl} can read-read\\ \jambox{({CCL})}
@@
 
-\ex\label{ex:syn-svc} In Serial Verb Construction (SVC):
-		\ea \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang kan nali chu-le wenti.\\
-		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look where come.out-\textsc{pfv} problem\\
-		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a look at where went wrong.'
-		\ex \gll ta dao jinian-tang dong-ce de yi chu chongxi-bu qing shifu bangmang \textit{kan}-\textit{kan} nali chu-le wenti.\\
-		she go.to memorial-hall east-side \textsc{de} one place film.developing-department ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
-		\glt `She went to a film developing department at the east side of the memorial hall to ask the master to help have a quick look at where went wrong.'
+\ex\label{ex:syn-svc} In a Serial Verb Construction (SVC):
+		\ea \gll \objex{ta1} \ldots\, \objex{qing3} \objex{shi1fu} \objex{bang1mang2} \objex{kan4} \objex{na3li3} \objex{chu1-le} \objex{wen4ti1}.\\
+		she {}  ask master help look where come.out-\textsc{pfv} problem\\
+		\glt `She \ldots\, asked the master to help have a look at where went wrong.'
+		\ex \gll \objex{ta1} \ldots\, \objex{qing3} \objex{shi1fu} \objex{bang1mang2} \obj{kan4-kan} \objex{na3li3} \objex{chu1-le} \objex{wen4ti1}.\\
+		she {} ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
+		\glt `She \ldots\, asked the master to help have a quick look at where went wrong.'
+		\z
 \z
 
-\ex With an expression of quantity: \label{ex:syn-quan}
-		\ea[]{\gll ta yi tian pao shi li.\\
+The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
+This is  because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent,
+which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}; \citealt[333]{SuiHu2016}).
+
+\ea %With an expression of quantity: 
+\label{ex:syn-quan}
+		\ea[]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \objex{pao3} \objex{shi2} \objex{li3}.\\
 		he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
 		\glt `He runs ten miles a day.'}
-		\ex[*]{\gll ta yi tian \textit{pao}-\textit{pao} shi li.\\
+		\ex[*]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \obj{pao3}-\obj{pao3} \objex{shi2} \objex{li3}.\\
 		he one day run-run ten mile\\}
@@
 In this section, we will first discuss the core meaning of the reduplication as well as the meaning of its different forms (\sectref{sec:core-sem}).
-We will then investigate the interaction of the reduplication with \textit{Aktionsarten} (\sectref{sec:Aktionsarten}) and aspect markers (\sectref{sec:aspM}).
+We will then investigate the interaction of the reduplication with verb classes (\sectref{sec:Aktionsarten}) and aspect markers (\sectref{sec:aspM}).
 
@@
 and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
-Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
+Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
 ``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
-\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication, as well.
- \citet[276]{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
- \citet[Sec. 3.1.3]{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.
+\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet[276]{Fan1964}, \citet[15]{Li1996} and \citet[1]{Qian2000} as the meaning of reduplication as well.
+ \citet[276]{Fan1964} further proposes a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
+ \citet[Sec. 3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.
 
-In general, all of the above cited research agreed that the reduplication expresses a short duration and/or a low frequency, which fits the definition of delimitativeness.
-\citet[152--154]{XiaoMcEnery2004} and \citet{Yang2003} argued that the core meaning of reduplication is delimitativeness, 
+In general, all of the above cited research agree that the reduplication expresses a short duration and/or a low frequency, which fits the definition of delimitativeness.
+\citet[152--154]{XiaoMcEnery2004} and \citet{Yang2003} argue that the core meaning of reduplication is delimitativeness, 
 while all other meanings are merely pragmatic extensions  in specific contexts.
-\citet[152--154]{XiaoMcEnery2004} pointed out that tentativeness and casualness are constrained by a number of contextual elements 
+\citet[152--154]{XiaoMcEnery2004} points out that tentativeness and casualness are constrained by a number of contextual elements 
 such as the reduplicated verb must be volitional and the subject of the sentence must be animate.
@@
 Among all instances of verbal reduplication they found in a corpus, all of them have a delimitative reading, while only some of them convey tentativeness or casualness.
-\citet{Yang2003} compared the sentence pairs with reduplicated verbs and their unreduplicated counterparts,
-and showed that the reduplication itself does not add a tentative, frequentative, casualness or increased agency meaning to the sentence.
+\citet{Yang2003} compares the sentence pairs with reduplicated verbs and their unreduplicated counterparts,
+and shows that the reduplication itself does not add a tentative, frequentative, casualness or increased agency meaning to the sentence.
 Rather, these additional meanings arise from the sentences or the contexts as a whole.
-She concluded that these additional meanings are results of meaning extensions of delimitativeness in specific contexts.
+She concludes that these additional meanings are results of meaning extensions of delimitativeness in specific contexts.
 We follow \citet{XiaoMcEnery2004} and \citet{Yang2003} and treat delimitativeness as the central meaning of reduplication,
@@
   \ea\label{ex:le-dyn-look}
-    \gll Wu Xumang kan-le zuo-an shi liuxia de jiaoyin \ldots\\ 
+    \gll \objex{Wu2} \objex{Xu4mang2} \objex{kan4-le} \objex{zuo4-an4} \objex{shi2} \objex{liu2xia4} de \objex{jiao3yin1} \ldots\\ 
     Wu Xumang look-\textsc{pfv} commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
@@
   \ex\label{ex:redup-dyn-look}
-    \gll Wu Xumang \textit{kan-le-kan} zuo-an shi liuxia de jiaoyin \ldots\\
+    \gll  \objex{Wu2} \objex{Xu4mang2} \objex{kan4-le-kan4} \objex{zuo4-an4} \objex{shi2} \objex{liu2xia4} de \objex{jiao3yin1} \ldots\\
     Wu Xumang look-\textsc{pfv}-look commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
@@
 
-As for A-\textit{yi}-A, \citet[273]{Fan1964} compared examples found in novels and plays and concluded that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
+As for A-\textit{yi}-A, \citet[273]{Fan1964} compares examples found in novels and plays and concludes that A-\textit{yi}-A has exactly the same meaning as its AA counterpart.
 She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
-\citet[Sec. 5]{Xing2000} considered that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
-The former conveys a casual attitude whereas the latter sounds more serious.
+\citet[Sec. 5]{Xing2000} considers that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
+The former conveys a casual attitude whereas the latter sounds more serious.%\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
 However, he stressed that there is no difference in the delimitative semantics of both forms,
@@
 The difference is also not absolute and often only shows a tendency.
-\citet{Xu2002} found out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
-But he also stated that these differences are pragmatic rather than semantic, 
-as he argued that AA and A-\textit{yi}-A can be used interchangeably in most cases,
+\citet{Xu2002} finds out that compared to A-\textit{yi}-A, one tends to use AA in contexts with strong emotional attitudes, urgent, casual, timid or uncertain contexts.
+But he also states that these differences are pragmatic rather than semantic, 
+as he argues that AA and A-\textit{yi}-A can be used interchangeably in most cases,
 and the specific differences in meaning only arise from specific contexts as a whole.
-\citet[15]{Yang2003} suggested that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
+\citet[15]{Yang2003} suggests that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
 We assume A-\textit{yi}-A to be a form of reduplication and that it has the same core semantics as AA.
 
-AA-\textit{kan} and A-\textit{kan}-\textit{kan} are described to express a ``try \ldots and find out'' meaning \citep[63]{Cheng2012}.
-\citet[290]{Tsao2001} also observed that the tentative meaning is particularly prominent when the reduplication is followed by \textit{kan} `look'.
+AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} are described to express a ``try \ldots\, and find out'' meaning \citep[63]{Cheng2012}.
+\citet[290]{Tsao2001} also observes that the tentative meaning is particularly prominent when the reduplication is followed by \obj{kan4} `look'.
 We still consider the tentativeness implied by these two forms to be a pragmatic extension of delimitativeness.
-The tentative meaning is made prominent by the verb \textit{kan} `look',
+The tentative meaning is made prominent by the verb \obj{kan4} `look',
 and the whole structure can be understood as ``do A a little bit and see''.
@@
 %%%%%%%%
-\subsubsection{Interaction with \textit{Aktionsarten}}\label{sec:Aktionsarten}
+\subsubsection{Interaction with verb classes}\label{sec:Aktionsarten}
 
-Previous research often claimed that the reduplication can only be used for verb classes of certain \textit{Aktionsarten}, while it is infelicitous for other ones.
- \citet[234--235]{LiThompson1981} and \citet[277--278]{Hong1999} suggested that reduplication is only possible for volitional activity verbs.
-\citet[70--71]{Dai1997} und \citet[290]{Tsao2001} both considered that reduplication can only be used in dynamic situations.
-The former further claimed that achievement verbs cannot be reduplicated.
- \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet[145]{BascianoMelloni2017} proposed that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
+The current study adopts the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
+The general term ``aspect'' is considered to encompass the following two components:
+situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
+and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
+Situation aspect can be further modeled as verb classes  at the lexical level
+and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
+The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
+where everything that might change the aspectual value of a verb is excluded
+and only the inherent features of the verb itself are considered
+(see \citealt[52]{XiaoMcEnery2004} for more details).
+This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
+but its verb class remains the same,
+as the aspectual change can be attributable to other components at the sentential level.
+This section is concerned with the interaction of the reduplication with verb classes,
+while Section~\ref{sec:asp} discusses the interaction with viewpoint aspect markers.
+%The combination with other constituents such as adjuncts is briefly touched upon below,
+%but a detailed discussion has to be left for future research.
+
+Previous research often claims that the reduplication can only be used for certain verb classes, while it is infelicitous for other ones.
+ \citet[234--235]{LiThompson1981} and \citet[277--278]{Hong1999} suggest that reduplication is only possible for volitional activity verbs.
+\citet[70--71]{Dai1997} and \citet[290]{Tsao2001} both consider that reduplication can only be used in dynamic situations.
+The former further claims that achievement verbs cannot be reduplicated.
+ \citet[155]{XiaoMcEnery2004}, \citet[20]{Arcodiaetal2014} and \citet[145]{BascianoMelloni2017} propose that only [$+$dynamic] and [$-$result] verbs can be reduplicated.
 This means that the reduplication can only interact with dynamic situations which encode no results and is consequently only compatible with activities and semelfactives, but not with states and achievements.
 
-\citet[53]{Chen2001} and \citet[10--11]{Yang2003} acknowledged that the reduplication of non\hyp{}vo\-li\-tion\-al verbs is more restricted than that of volitional ones.
-But \citet[381--382]{Zhu1998} listed a number of non\hyp{}volitional predicates that can be reduplicated.
-We found the examples shown in (\ref{ex:nonvol}) in {CCL} where non\nobreakdash-vo\-li\-tion\-al verbs \textit{weiqu} `feel wronged', \textit{ren-xing} `be willful' and \textit{diao} `drop' are reduplicated.
+\citet[53]{Chen2001} and \citet[10--11]{Yang2003} acknowledge that the reduplication of non\hyp{}vo\-li\-tion\-al verbs is more restricted than that of volitional ones.
+But \citet[381--382]{Zhu1998} lists a number of non\hyp{}volitional predicates that can be reduplicated.
+We found the examples shown in (\ref{ex:nonvol}) in {CCL} where non\nobreakdash-vo\-li\-tion\-al verbs \obj{wei3qu1} `feel wronged', \obj{ren4-xing4} `be willful' and \obj{diao4} `drop' are reduplicated.
 

### 2024-08-18 main.tex
Update 2024-08-18-17:19:01

@@
 
-\rightrunning{An HPSG account for verbal reduplication in Mandarin Chinese} % Short title
+\rightrunning{An HPSG account for deliminative verbal reduplication in Mandarin Chinese} % Short title
 
-\title{An HPSG account for verbal reduplication in Mandarin Chinese}
+\title{An HPSG account for deliminative verbal reduplication in Mandarin Chinese}
 
@@
 \begin{abstract}
-The current study presents an HPSG analysis for verbal reduplication in Mandarin Chinese.
+The current study presents an HPSG analysis for deliminative verbal reduplication in Mandarin Chinese.
 We provide a detailed description of the phenomenon.
-After discussing reduplication’s interaction with \textit{Aktionsarten} and aspect markers, we argue that it is a morphological rather than a syntactic process.
+After discussing reduplication’s interaction with \textit{Aktionsarten} and aspect markers, we argue that it is better analyzed as a morphological rather than a syntactic process.
 We put forward a lexical rule for verbal reduplication in Mandarin Chinese, and the different forms of reduplication are captured in an inheritance hierarchy.
 The interaction between verbal reduplication and aspect marking is handled by multiple inheritance.
-This analysis covers all forms of verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
+This analysis covers all forms of deliminative verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
 \keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}

### 2024-08-18 chapters/ch02-Phenomenon.tex
Update 2024-08-18-18:13:08

@@
 The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:syn-vi})--(\ref{ex:syn-svc}). 
-The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (for further discussions see \sectref{sec:aspM}).
+This suggests that a reduplicated verb can be treated as its unreduplicated counterpart in syntax (see \sectref{sec:word}).
+The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (see \sectref{sec:aspM} for further discussions on interactions with aspect markers). 
+The reduplication also cannot co-occur with an expression that quantifies the duration or the extent of the event described by the sentence due to its semantic properties (see \sectref{sec:adjuncts}).
 
@@
 
-The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
-This is  because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent,
-which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}; \citealt[333]{SuiHu2016}).
-
-\ea %With an expression of quantity: 
-\label{ex:syn-quan}
-		\ea[]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \objex{pao3} \objex{shi2} \objex{li3}.\\
-		he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
-		\glt `He runs ten miles a day.'}
-		\ex[*]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \obj{pao3}-\obj{pao3} \objex{shi2} \objex{li3}.\\
-		he one day run-run ten mile\\}
-		\z
-\z
 \end{sloppypar}
@@
 
+As shown in Section~\ref{sec:intro}, the reduplication seems to be connected to certain aspectual properties.
+The current study adopts the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
+The general term ``aspect'' is considered to encompass the following two components:
+situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
+and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
+Situation aspect can be further modeled as verb classes  at the lexical level
+and situation types (the interaction of verb classes and other constituents, such as adjuncts) at the sentential level \citep[33]{XiaoMcEnery2004}.
+The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
+where everything that might change the aspectual value of a verb is excluded
+and only the inherent features of the verb itself are considered
+(see \citealt[52]{XiaoMcEnery2004} for more details).
+This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
+but its verb class remains the same,
+as the aspectual change can be attributable to other components at the sentential level.
+%This section is concerned with the interaction of the reduplication with verb classes,
+%while Section~\ref{sec:asp} discusses the interaction with viewpoint aspect markers.
+%The combination with other constituents such as adjuncts is briefly touched upon below,
+%but a detailed discussion has to be left for future research.
+
 In this section, we will first discuss the core meaning of the reduplication as well as the meaning of its different forms (\sectref{sec:core-sem}).
-We will then investigate the interaction of the reduplication with verb classes (\sectref{sec:Aktionsarten}) and aspect markers (\sectref{sec:aspM}).
+We will then investigate the interaction of the reduplication with verb classes (\sectref{sec:Aktionsarten}), adjuncts (\sectref{sec:adjuncts}) and aspect markers (\sectref{sec:aspM}).
 
@@
 \subsubsection{Interaction with verb classes}\label{sec:Aktionsarten}
-
-The current study adopts the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
-The general term ``aspect'' is considered to encompass the following two components:
-situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
-and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
-Situation aspect can be further modeled as verb classes  at the lexical level
-and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
-The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
-where everything that might change the aspectual value of a verb is excluded
-and only the inherent features of the verb itself are considered
-(see \citealt[52]{XiaoMcEnery2004} for more details).
-This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
-but its verb class remains the same,
-as the aspectual change can be attributable to other components at the sentential level.
-This section is concerned with the interaction of the reduplication with verb classes,
-while Section~\ref{sec:asp} discusses the interaction with viewpoint aspect markers.
-%The combination with other constituents such as adjuncts is briefly touched upon below,
-%but a detailed discussion has to be left for future research.
 
@@
 and non\hyp{}volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.
+
+%%%%%%%%%
+\subsubsection{Interaction with adjuncts}\label{sec:adjuncts}
+
+The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
+This is  because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent,
+which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}; \citealt[333]{SuiHu2016}).
+This results from the properties of reduplication rather than the verb itself,
+as the verb itself can be combined with such an expression (\ref{ex:syn-quana}).
+
+\ea %With an expression of quantity: 
+\label{ex:syn-quan}
+\ea[]{\label{ex:syn-quana}\gll \objex{ta1} \objex{yi4} \objex{tian1} \objex{pao3} \objex{shi2} \objex{li3}.\\
+    he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
+    \glt `He runs ten miles a day.'}
+\ex[*]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \obj{pao3}-\obj{pao3} \objex{shi2} \objex{li3}.\\
+    he one day run-run ten mile\\}
+\z
+\z
 

### 2024-08-18 chapters/ch02-Phenomenon.tex
Update 2024-08-18-20:25:30

@@
 This suggests that a reduplicated verb can be treated as its unreduplicated counterpart in syntax (see \sectref{sec:word}).
-The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (see \sectref{sec:aspM} for further discussions on interactions with aspect markers). 
+The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (see \sectref{sec:aspM}).% for further discussions on interactions with aspect markers). 
 The reduplication also cannot co-occur with an expression that quantifies the duration or the extent of the event described by the sentence due to its semantic properties (see \sectref{sec:adjuncts}).

### 2024-08-18 chapters/ch02-Phenomenon.tex
Update 2024-08-18-22:12:26

@@
 		say-say-look\\ \jambox{AA-\obj{kan4}}
-		\ex \gll \objex{shuo1-kan4-kan4}\footnotemark\\
-		 say-look-look\\ \jambox{A-\obj{kan4}-\obj{kan4}}
+		\ex \gll \objex{shuo1-kan4-kan4}\\
+		 say-look-look\\ \jambox{A-\obj{kan4}-\obj{kan4}\footnotemark}
 		\z
@@
 \ea
-\gll keshi xian mujin, dajia ye zhihao \textit{weiqu-weiqu} le.\\
-but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
+\gll \objex{ke3shi4} \objex{xian4mu4jin1}, \objex{da4jia1} \objex{ye3} \objex{zhi3hao3} \obj{wei3qu1-wei3qu1} le.\\
+but now  everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
 \glt `But now, everybody can only feel wronged a little bit.'
@@
 \ex
-\gll ta-men neng zuo de buguo shi \textit{ren-ren-xing} shua dian'er xiao piqi \textit{diao-diao} yanlei shenme de.\\
-she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \jambox{({CCL})}
+\gll \objex{ta1-men} \objex{neng2} \objex{zuo4} de \objex{bu2guo4} \objex{shi4} \obj{ren4-ren4-xing4}, \objex{shua3} \objex{dian3'er} \objex{xiao3} \objex{pi2qi4}, \obj{diao4-diao} \objex{yan3lei4} \objex{shen2mede}.\\
+she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \\ \jambox{({CCL})}
 \glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
@@
 It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
-Compared to the questionable reduplication of the stative verb \textit{bing} `be sick' in (\ref{ex:redup-stat})
-and that of the achievement verb \textit{ying} `win' in (\ref{ex:redup-achiV}), 
+\citep[155]{XiaoMcEnery2004} classify \obj{bing4} `be sick' as a stative verb.
+Indeed, compared  to the questionable reduplication of \obj{bing4} `be sick' in (\ref{ex:redup-stat}),  
  the reduplication of the activity verb \textit{kan} `watch' in (\ref{ex:redup-actV})
-and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) is readily acceptable.
+and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) are readily acceptable.
 
@@
 \ea[?]
-{\gll ta \textit{bing-bing} jiu hao le.\\
+{\gll \objex{ta1} \obj{bing4-bing} \objex{jiu4} \objex{hao3} le.\\
 he be.sick-be.sick then well \textsc{ptc}\\ \jambox{\citep[155]{XiaoMcEnery2004}}
@@
 
-\ex[?]
-{\gll ta \textit{ying}-\textit{le}-\textit{ying} na chang bisai.\\
-he win-\textsc{pfv}-win that \textsc{clf} competition\\ \jambox{\citep[155]{XiaoMcEnery2004}}
-\glt Intended: `He won that competition a little bit.'}\label{ex:redup-achiV}
-
 \ex[]
-{\gll ta \textit{kan}-\textit{le}-\textit{kan} na chang bisai.\\
+{\gll \objex{ta1} \obj{kan4}-\obj{le}-\obj{kan4} \objex{na4} \objex{chang3} \objex{bi3sai4}.\\
 he watch-\textsc{pfv}-watch that \textsc{clf} competition\\
@@
 \ex[]
-{\gll ta \textit{kesou-kesou} jiu hao le.\\
+{\gll \objex{ta1} \obj{ke2sou4-ke2sou4} \objex{jiu4} \objex{hao3} le.\\
 he cough-cough then well \textsc{ptc}\\
@@
 
-However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
-Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.
+However, examples such as (\ref{ex:redup-achi-stat4}) can be found where \obj{bing4} `be sick' is reduplicated.
+
+\ea\label{ex:redup-achi-stat4}
+\gll \objex{wo3} \objex{zhen1} \objex{xiang3} \obj{bing4-yi-bing4}, \objex{xie1} \objex{ta1} \objex{ge} \objex{shi2} \objex{tian1} \objex{ban4} \objex{yue4}.\\
+I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
+\glt `I really want to be sick for a little while and rest for ten days or half a month.'
+\z
+
+As a reviewer points out, \citet[Sec. 3.3]{Tham2013} considers  \obj{bing4} `be sick' to be a basic change of state (COS) verb, i.e. `become sick'.
+In contrast, she uses \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as examples of stative verbs.
+\citet[680]{PeckEtAl2013} also list \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as stative verbs.
+For these two verbs, examples such as (\ref{ex:xihuan}) and (\ref{ex:xiangxin}) can be found.
+\ea\label{ex:xihuan}%这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
+\gll \objex{zhe4} \objex{che1} \objex{hao3} \objex{xing2} \objex{a}! \objex{zen3me} \objex{le}, \objex{wo3} \objex{jiu4} \obj{xi3huan1-xi3huan4} \objex{bu4xing2} \objex{me}?\\
+this car so cool \textsc{ptc} what \textsc{ptc} I just like-like cannot \textsc{ptc}\\\jambox{(BCC)}
+\glt `This car is so cool! What? I can't just like it for a little bit?'
+
+\ex\label{ex:xiangxin}%谁让我来相信相信 (CCL)
+\gll \objex{shei2} \objex{rang4} \objex{wo3} \objex{lai2} \objex{xiang1xin4-xiang1xin4}\\
+who let I come believe-believe\\\jambox{(CCL)}
+\glt `Who lets me believe him/her?'
+\z
+
+On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
+and indeed \citet[669--670]{Tham2013} herself noted,
+verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
+let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
+and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
+as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
+    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
+    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
+    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
+    these predicates are not included in our examples.}
+The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
+\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
+Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
+\objex{Wang2} Ān\objex{yu3} is another actor in the series.\\
+\\
+\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}.
+\objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
+Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
+\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'
+
+\ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
+\objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3} \ldots\\
+she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
+\glt `She \ldots\, really needs her mother to be present on scene for a little while \ldots'
+\z
+\footnotetext{\url{https://www.163.com/dy/article/FS1FKUC30534DZO1.html} (Accessed 26th  March 2024).}
+
+One might argue that even in the examples above, dynamic rather than stative meaning is conveyed.
+We argue that the dynamic interpretation does not come from the verb but from reduplication.
+The use of reduplication affects the situation aspect at the sentential level.
+And as we describe in \sectref{sec:core-sem}, the semantics of reduplication has the property dynamicity.
+Verbs such as \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene' are stative in a neutral context and thus, we consider the intrinsic feature of these verbs to be stative
+and they should be classified as stative verbs.
+The dynamic interpretation only arises when they are used in specific contexts, in this case, when they are reduplicated.
+
+Similar to stative verbs, the reduplication of achievement verbs is also not readily acceptable,
+as shown in (\ref{ex:redup-achiV}) with reduplication of \obj{ying2} `win'.
+
+\ea[?]
+{\gll \objex{ta1} \obj{ying2}-\obj{le}-\obj{ying2} \objex{na2} \objex{chang3} \objex{bi3sai4}.\\
+    he win-\textsc{pfv}-win that \textsc{clf} competition\\ \jambox{\citep[155]{XiaoMcEnery2004}}
+    \glt Intended: `He won that competition a little bit.'}\label{ex:redup-achiV}
+\z
+
+However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat5}) can be found.
+Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' are reduplicated.
 
@@
 
-\footnotetext[2]{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
-\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
-\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
+%\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
+%\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
 %\begin{sloppypar}
@@
 \ea\label{ex:redup-achi-stat1}
-\gll deng ren-men ba zhe jian shi \textit{wang}-\textit{wang} zai shuo ba.\footnotemark\\
+\gll \objex{deng3} \objex{ren2-men} ba \objex{zhe4} \objex{jian4} \objex{shi4} \obj{wang4}-\obj{wang} \objex{zai4} \objex{shuo1} ba.\footnotemark\\
 wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
 \glt `Let's wait until people forget this incident a little bit and then talk about it.'\\
+\footnotetext{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
+%\ex\label{ex:redup-achi-stat2}
+%\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
+%later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
+%\glt `Let's take a bath later and be comfortable for a little while.'\\
 
-\ex\label{ex:redup-achi-stat2}
-\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
-later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
-\glt `Let's take a bath later and be comfortable for a little while.'\\
+%\ex\label{ex:redup-achi-stat3}
+%\gll \textit{lian}-\textit{lian}-\textit{ai} shi keyi de, ban xishi dinghao chi yidian.\footnotemark\\
+%like-like-love \textsc{cop} ok \textsc{de} host wedding best late a.bit\\
+%\glt `It's ok to be in love a little bit, but it's better to get married a bit later.'\\
 
-\ex\label{ex:redup-achi-stat3}
-\gll \textit{lian}-\textit{lian}-\textit{ai} shi keyi de, ban xishi dinghao chi yidian.\footnotemark\\
-like-like-love \textsc{cop} ok \textsc{de} host wedding best late a.bit\\
-\glt `It's ok to be in love a little bit, but it's better to get married a bit later.'\\
-
-\ex\label{ex:redup-achi-stat4}
-\gll wo zhen xiang \textit{bing-yi-bing}, xie ta ge shi tian ban yue.\\
-I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
-\glt `I really want to be sick for a little while and rest for ten days or half a month.'
+\ex\label{ex:sheng}%我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
+\gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi}\ldots \\
+we women {} only can give.birth.to-give.birth.to child\\\jambox{(BCC)}
+\glt `We women can only give birth to children \ldots'
 
 \ex\label{ex:redup-achi-stat5}
-\gll jiao ta \textit{sheng-sheng} xiaohai, jiu zhidao zuo muqin de gan-ku le.\\
+\gll \objex{jiao4} \objex{ta1} \obj{sheng1-sheng1} \objex{xiao3hai2}, \objex{jiu4} \objex{zhi1dao4} \objex{zuo4} \objex{mu3qin1} de \objex{gan1-ku3} le.\\
 let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
@@
 
-This shows that although the reduplication does have a tendency to interact with volitional verbs and with activities and semelfactives due to its dynamic meaning, 
+The reduplication does not seem to cancel the \textit{telos} of achievements.
+Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
+\ea
+\ea[]{\label{ex:teloa}% 一块... 到附近市场买买东西 (CCL)
+    \gll \objex{yi2kuai4} \ldots\, \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\ldots\\
+    together {} arrive nearby market buy-buy thing\\\jambox{(CCL)}
+    \glt `(We) together \ldots\, went to the market nearby to buy some things.'}
+
+\ex[]{\label{ex:telob}% 两天后到附近市场买买东西
+    \gll \objex{liang3} \objex{tian1} \objex{hou4} \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}.\\
+    two day later arrive nearby market buy-buy thing\\
+    \glt `Two days later, (we) went to the market nearby to buy some things.}
+
+\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
+    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}.\\
+    arrive nearby market buy-buy thing two day\\
+    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
+\z\z
+The following continuation that cancels the \textit{telo} is also infelicitous (\ref{ex:telod}).
+\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
+\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}.\\
+arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
+\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
+\z
+These tests suggest that the reduplicated verbs are indeed achievements,
+rather than being used as activities.
+
+The examples presented in this section show that although the reduplication does have a tendency to interact with volitional verbs and with activities and semelfactives due to its dynamic meaning, 
 this is by no means a rigid constraint, 
-and non\hyp{}volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.
+and non\hyp{}volitional verbs, states and achievements can be reduplicated in appropriate contexts as well,
+ contrary to common beliefs in the literature.
+Thus, a theoretical account of reduplication should not restrict its use to only certain verb classes.
 

### 2024-08-19 replies-reviews.tex
Update 2024-08-19-15:50:11

@@
 
-Due to its unique features compared to the perfective aspect marker \textit{le} and the experiential aspect marker \textit{guo4},
+Due to its unique features compared to the perfective aspect marker \obj{le} and the experiential aspect marker \obj{guo4},
 the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.

### 2024-08-19 chapters/ch02-Phenomenon.tex
Update 2024-08-19-15:50:11

@@
 In this section, we will first discuss the core meaning of the reduplication as well as the meaning of its different forms (\sectref{sec:core-sem}).
-We will then investigate the interaction of the reduplication with verb classes (\sectref{sec:Aktionsarten}), adjuncts (\sectref{sec:adjuncts}) and aspect markers (\sectref{sec:aspM}).
+We will then investigate the interaction of the reduplication with verb classes (\sectref{sec:Aktionsarten}), aspect markers (\sectref{sec:aspM}) and other sentential components (\sectref{sec:adjuncts}) .
 
@@
 
+%%%%%%%%
+\subsubsection{Interaction with aspect markers}\label{sec:aspM}
+
+As mentioned in \sectref{sec:forms}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
+There is no consensus on which elements exactly are considered aspect markers in Mandarin Chinese. 
+We only discuss the most commonly recognized ones here.
+}
+We believe this incompatibility to be for semantic reasons.
+
+\citet[Ch. 4]{XiaoMcEnery2004} consider \obj{le}, \obj{guo4} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
+The perfective aspect marker \obj{le} is compatible with reduplication while the experiential aspect marker \obj{guo4} is not.
+\citet[128--131]{XiaoMcEnery2004} stated that \obj{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
+It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
+It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).
+
+\settowidth\jamwidth{\citep[129]{XiaoMcEnery2004}}
+
+\ea
+  \ea\label{ex:cry}
+    \gll \objex{wei4ci3}, \objex{Deng4} \objex{Li4jun1} \objex{shang1xin1} \objex{de} \objex{ku1-le} \objex{san1} \objex{tian1}.\\
+    for.this Deng Lijun sadly \textsc{de} cry-\textsc{pfv} three day\\ \jambox{\citep[129]{XiaoMcEnery2004}}
+    \glt `For this reason, Deng Lijun cried sadly for three days.'
+  \ex\label{ex:know}
+    \gll \objex{ta1} \objex{zhi1dao4-le} \objex{zhe4} \objex{shi4} de \objex{nei4-qing2}.\\
+    he know-\textsc{pfv} this matter \textsc{de} inside-information\\ \jambox{\citep[130]{XiaoMcEnery2004}}
+    \glt `He got to know the inside information on this matter.'
+  \z
+\z
+\obj{Le} is compatible with the reduplication, because its dynamicity can relate to not only the termination or instantiation of an event (a point of change), but also the process of the situation, just like that of the reduplication (see \sectref{sec:core-sem}).
+
+In comparison, the experiential aspect marker \obj{guo4} cannot co\hyp{}occur with a reduplicated verb, 
+because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
+namely that a situation has been experienced historically and that ``the final state of the situation no longer obtains'' at the reference time \citep[144]{XiaoMcEnery2004}. 
+Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \obj{guo4} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
+whereas \obj{le} in (\ref{ex:le-dyn}) conveys a change into the state of being a soldier \citep[149]{XiaoMcEnery2004}.
+
+\ea
+  \ea\label{ex:guo-dyn}
+    \gll \objex{ta1} \objex{dang1-guo4} \objex{bing1}.\\
+    he serve.as-\textsc{exp} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
+    \glt `He once served as a soldier.'
+  \ex\label{ex:le-dyn}
+    \gll \objex{ta1} \objex{dang1-le} \objex{bing1}.\\
+    he serve.as-\textsc{pfv} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
+    \glt `He became a soldier.'
+  \z
+\z
+It is clear that \obj{guo4} only indicates a change at the termination of a situation and cannot express the dynamicity within a situation.
+Hence, it is incompatible with the semantics of the reduplication.
+
+Due to the holistic semantics of the reduplication, it is incompatible with imperfective aspect markers: the durative aspect marker \obj{zhe} and the progressive aspect marker \obj{zai4}, as both only focus on  a part of the situation and do not view the situation as a whole \citep[Ch.
+5]{XiaoMcEnery2004}.
+
+From the illustration above, it seems that due to its semantics, reduplication can only be marked by \obj{le} but not the other aspect markers.
+
 %%%%%%%%%
-\subsubsection{Interaction with adjuncts}\label{sec:adjuncts}
+\subsubsection{Interaction with other sentential components}\label{sec:adjuncts}
 
@@
 
-%%%%%%%%
-\subsubsection{Interaction with aspect markers}\label{sec:aspM}
-
-As mentioned in Section \ref{sec:forms}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
-There is no consensus on which elements exactly are considered aspect markers in Mandarin Chinese. We only discuss the most commonly recognized ones here.
-}
-We believe this incompatibility to be for semantic reasons.
-
-\citet[Ch. 4]{XiaoMcEnery2004} considered \textit{le}, \textit{guo} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
-The perfective aspect marker \textit{le} is compatible with reduplication while the experiential aspect marker \textit{guo} is not.
-\citet[128--131]{XiaoMcEnery2004} stated that \textit{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
-It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
-It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).
-
-\settowidth\jamwidth{\citep[129]{XiaoMcEnery2004}}
-
-\ea
-  \ea\label{ex:cry}
-    \gll Weici, Deng Lijun shangxin de ku-le san tian.\\
-    for.this Deng Lijun sadly \textsc{de} cry-\textsc{pfv} three day\\ \jambox{\citep[129]{XiaoMcEnery2004}}
-    \glt `For this reason, Deng Lijun cried sadly for three days.'
-  \ex\label{ex:know}
-    \gll Ta zhidao-le zhe shi de nei-qing.\\
-    he know-\textsc{pfv} this matter \textsc{de} inside-information\\ \jambox{\citep[130]{XiaoMcEnery2004}}
-    \glt `He got to know the inside information on this matter.'
+A reviewer also notes that the reduplication appears frequently in imperative (example \ref{ex:redup-achi-stat1}) and conditional sentences (\ref{ex:cond}) as well as causative sentences with \obj{rang4}\slash\obj{jiao4}\slash\obj{shi3} `let/let/make' (examples \ref{ex:xiangxin}, \ref{ex:xiang}, \ref{ex:redup-achi-stat5}).
+\ea\label{ex:cond}
+\gll \objex{ni3} \objex{yao4shi4} \objex{gei3} \objex{wo3} \obj{zhi3-zhi} \objex{Li3-jia1} \objex{de} \objex{men2}, \objex{wo3} \objex{yuan4} \objex{gei3} \objex{ni3} \objex{gui4xia4}\\
+you if give I point-point Li-family \textsc{de} door I be.willing.to give you kneel.down\\\jambox{\citep[157]{XiaoMcEnery2004}}
+\glt `If you point at the door of Li's for me, I am willing to kneel down for you.'
 \z
-\z
-\textit{Le} is compatible with the reduplication, because its dynamicity can relate to not only the termination or instantiation of an event (a point of change), but also the process of the situation, just like that of the reduplication.
-
-In comparison, the experiential aspect marker \textit{guo} cannot co\hyp{}occur with a reduplicated verb, 
-because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
-namely that a situation has been experienced historically and that ``the final state of the situation no longer obtains'' at the reference time \citep[144]{XiaoMcEnery2004}. 
-Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \textit{guo} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
-whereas \textit{le} in (\ref{ex:le-dyn}) conveys a change into the state of being a soldier \citep[149]{XiaoMcEnery2004}.
-
-\ea
-  \ea\label{ex:guo-dyn}
-    \gll ta dang-guo bing.\\
-    he serve.as-\textsc{exp} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
-    \glt `He once served as a soldier.'
-  \ex\label{ex:le-dyn}
-    \gll ta dang-le bing.\\
-    he serve.as-\textsc{pfv} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
-    \glt `He became a soldier.'
-  \z
-\z
-It is clear that \textit{guo} only indicates a change at the termination of a situation and cannot express the dynamicity within a situation.
-Hence, it is incompatible with the semantics of the reduplication.
-
-Due to the holistic semantics of the reduplication, it is incompatible with imperfective aspect markers: the durative aspect marker \textit{zhe} and the progressive aspect marker \textit{zai}, as both only focus on  a part of the situation and do not view the situation as a whole \citep[Ch.
-5]{XiaoMcEnery2004}.
-
-From the illustration above, it seems that due to its semantics, reduplication can only be marked by \textit{le} but not the other aspect markers.
+This can  be attributed to the holistic semantics of reduplication (see \sectref{sec:core-sem}).
+%Due to its unique features compared to the perfective aspect marker \obj{le} and the experiential aspect marker \obj{guo4},
+As illustrated in \sectref{sec:aspM}, \obj{le} expresses a situation being realized,
+while \obj{guo4} conveys a situation already experienced,
+and thus, both rarely occur in future situations.
+The use of reduplication does not have these constraints.
+This makes the reduplication the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
+This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts,
+which are frequently used to describe future situations.
 

### 2024-08-19 replies-reviews.tex
Update 2024-08-19-20:05:18

@@
  Corpus data is generally natural and contextualized, which can be helpful when evaluating the examples through introspection \citep[921]{MM2009a}.
- In the case of this study, the corpus data mainly shows that stative verbs and achievements can also be reduplicated in certain contexts, contrary to the claims in previous studies.
+ In the case of this study, the corpus data shows that certain syntactic and semantic constraints that previous studies claim for reduplication in fact do not apply.
 Example sentences retrieved from the corpora are marked with their sources (``CCL'' or ``BCC'') behind them,
@@
 
-\textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category of the input.
+\textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category or valency of the input.
 To improve readability, English examples are used instead.

### 2024-08-19 chapters/ch02-Phenomenon.tex
Update 2024-08-19-20:05:18

@@
 The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
-\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981} and \citet[4--5]{Liao2014} listed reduplication under morphological processes. 
-By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claimed it to be syntactic.
+\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec. 4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
+By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claim it to be syntactic.
 %And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
-This section reviews the arguments in \citet{Xie2020}, applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
-and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
-(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
-The results argue for a morphological status of reduplication.
+This section reviews the arguments in \citet{Xie2020},
+and applies tests from \citeauthor{Dai1992} (\citeyear[Sec. 7]{Dai1992}, \citeyear[Sec. 2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
+ %applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
+%and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
+%(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
+The results argue for a morphological analysis of reduplication.
 
-\citet{Xie2020} compared the AA and the ABAB forms of reduplication with the AABB form and claimed that AA and ABAB are syntactic processes while AABB is morphological.
-She pointed out that AA and ABAB behave differently from AABB in their productivity, possibility of \textit{le} insertion, categorial stability, transitivity, and input/output constraints.
+\citet{Xie2020} compares the AA and the ABAB forms of reduplication with the AABB form and claims that AA and ABAB are syntactic processes while AABB is morphological.
+She points out that AA and ABAB behave differently from AABB in their productivity, possibility of \obj{le} insertion, categorial stability, transitivity, and input/output constraints.
 While AA and ABAB are highly productive, AABB shows low productivity. 
-\textit{Le} can be inserted freely into AA (\ref{ex:le-insertionAA}) and ABAB (\ref{ex:le-insertionABAB}) but not into AABB (\ref{ex:le-insertionAABB}).
+\obj{Le} can be inserted freely into AA (\ref{ex:le-insertionAA}) and ABAB (\ref{ex:le-insertionABAB}) but not into AABB (\ref{ex:le-insertionAABB}).
 
@@
 \ea\label{ex:le-insertionAA}
-  \ea \gll Yao Ming \textit{kan}-\textit{kan} ta de fanyi Ke Lin...\\
+  \ea \gll \objex{Yao2} \objex{Ming2} \obj{kan4}-\obj{kan4} \objex{ta1} de \objex{fan1yi4} \objex{Ke1} \objex{Lin2} \ldots\\
   Yao Ming look-look he \textsc{de} translator Ke Lin\\
-  \glt `Yao Ming looked at his translator Ke Lin a little bit...'
+  \glt `Yao Ming looked at his translator Ke Lin a little bit \ldots'
 
-  \ex \gll Yao Ming \textit{kan}-\textit{le}-\textit{kan} ta de fanyi Ke Lin...\\
+  \ex \gll \objex{Yao2} \objex{Ming2} \obj{kan4}-\obj{le}-\obj{kan4} \objex{ta1} de \objex{fan1yi4} \objex{Ke1} \objex{Lin2} \ldots\\
   Yao Ming look-\textsc{pfv}-look he \textsc{de} translator Ke Lin\\ \jambox{({CCL})}
-  \glt `Yao Ming looked at his translator Ke Lin a little bit...'
+  \glt `Yao Ming looked at his translator Ke Lin a little bit \ldots'
   \z
@@
 \ea\label{ex:le-insertionABAB}
-  \ea \gll ta \textit{heji}-\textit{heji}, dui Jiangqing shuo...\\
-  he consider-consider to Jiangqing say\\
- \glt `He considered a little bit, and told Jiangqing...'
+  \ea \gll \objex{ta1} \obj{he2ji}-\obj{he2ji}, \objex{dui4} \objex{Jiang1} \objex{Qing1} \objex{shuo1} \ldots\\
+  he consider-consider to Jiang Qing say\\
+ \glt `He considered a little bit, and told Jiang Qing \ldots'
 
-  \ex \gll ta \textit{heji}-\textit{le}-\textit{heji}, dui Jiangqing shuo...\\
-  he consider-\textsc{pfv}-consider to Jiangqing say\\ \jambox{({CCL})}
-  \glt `He considered a little bit, and told Jiangqing...'
+  \ex \gll \objex{ta1} \obj{he2ji}-\obj{le}-\obj{he2ji}, \objex{dui4} \objex{Jiang1} \objex{Qing1} \objex{shuo1} \ldots\\
+  he consider-\textsc{pfv}-consider to Jiang Qing say\\ \jambox{({CCL})}
+  \glt `He considered a little bit, and told Jiang Qing \ldots'
   \z
@@
 \ea\label{ex:le-insertionAABB}
-  \ea[]{\gll \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} jiu ba chulai le.\\
+  \ea[]{\gll \obj{yao2}-\obj{yao2}-\obj{huang4}-\obj{huang4} \objex{jiu4} \objex{ba2} \objex{chu1lai2} le.\\
   shake-shake-sway-sway then pull out \textsc{ptc}\\  \jambox{\citep[85]{Xie2020}}
@@
 
-  \ex[*]{\gll \textit{yao}-\textit{yao}-\textit{le}-\textit{huang}-\textit{huang} jiu ba chulai le.\\
+  \ex[*]{\gll \obj{yao2}-\obj{yao2}-\obj{le}-\obj{huang4}-\obj{huang4} \objex{jiu4} \objex{ba2} \objex{chu1lai2} le.\\
   shake-shake-\textsc{pfv}-sway-sway then pull out \textsc{ptc}\\ \jambox{\citep[85]{Xie2020}}}
@@
 \ea\label{ex:AABBadv}
-  \ea[*]{\gll dian-che \textit{yao-huang}-\textit{yao-huang} kai zou...\\
-  electric-car shake-sway-shake-sway drive away...\\ \jambox{\citep[86]{Xie2020}}}
+  \ea[*]{\gll \objex{dian4-che1} \obj{yao2-huang4}-\obj{yao2-huang4} \objex{kai1} \objex{zou3} \ldots\\
+  electric-car shake-sway-shake-sway drive away\\ \jambox{\citep[86]{Xie2020}}}
 
-  \ex[]{\gll dian-che \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} kai zou...\\
-  electric-car shake-shake-sway-sway drive away...\\ \jambox{\citep[86]{Xie2020}}
-  \glt `The tram drove away jiggly...'}
+  \ex[]{\gll \objex{dian4-che1} \obj{yao2}-\obj{yao2}-\obj{huang4}-\obj{huang4} \objex{kai1} \objex{zou3} \ldots\\
+  electric-car shake-shake-sway-sway drive away\\ \jambox{\citep[86]{Xie2020}}
+  \glt `The tram drove away jiggly \ldots'}
   \z
@@
 \ea\label{ex:AABBadj}
-  \ea[*]{\gll ...zuo zai  \textit{yao-huang}-\textit{yao-huang} de che shang\\
-  sit on shake-sway-shake-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}}
+  \ea[*]{\gll \ldots\,  \objex{zuo4} \objex{zai4}  \obj{yao2-huang4}-\obj{yao2-huang4} de \objex{che1} \objex{shang4}\\
+  {} sit on shake-sway-shake-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}}
 
-  \ex[]{\gll ...zuo zai  \textit{yao}-\textit{yao}-\textit{huang}-\textit{huang} de che shang\\
-  sit on shake-shake-sway-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}
-  \glt `...sit on the jiggling car'}
+  \ex[]{\gll \ldots\, \objex{zuo4} \objex{zai4}   \obj{yao2}-\obj{yao2}-\obj{huang4}-\obj{huang} de \objex{che1} \objex{shang4}\\
+  {} sit on shake-shake-sway-sway \textsc{de} car on\\ \jambox{\citep[86]{Xie2020}}
+  \glt `\ldots\, sit on the jiggling car'}
   \z
@@
 \ea\label{ex:trans}
-  \ea[]{\gll qiao-da gan-jing shi huanjie gan-qi de hao banfa.\\
+  \ea[]{\gll \objex{qiao1-da3} \objex{gan1-jing1} \objex{shi4} \objex{huan3jie3} \objex{gan1-qi4} de \objex{hao3} \objex{ban4fa3}.\\
   knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}
@@
 
-  \ex[]{\gll \textit{qiao-da}-\textit{qiao-da} gan-jing shi huanjie gan-qi de hao banfa.\\
+  \ex[]{\gll \obj{qiao1-da3}-\obj{qiao1-da3} \objex{gan1-jing1} \objex{shi4} \objex{huan3jie3} \objex{gan1-qi4} de \objex{hao3} \objex{ban4fa3}.\\
   knock-beat-knock-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}
@@
 
-   \ex[*]{\gll \textit{qiao}-\textit{qiao}-\textit{da}-\textit{da} gan-jing shi huanjie gan-qi de hao banfa.\\
+   \ex[*]{\gll \obj{qiao1}-\obj{qiao1}-\obj{da3}-\obj{da2} \objex{gan1-jing1} \objex{shi4} \objex{huan3jie3} \objex{gan1-qi4} de \objex{hao3} \objex{ban4fa3}\\
   knock-knock-beat-beat liver-channel \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\ \jambox{\citep[88]{Xie2020}}}
 
-  \ex[]{\gll \textit{qiao}-\textit{qiao}-\textit{da}-\textit{da} shi huanjie gan-qi de hao banfa.\\
+  \ex[]{\gll \obj{qiao1}-\obj{qiao1}-\obj{da3}-\obj{da3} \objex{shi4} \objex{huan3jie3} \objex{gan1-qi4} de \objex{hao3} \objex{ban4fa3}\\
    knock-knock-beat-beat \textsc{cop} relieve liver-\textit{qi} \textsc{de} good method\\
@@
 The two groups also have different input and output constraints.
-\citet{Xie2020} claimed that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see \sectref{sec:Aktionsarten}).
-in comparison, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
+\citet{Xie2020} claims that only dynamic and volitional verbs can undergo AA or ABAB reduplication (but see \sectref{sec:Aktionsarten}).
+In comparison, AABB requires its input to be a complex verb whose constituents are either synonymous, antonymous or logically coordinated (\ref{ex:AABB-input}). 
 Moreover, as can be seen in the translation in (\ref{ex:AABB-input}), the output of AABB has an increasing meaning, i.e.
@@
 \ea\label{ex:AABB-input}
-  \ea \gll duo-shan $\rightarrow$ \textit{duo}-\textit{duo}-\textit{shan}-\textit{shan}\\
+  \ea \gll \objex{duo3-shan3} $\rightarrow$ \obj{duo3}-\obj{duo3}-\obj{shan3}-\obj{shan2}\\
   hide-dodge {} hide-hide-dodge-dodge\\ \jambox{\citep[88]{Xie2020}}
@@
 
-  \ex \gll jin-chu $\rightarrow$ \textit{jin}-\textit{jin}-\textit{chu}-\textit{chu}\\
+  \ex \gll \objex{jin4-chu1} $\rightarrow$ \obj{jin4}-\obj{jin4}-\obj{chu1}-\obj1{chu}\\
   enter-exit {} enter-enter-exit-exit\\ \jambox{\citep[88]{Xie2020}}
@@
 
-  \ex \gll shuo-xiao $\rightarrow$ \textit{shuo}-\textit{shuo}-\textit{xiao}-\textit{xiao}\\
+  \ex \gll \objex{shuo1-xiao4} $\rightarrow$ \obj{shuo1}-\obj{shuo1}-\obj{xiao4}-\obj{xiao4}\\
   talk-laugh {} talk-talk-laugh-laugh\\ \jambox{\citep[88]{Xie2020}}
@@
 However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
-For instance, the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
-The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
-And inflections of tense in German do not change the valency of the input verb.
-Further, if \textit{le} is considered to be a morphological element (e.g.
-\citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \textit{le} does not have to be viewed as a syntactic
+For instance, the \obj{-able} derivation in English is a productive morphological process.
+Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.
+%the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
+%The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
+%And inflections of tense in German do not change the valency of the input verb.
+Further, if \obj{le} is considered to be a morphological element (e.g.
+\citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
 process either.
-It seems that \citet{Xie2020} only showed that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.
+It seems that \citet{Xie2020} only shows that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.
+
+A reviewer claims that \obj{le} insertion can be seen as a violation of lexical integrity,
+because it is never found in between the two constituents of a compound word,
+but must be placed after the whole unit.
+For instance, \citet[1282]{Her2006} claims that the V-\obj{gei3} sequence cannot be separated 
+and uses this as evidence for analyzing it as a single lexical item 
+(\obj{ji4-gei3-le} \obj{ta1} `send-give-\textsc{pfv} he, sent him' vs. ? \obj{ji4-le-gei3} \obj{ta1} `send-\textsc{pfv}-give he').
+In non-separable VO compounds, \obj{le} insertion also does not seem to be possible 
+(\obj{guan1-xin1-le} `close-heart-\textsc{pfv}, cared for' vs. ? \obj{guan1-le-}\obj{xin1} `close-\textsc{pfv}-heart').
+AABB
+
+In respond to this, we found counter-examples that show \obj{le} insertion in-between V-\obj{gei3} (\ref{ex:Vgei}) as well as \obj{guan1-xin1} `close-heart, care for' (\ref{ex:guanxin}) is possible.
+\ea\label{ex:Vgei}%还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
+\gll \ldots\, \objex{xu3duo1} \objex{nv2zi3}, \objex{jiang1} \objex{zi4ji3de} \objex{xiang4pian1} \ldots\, \objex{ji4-le-gei3} \objex{ta1}.\\
+{} many women take own photo {} send-\textsc{pfv}-give he\\\jambox{(CCL)}
+\glt `Many women \ldots\, sent him photos of themselves.'
+\z
+
+\ea\label{ex:guanxin}%许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
+\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-xin1}.\\
+many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\\jambox{(CCL)}
+\glt `Many comrades \ldots\, voluntarily cared for the patients.'
+\z
+
+In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.),
+and the patterns discussed here constitute a different process than the AABB pattern
+(see the discussions above, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
+it is not surprising that \obj{le} occurs at a different position.
 
 It is, therefore, necessary to resort to other tests that are intended to distinguish words from phrases. 
-Furthermore, we applied the same tests to Parallel Verb Compounds, which are inarguably words (because at least one element in the compound cannot appear in a sentence independently), 
-and {SVC}s, which are by definition phrases. 
-We then compared the test results of these three kinds of expressions to see whether the reduplication behaves in a more similar way to Parallel Verb Compounds or to {SVC}s.
+%Furthermore, we applied the same tests to Parallel Verb Compounds, which are inarguably words (because at least one element in the compound cannot appear in a sentence independently), 
+%and {SVC}s, which are by definition phrases. 
+%We then compared the test results of these three kinds of expressions to see whether the reduplication behaves in a more similar way to Parallel Verb Compounds or to {SVC}s.
+ \citeauthor{Dai1992} (\citeyear[32--33]{Dai1992}, \citeyear[117--120]{Dai1998}) proposes the modification and the expansion tests to distinguish words from phrases in Mandarin Chinese.
+%These tests requires further clarifications.
 
-\citet{Duanmu1998} and \citet{Schaefer2009} proposed the following four tests to
-distinguish words from phrases in Mandarin Chinese: semantic compositionality, phrasal extension,
-phrasal substitution and conjunction reduction.\footnote{It is important to note that none of these criteria are sufficient or necessary to determine the word or phrase status of an expression.
+First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
+This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g. an AP.
+\ea\label{ex:modVP} %开红色的门
+\gll \objex{kai1} \objex{hong2se4de} \objex{men2}\\
+open  red door\\
+\glt `open the red door'
+\z
+In contrast, the individual verbs in reduplication cannot be modified by an e.g. AdvP.
+(\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
+\ea[*]{\label{ex:modVV} %看偷偷地看
+    \gll \objex{kan4} \objex{tou1tou1de} \objex{kan4}\\
+    look secretly look\\
+}
+\z
+
+Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
+This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in-between.
+\ea\label{ex:inVCP}%开两次门
+%开门两次
+\ea \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
+open door three time\\
+\glt `open the door three times'
+
+\ex  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
+open three time door\\
+\glt `open the door three times'
+\z\z
+For reduplication, this is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
+\ea\label{ex:inVV}
+\ea[]{\gll \obj{kai1}-(\obj{le})-\obj{kai1} \objex{men2}\\
+    open-\textsc{pfv}-open door\\
+    \glt `open the door for a little while'}
+
+\ex[*]{%开(了)门(了)开
+    \gll \obj{kai1}-(\obj{le})-\obj{men2}-\obj{kai1}\\
+    open-\textsc{pfv}-door-open\\
+}
+\z\z
+
+Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as \textit{reduplication}) in other languages
+than syntactic reduplication (below as \textit{repetition} \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
+\citet[35--36]{Gil2005} considers non-iconicity and having only two (but not more) copies as sufficient but not necessary conditions for reduplication.
+He further proposes building one intonational group as sufficient and necessary condition for reduplication (p. 36).
+All three conditions are true for verbal reduplication in Mandarin Chinese (see \citealt[154]{Sui2018} on intonation of verbal reduplication in Mandarin Chinese).
+\citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.
+This is also the case for verbal reduplication in Mandarin Chinese.
+
+In sum, we maintain that verbal reduplication in Mandarin Chinese is better off analyzed as a morphological phenomenon.
+
+%\citet{Duanmu1998} and \citet{Schaefer2009} proposed the following four tests to
+%distinguish words from phrases in Mandarin Chinese: semantic compositionality, phrasal extension,
+%phrasal substitution and conjunction reduction.\footnote{It is important to note that none of these criteria are sufficient or necessary to determine the word or phrase status of an expression.
 Nevertheless, they together might suggest which of the two statuses is more likely.}
 
-The semantic criterion is that the meaning of a phrase is usually built up in a compositional way while that of a is word usually not \citetext{\citealp[140]{Duanmu1998}; \citealp[275]{Schaefer2009}}.
-The meaning of the reduplication is not compositional, as it does not mean that the event denoted by the verb happens twice or multiple times, but rather that the event happens for a short duration and/or for low frequency.
-This non-compositionality suggests that a reduplication is more word-like.
+%The semantic criterion is that the meaning of a phrase is usually built up in a compositional way while that of a is word usually not \citetext{\citealp[140]{Duanmu1998}; \citealp[275]{Schaefer2009}}.
+%The meaning of the reduplication is not compositional, as it does not mean that the event denoted by the verb happens twice or multiple times, but rather that the event happens for a short duration and/or for low frequency.
+%This non-compositionality suggests that a reduplication is more word-like.
 
-The syntactic criteria are all based on the Lexical Integrity Hypothesis according to \citet[60]{Huang1984}, as shown in (\ref{lih}):
+%The syntactic criteria are all based on the Lexical Integrity Hypothesis according to \citet[60]{Huang1984}, as shown in (\ref{lih}):
 
-\ea\label{lih}The Lexical Integrity Hypothesis\\
-No phrase-level rule may affect a proper subpart of a word.
-\z
+%\ea\label{lih}The Lexical Integrity Hypothesis\\
+%No phrase-level rule may affect a proper subpart of a word.
+%\z
 
-The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
-Optional elements that can possibly appear in a phrase should be able to be added into it,
-and subparts of a phrase should be able to be modified separately. 
-If the unit is a word, however, then neither of these should  be possible.
-As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
-As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec.
+%The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
+%Optional elements that can possibly appear in a phrase should be able to be added into it,
+%and subparts of a phrase should be able to be modified separately. 
+%If the unit is a word, however, then neither of these should  be possible.
+%As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
+%As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec.
 3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers  in Mandarin Chinese (\textit{le}, \textit{zhe} and \textit{guo}) to be morphological elements.
@@
 \citet{Travis2000}, \citet{Ramchand2008},  \citet[23]{Arcodiaetal2014}, \citet[146]{BascianoMelloni2017} considered all aspect information to be syntactically encoded.}
-And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
-Turning to separate modification,  the element in the reduplication cannot be modified individually. 
-Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
-as the adverbial cannot modify the second element in the reduplication alone.
-It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
-because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
-and it still modifies the whole predicate.
-(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.
+%And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
+%Turning to separate modification,  the element in the reduplication cannot be modified individually. 
+%Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
+%as the adverbial cannot modify the second element in the reduplication alone.
+%It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
+%because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
+%and it still modifies the whole predicate.
+%(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.
 
-\ea
-  \ea[]{\label{ex:ext-redup1}
-  \gll ta dui ziji qingsheng de \textit{xiao-le-xiao}.\\
-  he to \textsc{refl} quietly \textsc{de} laugh-\textsc{le}-laugh\\
-  \glt `He quietly laughed a little bit to himself.'}
+%\ea
+%  \ea[]{\label{ex:ext-redup1}
+%  \gll ta dui ziji qingsheng de \textit{xiao-le-xiao}.\\
+%  he to \textsc{refl} quietly \textsc{de} laugh-\textsc{le}-laugh\\
+%  \glt `He quietly laughed a little bit to himself.'}
 
-  \ex[*]{\label{ex:ext-redup2}
-  \gll ta dui ziji \textit{xiao}-\textit{le} qingsheng de \textit{xiao}.\\
-  he to \textsc{refl} laugh-\textsc{pfv} quietly \textsc{de} laugh\\}
+%  \ex[*]{\label{ex:ext-redup2}
+%  \gll ta dui ziji \textit{xiao}-\textit{le} qingsheng de \textit{xiao}.\\
+%  he to \textsc{refl} laugh-\textsc{pfv} quietly \textsc{de} laugh\\}
 
-  \ex[]{\label{ex:ext-redup3}
-  \gll ta qingsheng de dui ziji \textit{xiao-le-xiao}.\\
-  he quietly \textsc{de} to \textsc{refl} laugh-\textsc{pfv}-laugh\\
-  \glt `He quietly laughed a little bit to himself.'}
-  \z
-\z
+%  \ex[]{\label{ex:ext-redup3}
+% \gll ta qingsheng de dui ziji \textit{xiao-le-xiao}.\\
+%  he quietly \textsc{de} to \textsc{refl} laugh-\textsc{pfv}-laugh\\
+%  \glt `He quietly laughed a little bit to himself.'}
+%  \z
+%\z
 
-Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).
+%Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (\ref{ex:ext-pvc}).
 
-\ea\label{ex:ext-pvc}
-  \ea[]{
-  \gll ta gou-mai-le yi jian dayi.\\
-  he purchase-buy-\textsc{pfv} one \textsc{clf} coat\\
-  \glt `He bought a coat.'}
+%\ea\label{ex:ext-pvc}
+%  \ea[]{
+%  \gll ta gou-mai-le yi jian dayi.\\
+%  he purchase-buy-\textsc{pfv} one \textsc{clf} coat\\
+%  \glt `He bought a coat.'}
 
-  \ex[*]{
-  \gll ta gou-le-mai yi jian dayi.\\
-  he purchase-\textsc{pfv}-buy one \textsc{clf} coat\\}
+%  \ex[*]{
+%  \gll ta gou-le-mai yi jian dayi.\\
+%  he purchase-\textsc{pfv}-buy one \textsc{clf} coat\\}
 
-  \ex[*]{
-  \gll ta gou-le-yi-mai yi jian dayi.\\
-  he purchase-\textsc{pfv}-one-buy one \textsc{clf} coat\\}
+%  \ex[*]{
+%  \gll ta gou-le-yi-mai yi jian dayi.\\
+%  he purchase-\textsc{pfv}-one-buy one \textsc{clf} coat\\}
 
-  \ex[]{
-  \gll ta kaixin de gou-mai-le yi jian dayi.\\
-  he happily \textsc{de} purchase-buy-\textsc{pfv} one \textsc{clf} coat\\
-  \glt `He bought a coat happily.'}
+%  \ex[]{
+%  \gll ta kaixin de gou-mai-le yi jian dayi.\\
+%  he happily \textsc{de} purchase-buy-\textsc{pfv} one \textsc{clf} coat\\
+%  \glt `He bought a coat happily.'}
 
-  \ex[*]{
-  \gll ta gou kaixin de mai-le yi jian dayi.\\
-  he purchase happily \textsc{de} buy-\textsc{pfv} one \textsc{clf} coat\\}
-  \z
-\z
+%  \ex[*]{
+%  \gll ta gou kaixin de mai-le yi jian dayi.\\
+%  he purchase happily \textsc{de} buy-\textsc{pfv} one \textsc{clf} coat\\}
+%  \z
+%\z
 
-But an {SVC} readily allows other elements to appear between the two verbs (in (\ref{ex:ext-svc1}), the direct object of the first verb) and each verb can be modified separately (\ref{ex:ext-svc2}), as well.
+%But an {SVC} readily allows other elements to appear between the two verbs (in (\ref{ex:ext-svc1}), the direct object of the first verb) and each verb can be modified separately (\ref{ex:ext-svc2}), as well.
 
-\ea
-  \ea\label{ex:ext-svc1}
-  \gll ta zhong cai mai.\\
-  he plant vegetables sell\\
-  \glt `He plants vegetables and sells them.
+%\ea
+%  \ea\label{ex:ext-svc1}
+%  \gll ta zhong cai mai.\\
+%  he plant vegetables sell\\
+%  \glt `He plants vegetables and sells them.
 
-  \ex\label{ex:ext-svc2}
-  \gll ta xinku de zhong cai qinfen de mai.\\
-  he hardworkingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
-  \glt `He plants vegetables hard-workingly and sells them diligently.'
-  \z
-\z
-All in all, by the test of phrasal extension, reduplications behave more like words than like phrases.
+%  \ex\label{ex:ext-svc2}
+%  \gll ta xinku de zhong cai qinfen de mai.\\
+%  he hardworkingly \textsc{de} plant vegetables diligently \textsc{de} sell\\
+%  \glt `He plants vegetables hard-workingly and sells them diligently.'
+%  \z
+%\z
+%All in all, by the test of phrasal extension, reduplications behave more like words than like phrases.
 
-The second syntactic test is phrasal substitution, namely the substitution of smaller exemplars of a specific category with a full blown XP \citetext{\citealp[152]{Duanmu1998}; \citealp[280]{Schaefer2009}}.
-If a part of an expression is actually an XP that only contains one element, a full realization of this XP should be possible as well.
-Otherwise, this expression is considered to be a word.
-In a reduplication structure, it is ungrammatical to substitute each element with a full {VP} (\ref{ex:sub-redup}).
+%The second syntactic test is phrasal substitution, namely the substitution of smaller exemplars of a specific category with a full blown XP \citetext{\citealp[152]{Duanmu1998}; \citealp[280]{Schaefer2009}}.
+%If a part of an expression is actually an XP that only contains one element, a full realization of this XP should be possible as well.
+%Otherwise, this expression is considered to be a word.
+%In a reduplication structure, it is ungrammatical to substitute each element with a full {VP} (\ref{ex:sub-redup}).
 
-\ea\label{ex:sub-redup}
-  \ea[]{\label{ex-he-tasted-the-soup-a-little-bit}
-  \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
-    he taste-\textsc{pfv}-taste soup\\
-    \glt `He tasted the soup a little bit.'}
+%\ea\label{ex:sub-redup}
+%  \ea[]{\label{ex-he-tasted-the-soup-a-little-bit}
+%  \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
+ %   he taste-\textsc{pfv}-taste soup\\
+ %   \glt `He tasted the soup a little bit.'}
 
-    \ex[*]{
-    \gll ta \textit{chang} \textit{tang} \textit{le} \textit{chang} \textit{tang}.\\
-    he taste soup \textsc{pfv} taste soup\\}
-  \z
-\z
+ %   \ex[*]{
+ %   \gll ta \textit{chang} \textit{tang} \textit{le} \textit{chang} \textit{tang}.\\
+ %   he taste soup \textsc{pfv} taste soup\\}
+ % \z
+%\z
 
-It is the same case with Parallel Verb Compounds (\ref{ex:sub-pvc}).
+%It is the same case with Parallel Verb Compounds (\ref{ex:sub-pvc}).
 
-\ea[*]{
-\gll ta gou yi jian dayi mai le yi tiao kuzi.\\
-he purchase one \textsc{clf} coat buy \textsc{pfv} one \textsc{clf} pants\\}
-\label{ex:sub-pvc}
-\z
+%\ea[*]{
+%\gll ta gou yi jian dayi mai le yi tiao kuzi.\\
+%he purchase one \textsc{clf} coat buy \textsc{pfv} one \textsc{clf} pants\\}
+%\label{ex:sub-pvc}
+%\z
 
-However, it is grammatical to replace a reduced part of a {SVC} with a full VP (\ref{ex:sub-svc}).
+%However, it is grammatical to replace a reduced part of a {SVC} with a full VP (\ref{ex:sub-svc}).
 
-\ea\label{ex:sub-svc}
-\gll ta zhong cai mai (cai).\\
- he plant vegetables sell vegetables\\
-\glt `He plants vegetables and sells vegetables.'
- \z
-Again, reduplications look more word-like than phrase-like.
+%\ea\label{ex:sub-svc}
+%\gll ta zhong cai mai (cai).\\
+% he plant vegetables sell vegetables\\
+%\glt `He plants vegetables and sells vegetables.'
+ %\z
+%Again, reduplications look more word-like than phrase-like.
 
-The third syntactic criterion is conjunction reduction.
+%The third syntactic criterion is conjunction reduction.
 It should only be possible for coordinated phrases (\ref{ex:co-phrase}) and not for coordinated words (\ref{ex:co-word}) \citetext{\citealp[137]{Duanmu1998}; \citealp[283]{Schaefer2009}}.
 
-\settowidth\jamwidth{\citep[137]{Duanmu1998}}
+%\settowidth\jamwidth{\citep[137]{Duanmu1998}}
 
-\ea\label{ex:co-phrase}
-  \ea \gll [jiu de shu] gen [xin de shu]\\
-  old \textsc{de} book and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
-  \glt `old books and new books'
+%\ea\label{ex:co-phrase}
+ % \ea \gll [jiu de shu] gen [xin de shu]\\
+%  old \textsc{de} book and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
+%  \glt `old books and new books'
 
-  \ex \gll [jiu de gen xin de] shu\\
-  old \textsc{de} and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
-  \glt `old and new books'
-   \z
-\z
+%  \ex \gll [jiu de gen xin de] shu\\
+%  old \textsc{de} and new \textsc{de} book\\ \jambox{\citep[137]{Duanmu1998}}
+%  \glt `old and new books'
+%   \z
+%\z
 
-\ea\label{ex:co-word}
-  \ea[]{
-  \gll [huo-che] gen [qi-che]\\
-  fire-car and gas-car\\ \jambox{\citep[137]{Duanmu1998}}
-  \glt `train and automobile'}
+%\ea\label{ex:co-word}
+%  \ea[]{
+%  \gll [huo-che] gen [qi-che]\\
+%  fire-car and gas-car\\ \jambox{\citep[137]{Duanmu1998}}
+%  \glt `train and automobile'}
 
-  \ex[*]{
-  \gll [huo gen qi] che\\
-  fire and gas car\\ \jambox{\citep[137]{Duanmu1998}}}
-  \z
-\z
+%  \ex[*]{
+%  \gll [huo gen qi] che\\
+%  fire and gas car\\ \jambox{\citep[137]{Duanmu1998}}}
+%  \z
+%\z
 
-For the reduplication, conjunction reduction does not seem to be possible. 
-In (\ref{ex:co-redup1}), the reduplication \textit{jiao-jiao} `chew a little bit' is coordinated with a simple verb \textit{mo} `apply' together with the adverbial \textit{yidian} `a little bit'.
-Without the adverbial \textit{yidian} `a little bit', \textit{mo} `apply' by itself cannot express the additional `a little bit' meaning even when it is coordinated with a reduplicated verb.
-Similarly, in (\ref{ex:co-redup2}), the reduplication \textit{kan-le-kan} `look a little bit' is coordinated with the predicate \textit{zou-le chulai} `walked out'.
+%For the reduplication, conjunction reduction does not seem to be possible. 
+%In (\ref{ex:co-redup1}), the reduplication \textit{jiao-jiao} `chew a little bit' is coordinated with a simple verb \textit{mo} `apply' together with the adverbial \textit{yidian} `a little bit'.
+%Without the adverbial \textit{yidian} `a little bit', \textit{mo} `apply' by itself cannot express the additional `a little bit' meaning even when it is coordinated with a reduplicated verb.
+%Similarly, in (\ref{ex:co-redup2}), the reduplication \textit{kan-le-kan} `look a little bit' is coordinated with the predicate \textit{zou-le chulai} `walked out'.
 The verb in the latter case is not reduplicated and it cannot express the delimitative meaning either.
 
-\settowidth\jamwidth{(CCL)}
+%\settowidth\jamwidth{(CCL)}
 
-\ea
-  \ea\label{ex:co-redup1}
-  \gll wujian gong-xiu mo dian bohe-gao huo \textit{jiao}-\textit{jiao} kouxiangtang.\\
-    midday work-break apply a.little mint-cream or chew-chew chewing.gum\\ \jambox{({CCL})}
-    \glt `During the working break in the midday, apply a little bit of mint cream or chew some chewing gum a little bit.'
+%\ea
+%  \ea\label{ex:co-redup1}
+%  \gll wujian gong-xiu mo dian bohe-gao huo \textit{jiao}-\textit{jiao} kouxiangtang.\\
+%    midday work-break apply a.little mint-cream or chew-chew chewing.gum\\ \jambox{({CCL})}
+%    \glt `During the working break in the midday, apply a little bit of mint cream or chew some chewing gum a little bit.'
 
-   \ex\label{ex:co-redup2}
-   \gll Song Ailing \textit{kan}-\textit{le}-\textit{kan} yupen you zou-le chulai.\\
-   Song Ailing look-\textsc{pfv}-look bath.tub again walk-\textsc{pfv} out\\  \jambox{({CCL})}
-   \glt `Song Ailing looked at the bath tub a little bit and walked out again.'
-   \z
-\z
+%   \ex\label{ex:co-redup2}
+%   \gll Song Ailing \textit{kan}-\textit{le}-\textit{kan} yupen you zou-le chulai.\\
+%   Song Ailing look-\textsc{pfv}-look bath.tub again walk-\textsc{pfv} out\\  \jambox{({CCL})}
+%   \glt `Song Ailing looked at the bath tub a little bit and walked out again.'
+%   \z
+%\z
 
-Conjunction reduction is not possible for Parallel Verb Compounds as well.
-We can see in (\ref{ex:co-pvc}) that for the Parallel Verb Compounds \textit{gou-mai} `purchase-buy, buy' and \textit{gou\hyp{}zhi} `purchase\hyp{}place, purchase', it is neither possible to delete the first verb nor the second.
+%Conjunction reduction is not possible for Parallel Verb Compounds as well.
+%We can see in (\ref{ex:co-pvc}) that for the Parallel Verb Compounds \textit{gou-mai} `purchase-buy, buy' and \textit{gou\hyp{}zhi} `purchase\hyp{}place, purchase', it is neither possible to delete the first verb nor the second.
 
-\ea\label{ex:co-pvc}
-     \ea[*]{
-     \gll ta gou-mai-le yi jian dayi hai gou-le yi tiao kuzi.\\
-    he purchase-buy-\textsc{pfv} one \textsc{clf} coat and purchase-\textsc{pfv} one \textsc{clf} pants\\
-    \glt Intended: `He bought a coat and purchased a pair of pants.'}
+%\ea\label{ex:co-pvc}
+ %    \ea[*]{
+ %    \gll ta gou-mai-le yi jian dayi hai gou-le yi tiao kuzi.\\
+ %   he purchase-buy-\textsc{pfv} one \textsc{clf} coat and purchase-\textsc{pfv} one \textsc{clf} pants\\
+%    \glt Intended: `He bought a coat and purchased a pair of pants.'}
 
-    \ex[*]{
-    \gll ta gou-mai-le yi jian dayi hai -zhi-le yi tiao kuzi.\\
-    he purchase-buy-\textsc{pfv} one \textsc{clf} coat and place-\textsc{pfv} one \textsc{clf} pants\\
-   \glt  Intended: `He bought a coat and purchased a pair of pants.'}
-    \z
-\z
+%    \ex[*]{
+%    \gll ta gou-mai-le yi jian dayi hai -zhi-le yi tiao kuzi.\\
+%    he purchase-buy-\textsc{pfv} one \textsc{clf} coat and place-\textsc{pfv} one \textsc{clf} pants\\
+%   \glt  Intended: `He bought a coat and purchased a pair of pants.'}
+%    \z
+%\z
 
-By contrast, it is grammatical to delete a repeated part in a coordinated {SVC}. 
-In (\ref{ex:co-svc1}), while it is possible for the object of selling to be only cows, it is equally acceptable to interpret it as the person sells both vegetables and cows.
+%By contrast, it is grammatical to delete a repeated part in a coordinated {SVC}. 
+%In (\ref{ex:co-svc1}), while it is possible for the object of selling to be only cows, it is equally acceptable to interpret it as the person sells both vegetables and cows.
 With the second interpretation, (\ref{ex:co-svc1}) can be understood as a reduced version of (\ref{ex:co-svc2}).
 
-\ea
-  \ea\label{ex:co-svc1}
-  \gll ta zhong cai hai yang niu mai.\\
-  he plant vegetables and farm cow sell\\
-  \glt `He plants vegetables and farms cows and sells them.'
+%\ea
+%  \ea\label{ex:co-svc1}
+%  \gll ta zhong cai hai yang niu mai.\\
+%  he plant vegetables and farm cow sell\\
+%  \glt `He plants vegetables and farms cows and sells them.'
 
-  \ex\label{ex:co-svc2}
-  \gll ta zhong cai mai hai yang niu mai.\\
-  he plant vegetables sell and farm cow sell\\
-  \glt `He plants vegetables and sells them and farms cows and sells them.'
-   \z
-\z
-Once again, this criterion suggests that reduplications do not have this expected property of phrases.
+%  \ex\label{ex:co-svc2}
+%  \gll ta zhong cai mai hai yang niu mai.\\
+%  he plant vegetables sell and farm cow sell\\
+%  \glt `He plants vegetables and sells them and farms cows and sells them.'
+ %  \z
+%\z
+%Once again, this criterion suggests that reduplications do not have this expected property of phrases.
 
-Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. 
-In comparison, Parallel Verb Compounds failed all the tests as well, whereas {SVC}s passed all of them.
-This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an {SVC}.
-Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.
+%Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. 
+%In comparison, Parallel Verb Compounds failed all the tests as well, whereas {SVC}s passed all of them.
+%This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an {SVC}.
+%Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.

### 2024-08-19 chapters/ch04-Previous.tex
Update 2024-08-19-20:05:18

@@
 
-\citet{Ghomeshietal2004} provided an analysis within the theoretical framework of Parallel Architecture \citep{Jackendoff1997, Jackendoff2002} for Contrastive Reduplication (CRs) in English like (\ref{ex:salad}),\footnote{Capitalization indicates contrastive intonation.}
-as shown in Figure~\ref{ghomeshi-cr}.\footnote{{P} = phonological unit, {P/E/S CTR} = prototypical/extreme/salient contrast, XP$^{min}$ = XP without its specifier} 
+%\citet{Ghomeshietal2004} provided an analysis within the theoretical framework of Parallel Architecture \citep{Jackendoff1997, Jackendoff2002} for Contrastive Reduplication (CRs) in English like (\ref{ex:salad}),\footnote{Capitalization indicates contrastive intonation.}
+%as shown in Figure~\ref{ghomeshi-cr}.\footnote{{P} = phonological unit, {P/E/S CTR} = prototypical/extreme/salient contrast, XP$^{min}$ = XP without its specifier} 
 %They postulated a new syntactic category {CR}$^{syn}$ to incorporate the reduplicant.
@@
 %which modifies the semantics of  X/XP$^{min}$ (Z$_k$).
-\ea\label{ex:salad}
-I make the tuna salad, and you make the \textit{SALAD-salad}.
-\z
-\begin{figure}[h!]
-\centering
+%\ea\label{ex:salad}
+%I make the tuna salad, and you make the \textit{SALAD-salad}.
+%\z
+%\begin{figure}[h!]
+%\centering
 %\begin{multicols}{3}
-\begin{minipage}[t]{.3\linewidth}
-\begin{center}
-Phonology\\
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Phonology\\
 %\vspace{15pt}
-P$_{j, k}$ P$_k$
-\end{center}
-\end{minipage}
+%P$_{j, k}$ P$_k$
+%\end{center}
+%\end{minipage}
 %\columnbreak
-\begin{minipage}[t]{.3\linewidth}
-\begin{center}
-Syntax\\
-\begin{forest}
-for tree = {inner sep = 0pt,
-	s sep = 1pt,
-	anchor=children last,
-    	align=center}
-[X/XP$^{min}$
- [CR$^{syn}$$_j$]
- [X/XP$^{min}$$_k$]
-]
-\end{forest}
-\end{center}
-\end{minipage}
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Syntax\\
+%\begin{forest}
+%for tree = {inner sep = 0pt,
+%	s sep = 1pt,
+%	anchor=children last,
+%    	align=center}
+%[X/XP$^{min}$
+% [CR$^{syn}$$_j$]
+% [X/XP$^{min}$$_k$]
+%]
+%\end{forest}
+%\end{center}
+%\end{minipage}
 %\columnbreak
-\begin{minipage}[t]{.3\linewidth}
-\begin{center}
-Semantics
-\[
-\begin{bmatrix}
-Z_{k}\\
-\begin{bmatrix}
-P/E/S\\
-CTR
-\end{bmatrix}_{\!j}
-\end{bmatrix}
-\]
-\end{center}
-\end{minipage}
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Semantics
+%\[
+%\begin{bmatrix}
+%Z_{k}\\
+%\begin{bmatrix}
+%P/E/S\\
+%CTR
+%\end{bmatrix}_{\!j}
+%\end{bmatrix}
+%\]
+%\end{center}
+%\end{minipage}
 %\end{multicols}
-\caption{Analysis for {CR}s in English according to \citet[344]{Ghomeshietal2004}}
-\label{ghomeshi-cr}
-\end{figure}
+%\caption{Analysis for {CR}s in English according to \citet[344]{Ghomeshietal2004}}
+%\label{ghomeshi-cr}
+%\end{figure}
 
-Applying this to the reduplication in Mandarin Chinese, the structure should be something like \figref{ghomeshi-cn}.\footnote{{DELIM} = delimitative}\textsuperscript{,}\footnote{
-Although the reduplication in Mandarin Chinese does not have a contrastive meaning, 
-we preserve the notation of CR$^{syn}$ in \citet{Ghomeshietal2004} here to simply refer to the reduplicant.}
-The base verb is coindexed with its phonology and its semantics `look'. 
-The phonology of the reduplicant is coindexed with the phonology of the verb.
-The reduplicant is coindexed with the delimiative semantics
-and modifies the semantics of the base verb.
-The base verb and the reduplicant combine to a V.\footnote{In English, it makes sense to assume CR$^{syn}$ to be a syntactic unit, because the base can be XP$^{min}$ (e.g.
+%Applying this to the reduplication in Mandarin Chinese, the structure should be something like \figref{ghomeshi-cn}.\footnote{{DELIM} = delimitative}\textsuperscript{,}\footnote{
+%Although the reduplication in Mandarin Chinese does not have a contrastive meaning, 
+%we preserve the notation of CR$^{syn}$ in \citet{Ghomeshietal2004} here to simply refer to the reduplicant.}
+%The base verb is coindexed with its phonology and its semantics `look'. 
+%The phonology of the reduplicant is coindexed with the phonology of the verb.
+%The reduplicant is coindexed with the delimiative semantics
+%and modifies the semantics of the base verb.
+%The base verb and the reduplicant combine to a V.\footnote{In English, it makes sense to assume CR$^{syn}$ to be a syntactic unit, because the base can be XP$^{min}$ (e.g.
 \textit{OVER-THE-HILL-over-the-hill}).
-But for Mandarin Chinese, the base can only be V.
-As \citet[353]{Ghomeshietal2004} wrote: ``when applying to its smallest scope, X inside of a word, it has the feel of other things that attach there, i.e., morphological affixes''.
-It seems that it suffices to assume the reduplication in Mandarin Chinese to be a morphological phenomenon (cf. \sectref{sec:word}).
-We continue to call the second column ``syntax'' to preserve the consistency of the notations.
-}
-We draw the head on the left because all analyses mentioned above considered the first element in the reduplication to be the actual verb and the second element the reduplicant, 
-but this analysis itself does not forbid the head to be on the right side.
+%But for Mandarin Chinese, the base can only be V.
+%As \citet[353]{Ghomeshietal2004} wrote: ``when applying to its smallest scope, X inside of a word, it has the feel of other things that attach there, i.e., morphological affixes''.
+%It seems that it suffices to assume the reduplication in Mandarin Chinese to be a morphological phenomenon (cf. \sectref{sec:word}).
+%We continue to call the second column ``syntax'' to preserve the consistency of the notations.
+%}
+%We draw the head on the left because all analyses mentioned above considered the first element in the reduplication to be the actual verb and the second element the reduplicant, 
+%but this analysis itself does not forbid the head to be on the right side.
 
-\begin{figure}[h!]
-\centering
-\begin{minipage}[t]{.3\linewidth}
-\begin{center}
-Phonology\\
-\begin{forest}
-[P$_{j}$ [kan]] 
-\end{forest}
-\begin{forest}
-[P$_{j, k}$ [kan]]
-\end{forest}
-\end{center}
-\end{minipage}
+%\begin{figure}[h!]
+%\centering
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Phonology\\
+%\begin{forest}
+%[P$_{j}$ [kan]] 
+%\end{forest}
+%\begin{forest}
+%[P$_{j, k}$ [kan]]
+%\end{forest}
+%\end{center}
+%\end{minipage}
 %\columnbreak
-\begin{minipage}[t]{.3\linewidth}
-\begin{center}
-Syntax\\
-\begin{forest}
-[V
- [V$_j$]
- [CR$^{syn}$$_k$]
-]
-\end{forest}
-\end{center}
-\end{minipage}
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Syntax\\
+%\begin{forest}
+%[V
+% [V$_j$]
+% [CR$^{syn}$$_k$]
+%]
+%\end{forest}
+%\end{center}
+%\end{minipage}
 %\columnbreak
-\begin{minipage}[t]{.3\linewidth}
-\begin{center}
-Semantics
-\[
-\begin{bmatrix}
-\begin{bmatrix}
-DELIM\\([LOOK]_{j})
-\end{bmatrix}_{\!k}\\
-\end{bmatrix}
-\]
-\end{center}
-\end{minipage}
-\caption{Analysis for AA following \citet{Ghomeshietal2004}}
-\label{ghomeshi-cn}
-\end{figure}
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Semantics
+%\[
+%\begin{bmatrix}
+%\begin{bmatrix}
+%DELIM\\([LOOK]_{j})
+%\end{bmatrix}_{\!k}\\
+%\end{bmatrix}
+%\]
+%\end{center}
+%\end{minipage}
+%\caption{Analysis for AA following \citet{Ghomeshietal2004}}
+%\label{ghomeshi-cn}
+%\end{figure}
 
-As for the other forms of reduplication, A-\textit{le}-A can be viewed as two compositional processes \mbox{[[[A] -\textit{le}] -A]}.
-Furthermore, the \textit{yi} in A-\textit{yi}-A and A-\textit{le}-\textit{yi}-A can simply be viewed as a dangling phonological unit. 
-In this case, \phonliste{ yi } is neither coindexed with a syntactic unit nor with a semantic one.
+%As for the other forms of reduplication, A-\textit{le}-A can be viewed as two compositional processes \mbox{[[[A] -\textit{le}] -A]}.
+%Furthermore, the \textit{yi} in A-\textit{yi}-A and A-\textit{le}-\textit{yi}-A can simply be viewed as a dangling phonological unit. 
+%In this case, \phonliste{ yi } is neither coindexed with a syntactic unit nor with a semantic one.
 
-This analysis correctly captures the fact that the addition of \textit{yi} does not change the syntactic and semantic behavior of the reduplication.
-It also provides a formal account for the phonology of the reduplication.
-Nevertheless, by assuming a construction specially for the reduplication, this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese, unlike the affixation analyses described in \sectref{sec:asp}.
+%This analysis correctly captures the fact that the addition of \textit{yi} does not change the syntactic and semantic behavior of the reduplication.
+%It also provides a formal account for the phonology of the reduplication.
+%Nevertheless, by assuming a construction specially for the reduplication, this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese, unlike the affixation analyses described in \sectref{sec:asp}.
 

### 2024-08-19 chapters/ch02-Phenomenon.tex
Update 2024-08-19-20:22:03

@@
 (\obj{guan1-xin1-le} `close-heart-\textsc{pfv}, cared for' vs. ? \obj{guan1-le-}\obj{xin1} `close-\textsc{pfv}-heart').
-AABB
+The AABB form of reduplication also only accepts \obj{le} to its right but not in-between (\ref{ex:yaohuang}).
+\ea\label{ex:yaohuang} %我趁机从大货车以及左边的轿车车门上贴肤而过，	摇摇晃晃了	几下
+\ea[]{\gll \objex{wo3} \ldots\, \obj{yao2-yao2-huang4-huang3-le} \objex{ji3} \objex{xia4} \ldots\\
+I {} shake-shake-sway-sway-\textsc{pfv} several time\\\jambox{(CCL)}
+\glt `I shook and swayed several times \ldots'}
+
+\ex[*]{ \gll \objex{wo3} \ldots\, \obj{yao2-yao2-le-huang4-huang3} \objex{ji3} \objex{xia4} \ldots\\
+I {} shake-shake-\textsc{pfv}-sway-sway several time\\}
+\z\z
 

### 2024-08-23 chapters/ch04-Previous.tex
Update 2024-08-23-17:36:32

@@
 Previous analyses on the reduplication in Mandarin Chinese and in other languages can be classified
-into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect marker (\sectref{sec:asp}), and
+into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect modifier (\sectref{sec:asp}), and
 as a special reduplication construction (\sectref{sec:construc}).\footnote{The term \textit{construction} is used here in its general sense, not in the sense of Construction Grammar.} 
@@
 
-\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
+\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyze the reduplication in Mandarin Chinese
 as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
 The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
-A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).
+A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \obj{ci4} in (\ref{ex:clf}).
 
@@
 \ea\label{ex:clf}
-\gll mei che guo yi ci huang\\
+\gll \objex{mei2} \objex{che3} \objex{guo4} \objex{yi2} \objex{ci4} \objex{huang3}\\
 not tell \textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
@@
 the second element is a verbal classifier borrowed from a verb, 
-and \textit{yi} `one' is an optional pseudo-numeral that only has an abstract `a little bit' meaning.
+and \obj{yi} `one' is an optional pseudo-numeral that only has an abstract `a little bit' meaning.
 The analysis is syntactic.
@@
 Both the reduplication and the verbal classifier phrase serve to quantify the duration or the extent of a situation. 
-A reduplication structure can often be paraphrased into a verbal classifier phrase such as \textit{yi xia} ‘once, a while’, \textit{yi hui} ‘a while’, as illustrated in (\ref{ex:redup-clf}).
+A reduplication structure can often be paraphrased into a verbal classifier phrase such as \obj{yi2} \obj{xia4} ‘once, a while’, \obj{yi2} \obj{hui4} ‘a while’, as illustrated in (\ref{ex:redup-clf}).
 
 \ea\label{ex:redup-clf}
-	\ea \gll \textit{deng}-\textit{deng} wo.\\
+	\ea \gll \obj{deng3}-\obj{deng3} \objex{wo3}.\\
 		wait-wait I\\
 		\glt `Wait for me a little bit.'
-	\ex \gll deng wo yi xia.\\
+	\ex \gll \objex{deng3} \objex{wo3} \objex{yi2} \objex{xia4}.\\
 	wait I one \textsc{clf}\\
@@
 However, there are several arguments suggesting that the reduplication cannot be analyzed the same way as a verbal classifier phrase.
-First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.
+First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.\footnote{
+One reviewer notes that the objects that can be placed in between the verbal classifier phrase is usually limited to pronouns and proper nouns.
+We found some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
+\ea%她看了他的脸一下。(CCL)
+\gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
+she look-\textsc{pfv} his face one time\\\jambox{(CCL)}
+\glt `She took a look at his face.'
+
+\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
+\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
+he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
+\glt `He just took a look at the glass and the glass just broke.'
+\z
+We think it has to do with the length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
+%This is not necessarily a syntactic constraint
+
+Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
+the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+}
 
 \ea\label{ex:clf-sep}
-  \ea \gll ni deng yi xia Zhangsan!\\
+  \ea \gll \objex{ni3} \objex{deng3} \objex{yi2} \objex{xia4} \objex{Zhang1san1}!\\
    you wait one \textsc{clf} Zhangsan\\
    \glt `Wait for Zhangsan for a while!'
-  \ex \gll ni deng Zhangsan yi xia!\\
+  \ex \gll \objex{ni3} \objex{deng3} \objex{Zhang1san1} \objex{yi2} \objex{xia4}!\\
    you wait Zhangsan one \textsc{clf}\\
@@
 \ea\label{ex:redup-sep}
-  \ea[]{\gll ni \textit{deng}-\textit{yi}-\textit{deng} Zhangsan!\\
+  \ea[]{\gll \objex{ni3} \obj{deng3}-\obj{yi}-\obj{deng3} \objex{Zhang1san1}!\\
    you wait-one-wait Zhangsan\\
    \glt `Wait for Zhangsan a little bit!'}
-  \ex[*]{\gll ni \textit{deng} Zhangsan \textit{yi} \textit{deng}!\\
+  \ex[*]{\gll \objex{ni3} \obj{deng3} \objex{Zhang1san1} \obj{yi} \obj{deng3}!\\
   you wait Zhangsan one wait\\}
@@
 
-Second, unlike verbal classifiers (\ref{ex:clf-num}), the \textit{yi} ‘one’ in A-\textit{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.
+Second, unlike verbal classifiers (\ref{ex:clf-num}), the \obj{yi} ‘one’ in A-\obj{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.
 
 \ea\label{ex:clf-num}
-  \ea \gll ta pai-le wo yi xia.\\
+  \ea \gll \objex{ta1} \objex{pai1}-le \objex{wo3} \objex{yi2} \objex{xia4}.\\
    he pat-\textsc{pfv} I one \textsc{clf}\\
    \glt `He patted me once.'
-   \ex \gll ta pai-le wo liang xia.\\
+   \ex \gll \objex{ta1} \objex{pai1}-le \objex{wo3} \objex{liang3} \objex{xia4}.\\
     he pat-\textsc{pfv} I two \textsc{clf}\\
@@
 \ea\label{ex:redup-num}
-  \ea[]{\gll ta \textit{pai}-\textit{le}-\textit{yi}-\textit{pai} wo.\\
+  \ea[]{\gll \objex{ta1} \obj{pai1}-\obj{le}-\obj{yi}-\obj{pai1} \objex{wo3}.\\
    he pat-\textsc{pfv}-one-pat I\\
    \glt `He patted me a little bit.'}
-   \ex[*]{\gll ta \textit{pai}-\textit{le}-\textit{liang}-\textit{pai} wo.\\
+   \ex[*]{\gll \objex{ta1} \obj{pai1}-\obj{le}-\obj{liang3}-\obj{pai1} \objex{wo3}.\\
    he pat-\textsc{pfv}-two-pat I\\}
@@
 
-Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.
+Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.\footnote{
+One reviewer suggests that the loss of the idiomatic meaning in (\ref{ex:clf-idiom}) but not in (\ref{ex:redup-idiom}) may be attributed to the use of the numeral \obj{san1} `three' in (\ref{ex:clf-idiom}),
+because if \obj{san1} \obj{xia3} `three times' is replaced with \objex{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
+We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special, 
+but it is \obj{yi2} \obj{xia4} `once' that is special.
+We can replace \obj{san1} `three' with any number above two,
+and the distinction still exist.
+But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
+We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
+In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
+but as duration adverbials as a whole,
+thus differing them from ``actual'' verbal classifier phrases with other numerals.
+}
 
@@
   \ea\label{ex:idiom}
-  \gll bao fo-jiao\\
+  \gll \objex{bao4} \objex{fo2}-\objex{jiao3}\\
   clasp Buddha-foot\\
@@
    \ex\label{ex:clf-idiom}
-   \gll ta kaoshi qian bao-le san xia fo-jiao.\\
+   \gll \objex{ta1} \objex{kao3shi4} \objex{qian2} \objex{bao4}-le \objex{san3} \objex{xia4} \objex{fo2}-\objex{jiao3}.\\
    he exam before clasp-\textsc{pfv} three \textsc{clf} Buddha-foot\\
@@
    \ex\label{ex:redup-idiom}
-   \gll ta kaoshi qian \textit{bao}-\textit{le}-\textit{bao} fo-jiao.\\
+   \gll \objex{ta1} \objex{kao3shi4} \objex{qian2} \obj{bao4}-\obj{le}-\obj{bao4} \objex{fo2}-\objex{jiao3}.\\
    he exam before clasp-\textsc{pfv}-clasp Buddha-foot\\
@@
 %%%%%%%%%%%
-\subsection{The reduplicant as an aspect marker}\label{sec:asp}
+\subsection{The reduplicant as an aspect modifier}\label{sec:asp}
 
-A number of studies consider the reduplication to be a delimitative aspect marker \citep{Arcodiaetal2014, BascianoMelloni2017, YangWei2017} 
-due to its delimitative aspectual meaning. 
-\citet{Travis1999, Travis2000} also analyzed the reduplication in Tagalog as an imperfective aspect marker.
+A number of studies consider the reduplication to be an element that modifies the aspectual properties of the base verb \citep{Arcodiaetal2014, BascianoMelloni2017, YangWei2017} 
+due to the delimitative aspectual meaning of reduplication. 
+\citet{Travis1999, Travis2000} also analyzes the reduplication in Tagalog as an imperfective aspect marker.
 
@@
 
- \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} analyzed the reduplication within the
+ \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} analyze the reduplication within the
 framework of First Phase Syntax \citep{Ramchand2008}.
-\citet{Ramchand2008} proposed that an event is comprised of the following phrases: 
+\citet{Ramchand2008} propose that an event is comprised of the following phrases: 
 the causative subevent (\textit{init}P), the process subevent (\textit{proc}P) and the result subevent (\textit{res}P), which are ordered hierarchically, as illustrated in \figref{tree:ramchand}.\footnote{
@@
 \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
-and that the second element is an aspect marker, which resides in the complement position of \textit{proc}, as it delimits the process of the event. 
+and that the second element is the copy of the verb, which resides in the complement position of \textit{proc} and serves as an event delimiter.
 Since the second element occupies the same syntactic position as \textit{res}P, it should have complementary distribution with \textit{res}P
@@
 
- \citet[229]{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
- \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
-He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}),
-while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).
+ \citet[229]{YangWei2017} endorse the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+ \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
+He observed that  \obj{zhe} `\textsc{prog}', \obj{le} `\textsc{pfv}' and \obj{wan2} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}),
+while \obj{zai4} `\textsc{dur}' and \obj{guo4} `\textsc{exp}' can occur without further information (\ref{ex:complete}).
 
 \ea\label{ex:incomplete}
- \gll Xiaoli chi-zhe/le/wan fan *(le).\\
+ \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan4} fan *(le).\\
  Xiaoli eat-\textsc{prog}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
@@
 \ea\label{ex:complete}
-\gll Xiaoli (gangcai) zai ku/ku-guo.\\
+\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo4}.\\
 Xiaoli just.now \textsc{dur} cry/cry-\textsc{exp}\\
@@
 He thus proposed three aspect positions under TP.
-\textit{zai} and \textit{guo} reside under Asp$_1$, while \textit{zhe} and \textit{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \textit{wan} can only occur with certain types of predicate.
+\textit{zai} and \textit{guo} reside under Asp$_1$, while \textit{zhe} and \textit{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \obj{wan2} can only occur with certain types of predicate.
 This differentiation does not play a role for our purpose and will not be further discussed here.}
@@
 \ea\label{ex:redup-tsai}
-\ea[*] {\gll ta \textit{xiao}-\textit{xiao}\\
+\ea[*] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}\\
 he laugh-laugh\\}
-\ex[] {\gll ta \textit{xiao}-\textit{le}-\textit{xiao}\\
+\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}\\
 he laugh-\textsc{pfv}-laugh\\
 \glt `He laughed a little.'}
-\ex[] {\gll ta \textit{xiao}-\textit{xiao}, bu shuohua\\
+\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}, \objex{bu4} \objex{shuo1hua4}\\
 he laugh-laugh not speak\\
@@
 This analysis would result in a mismatch between syntax and semantics. 
-Even though \textit{le}, \textit{guo} and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
-\textit{guo} is situated under Asp$_1$ while \textit{le} and the reduplication are under Asp$_2$, as can be seen from \figref{tree:redupasp}.
+Even though \obj{le}, \obj{guo4} and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
+\obj{guo4} is situated under Asp$_1$ while \obj{le} and the reduplication are under Asp$_2$, as can be seen from \figref{tree:redupasp}.
 
-In sum, both analyses of the reduplicant as an aspect marker do not seem to be convincing.
+In sum, both analyses of the reduplicant as an aspect modifier do not seem to be convincing.
 
@@
 
-The following section discusses previous literature which proposed a special construction for the reduplication.
+%The following section discusses previous literature which proposed a special construction for the reduplication.
 
@@
 
-\citet*{FanSongBond2015} provided a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
-They considered reduplication to be a morphological process and modeled it via lexical rules.
-They provided the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
-and further proposed \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
+\citet*{FanSongBond2015} provide a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
+They consider reduplication to be a morphological process and modeled it via lexical rules.
+They provide the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
+and further propose \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
 as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.\footnote{%
@@
 
-This approach provided a unified account for adjectival and verbal reduplication.
+This approach provides a unified account for adjectival and verbal reduplication.
 Their commonalities are captured by inheritance hierarchies of the intensifier predicates and the lexical rules.

### 2024-08-23 chapters/ch05-Analysis.tex
Update 2024-08-23-17:36:32

@@
 
-\newpage
+%\newpage
 \ea\label{avm:vle}
@@
 \z
-For example (\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
+For example %(\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as
+ (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
 where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
 \ea\label{ex-he-tasted-the-soup-a-little-bit2}
-    \gll ta \textit{chang}-\textit{le}-\textit{chang} tang.\\
+    \gll \objex{ta1} \obj{chang2}-\obj{le}-\obj{chang2} \objex{tang1}.\\
     he taste-\textsc{pfv}-taste soup\\
@@
 
-\footnotetext[18]{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
-\footnotetext[19]{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
-\footnotetext[20]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
-\footnotetext[21]{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
-\footnotetext[22]{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
-
 \begin{sloppypar}
@@
 \ea\label{ex:AByiAB-lu}
-\gll ni yu wo \textit{zhengli-yi-zhengli}.\footnotemark\\
+\gll \objex{ni3} \objex{yu3} \objex{wo3} \obj{zheng3li3-yi-zheng3li3}.\footnotemark\\
 you let me arrange-one-arrange\\
 \glt `Let me arrange it a little bit!'
+\footnotetext{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
 
 \ex\label{ex:AByiAB-pu}
-\gll ni \textit{dating-yi-dating}.\footnotemark\\
+\gll \objex{ni3} \obj{da3ting1-yi-da3ting1}.\footnotemark\\
 you inquire-one-inquire\\
 \glt `Inquire about it a little bit!'
+\footnotetext{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
 
 \ex\label{ex:AByiAB-rou1}
-\gll ge ge dian-tou \textit{weixiao-yi-weixiao}.\footnotemark\\
+\gll \objex{ge4} \objex{ge4} \objex{dian3-tou2} \obj{wei1xiao4-yi-wei1xiao4}.\footnotemark\\
 \textsc{clf} \textsc{clf} nod-head smile-one-smile\\
 \glt `Each one nodded his head and smiled a little bit.'
+\footnotetext{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
 
 \ex\label{ex:AByiAB-rou2}
-\gll ta \textit{weixiao-le-yi-weixiao}, you \textit{mingxiang-le-yi-mingxiang}.\footnotemark\\
+\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3-le-yi-ming2xiang3}.\footnotemark\\
 he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\
 \glt `He smiled a little bit and meditated a little bit.'
+\footnotetext{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
 
 \ex\label{ex:AByiAB-li}
-\gll feichang yansu de ba jinshi yanjing \textit{duanzheng-le-yi-duanzheng}.\footnotemark\\
+\gll \objex{fei1chang2} \objex{yan2su3} de \objex{ba3} \objex{jin4shi4} \objex{yan3jing4} \obj{duan1zheng4-le-yi-duan1zheng4}.\footnotemark\\
 very seriously \textsc{de} \textsc{ba} nearsighted glasses straighten-\textsc{pfv}-one-straighten\\
 \glt `[He] very seriously straightened the nearsighted glasses quickly.'
+\footnotetext{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
 
 \ex\label{ex:ABleyiAB-ccl}
-\gll jiduo sanluan-zhe de chuan li de dengguang, ye huyinhumie de \textit{bianhuan-le-yi-bianhuan} weizhi.\\
+\gll \objex{ji3duo1} \objex{san3luan4}-zhe de \objex{chuan2} \objex{li3} de \objex{deng1guang1}, \objex{ye3} \objex{hu1yin1hu1mie4} de \obj{bian4huan4-le-yi-bian4huan4} \objex{wei4zhi}.\\
 many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
@@
 The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
-Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.
+Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.\footnote{
+One reviewer suggests that given that AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}),
+these rare occurrences can be seen as relics of this usage.
+}
 
-AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\textit{kan} and A-\textit{kan}-\textit{kan} can also be accounted for by the lexical rules proposed in this section.
+AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} can also be accounted for by the lexical rules proposed in this section.
 They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
@@
 }
-AA-\textit{kan} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \textit{kan} `look',
-whereas A-\textit{kan}-\textit{kan} is the compound of a monosyllabic verb (A) and the reduplication of \textit{kan} `look'.
-A-\textit{yi}-A-\textit{kan} is also possible, though rare, presumably also due to its length.
-An inquiry in CCL found 55 hits of A-\textit{yi}-A-\textit{kan}.
+AA-\obj{kan4} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \obj{kan4} `look',
+whereas A-\obj{kan4}-\obj{kan4} is the compound of a monosyllabic verb (A) and the reduplication of \obj{kan4} `look'.
+A-\obj{yi}-A-\obj{kan4} is also possible, though rare, presumably also due to its length.
+An inquiry in CCL found 55 hits of A-\obj{yi}-A-\obj{kan4}.
 A sample is listed in (\ref{ex:AyiAkan}).
@@
 \ea
-\gll teyi gongneng de yanjiuzhe-men bufang ruci \textit{shi-yi-shi-kan} \ldots\\
+\gll \objex{te4yi4} \objex{gong1neng2} de \objex{yan2jiu1zhe3}-men \objex{bu4fang2} \objex{ru2ci3} \obj{shi4-yi-shi4-kan4} \ldots\\
 special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
-\glt `Researchers of special power may as well have a try as such as see \ldots'
+\glt `Researchers of special power may as well have a try as such and see \ldots'
 
 \ex 
-\gll danshi dui fa mei fa-guo hege-zheng, yijing shuo bu qing le, xuyao \textit{cha-yi-cha-kan}.\\
+\gll \objex{dan4shi4} \objex{dui4} \objex{fa1} \objex{mei2} \objex{fa1}-\objex{guo4} \objex{he2ge2-zheng4}, \objex{yi3jing1} \objex{shuo1} \objex{bu4} \objex{qing1} le, \objex{xu1yao4} \obj{cha2-yi-cha2-kan4}.\\
 but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
@@
 \ex
-\gll rang wo lai \textit{cai-yi-cai-kan}.\\
+\gll \objex{rang4} \objex{wo3} \objex{lai2} \obj{cai1-yi-cai1-kan4}.\\
 let I come guess-one-guess-look\\ \jambox{({CCL})}
@@
 \ex
-\gll da-laoban-men yao \textit{deng-yi-deng-kan}\\
+\gll \objex{da4-lao3ban3}-men \objex{yao4} \obj{deng3-yi-deng3-kan4}\\
 big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
@@
 \ex
-\gll furen ni dao \textit{shu-yi-shu-kan}, zhe zhu hua de huaduo gong you ji zhong yanse.\\
+\gll \objex{fu1ren2} \objex{ni3} \objex{dao4} \obj{shu3-yi-shu3-kan4}, \objex{zhe4} \objex{zhu1} \objex{hua1} de \objex{hua1duo3} \objex{gong4} \objex{you3} \objex{ji3} \objex{zhong3} \objex{yan2se4}.\\
 madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
@@
 \z
-Due to the prominent tentative, trying meaning of AA-\textit{kan} and A-\textit{kan}-\textit{kan}, they are not compatible with the perfective aspect marker \textit{le} semantically,
+Due to the prominent tentative, trying meaning of AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4}, they are not compatible with the perfective aspect marker \obj{le} semantically,
 as one usually cannot try something that is already realized.
-Thus, structures such as  A\hyp{}\textit{le}\hyp{}A\hyp{}\textit{kan} and A\hyp{}\textit{kan\hyp{}le\hyp{}kan} are considered pragmatically infelicitous.
+Thus, structures such as  A\hyp{}\obj{le}\hyp{}A\hyp{}\obj{kan4} and A\hyp{}\obj{kan4\hyp{}le\hyp{}kan4} are considered pragmatically infelicitous.
 \end{sloppypar}

### 2024-08-23 chapters/ch06-Conclusion.tex
Journal version + document for documenting changes
Update 2024-08-23-17:36:32

@@
 The current study provides a new HPSG account for verbal reduplication in Mandarin Chinese.
-We present empirical evidence that reduplication is possible with all \textit{Aktionsarten}.
-We give a semantic explanation for the incompatibility of reduplication with aspect markers other than \textit{le}.
+We present empirical evidence that reduplication is possible with all verb classes.
+We give a semantic explanation for the incompatibility of reduplication with aspect markers other than \obj{le}.
 We argue that reduplication is a morphological rather than a syntactic process.
@@
 so that all productive forms of reduplication are derivable by lexical rules.
-The analysis is implemented as part of the CoreGram project \citep{MuellerCoreGram} in a Chinese
-grammar in the TRALE system \citep{MeurersEtAl2002, Penn2004}.
+The analysis is implemented as part of a computer-processable grammar of Mandarin Chinese.
+%The analysis is implemented as part of the CoreGram project \citep{MuellerCoreGram} in a Chinese
+%grammar in the TRALE system \citep{MeurersEtAl2002, Penn2004}.

### 2024-08-23 main.tex
Update 2024-08-19-20:05:18
Update 2024-08-23-17:36:32

@@
 
-\title{An HPSG account for deliminative verbal reduplication in Mandarin Chinese}
+\title{Deliminative verbal reduplication in Mandarin Chinese}
 
@@
 We provide a detailed description of the phenomenon.
-After discussing reduplication’s interaction with \textit{Aktionsarten} and aspect markers, we argue that it is better analyzed as a morphological rather than a syntactic process.
+After discussing reduplication’s interaction with verb classes and aspect markers, we argue that it is better analyzed as a morphological rather than a syntactic process.
 We put forward a lexical rule for verbal reduplication in Mandarin Chinese, and the different forms of reduplication are captured in an inheritance hierarchy.

### 2024-08-25 chapters/ch02-Phenomenon.tex
Update 2024-08-25-21:23:36

@@
 The reduplication has a similar syntactic distribution as an unreduplicated verb (\ref{ex:syn-vi})--(\ref{ex:syn-svc}). 
-This suggests that a reduplicated verb can be treated as its unreduplicated counterpart in syntax (see \sectref{sec:word}).
-The reduplication cannot be aspect marked, though, except with the perfective aspect marker \textit{le} (see \sectref{sec:aspM}).% for further discussions on interactions with aspect markers). 
-The reduplication also cannot co-occur with an expression that quantifies the duration or the extent of the event described by the sentence due to its semantic properties (see \sectref{sec:adjuncts}).
+%This suggests that a reduplicated verb can be treated as its unreduplicated counterpart in syntax (see \sectref{sec:word}).
 
@@
 		\glt `He laughed.'
-		\ex \gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}.\\
+		\ex\label{ex:xiaole} \gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}.\\
 		he laugh-\textsc{pfv}-laugh\\
@@
 
-\ex Under negation:
-		\ea \gll \objex{wei4shen2me} \objex{wo3} \objex{bu4} \objex{kan4} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4} \ldots\\
-		why I not look he other aspect \textsc{de} progress\\
-		\glt `Why don't I look at his progress in other aspects?'
-		\ex \gll  \objex{wei4shen2me} \objex{wo3} \objex{bu4} \obj{kan4-kan} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4}\ldots\\
-		why I not look-look he other aspect \textsc{de} progress \\ \jambox{({CCL})}
-		\glt `Why don't I look a little bit at his progress in other aspects?'
-		\z
-
 \ex In a \textit{ba}-construction:
@@
 \end{sloppypar}
+
+\citet{SuiHu2016} claim that the syntactic distribution of the deliminative reduplication is subject to the following constraints.
+First, it cannot appear in a relative clause without a modal verb, providing the contrast in (\ref{ex:rel-suihu}) as an example \citep[319]{SuiHu2016}.
+\ea\label{ex:rel-suihu}
+\ea[]{ \gll {[[\objex{tong2xue2-men}} \objex{tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
+student-\textsc{pl} discuss \textsc{de} this \textsc{clf} question very important\\
+\glt `The question that the students discussed is very important.'}
+
+\ex[*]{ \gll {[[\objex{tong2xue2-men}} \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
+student-\textsc{pl} discuss-discuss \textsc{de} this \textsc{clf} question very important\\}
+%\glt `The question that the students discussed is very important.'}
+
+\ex[]{ \gll {[[\objex{tong2xue2-men}} \objex{xu1yao4} (\objex{zai4}) \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
+    student-\textsc{pl} need again discuss-discuss \textsc{de} this \textsc{clf} question very important\\
+    \glt `The question that the students need to discuss (again) is very important.'}
+\z\z
+This claim can be falsified by (\ref{ex:rel-ccl}) found in CCL.
+We thus consider the contrast in (\ref{ex:rel-suihu}) a matter of providing a proper context.
+\ea\label{ex:rel-ccl}
+\gll \objex{er2qie3} \objex{yan3-qian2} \objex{zhe4} \objex{[[ku3-liu2} \objex{ta1} \objex{zai4} \obj{tan2-tan} \objex{de]} \objex{ren2]} \ldots\\
+moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\
+\glt `Moreover, this person in front of her who is trying hard to make her stay to discuss a bit more \ldots'
+\\\jambox{(CCL)}
+\z
+
+Secondly, \citet[319]{SuiHu2016} show that the reduplication cannot co-occur with a duration or frequency phrase (\ref{ex:durfreq}).
+\ea\label{ex:durfreq}
+\ea[]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \objex{tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
+this \textsc{clf} question everybody still need.to discuss one while/several time\\
+\glt `As for this question, everybody still needs to discuss it for a while/several times.'}
+
+\ex[*]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \objex{tao3lun4-tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
+    this \textsc{clf} question everybody still need.to discuss-discuss one while/several time\\}
+%    \glt `As for this question, everybody still needs to discuss it for a while/several times.'}
+\z\z
+As we will show in \sectref{sec:adjuncts}, this can be explained by the redundant semantics of the reduplication and duration and frequency phrases.
+%with an expression that quantifies the duration or the extent of the event described by the sentence due to its semantic properties (see \sectref{sec:adjuncts} for a detailed discussion).
+
+Thirdly, \citet[319]{SuiHu2016} note that reduplicated verbs cannot be aspect marked (\ref{ex:redup-asp}).
+\ea\label{ex:redup-asp}
+\ea[]{ \gll \objex{wo3} \objex{kan4-le/guo4/zhe} \objex{zhe4} \objex{ben3} \objex{shu1}\\
+I read-\textsc{pfv/exp/dur} this \textsc{clf} book\\
+\glt `I read/have read/am reading this book.'
+}
+\ex[*]{ \gll \objex{wo3} \objex{kan4-kan4-le/guo4/zhe} \objex{zhe4} \objex{ben3} \objex{shu1}\\
+    I read-read-\textsc{pfv/exp/dur} this \textsc{clf} book\\
+%    \glt `I read/have read/am reading this book.'
+}
+\z\z
+However, as shown in (\ref{ex:xiaole}), \obj{le} can occur in between the reduplicated verb
+ and expresses the perfective aspectual meaning, that the event denoted by the sentence is realized.
+Thus, we argue that the reduplication can in fact be aspect marked,
+but only by \obj{le} `\textsc{pfv}' but not the other aspect markers.
+As we will argue in \sectref{sec:aspM}, this is also not a syntactic but a semantic constraint.
+%, though, except with the perfective aspect marker \textit{le} (see \sectref{sec:aspM}).% for further discussions on interactions with aspect markers).
+
+\citet[319]{SuiHu2016} further claim that the reduplication cannot be embedded under negation. 
+But (\ref{ex:redup-neg}) shows that this is not the case.
+\ea \label{ex:redup-neg}
+\ea \gll \objex{wei4shen2me} \objex{wo3} \objex{bu4} \objex{kan4} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4} \ldots\\
+why I not look he other aspect \textsc{de} progress\\
+\glt `Why don't I look at his progress in other aspects?'
+\ex \gll  \objex{wei4shen2me} \objex{wo3} \objex{bu4} \obj{kan4-kan} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4}\ldots\\
+why I not look-look he other aspect \textsc{de} progress \\ \jambox{({CCL})}
+\glt `Why don't I look a little bit at his progress in other aspects?'
+\z\z
+
+Finally, \citet[322]{SuiHu2016} claim that a reduplicated verb cannot combine with a quantized object.
+However, example (\ref{ex:quantobj}) proves otherwise.
+\ea\label{ex:quantobj}
+\gll \objex{ta1} \ldots\, \obj{kan4-kan} \objex{san1} \objex{ge4} \objex{ren2} \objex{he2} \objex{na4} \objex{liang4} \objex{che1zi} \dots\\
+he {} look-look three \textsc{clf} person and that \textsc{clf} car\\
+\glt `He took a look at the three people and that car \ldots'
+\z
+
+In sum, we consider that the reduplication has a similar syntactic distribution as an unreduplicated verb,
+and the incompatibility of the reduplication with duration and frequency phrases 
+as well as aspect markers other than \obj{le} can be explained semantically, 
+as we will show in the next section.
 

### 2024-08-25 chapters/ch04-Previous.tex
Update 2024-08-25-21:23:36

@@
 Both the reduplication and the verbal classifier phrase serve to quantify the duration or the extent of a situation. 
-A reduplication structure can often be paraphrased into a verbal classifier phrase such as \obj{yi2} \obj{xia4} ‘once, a while’, \obj{yi2} \obj{hui4} ‘a while’, as illustrated in (\ref{ex:redup-clf}).
+A reduplication structure can often be paraphrased into a verbal classifier phrase such as \obj{yi2} \obj{xia4} `once, a while', \obj{yi2} \obj{hui4} `a while', as illustrated in (\ref{ex:redup-clf}).
 

### 2024-08-25 chapters/ch06-Conclusion.tex
Update 2024-08-25-21:23:36

@@
 
-The current study provides a new HPSG account for verbal reduplication in Mandarin Chinese.
+The current study provides a new HPSG account for delimitative verbal reduplication in Mandarin Chinese.
 We present empirical evidence that reduplication is possible with all verb classes.
 We give a semantic explanation for the incompatibility of reduplication with aspect markers other than \obj{le}.
-We argue that reduplication is a morphological rather than a syntactic process.
+We argue that reduplication is better analyzed as a morphological rather than a syntactic process.
 We model reduplication as a lexical rule,

### 2024-08-25 chapters/ch02-Phenomenon.tex
Update 2024-08-25-22:08:04

@@
 Finally, \citet[322]{SuiHu2016} claim that a reduplicated verb cannot combine with a quantized object.
-However, example (\ref{ex:quantobj}) proves otherwise.
+However, examples in (\ref{ex:quantobj}) prove otherwise.
 \ea\label{ex:quantobj}
-\gll \objex{ta1} \ldots\, \obj{kan4-kan} \objex{san1} \objex{ge4} \objex{ren2} \objex{he2} \objex{na4} \objex{liang4} \objex{che1zi} \dots\\
-he {} look-look three \textsc{clf} person and that \textsc{clf} car\\
+\ea\gll \objex{ta1} \ldots\, \obj{kan4-kan} \objex{san1} \objex{ge4} \objex{ren2} \objex{he2} \objex{na4} \objex{liang4} \objex{che1zi} \dots\\
+he {} look-look three \textsc{clf} person and that \textsc{clf} car\\\jambox{(CCL)}
 \glt `He took a look at the three people and that car \ldots'
-\z
+
+\ex \gll \objex{wo3} \objex{xiang3} \objex{zhuo2zhong4} \obj{shuo1-shuo} \objex{liang2} \objex{ge4} \objex{hu4xiang1} \objex{lian2xi4-zhe} \objex{de} \objex{zhong4yao4} \objex{cheng2guo3}: \ldots\\
+I want emphasize say-say two \textsc{clf} each.other connect-\textsc{dur} \textsc{de} important result\\
+\glt `I want to highlight two important interconnecting results.'
+\z\z
 

### 2024-08-25 chapters/ch02-Phenomenon.tex
Update 2024-08-25-22:21:22

@@
 \gll \objex{er2qie3} \objex{yan3-qian2} \objex{zhe4} \objex{[[ku3-liu2} \objex{ta1} \objex{zai4} \obj{tan2-tan} \objex{de]} \objex{ren2]} \ldots\\
-moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\
+moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\\jambox{(CCL)}
 \glt `Moreover, this person in front of her who is trying hard to make her stay to discuss a bit more \ldots'
-\\\jambox{(CCL)}
 \z

### 2024-08-25 chapters/ch02-Phenomenon.tex
Update 2024-08-25-22:47:44

@@
 \ex \gll \objex{wo3} \objex{xiang3} \objex{zhuo2zhong4} \obj{shuo1-shuo} \objex{liang2} \objex{ge4} \objex{hu4xiang1} \objex{lian2xi4-zhe} \objex{de} \objex{zhong4yao4} \objex{cheng2guo3}: \ldots\\
-I want emphasize say-say two \textsc{clf} each.other connect-\textsc{dur} \textsc{de} important result\\
-\glt `I want to highlight two important interconnecting results.'
+I want emphasize say-say two \textsc{clf} each.other connect-\textsc{dur} \textsc{de} important outcome\\
+\glt `I want to highlight two important interconnected outcomes.'
 \z\z

### 2024-09-05 replies-reviews.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers

@@
 
-\usepackage{csquotes}
+%\usepackage{csquotes}
 
@@
 lexical integrity”, i.e. they form a single lexical item (745 T fih ji-géi-le ta vs. * 77 T 431 Ji-le géi ta).
-\itdopt{St. Mü.: fix brackets and references to examples.}
+\itdopt{St. Mü.: fix brackets and references to examples. The quoted text contains Chinese
+  characters. Please try to insert them. Also for the examples below.}
 
@@
 \item Pp.
-26, lines 24-25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
+26, lines 24--25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
 [] indicates an underspecified list which could be empty or not''.
@@
 
-\textbf{Answer:} \itdopt{Stefan, say something.}
+\textbf{Answer:} \itdopt{Stefan, say something. StMü: I would suggest to ignore this comment. }
 
@@
 \item
-p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
+p. 20, lines 28--31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
 element in the reduplication is the actual verb, which resides under init and proc, and that the
@@
 p.
-32, lines 28-34: “Although these forms are generally considered unacceptable (Li \& Thompson 1981: 30; Hong 1999: 275-276; Basciano \& Melloni 2017: 160; Yang \& Wei 2017: 239), Fan (1964: 269) and Sui (2018: 143) considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.” Given that these patterns were possible in previous stages of the language (see a.0.
+32, lines 28--34: “Although these forms are generally considered unacceptable (Li \& Thompson 1981: 30; Hong 1999: 275-276; Basciano \& Melloni 2017: 160; Yang \& Wei 2017: 239), Fan (1964: 269) and Sui (2018: 143) considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.” Given that these patterns were possible in previous stages of the language (see a.0.
 Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.
@@
 \textbf{Answer:} add a footnote
+
+\itdopt{St.Mü.: Did you add a footnote or is this something to be done?}
 %%%%%%%%%%%%%%%%%%%%%%
@@
 For additional comments, please refer to the attached PDF file.
+
+\itdopt{St.Mü.: This is the original review. We should say something about it. For example point to
+  explanations above or say that the issues will be taken up below when we discuss the reviewers
+  detailed comments.}
 
@@
 
+\itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
+  adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
+  spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
+nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}
+
 %%%%%%%%%%%%%%%%%
@@
 
-Examples (27) and (28) serve as illustrations to demonstrate the application of the 'Lexical Integrity Hypothesis' in distinguishing PVC from SVC.
+Examples (27) and (28) serve as illustrations to demonstrate the application of the ``Lexical Integrity Hypothesis'' in distinguishing PVC from SVC.
 
@@
 \textbf{Answer:} See above.
+
+\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}
+
 %%%%%%%%%%%%%%%%%%%
@@
 
+\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}
+
 \item
@@
 \textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category or valency of the input.
-To improve readability, English examples are used instead.
+To improve readability, English examples are used instead now.
 
@@
 
+\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to
+  exactly. For example: See the answers to Reviewer X, point Y on page Z. If you did something in
+  the text to react, say so. This pleases reviewers. They are the kings/queens and want to be take seriously.}
+
 \item
-In Page 14, the draft makes use of a new terminology such as “word-like”.
+In Page 14, the draft makes use of a new terminology such as ``word-like''.
 Of course, I can understand the meaning within the context.
@@
 \textbf{Answer:} reformulate as ``behaves more similar to a word''.
+
+\itdopt{St. Mü.: Was hast Du denn hier gemacht? Das scheint im Text jetzt ganz auskommentiert zu sein.}
 
@@
 \item
-In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs.
-Is it what the author(s) invent only for modeling the verbal reduplication in this drat?
-If so, the author(s) want to account more for how it works in AVMs.
-Otherwise, the author(s) might be better to refer to the previous analysis about the notion.
-\itdopt{Stefan}
+In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs. Is it what
+the author(s) invent only for modeling the verbal reduplication in this drat? If so, the author(s)
+want to account more for how it works in AVMs. Otherwise, the author(s) might be better to refer to
+the previous analysis about the notion.
+
+\noindent
+\textbf{Answer: } We added a footnote on first appearance explaining that the \etag is a more
+explicit version of the usual ``\ldots''.
 
@@
 
-\itdopt{Stefan}
+%\itdopt{Stefan. Question to Yanru: Which example should we analyze?}
+\noindent
+\textbf{Answer: } We added a figure with the analysis of \emph{chang2-le-chang2} and some
+accompanying text.
+
 \end{enumerate}

### 2024-09-05 chapters/ch02-Phenomenon.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers

@@
 \ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
-\objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3} \ldots\\
+\gll \objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3}~\ldots\\
 she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
@@
 %%%%%%%%%%%%
-\subsection{Word vs. phrase}\label{sec:word}
+\subsection{Word vs.\ phrase}\label{sec:word}
 

### 2024-09-05 chapters/ch05-Analysis.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers

@@
 input verb with the possibility to have further phonological material in between.  \etag{} indicates
-an underspecified list which could be empty or not.  A delimitative relation is appended to the
-\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb as
-argument.  The label of the output \iboxb{2} is identified with the label of the input and with the
+an underspecified list which could be empty or not.\footnote{%
+The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
+follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
+notation, since we think this is more
+precise than simply using three dots.}
+A delimitative relation is appended to the
+\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
+argument. The list of relations contains so-called elementary predications. There is no complicated
+embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
+label can be used as an argument of another relation or in scope constraints, which are not provided
+here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
+elementary predication that is considered the top-most one in the \relsl. Other elementary
+predications may share the label or have arguments with labels of other elementary predications. We
+will discuss an example below when we discuss the perfective lexical rule.
+The label of the output \iboxb{2} is identified with the label of the input and with the
 label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
@@
 Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
-constraints inherited from \type{perfective-lr} and \type{verbal-reduplication-lr}:
+constraints inherited from \type{perfective-lr} and \type{verbal-redu\-pli\-ca\-tion-lr}:\\
 %\resizebox{\linewidth}{!}{
@@
             phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
-            \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
+            \punk{synsem\textbar loc\textbar cont\textbar ltop}{ \2}\\ 
             rels & <[\type*{perfective-rel}\\
@@
 \ex   % \scalebox{.9}{%
+\label{avm:a-le-a-lr}
     \type{a-le-a-lr} \impl\\
@@
 \z
+
+The analysis of (\ref{ex-he-tasted-the-soup-a-little-bit2}) is shown in tree format in
+Figure~\ref{fig-he-tasted-the-soup-a-little-bit}. The \textsc{lex-dtr} is the daughter in the tree.
+\begin{figure}[htbp]
+\centering
+\begin{forest}
+[        \avm{
+            [\type*{a-le-a-lr}\\
+            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \1\\
+            synsem\textbar loc & [ cat  & [ head  & verb\\
+                                            spr   & < NP$_{\6}$ >\\
+                                            comps & < NP$_{\7}$ > ]\\
+                                   cont & [ ltop & \2\\
+                                            ind  & \ibox{3} ]] \\
+            rels & <[\type*{perfective-rel}\\
+            lbl & \2\\
+            arg0 & \3\\
+            arg1 & \4]> $\oplus$ \5 $\oplus$
+            <[\type*{delimitative-rel}\\
+            lbl  & \4\\
+            arg0 & \3]> ]
+    }
+[\avm{ [phon & \1 \phonliste{ chang2 }\\
+       synsem\textbar loc & [cat  & [ head  & verb\\
+                                      spr   & < NP$_{\6}$ >\\
+                                      comps & < NP$_{\7}$ > ]\\
+                             cont & [ ltop & \4\\
+                                      ind  & \3]]\\
+        rels & \5 < [\type{taste}\\
+                     lbl  & \4\\
+                     arg0 & \3\\
+                     arg1 & \6\\
+                     arg2 & \7 ] > ]
+}]]
+\end{forest}
+
+\caption{Analysis of \emph{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
+\end{figure}
+
+The figure shows how the lexical item for \emph{chang2} `to taste' is inserted as a daughter into
+the \type{a-le-a-lr} lexical rule. The arguments of \emph{chang2} `to taste' are represented within the \spr and
+the \compsl (see \citet{GSag2000a-u} for English) and the respective argument NPs are linked to the
+arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
+the stimulus. See \citet{DKW2021a} for more on linking. The part of speech of the lexical item
+(\type{verb}) and the valence information is carried over from the daughter to the mother
+unchanged. The semantic contribution of the daughter verb, the value of \ibox{5}, is inserted into
+the \relsl of the mother as it was specified in the constraints on the type
+\type{perfective-reduplication-lr} in (\ref{avm:pfv-redup}). The \textsc{phon} value of the mother
+is the concatentation of \emph{chang2}, \emph{le} and \emph{chang2}, as specified in the constraint
+on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \emph{chang2-le-chang2} then
+combines with its object forming a VP. This VP is combined with the subject resulting in a complete
+verbal projection, a sentence. \emph{chang-le-chang} behaves in the same way as the simple \emph{chang2}.
 

### 2024-09-06 replies-reviews.tex
add references to 'see above'

@@
 
-\section{Reviewer 1}
+\section{Reviewer 1}\label{sec:1}
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:}\label{verbclass}
 First, the notion of ``aspect'' adopted in this article has to be explained in more detail.
@@
 \ea\label{ex:xihuan}%这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
-\gll \objex{zhe4} \objex{che1} \objex{hao3} \objex{xing2} \objex{a}! \objex{zen3me} \objex{le}, \objex{wo3} \objex{jiu4} \obj{xi3huan1-xi3huan4} \objex{bu4xing2} \objex{me}?\\
+\gll \objex{zhe4} \objex{che1} \objex{hao3} \objex{xing2} \objex{a}! \objex{zen3me} \objex{le}, \objex{wo3} \objex{jiu4} \obj{xi3huan1-xi3huan1} \objex{bu4xing2} \objex{me}?\\
 this car so cool \textsc{ptc} what \textsc{ptc} I just like-like cannot \textsc{ptc}\\\jambox{(BCC)}
@@
 As noted briefly in Sec. 2.2 in the previous version of the paper,
-the reduplication is incompatible with an expression that quantifies the duration or the extent of the event,
+the reduplication is incompatible with an expression that quantifies the duration or the extent of the event (\ref{ex:syn-quan}),
  because the reduplication already contains a (abstract) quantity meaning, namely a short duration or a small extent (transitoriness),
  which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}, \citealt[333]{SuiHu2016}).
+ \ea %With an expression of quantity: 
+ \label{ex:syn-quan}
+ \ea[]{\label{ex:syn-quana}\gll \objex{ta1} \objex{yi4} \objex{tian1} \objex{pao3} \objex{shi2} \objex{li3}.\\
+     he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
+     \glt `He runs ten miles a day.'}
+ \ex[*]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \obj{pao3}-\obj{pao3} \objex{shi2} \objex{li3}.\\
+     he one day run-run ten mile\\}
+ \z
+ \z
 % The same can be argued for the incompatibility of reduplication and a quantized object () , as both serve to delimit the event expressed by the base verb \citep[322]{SuiHu2016}.
@@
 %%%%%%%%%%%%%%%%%%%%
-\textbf{Answer:}
+\textbf{Answer:}\label{morph}
 Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
@@
 
-%%%%%%%%%%%%%%%%%%%%%
-\textbf{Answer:}
-As explained above, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
-The incompatibility with the progressive aspect marker is explained in the Semantics section.
-%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%
-%% Stefan
-\item
+%\item
 The proposed analysis appears to have a descriptive rather than an explanatory power.
@@
 
-\textbf{Answer:} \itdopt{Stefan, say something. StMü: I would suggest to ignore this comment. }
+%\textbf{Answer:} \itdopt{Stefan, say something. StMü: I would suggest to ignore this comment. }
+
+%%%%%%%%%%%%%%%%%%%%%
+\textbf{Answer:}
+As explained in point \ref{verbclass} on page \pageref{verbclass}, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
+The incompatibility with the progressive aspect marker is explained in the Semantics section.
+%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\textbf{Answer:} add footnote
+\textbf{Answer:}A footnote is added to the example to point this out: 
+``As a reviewer comments, this example also involves the reduplication of V1 of a resultative compound. 
+This runs counter to exiting literature on this subject which consistently maintains that resultative compounds are not amenable to reduplication''.
 
@@
 
-\textbf{Answer:} See above.
+\textbf{Answer:} See the answer to point \ref{verbclass} on page \pageref{verbclass}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-\textbf{Answer:} add a footnote
+\textbf{Answer:} A footnote is added to this sentence to point this out: 
+``One reviewer suggests that given that AB-\obj{yi}-AB and AB-\obj{le}-\obj{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}), these rare occurrences can be seen as relics of this usage''.
 
-\itdopt{St.Mü.: Did you add a footnote or is this something to be done?}
+%\itdopt{St.Mü.: Did you add a footnote or is this something to be done?}
 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Reviewer 2}
+\section{Reviewer 2}\label{sec:2}
 \begin{enumerate}
@@
 %%%%%%%%%%%%%%%%%%%
-\textbf{Answer:} See above.
+\textbf{Answer:} Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
+The different syntactic behaviors of the reduplication and a VP are compared
+and the behavior of the reduplication is compatible with a lexical analysis.
+The comparison with Parallel Verb Compounds and Serial Verb Constructions are not substantial to our arguments and is thus removed.
+See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for more details.
 
-\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}
+%\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}
 
@@
 
-\textbf{Answer:} see above.
+\textbf{Answer:} 
+the notion of ``aspect'' adopted in this article has to be explained in more detail.
+We adopt the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
+The general term ``aspect'' is considered to encompass the following two components:
+situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
+and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
+Situation aspect can be further modeled as verb classes (dubbed ``Aktionsart'' in the previous version of this paper) at the lexical level
+and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
+The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
+where everything that might change the aspectual value of a verb is excluded
+and only the inherent features of the verb itself are considered
+(see \citealt[52]{XiaoMcEnery2004} for more details).
+This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
+but its verb class remains the same,
+as the aspectual change can be attributable to other components at the sentential level.
+This section is concerned with the interaction of the reduplication with verb classes,
+while the next section discusses the interaction with viewpoint aspect markers.
+The combination with other constituents such as adjuncts is briefly touched upon below,
+but a detailed discussion has to be left for future research.
 
@@
 
-\textbf{Answer:} fixed.
+\textbf{Answer:} We fixed the typo.
 
@@
 \textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category or valency of the input.
-To improve readability, English examples are used instead now.
+To improve readability, English examples of ``-able'' derivation and ``-ed'' inflection are used instead now.
 
@@
 
-\textbf{Answer:} See above.
+\textbf{Answer:} 
+Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
+The tests of semantic compositionality and conjunction reduction are deemed unreliable,
+and only phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998})
+and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}) remain.
+The explanations to the tests are simplified and illustrated with examples.
+See the answer to Reviewer \ref{sec:1}, point \ref{morph} on page \pageref{morph} for more detail.
 
-\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to
-  exactly. For example: See the answers to Reviewer X, point Y on page Z. If you did something in
-  the text to react, say so. This pleases reviewers. They are the kings/queens and want to be take seriously.}
+%\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to
+%  exactly. For example: See the answers to Reviewer X, point Y on page Z. If you did something in
+%  the text to react, say so. This pleases reviewers. They are the kings/queens and want to be take seriously.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-\textbf{Answer:} reformulate as ``behaves more similar to a word''.
+\textbf{Answer:} We reformulate ``word-like'' as expressions such as ``behaves more similar to a word'', ``is compatible with a lexical analysis''.
 
-\itdopt{St. Mü.: Was hast Du denn hier gemacht? Das scheint im Text jetzt ganz auskommentiert zu sein.}
+%\itdopt{St. Mü.: Was hast Du denn hier gemacht? Das scheint im Text jetzt ganz auskommentiert zu sein.}
 
@@
 \noindent
-\textbf{Answer: } We added a figure with the analysis of \emph{chang2-le-chang2} and some
+\textbf{Answer: } We added a figure with the analysis of \obj{chang2-le-chang2} and some
 accompanying text.

### 2024-09-06 replies-reviews.tex
add explanation to aktionsart

@@
 \textbf{Answer:} 
+In the original version of our paper, \textit{Aktionsart} is used to refer to the classification of lexical verbs based on their aspectual properties.
+This term is first used in this sense by \citet{Agrell1908}.%78
+Since the term \textit{Aktionsart} is used for different senses as well,
+we now refer to this classification as verb class to avoid confusion.
+
 the notion of ``aspect'' adopted in this article has to be explained in more detail.

### 2024-09-06 replies-reviews.tex
add more explanations to Aktionsart

--- 2024-09-06 replies-reviews.tex
@@
 and the behavior of the reduplication is compatible with a lexical analysis.
-The comparison with Parallel Verb Compounds and Serial Verb Constructions are not substantial to our arguments and is thus removed.
+The comparisons with Parallel Verb Compounds and SVCs are not substantial to our arguments and is thus removed.
 See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for more details.
@@
 \textbf{Answer:} 
-the notion of ``aspect'' adopted in this article has to be explained in more detail.
-We adopt the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
-The general term ``aspect'' is considered to encompass the following two components:
-situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
-and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
-Situation aspect can be further modeled as verb classes (dubbed ``Aktionsart'' in the previous version of this paper) at the lexical level
-and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
-The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
-where everything that might change the aspectual value of a verb is excluded
-and only the inherent features of the verb itself are considered
-(see \citealt[52]{XiaoMcEnery2004} for more details).
-This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
-but its verb class remains the same,
-as the aspectual change can be attributable to other components at the sentential level.
-This section is concerned with the interaction of the reduplication with verb classes,
-while the next section discusses the interaction with viewpoint aspect markers.
-The combination with other constituents such as adjuncts is briefly touched upon below,
-but a detailed discussion has to be left for future research.
+In the original version of our paper, \textit{Aktionsart} is used to refer to the classification of lexical verbs based on their aspectual properties.
+This term is first used in this sense by \citet{Agrell1908}. %78
+Since the term \textit{Aktionsart} is used in different senses as well,
+we now refer to this classification as verb class to avoid confusion.
 
-\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}
+Modern approaches to verb classes starts with \citet{Vendler1957}, 
+who proposes four verb classes: state, activity, accomplishment and achievement.
+\citet{Smith1991} adds another verb class: semelfactive.
+These five verb classes can be differentiated using three binary features, as shown in Table~\ref{tab:verbclass} \citep[34, 39]{XiaoMcEnery2004}.
+\begin{table}
+\begin{tabular}{lllll}
+ \hline
+ Verb class & [$\pm$ dynamic] & [$\pm$ durative] & [$\pm$ telic] & Examples\\
+ \hline
+ stative & $-$ & + & $-$ & know, love, believe\\
+ activity & + & + & $-$ & run, walk, swim\\
+ accomplishment & + & + & + & walk to school\\
+ achievement & + & $-$ & + & find, reach, win\\
+ semelfactive & + & $-$ & $-$ & tap, knock\\
+ \hline
+ \end{tabular}    
+ \caption{Verb classes and their aspectual features.}
+  \label{tab:verbclass}
+\end{table}
+
+%\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}
 

### 2024-09-06 replies-reviews.tex
fixed references, add chinese characters

@@
 Regarding volitionality, it should be noted that, as reported in various grammars, while it is generally true that verbs describing events not controlled by an agent cannot be reduplicated, some of them, under certain circumstances (e.g.
-in imperative or conditional sentences, or in causative \obj{rang/jiao/shi} sentences, as in ex.
+in imperative or conditional sentences, or in causative \obj{rang4/jiao4/shi3} sentences, as in ex.
 (15e) provided by the author(s)), can reduplicate (it might be worthwhile to delve into why this occurs in such sentence structures).
@@
 It has been observed that some stative verbs, e.g.
-bing ‘be sick’, are basically change of state predicates, which means that they are dynamic (see e.g.
-Tham 2013: 663; see also Sybesma 1997, Liu 2010, Peck, Lin \& Sun 2013; Basciano 2019).
+\obj{bing4} ‘be sick’, are basically change of state predicates, which means that they are dynamic (see e.g.
+\citealt[663]{Tham2013}; see also \citealt{Sybesma1997, Liu2010, PeckEtAl2013, Basciano2019}).
 The same goes for those verbs expressing psychological states which can have a dynamic interpretation, as e.g.
-liaojié `understand' (Basciano \& Melloni 2017, fn.
-3).
-With regard to achievements, it is worth considering whether, in certain circumstances (the cases in which they are reduplicated), they assume a reading that cancels the felos.
+\obj{liao3jie3} `understand' \citep[fn.
+3]{BascianoMelloni2017}.
+With regard to achievements, it is worth considering whether, in certain circumstances (the cases in which they are reduplicated), they assume a reading that cancels the \textit{telos}.
 Anyway, since these cases are not the rule, I do not think they can be taken as an argument against the constraints on the action type of the base verb.
@@
 (e.g.
-\& (1) — AN/ kan (le ) san ge xidoshi ‘read for three hours’ vs.
-*\& (1) \& =AW kan (le ) kan san ge xicioshi (both reduplication and for X time expressions set a boundary to the event) / IEETS zhéngzai kan / *EAEG TG zhéngzai kan kan).
+看（了）三个小时 \obj{kan4} \obj{(le)} \obj{san1} \obj{ge} \obj{xiao3shi2} `read for three hours' vs.
+*看（了）看三个小时 \obj{kan4} \obj{(le)} \obj{kan4} \obj{san1} \obj{ge} \obj{xiao3shi2} (both reduplication and for X time expressions set a boundary to the event) / 正在看 \obj{zheng4zai4} \obj{kan4} / *正在看看 \obj{zheng4zai4} \obj{kan4} \obj{kan}).
+
 In order to get a clearer picture and to find a semantic explanation for these facts, one should look at what these ‘special’ cases of reduplication have in common and try to draw generalizations: why can some stative and achievement verbs reduplicate under certain circumstances, while other cannot?
@@
 
-compositional (see e.g. kick the bucket, shoot the breeze). Also, take verb-object constructions,
-which are ambiguous between words and phrases: e.g. 1:0> dan-xin ‘take on-heart, worry” has a
+compositional (see e.g. \textit{kick the bucket}, \textit{shoot the breeze}). Also, take verb-object constructions,
+which are ambiguous between words and phrases: e.g. 担心 \obj{dan1-xin1} `take on-heart, worry' has a
 non-compositional meaning, suggesting that it is a word, but is separable, suggesting that it is a
-phrase (see Huang 1984). On p. 14, the author(s) state(s): “The meaning of the reduplication is not
+phrase (see \citealt{Huang1984}). 
+On p. 14, the author(s) state(s): “The meaning of the reduplication is not
 compositional, as it does not mean that the event denoted by the verb happens twice or multiple
@@
 marker le is unexpected. In fact, it is never found in between the two constituents of a compound
-word, as the author(s) also show(s) in (27c). Her (2006: 1282), talking about V-4 géi sequences,
-states that “The simple fact that the V-gei sequence cannot be separated, as in (19¢) indicates its
-lexical integrity”, i.e. they form a single lexical item (745 T fih ji-géi-le ta vs. * 77 T 431 Ji-le géi ta).
-\itdopt{St. Mü.: fix brackets and references to examples. The quoted text contains Chinese
-  characters. Please try to insert them. Also for the examples below.}
+word, as the author(s) also show(s) in (27c). \citet[1282]{Her2006}, talking about V-给 \obj{gei3} sequences,
+states that ``The simple fact that the V-gei sequence cannot be separated, as in (19c) indicates its
+lexical integrity'', i.e. they form a single lexical item (寄给了他 \obj{ji4-gei3-le} \obj{ta1} vs. * 寄了给她 \obj{ji4-le} \obj{gei3} \obj{ta1}).
+%\itdopt{St. Mü.: fix brackets and references to examples. The quoted text contains Chinese
+%  characters. Please try to insert them. Also for the examples below.}
+Even if you assume that aspect markers are suffixes (morphological elements), they should not be placed in between the constituents of compounds, because this violates lexical integrity (as shown in ex.
+27b by the author(s)): the suffix \obj{le} must be placed after the whole complex verb, which forms a single lexical unit, and not within it.
+In fact, in (non-separable) verb-object compounds, which are lexical units, 了 \obj{le} is never placed after the verbal constituent (关心了 \obj{guan1-xin1-le} / *关了心 \obj{guan1-le} \obj{xin1} vs.
+骑了马 \obj{qi2-le} \obj{ma3}).
+It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker /e can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern.
 
-Even if you assume that aspect markers are suffixes (morphological elements), they should not be placed in between the constituents of compounds, because this violates lexical integrity (as shown in ex.
-27b by the author(s)): the suffix /e must be placed after the whole complex verb, which forms a single lexical unit, and not within it.
-In fact, in (non-separable) verb-object compounds, which are lexical units, | /e is never placed after the verbal constituent (F0» T guan-xin-le | *% T > guan-le xin vs.
-% | % gi-le md).
-
-It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker /e can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern.
 Also, I do not understand the comparison with SVCs.
-Let’s say that reduplication is a syntactic phenomenon, but that does not mean that it is a SVC, i.e.
+Let's say that reduplication is a syntactic phenomenon, but that does not mean that it is a SVC, i.e.
 a sequence of verbs or verb phrases in a relation of coordination or subordination, which are basically independent of each other.
@@
 Therefore, syntactic objects should not be included in the reduplication; it is not repetition of phrases.
-Indeed, if the object is part of a non-separable verb-object compound (which is a lexical unit), it is included in the reduplication (F</0> 0> guan-xin guan-xin/*  K> guan-guan xin vs.
-WsBkE tico-tiao wii | * B FEBEE ticown tiaowii).
+Indeed, if the object is part of a non-separable verb-object compound (which is a lexical unit), it is included in the reduplication (关心关心 \obj{guan1-xin1} \obj{guan1-xin1}/*  关关心 \obj{guan1-guan1} \obj{xin1} vs.
+跳跳舞 \obj{tiao4-tiao} \obj{wu3} / * 跳舞跳舞 \obj{tiao4wu3} \obj{tiao4wu3}).
 
@@
 This criterion can only be applied to set apart coordinated phrases from coordinate compound words with a head in common (e.g.
-‘K huiché e ¥4 giché in (33) share the head  ché ‘vehicle’).
+火车 \obj{huo3che1} e 汽车 \obj{qi4che1} in (33) share the head  车 \obj{che1} `vehicle').
 But the examples provided by the author(s) to argue against conjunction reduction with reduplicated verbs are completely different: the verbs do not have the head in common (exx.
@@
 Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
-author(s) say(s): “The following section discusses previous literature which proposed a special
-construction for the reduplication”. However, it becomes evident that the phenomenon under
-examination is entirely different from Mandarin verbal reduplication. Ghomeshi et al. (2004) analyze
+author(s) say(s): ``The following section discusses previous literature which proposed a special
+construction for the reduplication''. However, it becomes evident that the phenomenon under
+examination is entirely different from Mandarin verbal reduplication. \citet{Ghomeshietal2004} analyze
 a phenomenon which is well attested in world languages, even in those without productive
 reduplication, i.e. contrastive focus reduplication/repetition, which involves the repetitions of
-words and sometimes phrases (Oh, we re not LIVING-TOGETHER-living-together, Gomeshi et al.
-2004: 308).
-Their function is “to focus the denotation of the reduplicated element on a more sharply delimited, more specialized, range” (Gomeshi etal.
-2004: 308); for example, in ex.
+words and sometimes phrases (Oh, we re not LIVING-TOGETHER-living-together, \citealt[308]{Ghomeshietal2004}).
+Their function is “to focus the denotation of the reduplicated element on a more sharply delimited, more specialized, range” \citep[308]{Ghomeshietal2004}; for example, in ex.
 (47) cited by the author(s) SALAD-salad means green salad vs.
@@
 This has nothing to do with diminishing verbal reduplication in Mandarin.
-The authors’ endeavor to apply the analysis proposed for contrastive focus reduplication to Mandarin verbal reduplication raises questions about its rationale (why?
+The authors' endeavor to apply the analysis proposed for contrastive focus reduplication to Mandarin verbal reduplication raises questions about its rationale (why?
 These two phenomena are fundamentally distinct and serve different linguistic functions).
-Consequently, attempting to employ the same analytical framework for both is problematic, and, indeed, the author(s) conclude(s) that: “this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese”.
+Consequently, attempting to employ the same analytical framework for both is problematic, and, indeed, the author(s) conclude(s) that: ``this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese''.
 This is precisely because contrastive focus repetition/reduplication is a different phenomenon with a different function, and Mandarin verbal reduplication cannot be analyzed in the same way.
-Furthermore, the author(s) suggest(s) that this approach “[...] also provides a formal account for the phonology of the reduplication”.
+Furthermore, the author(s) suggest(s) that this approach ``[\ldots] also provides a formal account for the phonology of the reduplication''.
 However, contrastive focus reduplication/repetition generally does not involve morpho-phonological readjustment phenomena, which are typically found in reduplication.
-As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).
+As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (\obj{kan4} > \obj{kan4} \obj{kan}).
 
@@
 %% YL
-\item Pp.
+\item p.
 26, lines 24--25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between.
-[] indicates an underspecified list which could be empty or not''.
-However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements.
+\etag indicates an underspecified list which could be empty or not''.
+However, it is not entirely clear what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
 This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
@@
 The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
-
 %\item
@@
 \item
-I would add tones to the pinyin transcription.
+I would add tones to the \textit{pinyin} transcription.
 
 %%%%
-\textbf{Answer:} done
+\textbf{Answer:} We added the tones.
 
@@
 \item
-p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
+p. 18, exx. (39b): to the best of my knowledge, the object can be placed before 一下 \obj{yixia} only in limited cases (pronouns and proper nouns).
 %%%%%%%%%%%%%
@@
 \item
-p. 20, lines 28--31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
-element in the reduplication is the actual verb, which resides under init and proc, and that the
-second element is an aspect marker, which resides in the complement position of proc, as it delimits
-the process of the event”. Based on my understanding, these authors do not claim that the second
+p. 20, lines 28--31: ``\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first
+element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, and that the
+second element is an aspect marker, which resides in the complement position of \textit{proc}, as it delimits
+the process of the event''. Based on my understanding, these authors do not claim that the second
 element serves as an aspect marker. They propose that the verb and the reduplicant are the spell-out
-of two copies of the same lexical item within the vP domain: the reduplicant is the lower copy, in
+of two copies of the same lexical item within the \textit{v}P domain: the reduplicant is the lower copy, in
 complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.
@@
 p.
-32, lines 28--34: “Although these forms are generally considered unacceptable (Li \& Thompson 1981: 30; Hong 1999: 275-276; Basciano \& Melloni 2017: 160; Yang \& Wei 2017: 239), Fan (1964: 269) and Sui (2018: 143) considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.” Given that these patterns were possible in previous stages of the language (see a.0.
-Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.
+32, lines 28--34: ``Although these forms are generally considered unacceptable (\citealt[30]{LiThompson1981}; \citealt[275--276]{Hong1999}; \citealt[160]{BascianoMelloni2017}; \citealt[239]{YangWei2017}), \citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.'' Given that these patterns were possible in previous stages of the language (see a.o.
+\citealt{BascianoMelloni2017}), these rare occurrences can be seen as relics of this usage.
 
@@
 technical terms like LTOP, catering to readers less familiar with them.
+
+\textbf{Answer:} These terms will be explained in detail in point \ref{ltop} on page \pageref{ltop}.
+
+\item
 The authors employ various tests to assert that verb reduplication exhibits more word-like
@@
 Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
+
 Despite these strengths, certain questions warrant attention. The primary concern revolves around
@@
 some, e.g., separate modification of subparts within a constituent.
+
 In light of this, concluding that verb reduplication is more word-like and less phrase-like is
@@
 that verb reduplication should be morphological more convincing.
+
 For additional comments, please refer to the attached PDF file.
 
-\itdopt{St.Mü.: This is the original review. We should say something about it. For example point to
-  explanations above or say that the issues will be taken up below when we discuss the reviewers
-  detailed comments.}
+\textbf{Answer:}
+Based on the suggestions by the reviewers and further literature research, the section on word vs. phrase is drastically revised.
+The different syntactic behaviors of the reduplication and a VP are compared,
+and we conclude that the behavior of the reduplication is compatible with a lexical analysis.
+The comparisons with Parallel Verb Compounds and SVCs are not substantial to our arguments and are thus removed.
+See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for more details. 
+%\itdopt{St.Mü.: This is the original review. We should say something about it. For example point to
+%  explanations above or say that the issues will be taken up below when we discuss the reviewers
+%  detailed comments.}
 
@@
 
-I am curious about the acceptability of this form 'A-kan-kan.' For instance, phrases like 'shuo-kan-kan' ('say-look-look') or 'ting-kan-kan' ('listen-look-look') do not seem acceptable to me.
+I am curious about the acceptability of this form `A-kan-kan.' For instance, phrases like `shuo-kan-kan' (`say-look-look') or `ting-kan-kan' (`listen-look-look') do not seem acceptable to me.
 
@@
 One of the key questions addressed in this paper pertains to whether verb reduplication is best understood as a morphological or a syntactic phenomenon.
-However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication (Xie, 2020).
+However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication \citep{Xie2020}.
 
@@
 
+I have reservations about this argument.Typically, the meaning of a phrase is constructed in a compositional manner, meaning that the individual parts contribute to the overall meaning, or it remains transparent (e.g., \citealt{Schaefer2009}).
+When it comes to verb reduplication, determining whether or not the meaning is transparent\slash compositional might pose a challenge.
+On one hand, the core meaning of a verb often remains unaltered\slash transparent even with reduplication.
+On the other hand, verb reduplication does introduce additional nuances, such as delimitativeness.
+Additionally, the authors suggest that reduplication might be compositional if it expresses a `twice or multiple times' concept, yet non-compositional if it indicates a notion of short duration.
+Leaving aside the question of whether `compositional' can be interpreted in this manner, it remains noteworthy that that what prior studies identified as morphological verb reduplication (AABB form) does convey a sense of repetition (or say, multiple times) and can be considered compositional.
+In summary, whether or not verb reduplication is compositional remains unclear.
+
+R2 comments on example (26).
+
 Example (26) was employed to demonstrate that verb reduplication can be modified by an adverb as a whole but cannot have a part of it modified.
@@
 
-However, the issue at hand is that even a standard verb phrase cannot be modified in this manner. Consider the following examples, in which the phrase 'dakai men' is a phrase rather than a word.
+However, the issue at hand is that even a standard verb phrase cannot be modified in this manner. Consider the following examples, in which the phrase `dakai men' is a phrase rather than a word.
 
-(1) ta qingsheng de dakai men.
-       he  quietly    DE open door
-      'He opened the door quietly.'
+\ea
+\gll ta qingsheng de dakai men.\\
+       he  quietly    \textsc{de} open door\\
+\glt      'He opened the door quietly.'
+\z
 
-(2) * ta dakai qingsheng de men.
-         he open quietly       DE door
-         'He opened the door quietly.'
+\ea[*]{\gll ta dakai qingsheng de men.\\
+         he open quietly       \textsc{de} door\\
+\glt         'He opened the door quietly.'}
+\z
 
@@
 
+R2 comments on the following passage: Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (27).
+
 Examples (27) and (28) serve as illustrations to demonstrate the application of the ``Lexical Integrity Hypothesis'' in distinguishing PVC from SVC.
@@
 construed as a form of phrase-level operation, potentially conflicting with the author's perspective
-of regarding 'le' as a morphological process.
+of regarding `le' as a morphological process.
+
+R2 comments on the following passage:  conjunction reduction does not seem to be possible.
 
@@
 Moreover, in Mandarin, conjunctions can only be employed with nouns and not with verbs phrases or
-clauses (Schafer, 2009). If this holds true, it is less likely to observe conjunction reduction for
+clauses \citep{Schaefer2009}. If this holds true, it is less likely to observe conjunction reduction for
 verb phrases. Consequently, it would be inappropriate to assert that verb reduplication is more
@@
 conjunction reduction.
+
+R2 comments on the following passage: Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status.
+In comparison, Parallel Verb Compounds failed all the tests as well, whereas SVCs passed all of them.
+This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an SVC.
+Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.
 
@@
 %%%%%%%%%%%%%%%%%%%
-\textbf{Answer:} Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
-The different syntactic behaviors of the reduplication and a VP are compared
-and the behavior of the reduplication is compatible with a lexical analysis.
-The comparisons with Parallel Verb Compounds and SVCs are not substantial to our arguments and is thus removed.
-See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for more details.
+\textbf{Answer:} 
+See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for a detailed answer.
 
@@
 \item
+R2 comments on the following passage: Third, idioms (43a) lose their idiomatic meaning when used with verbal classifiers (43b), but maintain their idiomatic meaning with reduplications (43c)
+
 The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
-presence of the number 'san' in (43b). If 'san xia' is replaced with 'yi xia,' which remains a
+presence of the number `san' in (43b). If `san xia' is replaced with `yi xia,' which remains a
 verbal classifier, the idiomatic meaning is perserved. In this case, there appears to be no
@@
 \item
+R2 comments on the following passage: They provided
+22 the lexical rule (48) for reduplication in general, and further proposed \textit{redup-a-lr} and \textit{redup-v-lr} as subtypes of redup-type, as illustrated in (49) and (50) respectively.
+
 It would enhance reader comprehension if the authors could provide a brief illustration of symbols
@@
 proposals in Section 4.
+
+\textbf{Answer:}\label{ltop}
 \itdopt{Stefan}
@@
 \item
+R2 comments on (57).
+
 Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).
@@
 \item
-In Page 2, the draft says that CCL corpus was explored in addition to the author(s)’ intuition.
+In Page 2, the draft says that CCL corpus was explored in addition to the author(s)' intuition.
 I think this corpus-based method to bolster the acceptability judgments of the verbal reduplication expressions would be one of the merits in the current draft.
@@
 Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
-The tests of semantic compositionality and conjunction reduction are deemed unreliable,
-and only phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998})
-and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}) remain.
+We now only use the tests of phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998})
+and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
 The explanations to the tests are simplified and illustrated with examples.

### 2024-09-09 replies-reviews.tex
typeset reviewer replies, add section numbers, fix tones

@@
 
-%\usepackage{csquotes}
+\usepackage{csquotes}
 
@@
 as the aspectual change can be attributable to other components at the sentential level.
-This section is concerned with the interaction of the reduplication with verb classes,
-while the next section discusses the interaction with viewpoint aspect markers.
-The combination with other constituents such as adjuncts is briefly touched upon below,
-but a detailed discussion has to be left for future research.
+Section 2.3.2 is concerned with the interaction of the reduplication with verb classes,
+while the Section 2.3.3 discusses the interaction with viewpoint aspect markers.
+The combination with other sentential components such as adjuncts is also discussed in Section 2.3.4.%is briefly touched upon below,
+%but a detailed discussion has to be left for future research.
 
 Second, there are more examples.
-Regarding volitionality, although (15e) is a causative sentence, (13a--b) are not imperative, conditional or causative (more on this below).
+Regarding volitionality, although (15e) in the previous version of the paper is a causative sentence, (13a--b) in the previous version of the paper (17a--b in the current version) are not imperative, conditional or causative (more on this below).
 Example (\ref{ex:sheng}) shows the same verb \obj{sheng1} `give birth to' as in (15e) reduplicated in a declarative sentence.
@@
 Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
-\objex{Wang2} \objex{An1yu3} is another actor in the series.\\
+\objex{Wang2} \objex{Ānyu3} is another actor in the series.\\
 \\
 \gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}.
-\objex{Wang2} \objex{An1yu3} \objex{ni3} \objex{kuai4dian} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
+\objex{Wang2} \objex{Ānyu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
 Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
@@
 
-With regard to achievements, the reduplication does not seem to cancel the telos.
+With regard to achievements, the reduplication does not seem to cancel the \textit{telos}.
 Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
@@
 \z\z
-The following continuation that cancels the telo is also infelicitous (\ref{ex:telod}).
+The following continuation that cancels the \textit{telos} is also infelicitous (\ref{ex:telod}).
 \ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
@@
 
-Finally, as we discussed in Sec. 2.3.1 in the previous version of the paper, the semantics of the reduplication has the properties of tansitoriness, holisticity and dynamicity.
+Finally, as we discuss in Section 2.3.1, the semantics of the reduplication has the properties of tansitoriness, holisticity and dynamicity.
 This means that the use of reduplication affects the situation aspect at the sentential level.
@@
 
-As noted briefly in Sec. 2.2 in the previous version of the paper,
+As noted briefly in Section 2.2 in the previous version of the paper,
 the reduplication is incompatible with an expression that quantifies the duration or the extent of the event (\ref{ex:syn-quan}),
@@
 the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
-\textit{Le} expresses a situation being realized,
-while \textit{guo4} conveys a situation already experienced,
+\obj{Le} expresses a situation being realized,
+while \obj{guo4} conveys a situation already experienced,
 and thus, both rarely occur in future situations.
@@
 which are frequently used to describe future situations.
+
+We now  dedicate Section 2.3.4 specifically to discuss the interaction of reduplication with duration\slash frequency phrases and with conditional, imperative and causative sentences 
+to highlight the influence of the reduplication on the situation aspect at the sentential level.
 
@@
 骑了马 \obj{qi2-le} \obj{ma3}).
-It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker /e can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern.
+It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker \obj{le} can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern.
 
@@
 \z\z
+
+The above two tests seem to indicate a lexical analysis.
 % If we analyze reduplication as a phrasal operation, we would expect the structure of
@@
 
-Regarding the position of \obj{le}, there are counter-examples that show V-\obj{le-gei3} (\ref{ex:Vgei}) as well as \obj{guan1-le-xin1} `close-\textsc{pfv}-heart, care for' (\ref{ex:guanxin}) are possible.
+Regarding the position of \obj{le}, there are counter-examples that show V-\obj{le-gei3} (\ref{ex:Vgei}) as well as \obj{guan1-le-}\obj{xin1} `close-\textsc{pfv}-heart, care for' (\ref{ex:guanxin}) are possible.
 \ea\label{ex:Vgei}%还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
@@
 \ea\label{ex:guanxin}%许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
-\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-xin1}.\\
+\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-}\obj{xin1}.\\
 many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\\jambox{(CCL)}
@@
 
-Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as reduplication) in other languages
-than syntactic reduplication (below as repetition \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
+Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as \textit{reduplication}) in other languages
+than syntactic reduplication (below as \textit{repetition} \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
 \citet[35--36]{Gil2005} considers non-iconicity and having only two copies as sufficient but not necessary conditions for reduplication.
@@
 \obj{le} `\textsc{pfv}' marks the perfective aspect.
-The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Semantics Section.
+The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.
 
@@
 %明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
-\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{liang2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\footnotemark\\
+\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{lian2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\footnotemark\\
 Ming agian call Qi also call Ming in.succession call two call Qi thus bow\\
@@
 \z
-\footnotetext{\obj{Song4dai3} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p. 519 as cited in \citet[13]{Zhang2000}}
+\footnotetext{\obj{Song4dai4} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p. 519 as cited in \citet[13]{Zhang2000}}
 In this case, \obj{yi1} `one' cannot be replaced by other numerals.
@@
 
-Besides the obvious conceptual reason that  \obj{yi1} `one' means `little, few',
+Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little, few',
 there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
@@
 \textbf{Answer:}
-As explained in point \ref{verbclass} on page \pageref{verbclass}, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
-The incompatibility with the progressive aspect marker is explained in the Semantics section.
+As explained in point \ref{verbclass} on page \pageref{verbclass}, we propose that verbs of all lexical aspects can be reduplicated given suitable contexts.
+The incompatibility with the progressive aspect marker is explained in Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.
 %%%%%%%%%%%%%%%%%%%%%
@@
 \noindent
-\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''
+\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of \textit{proc} and serves as an event delimiter.''
 
@@
 adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
-Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
+Recursion Semantics \citep{Copestakeetal2005}, presents advantages over prior analyses.
 
@@
 \item
+\begin{displayquote}
 R2 comments on the following passage: A-\obj{kan4-kan4}
+\end{displayquote}
 
@@
 \item
-R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
-AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-kan, A-kan-kan,
-AAB, A-yi-AB, A-le-AB will also be mentioned.
+\begin{displayquote}
+R2 comments on the following passage: The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le-yi}-A, ABAB and
+AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-\textit{kan}, A-\textit{kan-kan},
+AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned.
+\end{displayquote}
 
@@
 This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
-This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi2-zhi3-dian2-dian3} `point-point-gesture-gesture, gossip'.
+This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi3-zhi3-dian3-dian3} `point-point-gesture-gesture, gossip'.
 %Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
@@
 \item
+\begin{displayquote}
 R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
@@
 non-compositionality suggests that a reduplication is more word-like.
+\end{displayquote}
 
@@
 
+\begin{displayquote}
 R2 comments on example (26).
+\end{displayquote}
 
@@
 
+\begin{displayquote}
 R2 comments on the following passage: Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (27).
+\end{displayquote}
 
@@
 
-In reference to (25), it is explained that the Lexical Integrity Hypothesis posits that 'No
+In reference to (25), it is explained that the Lexical Integrity Hypothesis posits that `No
 phrase-level rule may affect a proper subpart of a word.' However, it is noteworthy that the authors
@@
 
+\begin{displayquote}
 R2 comments on the following passage:  conjunction reduction does not seem to be possible.
+\end{displayquote}
 
@@
 
+\begin{displayquote}
 R2 comments on the following passage: Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status.
@@
 Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.
+\end{displayquote}
 
@@
 However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase.
-This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like 'Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)).
+This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like `Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)).
 Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate.
@@
 \item
+\begin{displayquote}
 R2 comments on the following passage: Third, idioms (43a) lose their idiomatic meaning when used with verbal classifiers (43b), but maintain their idiomatic meaning with reduplications (43c)
+\end{displayquote}
 
@@
 \item
+\begin{displayquote}
 R2 comments on the following passage: They provided
 22 the lexical rule (48) for reduplication in general, and further proposed \textit{redup-a-lr} and \textit{redup-v-lr} as subtypes of redup-type, as illustrated in (49) and (50) respectively.
+\end{displayquote}
 
@@
 \item
+\begin{displayquote}
 R2 comments on (57).
+\end{displayquote}
 
@@
 another constraint. A constraint that is a subtype in the hierarchy. The type
-perfective-reduplication-lr in (51), which says that the PHON value of the daughter \ibox{1} appears
-twice in the PHON value of the mother with some other material (\etag) between the two occurrences of \ibox{1}.
+\type{perfective-reduplication-lr} in (51), which says that the PHON value of the daughter \ibox{1} appears
+twice in the PHON value of the mother with some other material ( \etag ) between the two occurrences of \ibox{1}.
 %%%%%%%%%%%%%%%%%%%%
@@
 \textbf{Answer:} 
-In the original version of our paper, \textit{Aktionsart} is used to refer to the classification of lexical verbs based on their aspectual properties.
+In the previous version of our paper, \textit{Aktionsart} is used to refer to the classification of lexical verbs based on their aspectual properties.
 This term is first used in this sense by \citet{Agrell1908}. %78
@@
 
-Modern approaches to verb classes starts with \citet{Vendler1957}, 
+Modern approaches to verb classes start with \citet{Vendler1957}, 
 who proposes four verb classes: state, activity, accomplishment and achievement.
@@
 The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
-Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
+\begin{displayquote}
+\citet{Duanmu1998} and \citet{Schaefer2009} proposed the following four tests to distinguish words from phrases
 in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
 conjunction reduction.
+\end{displayquote}
 

### 2024-09-09 chapters/ch02-Phenomenon.tex
typeset reviewer replies, add section numbers, fix tones

@@
 \gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}.
-\objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
+\objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
 Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
@@
 \z\z
+The above two tests seem to indicate a lexical analysis.
 

### 2024-09-09 replies-reviews.tex
add tones, fix typos, add a footnote based on reviewer replies

@@
 Second, there are more examples.
-Regarding volitionality, although (15e) in the previous version of the paper is a causative sentence, (13a--b) in the previous version of the paper (17a--b in the current version) are not imperative, conditional or causative (more on this below).
+Regarding volitionality, although (15e) in the previous version of the paper (25c in the current version) is a causative sentence, (13a--b) in the previous version of the paper (17a--b in the current version) are not imperative, conditional or causative (more on this below).
 Example (\ref{ex:sheng}) shows the same verb \obj{sheng1} `give birth to' as in (15e) reduplicated in a declarative sentence.
@@
 First, the modification test suggests that subparts of a word cannot be modified at a phrasal level.
-This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g. an AP.
+This is possible for a VP (\ref{ex:modVP}), as the NP inside of the VP can be modified by e.g.\ an AP.
 \ea\label{ex:modVP} %开红色的门
@@
 \z
-In contrast, the individual verbs in reduplication cannot be modified by an e.g. AdvP.
+In contrast, the individual verbs in reduplication cannot be modified by an e.g.\ AdvP.
 (\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
+This shows that it has nothing to do with the relative position of the verb and the AdvP.
 \ea[*]{\label{ex:modVV} %看偷偷地看
@@
 \obj{le} `\textsc{pfv}' marks the perfective aspect.
-The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.
+The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.
 
@@
 
-Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little, few',
+Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little/few',
 there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.

### 2024-09-09 chapters/ch02-Phenomenon.tex
add tones, fix typos, add a footnote based on reviewer replies

@@
 
- \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compared the AA, ABAB and AABB forms of reduplication 
+ \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compare the AA, ABAB and AABB forms of reduplication 
 and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
-Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identified that AA and ABAB have a diminishing meaning, 
+Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 
 namely that the event happens for a short duration or to a small extent. 
 By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
-\citet[Sec. 3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
+\citet[Sec. 3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
 whereas the productivity of AABB is low. 
-She further showed that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
-\citet[277]{Fan1964} proposed that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
+She further shows that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
+\citet[277]{Fan1964} proposes that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
 while AABB developed from the reiterative rhetoric from Old Chinese. 
@@
 The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
-AA-\textit{kan}, A-\textit{kan}-\textit{kan}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
+AA-\obj{kan4}, A-\obj{kan4}-\obj{kan4}, AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned occasionally to provide further arguments.
 In what follows, the term \textit{reduplication} will be used  to refer specifically to the AA, A\hyp{}\textit{yi}\hyp{}A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms, if not specified otherwise.
@@
 
-Secondly, \citet[319]{SuiHu2016} show that the reduplication cannot co-occur with a duration or frequency phrase (\ref{ex:durfreq}).
+Secondly, \citet[319]{SuiHu2016} show that the reduplication cannot co-occur with a duration or a frequency phrase (\ref{ex:durfreq}).
 \ea\label{ex:durfreq}
@@
 
-The reduplication has a \textit{delimitativeness} meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
+The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
 4.3]{XiaoMcEnery2004}).
@@
 She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
-\citet[Sec. 5]{Xing2000} considers that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
-The former conveys a casual attitude whereas the latter sounds more serious.%\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
-However, he stressed that there is no difference in the delimitative semantics of both forms,
+\citet[Sec. 5]{Xing2000} considers that the major  difference  between AA and A-\textit{yi}-A lies in the speaker's attitude.
+The former conveys a casual attitude whereas the latter sounds more serious. %\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
+However, he stresses that there is no difference in the delimitative semantics of both forms,
 and that the variance in meaning is a pragmatic one.
@@
 as he argues that AA and A-\textit{yi}-A can be used interchangeably in most cases,
-and the specific differences in meaning only arise from specific contexts as a whole.
+and the differences in meaning only arise from specific contexts as a whole.
 \citet[15]{Yang2003} suggests that AA and A-\textit{yi}-A have the same core meaning, while A-\textit{yi}-A implies a slightly more serious attitude than AA due to its length.
@@
 It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
-\citep[155]{XiaoMcEnery2004} classify \obj{bing4} `be sick' as a stative verb.
+\citet[155]{XiaoMcEnery2004} classify \obj{bing4} `be sick' as a stative verb.
 Indeed, compared  to the questionable reduplication of \obj{bing4} `be sick' in (\ref{ex:redup-stat}),  
- the reduplication of the activity verb \textit{kan} `watch' in (\ref{ex:redup-actV})
-and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) are readily acceptable.
+ the reduplication of the activity verb \obj{kan4} `watch' in (\ref{ex:redup-actV})
+and that of the semelfactive verb \obj{ke2sou4} `cough' in (\ref{ex:redup-semel}) are readily acceptable.
 
@@
     Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
-    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
+    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g.\ \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
     and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
@@
 However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat5}) can be found.
-Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' are reduplicated.
+Here, achievement verbs like \obj{wang4} `forget' and \obj{sheng1} `give birth to' are reduplicated.
 
@@
 \glt `Let's wait until people forget this incident a little bit and then talk about it.'\\
-\footnotetext{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
+\footnotetext{\objex{Liu2}, \objex{Zhen1}. 1963. \obj{Chang2} \obj{chang2} \obj{de} \obj{liu2shui3} \textit{[Long long water]}, 72. Beijing: The Writers Publishing House.}
 %\ex\label{ex:redup-achi-stat2}
@@
 \z\z
-The following continuation that cancels the \textit{telo} is also infelicitous (\ref{ex:telod}).
+The following continuation that cancels the \textit{telos} is also infelicitous (\ref{ex:telod}).
 \ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
@@
 
-As mentioned in \sectref{sec:forms}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
+As mentioned in \sectref{sec:syn-dis}, the reduplication can only be marked by the perfective aspect marker \textit{le} but not other aspect markers.\footnote{
 There is no consensus on which elements exactly are considered aspect markers in Mandarin Chinese. 
@@
 %(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
-The results argue for a morphological analysis of reduplication.
+The results are compatible with a lexical analysis.
 
@@
 
-  \ex \gll \objex{jin4-chu1} $\rightarrow$ \obj{jin4}-\obj{jin4}-\obj{chu1}-\obj1{chu}\\
+  \ex \gll \objex{jin4-chu1} $\rightarrow$ \obj{jin4}-\obj{jin4}-\obj{chu1}-\obj{chu1}\\
   enter-exit {} enter-enter-exit-exit\\ \jambox{\citep[88]{Xie2020}}
@@
 %And inflections of tense in German do not change the valency of the input verb.
-Further, if \obj{le} is considered to be a morphological element (e.g.
-\citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
+Further, if \obj{le} is considered to be a morphological element (e.g.\ \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
 process either.
@@
 and uses this as evidence for analyzing it as a single lexical item 
-(\obj{ji4-gei3-le} \obj{ta1} `send-give-\textsc{pfv} he, sent him' vs. ? \obj{ji4-le-gei3} \obj{ta1} `send-\textsc{pfv}-give he').
+(\obj{ji4-gei3-le} \obj{ta1} `send-give-\textsc{pfv} he, sent him' vs. ?\ \obj{ji4-le-gei3} \obj{ta1} `send-\textsc{pfv}-give he').
 In non-separable VO compounds, \obj{le} insertion also does not seem to be possible 
-(\obj{guan1-xin1-le} `close-heart-\textsc{pfv}, cared for' vs. ? \obj{guan1-le-}\obj{xin1} `close-\textsc{pfv}-heart').
-The AABB form of reduplication also only accepts \obj{le} to its right but not in-between (\ref{ex:yaohuang}).
+(\obj{guan1-xin1-le} `close-heart-\textsc{pfv}, cared for' vs. ?\ \obj{guan1-le-}\obj{xin1} `close-\textsc{pfv}-heart').
+The AABB form of reduplication also only accepts \obj{le} to its right but not in between (\ref{ex:yaohuang}).
 \ea\label{ex:yaohuang} %我趁机从大货车以及左边的轿车车门上贴肤而过，	摇摇晃晃了	几下
@@
 
-In respond to this, we found counter-examples that show \obj{le} insertion in-between V-\obj{gei3} (\ref{ex:Vgei}) as well as \obj{guan1-xin1} `close-heart, care for' (\ref{ex:guanxin}) is possible.
+In respond to this, we found counter-examples that show \obj{le} insertion in between V-\obj{gei3} (\ref{ex:Vgei}) as well as \obj{guan1-xin1} `close-heart, care for' (\ref{ex:guanxin}) is possible.
 \ea\label{ex:Vgei}%还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
@@
 
-In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.),
+In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides psycholinguistic evidence),
 and the patterns discussed here constitute a different process than the AABB pattern
@@
 
-It is, therefore, necessary to resort to other tests that are intended to distinguish words from phrases. 
+It is, therefore, necessary to resort to other tests that are intended to distinguish words from phrases in Mandarin Chinese. 
 %Furthermore, we applied the same tests to Parallel Verb Compounds, which are inarguably words (because at least one element in the compound cannot appear in a sentence independently), 
@@
 Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
-This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in-between.
+This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in between.
 \ea\label{ex:inVCP}%开两次门

### 2024-09-09 chapters/ch05-Analysis.tex
add tones, fix typos, add a footnote based on reviewer replies

@@
 
-\citet[246]{MuellerLipenkova2013} proposed the perfective lexical rule given in (\ref{avm:pfv-old}), 
+\citet[246]{MuellerLipenkova2013} propose the perfective lexical rule given in (\ref{avm:pfv-old}), 
 adapted to the formalization adopted in the current paper.
@@
 Specifically, \type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} specifies the middle phonological material as
-\phonliste{ le, yi }, while \type{a-le-a} specifies it as \phonliste{ le } only.
+\phonliste{ le, yi }, while \type{a-le-a} specifies it as \phonliste{ le } only.\footnote{
+A reviewer wants to know what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
+He/she states that this aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
+
+\obj{le} `\textsc{pfv}' marks the perfective aspect.
+The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in Section~\ref{sec:aspM}.
+
+As for \obj{yi} `one', its use stems from the historical development of delimitative verbal reduplication but is synchronically opac.
+\citet[13--15]{Zhang2000} shows that delimitative verbal reduplication originates from the ``V + numeral + verbal classifier'' phrase,
+where the verbal classifier is borrowed from a verb of the same form, as shown in (\ref{ex:hist1}) from \obj{Song4dai4} \obj{juan4}: \obj{Xu1tang2} \obj{He2shang} \obj{yu3lu4} \textit{[The Song dynasty volume: Quotations from Abbot Xutang]} p.
+387 as cited in \citet[12]{Zhang2000}.
+\ea\label{ex:hist1}
+%明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
+\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{lian2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\\
+Ming agian call Qi also call Ming in.succession call two call Qi thus bow\\
+\glt `Ming called again. Qi called too. Ming called twice. Qi thus bowed.'
+\z
+Here the numeral refers to the actual number of the action taking place
+and can be any number.
+This evolves into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
+but simply conveys that the action happens in a short period of time or for only few times. 
+Consider (\ref{ex:hist2}) from \obj{Song4dai4} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p.
+519 as cited in \citet[13]{Zhang2000}.
+\ea\label{ex:hist2}
+%且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
+\gll \objex{qie3} \obj{xie1-yi-xie1} \objex{le}, \objex{qu4} \objex{zuo4} \objex{di4}.\\
+just rest-one-rest \textsc{ptc} go sit ground\\
+\glt `(Let me) just take a rest and go sit on the ground.'
+\z
+In this case, \obj{yi1} `one' cannot be replaced by other numerals.
+Since V-\obj{yi}-V does not express the actual number of the action anymore,
+it became possible to delete the \obj{yi1} `one',
+hence the use of the VV (or AA) form, too.
+
+Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
+This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure
+and is only there as a historical remnant.
+In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds
+
+Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little/few',
+there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
+In Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
+where the \obj{li} is fixed and also does not bear any meaning.
+\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
+and the second syllable in A-\obj{li}-AB occupies an unstressed position.
+We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
+This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
+But a phonological account is out of the scope of this paper and has to be left for further research.
+
+The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
+}
 
@@
 
-\caption{Analysis of \emph{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
+\caption{Analysis of \obj{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
 \end{figure}
 
-The figure shows how the lexical item for \emph{chang2} `to taste' is inserted as a daughter into
+The figure shows how the lexical item for \obj{chang2} `to taste' is inserted as a daughter into
 the \type{a-le-a-lr} lexical rule. The arguments of \emph{chang2} `to taste' are represented within the \spr and
-the \compsl (see \citet{GSag2000a-u} for English) and the respective argument NPs are linked to the
+the \compsl (see \citealt{GSag2000a-u} for English) and the respective argument NPs are linked to the
 arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
@@
 \type{perfective-reduplication-lr} in (\ref{avm:pfv-redup}). The \textsc{phon} value of the mother
-is the concatentation of \emph{chang2}, \emph{le} and \emph{chang2}, as specified in the constraint
-on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \emph{chang2-le-chang2} then
+is the concatentation of \obj{chang2}, \obj{le} and \obj{chang2}, as specified in the constraint
+on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \obj{chang2-le-chang2} then
 combines with its object forming a VP. This VP is combined with the subject resulting in a complete
-verbal projection, a sentence. \emph{chang-le-chang} behaves in the same way as the simple \emph{chang2}.
+verbal projection, a sentence. \obj{chang2-le-chang2} behaves in the same way as the simple \obj{chang2}.
 
@@
 \glt `Let me arrange it a little bit!'
-\footnotetext{\textit{Yuanqu xuan: Luzhailang [Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
+\footnotetext{\obj{Yuan2qu3} \obj{xuan3}: \obj{Lu3zhai1lang2} \textit{[Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
 
@@
 \glt `Inquire about it a little bit!'
-\footnotetext{\textit{Yuan Ming juan: Piaotongshi [Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
+\footnotetext{\obj{Yuan2} \obj{Ming2} \obj{juan4}: \obj{Piao2tong1shi4} \textit{[Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
 
@@
 \glt `Each one nodded his head and smiled a little bit.'
-\footnotetext{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
+\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
 
@@
 \glt `He smiled a little bit and meditated a little bit.'
-\footnotetext{Rou, Shi. 1975. \textit{Roushi xiaoshuo xuanji [Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
+\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
 
@@
 \glt `[He] very seriously straightened the nearsighted glasses quickly.'
-\footnotetext{Li, Jieren. 1962. \textit{Da bo [Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
+\footnotetext{\objex{Li3}, \objex{Jie2ren2}. 1962. \obj{Da4} \obj{bo1} \textit{[Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
 
@@
 2]{Her1996}; \citeyear[Sec.
-3.1]{Her2010}) argued that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
+3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
     Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.

### 2024-09-30 chapters/ch02-Phenomenon.tex
fixed spacing after "Sect."

--- 2024-09-05 chapters/ch02-Phenomenon.tex
@@
 By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
-\citet[Sec. 3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
+\citet[Sec.\,3.1]{Xie2020} also found that AA and ABAB have relatively high productivity, 
 whereas the productivity of AABB is low. 
@@
 The reduplication has a \textit{delimitativeness} meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
-4.3]{XiaoMcEnery2004}).
+\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}).
 To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
@@
  \citet[276]{Fan1964} further proposes a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
- \citet[Sec. 3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.
+ \citet[Sec.\,3.1.3]{Zhu1998} suggests that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.
 
@@
 She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
-\citet[Sec. 5]{Xing2000} considers that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
+\citet[Sec.\,5]{Xing2000} considers that the major  difference in meaning  between AA and A-\textit{yi}-A lies in the speaker's attitude.
 The former conveys a casual attitude whereas the latter sounds more serious.%\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
@@
 
-As a reviewer points out, \citet[Sec. 3.3]{Tham2013} considers  \obj{bing4} `be sick' to be a basic change of state (COS) verb, i.e. `become sick'.
+As a reviewer points out, \citet[Sec.\,3.3]{Tham2013} considers  \obj{bing4} `be sick' to be a basic change of state (COS) verb, i.e. `become sick'.
 In contrast, she uses \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as examples of stative verbs.
@@
 let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
-and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
+and examples in  \citet[Sec.\,3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
 as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
-    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
-    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
-    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
+    Note that most examples of ILSs in \citet[Sec.\,3.3.3]{XiaoMcEnery2004} are adjectives.
+    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec.\,2.2]{Tsao2001}, \citealt[Sec.\,4.1]{FanSongBond2015}, \citealt[Sec.\,3]{Sui2018}),
+    and further, COS verbs can be systematically derived from adjectives \citep[Sec.\,3]{Tham2013},
     these predicates are not included in our examples.}
@@
 The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
-\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec. 4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
+\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981}, \citet[Sec.\,4.1]{Dai1992} and \citet[4--5]{Liao2014} list reduplication under morphological processes. 
 By contrast, \citet[23]{Arcodiaetal2014}, \citet{Xiong2016}, \citet[146]{BascianoMelloni2017}, \citet[229--231]{YangWei2017}, \citet[330]{MelloniBasciano2018} and \citet{Xie2020}  claim it to be syntactic.
@@
 This section reviews the arguments in \citet{Xie2020},
-and applies tests from \citeauthor{Dai1992} (\citeyear[Sec. 7]{Dai1992}, \citeyear[Sec. 2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
+and applies tests from \citeauthor{Dai1992} (\citeyear[Sec.\,7]{Dai1992}, \citeyear[Sec.\,2.3--2.4]{Dai1998}) to distinguish words from phrases in Mandarin Chinese.
  %applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
@@
 and the patterns discussed here constitute a different process than the AABB pattern
-(see the discussions above, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
+(see the discussions above, also \citealt[Sec.\,4.3]{Deng2013}, \citealt[Sec.\,2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
 it is not surprising that \obj{le} occurs at a different position.
@@
 %As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
-%As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec.
-3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers  in Mandarin Chinese (\textit{le}, \textit{zhe} and \textit{guo}) to be morphological elements.
+%As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec.\,3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers  in Mandarin Chinese (\textit{le}, \textit{zhe} and \textit{guo}) to be morphological elements.
 E.g.

### 2024-09-30 chapters/ch04-Previous.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers

@@
 We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
-In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
+In this case, it is easy to interpret \obj{yi2} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
 but as duration adverbials as a whole,
@@
 framework of First Phase Syntax \citep{Ramchand2008}.
-\citet{Ramchand2008} propose that an event is comprised of the following phrases: 
+\citet{Ramchand2008} proposes that an event is comprised of the following phrases: 
 the causative subevent (\textit{init}P), the process subevent (\textit{proc}P) and the result subevent (\textit{res}P), which are ordered hierarchically, as illustrated in \figref{tree:ramchand}.\footnote{
@@
  \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
-He observed that  \obj{zhe} `\textsc{prog}', \obj{le} `\textsc{pfv}' and \obj{wan2} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}),
+He observes that  \obj{zhe} `\textsc{prog}', \obj{le} `\textsc{pfv}' and \obj{wan2} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}),
 while \obj{zai4} `\textsc{dur}' and \obj{guo4} `\textsc{exp}' can occur without further information (\ref{ex:complete}).
@@
 He thus proposed three aspect positions under TP.
-\textit{zai} and \textit{guo} reside under Asp$_1$, while \textit{zhe} and \textit{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \obj{wan2} can only occur with certain types of predicate.
+\obj{zai4} and \obj{guo4} reside under Asp$_1$, while \obj{zhe} and \obj{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \obj{wan2} can only occur with certain types of predicate.
 This differentiation does not play a role for our purpose and will not be further discussed here.}
@@
         [...
-        [AspP$_1$ (outer aspect) [Asp$_1$\\zai/guo]
+        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo4}]
         [\textit{v}P [\textit{v}]
-        [AspP$_2$ (middle aspect) [Asp$_2$\\zhe/le/reduplication]
-        [VP [V-Asp$_3$ (inner aspect)\\wan]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe}/\obj{le}/reduplication]
+        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
         ]
@@
 \citet*{FanSongBond2015} provide a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
-They consider reduplication to be a morphological process and modeled it via lexical rules.
+They consider reduplication to be a morphological process and model it via lexical rules.
 They provide the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
@@
   lexical rules \citep{BC99a,Meurers2001a} despite the notation that is commonly assumed.
+
+  \textsc{hook} is a technical feature for sharing information. \textsc{ltop} and \textsc{lbl} will
+  be explained in Section~\ref{sec:analysis} below.
 }
@@
 This is not true. 
-\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec. 3.1]{Xie2020}  all considered both AA and ABAB to be productive,
-and \citet[36]{Xing2000stat} concluded that AAB is productive as well.
+\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec. 3.1]{Xie2020}  all consider both AA and ABAB to be productive,
+and \citet[36]{Xing2000stat} concludes that AAB is productive as well.
 Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.

### 2024-09-30 chapters/ch01-Intro.tex
spacing

@@
 In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
-4.3]{XiaoMcEnery2004}).
+\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}).
 This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
@@
 	\ex
-	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\objex{chang} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
+	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\obj{chang} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
 	please you taste-taste this \textsc{clf} dish\\

### 2024-09-30 chapters/ch02-Phenomenon.tex
spacing

--- 2024-09-09 chapters/ch02-Phenomenon.tex
@@
 By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
-\citet[Sec. 3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
+\citet[Sec.\,3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
 whereas the productivity of AABB is low. 
@@
 
-The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.
-4.3]{XiaoMcEnery2004}).
+The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}).
 To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
@@
 She thus assumed that AA is merely a form of A-\textit{yi}-A, where the \textit{yi} is omitted phonologically.
-\citet[Sec. 5]{Xing2000} considers that the major  difference  between AA and A-\textit{yi}-A lies in the speaker's attitude.
+\citet[Sec.\,5]{Xing2000} considers that the major  difference  between AA and A-\textit{yi}-A lies in the speaker's attitude.
 The former conveys a casual attitude whereas the latter sounds more serious. %\footnote{This can be a register effect. Register project sponsorship xxxxxxx}
@@
 let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
-and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
+and examples in  \citet[Sec.\,3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
 as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
-    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
-    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g.\ \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
-    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
+    Note that most examples of ILSs in \citet[Sec.\,3.3.3]{XiaoMcEnery2004} are adjectives.
+    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g.\ \citealt[Sec.\,2.2]{Tsao2001}, \citealt[Sec.\,4.1]{FanSongBond2015}, \citealt[Sec.\,3]{Sui2018}),
+    and further, COS verbs can be systematically derived from adjectives \citep[Sec.\,3]{Tham2013},
     these predicates are not included in our examples.}

### 2024-09-30 chapters/ch04-Previous.tex
spacing

@@
 This is not true. 
-\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec. 3.1]{Xie2020}  all consider both AA and ABAB to be productive,
+\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec.\,3.1]{Xie2020}  all consider both AA and ABAB to be productive,
 and \citet[36]{Xing2000stat} concludes that AAB is productive as well.

### 2024-09-30 chapters/ch05-Analysis.tex
spacing

@@
 Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
-    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.
-2]{Her1996}; \citeyear[Sec.
-3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
+    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.\,2]{Her1996}; \citeyear[Sec.\,3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
     Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.

### 2024-09-30 replies-reviews.tex
AABB comment, features ARG0-3 erklärt

@@
 
-\itdopt{Stmü: Fix examples and referecnes to them.}
+%\itdopt{Stmü: Fix examples and referecnes to them.}
 
@@
 
-\itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
-  adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
-  spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
-nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}
+Note that technically accounting for AABB under current assumptions is not difficult. The phonology
+can be split into two parts A and B and be combined to yield AABB in the output of a lexical
+rule. What has to be examined carefully in future work
+is the empirical domain of these reduplications.
+
+% \itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
+%   adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
+%   spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
+% nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}
 
@@
 \textbf{Answer:}\label{ltop}
-\itdopt{Stefan}
+We added a footnote about \textsc{hook} and explained \textsc{ltop}, \textsc{ind} and \textsc{arg}
+in the analysis section.
 

### 2024-09-30 chapters/ch05-Analysis.tex
AABB comment, features ARG0-3 erklärt

@@
 \textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
-argument. The list of relations contains so-called elementary predications. There is no complicated
+argument (\textsc{arg0}, \ldots, \textsc{arg3} are feature names for arguments. The values are
+indices or events similar to variables in normal predicate logic.). The list of relations contains so-called elementary predications. There is no complicated
 embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The

### 2024-09-30 replies-reviews.tex
fixed typos, formulations

@@
 another constraint. A constraint that is a subtype in the hierarchy. The type
-\type{perfective-reduplication-lr} in (51), which says that the PHON value of the daughter \ibox{1} appears
+\type{perfective-reduplication-lr} in (51) (59 in the current version of the paper), which says that the PHON value of the daughter \ibox{1} appears
 twice in the PHON value of the mother with some other material ( \etag ) between the two occurrences of \ibox{1}.

### 2024-09-30 chapters/ch01-Intro.tex
fixed typos, formulations

@@
 The data in this paper was drawn from several sources.
-In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} and the BCC corpus \citep{BCC} was also consulted.
+In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} and the BCC corpus \citep{BCC} were also consulted.
 Further, examples from novels and plays written by native speakers were considered.

### 2024-09-30 chapters/ch02-Phenomenon.tex
fixed typos, formulations

@@
 On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
-and indeed \citet[669--670]{Tham2013} herself noted,
+and indeed \citet[669--670]{Tham2013} herself note,
 verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
@@
 The perfective aspect marker \obj{le} is compatible with reduplication while the experiential aspect marker \obj{guo4} is not.
-\citet[128--131]{XiaoMcEnery2004} stated that \obj{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
+\citet[128--131]{XiaoMcEnery2004} state that \obj{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
 It can be combined with a situation with a dynamic internal structure, such as crying in (\ref{ex:cry}).
@@
 
-The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{ \citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
+The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{\citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
 This is  because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent,
@@
 
-In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides psycholinguistic evidence),
+In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provide psycholinguistic evidence),
 and the patterns discussed here constitute a different process than the AABB pattern
@@
 %We then compared the test results of these three kinds of expressions to see whether the reduplication behaves in a more similar way to Parallel Verb Compounds or to {SVC}s.
- \citeauthor{Dai1992} (\citeyear[32--33]{Dai1992}, \citeyear[117--120]{Dai1998}) proposes the modification and the expansion tests to distinguish words from phrases in Mandarin Chinese.
+ For this purpose, \citeauthor{Dai1992} (\citeyear[32--33]{Dai1992}, \citeyear[117--120]{Dai1998}) proposes the modification and the expansion tests.
 %These tests requires further clarifications.
@@
 \z\z
-The above two tests seem to indicate a lexical analysis.
+The above two tests seem to indicate a lexical analysis for reduplication.
 
 Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as \textit{reduplication}) in other languages
-than syntactic reduplication (below as \textit{repetition} \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
+than syntactic reduplication (below as \textit{repetition}; \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
 \citet[35--36]{Gil2005} considers non-iconicity and having only two (but not more) copies as sufficient but not necessary conditions for reduplication.
 He further proposes building one intonational group as sufficient and necessary condition for reduplication (p. 36).
-All three conditions are true for verbal reduplication in Mandarin Chinese (see \citealt[154]{Sui2018} on intonation of verbal reduplication in Mandarin Chinese).
+All three conditions are true for verbal reduplication in Mandarin Chinese (see \citealt[154]{Sui2018} on the intonation of verbal reduplication in Mandarin Chinese).
 \citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.

### 2024-09-30 chapters/ch04-Previous.tex
fixed typos, formulations

@@
 One reviewer suggests that the loss of the idiomatic meaning in (\ref{ex:clf-idiom}) but not in (\ref{ex:redup-idiom}) may be attributed to the use of the numeral \obj{san1} `three' in (\ref{ex:clf-idiom}),
-because if \obj{san1} \obj{xia3} `three times' is replaced with \objex{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
+because if \obj{san1} \obj{xia3} `three times' is replaced with \obj{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
 We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special, 
@@
 
-\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
+\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assume that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
 and that the second element is the copy of the verb, which resides in the complement position of \textit{proc} and serves as an event delimiter.

### 2024-09-30 chapters/ch05-Analysis.tex
fixed typos, formulations

@@
 \gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{lian2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\\
-Ming agian call Qi also call Ming in.succession call two call Qi thus bow\\
-\glt `Ming called again. Qi called too. Ming called twice. Qi thus bowed.'
+Ming again yell Qi also yell Ming in.succession yell two yell Qi thus bow\\
+\glt `Ming yelled again. Qi yelled too. Ming yelled twice. Qi thus bowed.'
 \z
@@
 and can be any number.
-This evolves into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
+This evolved into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
 but simply conveys that the action happens in a short period of time or for only few times. 
@@
 there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
-In Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
+In Mandarin Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
 where the \obj{li} is fixed and also does not bear any meaning.
@@
 The figure shows how the lexical item for \obj{chang2} `to taste' is inserted as a daughter into
-the \type{a-le-a-lr} lexical rule. The arguments of \emph{chang2} `to taste' are represented within the \spr and
+the \type{a-le-a-lr} lexical rule. The arguments of \obj{chang2} `to taste' are represented within the \spr and
 the \compsl (see \citealt{GSag2000a-u} for English) and the respective argument NPs are linked to the
@@
 Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
-Although these forms are generally considered unacceptable \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}}, 
-\citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognized that these two forms are rare.
+Although these forms are considered unacceptable by some authors \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}},
+\citet[269]{Fan1964} and \citet[143]{Sui2018} consider AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognize that these two forms are rare.
 Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin %(12th to 20th centuries)
@@
 \ex\label{ex:AByiAB-rou2}
-\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3-le-yi-ming2xiang3}.\footnotemark\\
+\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3}-\obj{le-yi}-\obj{ming2xiang3}.\footnotemark\\
 he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\

### 2025-04-05 replies-reviews2.tex
create and format 2nd reviewer reply document

%% -*- coding:utf-8 -*-
\documentclass[fleqn,twoside]{article}

\usepackage[
style = langsci-unified,
backend = biber,
natbib = true,
]{biblatex}
\addbibresource{Bib.bib}

\usepackage{xcolor}
\definecolor{lsDOIGray}{cmyk}{0,0,0,0.45}

\usepackage{csquotes}

\input{localpackages}
\input{localcommands}
%\usepackage{fontspec}

%\newtoggle{draft}\togglefalse{draft}
\newtoggle{draft}\toggletrue{draft}

%\usepackage{hyperref}
%\hypersetup{colorlinks=false, pdfborder={0 0 0}}

%\usepackage{unified-biblatex}

%\let\citew\citealp
%\newcommand{\page}{}
%\bibliography{Bib,bib-abbr,biblio}

%\usepackage{langsci-forest-setup}

%\usepackage{german}%

%\selectlanguage{USenglish}

%\usepackage{abbrev,merkmalstruktur,article-ex,makros.2e,mycommands,eng-date,my-xspace}
%\usepackage{my-gb4e-article}

%\usepackage{soul}

%\usepackage{forest}

\let\citew\cite

\newcommand{\is}[1]{}

\begin{document}
\noindent
{\large\bf Replies to 2nd round of reviews of \emph{An HPSG account for verbal reduplication in Mandarin Chinese}}

\noindent
Dear editors,

Thank you very much again for the positive reviews. The following text is a repetition of the points the
reviewers raised and an explanation of how we addressed open issues.

\section{Reviewer 1}\label{sec:1}

\begin{enumerate}
%%%%% YL
\item p. 2-3, ex. (3). Regarding the verb 来往 \textit{lai-wang}, it actually refers to two different verbs: (1) `come
and go,' a coordinate verb, and (2) `communicate.' In some dictionaries, the second syllable of the
latter (`communicate') is marked as having a neutral tone. The first verb, which has a coordinate
structure, reduplicates as AABB, while the second reduplicates as ABAB. In principle, the verb
meaning `communicate' should not reduplicate as AABB, just as the verb meaning `come and go'
should not reduplicate as ABAB.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 7, lines 29--31: ``Finally, \citet[322]{SuiHu2016} claim that a reduplicated verb cannot combine with
a quantized object.''

This statement holds true only for accomplishments, not activities. With accomplishments, verbs
become telic when followed by a quantized object (see \citealt{Verkuyl1972}). This is not the case for
activities. The examples provided in (15) do not contain accomplishment verbs, so their acceptability
is expected. Please double-check the statement by  \citet[322]{SuiHu2016}.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 14, lines 11--14: ``The reduplication does not seem to cancel the \textit{telos} of achievement'' and related
answer to reviewer1’s comment.

It appears the author(s) misunderstood the reviewer’s comment. What the reviewer meant was that in
certain contexts, achievements can act like activities (as if the \textit{telos} is cancelled), allowing them to be
reduplicated. The reviewer did not suggest that reduplication cancels the \textit{telos}; on the contrary,
reduplication sets a boundary for the event, which is why it is mainly compatible with activities. This
explains why reduplicated verbs are not compatible with ``for-X-time'' expressions, as both
reduplication and ``for-X-time'' expressions set boundaries on the event, making them incompatible
together. In fact, while the base verb can appear with ``for-X-time'' expressions, such as 有一次，我看了一天的书，既累又困 (BCC corpus), but the reduplicated verb cannot: *我看了看一天的书.
The author(s) correctly state on p. 16, lines 21: ``Reduplication is incompatible with expressions
quantifying the duration or extent of the event expressed in the sentence (\citealt[83--84]{Li1998}; \citealt[114--115]{Chen2005})''. Indeed, both reduplication and duration expressions set boundaries on the event.
The author(s) conclude in lines 37--38: ``These tests suggest that reduplicated verbs are indeed
achievements, rather than being used as activities.'' I fail to see why reduplicated verbs should be
considered activities, given their semantics. Also, note that in example (26), the verb \textit{mai} (`buy') is
not an achievement but rather an accomplishment. As for example (26b), \textit{liang tian hou} (`two days
later') is not an ``in X-time'' expression. An ``in X-time'' expression would be something like \textit{he read
three books \ul{in two days}}. Therefore, (26b) is not a good example to illustrate the author(s)' point.
This passage (from line 11 to line 38) must be revised or perhaps eliminated altogether.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 15, lines 25--28: ``\textit{Le} is compatible with the reduplication, because its dynamicity can relate to not
only the termination or instantiation of an event (a point of change), but also the process of the
situation, just like that of the reduplication (see Section 2.3.1)''. This passage is unclear. Please revise
it for clarity.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item P. 16, lines 31--34: ``A reviewer also notes that the reduplication appears frequently in imperative
(example 25a) and conditional sentences (31) as well as causative sentences with \pinyin{rang4/jiao4/shi3}
`let/let/make' (examples 21, 22, 25c).''
This is not exactly what the reviewer stated. The reviewer was not referring to reduplicated verbs in
general. Rather, s/he noted that, as described in various grammars, verbs depicting events not
controlled by an agent (which normally cannot be reduplicated) sometimes undergo reduplication,
especially in imperative, conditional, or causative sentences. I am not sure if reduplication, in general,
tends to appear specifically in these sentence types. It seems to me that it appears frequently in other
contexts as well. The claim ``This explains the general tendency for reduplication to appear in
conditional clauses, imperative, or causative contexts, frequently describing future situations'' (p. 17,
lines 4--6) should be reconsidered.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 19, lines 29--31: ``Tense inflections in English such as -ed change neither the category nor the
valency of the input verb''.

Since this is an inflectional affix, it is not appropriate to make this comparison. Inflectional affixes
are obligatory, and they constitute a different phenomenon.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 20, lines 23--27: ``In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provide psycholinguistic evidence), and the patterns discussed here constitute a different
process than the AABB pattern (see the discussions above, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}), it is not surprising that le occurs at a different position''.
However, le insertion represents a case of lexical integrity violation (meaning the reduplicated verb
does not form a word), unless it is considered as an instance of infixation.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 21, examples in (44): It would be better to use a pronoun as the object in (44a), as it is undeniable
that pronoun objects appear in that position.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 21, lines 21--24: ``Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with
morphological reduplication (below as reduplication) in other languages than syntactic reduplication
(below as repetition; \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).''

Be careful: stating that reduplication is a syntactic phenomenon does not mean it is an instance of
repetition. Arguing that diminishing reduplication is a syntactic phenomenon affecting the vP domain
and proposing a syntactic analysis (as in \citealt{Arcodiaetal2014} and \citealt{BascianoMelloni2017}) does not imply that it is syntactic repetition; they are two different phenomena.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p.23, lines 29--31: ``Third, idioms (52a) lose their idiomatic meaning when used with verbal classifiers
(52b) but maintain their idiomatic meaning with reduplications (52c) \citep[230--231]{YangWei2017}.''
It would be useful to specify that this applies except when 一下 \textit{yixia} is used, which indicates short
duration.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 25, lines 37--41: ``This suggests that the reduced acceptability of reduplicated achievement and
stative verbs is semantic rather than structural. Their use is possible in specific contexts and should
not be ruled out syntactically. Consequently, this proposal does not seem to offer an appropriate
account for reduplication.''

This depends on whether such verbs can, in certain circumstances, behave differently, acquiring some
aspectual properties of other verb classes. This can happen also with adjctives. For example, the
adjective 高兴 `happy', which typically reduplicates as 高高兴兴 (AABB, adjectival increasing
reduplication), can under certain conditions describe a process, acquiring verbal features, and
reduplicate as ABAB: e.g., 让他高兴高兴 (BCC corpus). It is not the case that all adjectives can
undergo diminishing ABAB reduplication.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 26, line 26: \textit{zhe} is durative rather than progressive.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item P. 26, lines 27--28: ``He observes that \textit{zhe} `PROG', \textit{le} `PFV' and \pinyin{wan2} `COMPL' necessarily occur
with additional information about the event denoted by the sentence (53), while \pinyin{zai4} `dur' and \pinyin{guo4}
`EXP' can occur without further information (54).''

This passage is not completely clear. Please revise and clarify it. Also, the aspect marker 过 \textit{guo}
should be toneless.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 27, lines 37--40: Pleasc explain the mismatch more thoroughly.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\item p. 29, line 29: Indeed, AAB reduplication is basically a reduplication of a monosyllabic verb followed
by an object, so it is productive as AA.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}

\end{enumerate}

\section{Reviewer 2}\label{sec:2}

\begin{enumerate}
    %%%%% YL
    \item Example (11) is not entirely convincing in its attempt to challenge \citegen{SuiHu2016} proposal. Sui and Hu suggest that verb reduplication can occur in relative clauses when licensed by modal verbs, as these verbs check the relevant features enabling reduplication. Furthermore, they note that certain verbs, such as 打算 \textit{dǎsuàn} (`plan'), 让 \textit{ràng} (`let'), and 叫 \textit{jiào} (`ask') can also license verb
    reduplication. In example (11), the verb 苦留 \textit{kǔliú} (`trying hard to make stay')
    appears to function in a similar licensing role. If this interpretation is accurate, the example does not effectively challenge Su and Hu’s argument. It may be helpful for the authors to clarify why 苦留 \textit{kǔliú} is distinct from other licensing verbs or to provide additional examples that counter Sui and Hu's claims.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:}

    \item Using example (14), the authors suggest that negation can modify verb reduplication and challenge prior studies that emphasize constraints on their co-occurrence. However, it is important to note that example (14b) is situated in an interrogative context. As \citet{SuiHu2016} highlight, negation modifying verb reduplication is not acceptable in \textit{affirmative} sentences. Similar constraints are reported in earlier literature, such as \citet{Shen1995} and \citet{Liu1983} (see \citealt{Xie2018} for a review).
    For instance, the sentence 你不复习复习功课 \textit{Nǐ bù fùxí fùxí gōngkè} (`You do not review your lessons’) is not acceptable, whereas 你不复习复习功课吗? \textit{Nǐ
    bù fùxí fùxí gōngkè ma}? (`Aren't you going to review your lessons?') is acceptable. This suggests that reduplication with negation is permitted in certain contexts, such as interrogative or emphatic sentences, but not in other contexts, like affirmative statements. The authors should consider addressing these contextual nuances to strengthen their analysis.

    In summary, while Section 2.2 effectively demonstrates that the distribution of reduplicated verbs is broader than previously reported, it is essential to acknowledge that some examples represent special cases.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:}

    \item On Page 20, the authors use the modification test (\citep{Dai1992} to argue that verb reduplication behaves like words rather than phrases. Example (43) illustrates that adverbs cannot be inserted within a verb reduplication. However, this argument could be strengthened by addressing the following point: The rationale for inserting the adverb within the reduplication is not very clear. Even for typical verb phrases like 开门 \textit{kāi mén} (`open the door'), adverbs cannot be inserted between the verb and its
    object (e.g., 开偷偷地门 \textit{kāi tōutōu de mén} `open the door secretly' is ungrammatical).
    This suggests that the inability to insert an adverb is not unique to reduplication and may not prove its word-like property.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:}

    \item The application of MRS within the HPSG framework represents a central focus of this paper. It might be helpful to explicitly acknowledge that the integration of MRS into the HPSG framework has been explored in prior research, such as \citet{Copestakeetal2005}. Addressing this would situate the current analysis more clearly within the broader theoretical landscape and strengthen its overall credibility.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:}
    \todo[inline]{Stefan, say something}

\end{enumerate}

{\sloppy
\printbibliography[heading=subbibliography,notkeyword=this]
}
\end{document}

%      <!-- Local IspellDict: en_US-w_accents -->

### 2025-06-06 replies-reviews2.tex
answered most reviewer comments

@@
 \noindent
-{\large\bf Replies to 2nd round of reviews of \emph{An HPSG account for verbal reduplication in Mandarin Chinese}}
+{\large\bf Replies to 2nd round of reviews of \emph{An HPSG account for verbal reduplication in Mandarin Chinese}}\\
 
 \noindent
-Dear editors,
+Dear editors,\\
 
+\noindent
 Thank you very much again for the positive reviews. The following text is a repetition of the points the
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} Example (3)  in the manuscript only serves to
+ illustrate the different forms of verbal reduplication in Mandarin Chinese
+  without discussing their meaning. 
+  We included the translation to the examples 
+  to make the distinction in meaning clearer, 
+  as shown below in (\ref{ex:laiwang}).
+
+\ea\label{ex:laiwang} for disyllabic verbs: \obj{lai2-wang3} come-go `come and go/communicate'
+\ea \gll \objex{lai2-wang3-lai2-wang3}\\
+come-go-come-go\\ \jambox{ABAB}
+\glt `communicate a little bit'
+
+\ex \gll \objex{lai2-wang3-le-lai2-wang3}\\
+come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
+\glt `communicated a little bit'
+
+\ex \gll \objex{lai2-lai2-wang3-wang3}\\
+come-come-go-go\\ \jambox{AABB}
+\glt `coming and going'
+
+\z\z
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} After double-checking,
+ \citet[322]{SuiHu2016} indeed argue that verbal reduplication cannot take a quantized object, 
+ claiming that the following example (\ref{ex:qobj}) is ungrammatical.
+
+\ea\label{ex:qobj}
+\gll \objex{wo3} \obj{kan4-kan4} \objex{san1} \objex{ben3} \objex{shu1}.\\
+I look-look three \textsc{clf} book\\ \jambox{\citep[322]{SuiHu2016}} 
+\glt `I will read three books a little bit.'
+\z
+
+We can also find examples of reduplicated accomplishments followed by quantized objects in CCL and BCC, as shown in (\ref{ex:qobj1}--\ref{ex:qobj2}) below.
+% 吃?吃三种?局，一是吃口味，一是吃氛围，一是吃免费。(CCL 2010s\201x\网络语料\微博\weibo_062.txt)
+\ea\label{ex:qobj1}
+% 其实他一直想写写两位老师 （CCL 2010s\201x\网络语料\微信公众号\Wechat_123.txt）
+\gll \objex{qi2shi2} \objex{ta1} \objex{yi4zhi2} \objex{xiang3} \obj{xie3-xie3} \objex{liang3} \objex{wei4} \objex{lao3shi1} \ldots\\
+actually he always want write-write two \textsc{clf} teacher\\ \jambox{(CCL)}
+\glt `Actually, he has always wanted to write a bit about two teachers.'
+
+\ex\label{ex:qobj2}% 男人跟男人的沟通比较快，打打球、喝喝两 杯就行了。（BCC 微博）
+\gll \objex{nan2ren2} \objex{gen1} \objex{nan2ren2} \objex{de} \objex{gou1tong1} \objex{bi3jiao4} \objex{kuai4}, \ldots\, \obj{he1-he1} \objex{liang3} \objex{bei1} \objex{jiu4} \objex{xing2} \objex{le}.\\
+man and man \textsc{de} communication relatively fast {} drink-drink two cup just ok \textsc{ptc}\\ \jambox{(BCC)}
+\glt `The communication between men is relatively fast, \ldots\, they just need to drink two cups together.'
+
+% 可我还是壮着胆子想写写一 个同行。 （BCC 人民日报1996）
+%农民们就卖卖五样东西，大酱、葱、煎饼、鸡蛋、苞米。（CCL 2010s\201x\网络语料\微信公众号\Wechat_157.txt）
+\z
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} This passage is removed.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} This passage is revised as follows 
+and moved before example (28) to directly follow the passage before: 
+``As shown in Section 2.3.1, reduplication can also express
+ dynamicity of both a time point and a time period, 
+ like just \obj{le} illustrated here. 
+ Therefore, \obj{le} is compatible with reduplication.''
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} This passage is removed. 
+Instead, a footnote is added to Section 2.3.2 at the discussion on 
+the reduplication of non-volitional verbs in example (17): 
+``A reviewer notes that verbs depicting events not controlled 
+by an agent sometimes can undergo reduplication, 
+especially in imperative, conditional, or causative sentences. 
+It is worthwhile to delve into why such sentence structures
+ enable reduplication for these verbs. 
+ It is also worth noting that the sentences in (17) 
+ are not imperative, conditional or causative sentences. 
+ This shows that non-volitional verbs can also be reduplicated
+  outside of the aforementioned sentence structures''.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} This example only serves to illustrate our argument 
+that a morphological process does not necessarily change 
+the category or the valency of the input verb, 
+and inflection is a morphological process that 
+does not change the category or the valency of the input verb. 
+We do not claim reduplication to be either inflection or derivation.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} It is considered an instance of infixation.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} We do not claim that the syntactic analyses of reduplication consider it as repetition. We added a footnote to clarify this point.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} We modified footnote 11 as follows to make this point clearer: ``This applies except when \obj{yi2 xia4} `once' is used.
+Because of this, one reviewer suggests that the lost of the idiomatic interpretation may be attributed to the use of the numeral \obj{san1} `three' in (52b).
+We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special,
+but it is \obj{yi2} \obj{xia4} `once' that is special.
+We can replace \obj{san1} `three' with any number above two,
+and the distinction still exist.
+But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
+We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
+In this case, it is easy to interpret \obj{yi2} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
+but as duration adverbials as a whole,
+thus differing them from ``actual'' verbal classifier phrases with other numerals''.
 
@@
 This depends on whether such verbs can, in certain circumstances, behave differently, acquiring some
-aspectual properties of other verb classes. This can happen also with adjctives. For example, the
+aspectual properties of other verb classes. This can happen also with adjectives. For example, the
 adjective 高兴 `happy', which typically reduplicates as 高高兴兴 (AABB, adjectival increasing
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} We cannot exclude these verbs syntactically but can semantically.
+\todo[inline]{YL to do: elaborate}
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} We corrected this.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} We modified the passage as follows and added more examples to make it clearer: 
+``He observes that a minimal sentence, 
+which only contains a verb marked by \obj{zhe} `\textsc{dur}',
+ \obj{le} `\textsc{pfv} or \obj{wan2} \textsc{compl} 
+ and its arguments, 
+ seems incomplete without further sentential elements 
+ such as the sentence final particle \obj{le} 
+ or a temporal adverbial like \obj{gang1cai2} `just now' (53). 
+ In contrast, a minimal sentence with a verb marked by  \obj{zai4} `prog' or \obj{guo4}
+ `\textsc{exp}'  and its arguments can stand alone (54).''
 
-\item p. 27, lines 37--40: Pleasc explain the mismatch more thoroughly.
+We changed the tone of \obj{guo} to be toneless.
+
+\item p. 27, lines 37--40: Please explain the mismatch more thoroughly.
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} This passage is modified as follows: 
+``This analysis would result in a mismatch between syntax and semantics. 
+Even though \obj{le} and \obj{guo} both mark perfective aspects (Section 2.3.3, \citealt{Dai1997, XiaoMcEnery2004}),
+\obj{guo} is situated under Asp$_1$ while \obj{le} is under Asp$_2$, as can be seen from Figure 3.
+However, on the surface structure, both \obj{le} and \obj{guo} occur in the same position, directly following the verb.
+If we assume that the aspect markers are base-generated in different positions 
+and then move to the same position following the verb, 
+then there needs to be extra explanations given as to why \obj{zai4} occurs before the verb''.
+\todo[inline]{YL to do: check}
 
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} Yes, and this is also addressed in our analysis in Section 4.
+\todo[inline]{YL to do: add page number}
 
@@
     \noindent
-    \textbf{Answer:}
+    \textbf{Answer:} We also found the following examples with reduplication embedded under negation in affirmative sentences (\ref{ex:neg1}--\ref{ex:neg3}).
+
+\ea\label{ex:neg1}
+    % 你们只知道责备人家，全不想想自己。(CCL 1910s\1916\文学\小说笔记\1916_5 向恺然 留东外史.txt)
+\gll \objex{ni3-men} \objex{zhi3} \objex{zhi1dao4} \objex{ze2bei4} \objex{ren2jia1}, \objex{quan2} \objex{bu4} \obj{xiang3-xiang3} \objex{zi4ji3}.\\
+you-\textsc{pl} only know blame others at.all not think-think self\\ \jambox{(CCL)}
+\glt `You only blame others, not thinking about yourselves at all.'
+
+    % 曾孝一听，登时无名火起，说怎么着，他欺侮我的孩子，可以，也不打听打听，我们家人多，非先去把他家拆个土平，把周家小老婆子，拉在十字路口儿，非撕了他不行。(CCL 1910s\191x\文学\191x_estimated 爱新觉罗·勋锐 评讲聊斋.txt)
+
+    % 吊膀子是你的生性使然，你自己曾对我说过，你见了少年生得好的女人，若不转转念头，你心中便像有什么事放不下似的。(CCL 1910s\1916\文学\小说笔记\1916_5 向恺然 留东外史.txt)
+
+    \ex\label{ex:neg2}
+    % 所谓职业的读书者，譬如学生因为升学，教员因为要讲功课，不翻翻书，就有些危险的就是。(CCL 1920s\1928\文学\1928 鲁迅 而已集.txt)
+    \gll \objex{jiao4yuan2} \ldots\, \objex{bu4} \obj{fan1-fan1} \objex{shu1}, \objex{jiu4} \objex{you3xie1} \objex{wei1xian3} \objex{de} \objex{jiu4} \objex{shi4}.\\
+    lecturer {} not flip-flip book just somewhat dangerous \textsc{de} just be\\ \jambox{(CCL)}
+    \glt `If lecturers do not read books, then it is a bit dangerous.'
+
+    \ex\label{ex:neg3}
+    % 花儿匠简直不管事了，你看，什么东西也不收拾收拾。(CCL 	1930s\1932\文学\1932 张恨水 金粉世家.txt)
+    \gll \objex{hua1erjiang4} \objex{jian3zhi2} \objex{bu4} \objex{guan3} \objex{shi4} \objex{le}, \ldots\, \objex{shen2me} \objex{dong1xi} \objex{ye3} \objex{bu4} \obj{shou1shi-shou1shi}.\\
+    florist at.all not care thing \textsc{ptc} {} what thing also not tidy-tidy\\ \jambox{(CCL)}
+    \glt `The florist did not care about anything at all, did not tidy up anything.'
+\z
+
+    We recognize these uses require specific context information.
 
@@
     \noindent
-    \textbf{Answer:}
+    \textbf{Answer:} The rationale of the test in (43) to insert an adverb in-between the reduplication is that a verb can be modified by an adverb but not an adjective as in (42).
+    In Mandarin Chinese, adverb modification is only permitted pre-verbally and not post-verbally, as illustrated in the example below (\ref{ex:adv}).
+    \ea\label{ex:adv}
+    \ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}\\
+    he quietly go-\textsc{pfv}\\
+    \glt `He quietly went away.'
+    }
+    \ex[*]{\gll \objex{ta1} \objex{zou3-le} \objex{qiao1qiao1de}\\
+    he go-\textsc{pfv} quietly\\
+    }
+    \z\z
+    Therefore, the general explanation for the ungrammaticality of \obj{kai1} \obj{tou1tou1de} \obj{men2} is that the adverb cannot occur after the verb.
+    This is not a problem in (43) as the adverb can, in principle, be interpreted as modifying the second verb.
+    \todo[inline]{YL: citation}
 

### 2025-06-07 replies-reviews2.tex
answered more comments

@@
  dynamicity of both a time point and a time period, 
- like just \obj{le} illustrated here. 
+ just like \obj{le} illustrated here. 
  Therefore, \obj{le} is compatible with reduplication.''
@@
 \noindent
-\textbf{Answer:}
+\textbf{Answer:} This part uses the example provided by Reviewer 2.
+We decided to keep (44a) as it is to maintain the consistency among other minimal pairs.
+Our native speaker informants consider (44a) to be grammatical, and we can also find similar sentences in corpora.
 
@@
 \noindent
-\textbf{Answer:} We do not claim that the syntactic analyses of reduplication consider it as repetition. We added a footnote to clarify this point.
+\textbf{Answer:} We do not claim that the syntactic analyses consider reduplication to be repetition. We added a footnote to clarify this point.
 
@@
 \noindent
-\textbf{Answer:} We cannot exclude these verbs syntactically but can semantically.
-\todo[inline]{YL to do: elaborate}
+\textbf{Answer:} As we explained in our previous reply, 
+verb classes are determined solely based on 
+the inherent features of the verb itself
+(\citealt[52]{XiaoMcEnery2004}).
+This means that even though the same verb may express different aspectual properties in different contexts,
+its verb class remains the same.
+The change in aspectual properties can be attributable to other components at the sentential level, such as the use of reduplication.
+We also showed in Section 2.3.2 many examples of achievement and stative verbs being reduplicated.
+We argue that all verbs are \textit{syntactically} compatible with reduplication, 
+and therefore, this possibility should not be \textit{syntactically} ruled out.
+We do recognize that reduplication requires specific situational information, 
+namely a situation that is compatible with its deliminative meaning,
+but we believe this is a \textit{semantic} constraint.
 
@@
 \noindent
-    \textbf{Answer:}
+\textbf{Answer:} We modified this passage to include \citegen{SuiHu2016} observation 
+that reduplication is possible in relative clauses with 
+verbs with modal or mood meanings as follows: ``\citet[319, 332]{SuiHu2016} claim that reduplication cannot appear in a relative clause without a modal verb or a verb with a modal or mood meaning, such as \obj{da3suan4} `plan', \obj{rang4} `let' and \obj{jiao4} `ask'''.
+
+However, we also found examples such as the following ones in (\ref{ex:rel1}--\ref{ex:rel2}), 
+where reduplication occurs in relative clauses without modal or mood verbs.
+
+    % 随便看看的粉丝	群 (BCC 微博)
+
+\ea\label{ex:rel1}
+    % 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
+    \gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3} \objex{shi2} \objex{tiao2} \objex{wei1bo2}!\\
+    you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} some ten \textsc{clf} Weibo\\ \jambox{(BCC)}
+    \glt `The government affairs Weibo account that you look at \ldots\, reposted dozens of Weibo posts.'
+
+    % 大年初一参差光谷，初二去，初三去看看的店 （BCC 微博）
+
+    % 像是习惯路过了不进去看看的店 。（BCC 微博）
+
+    % 刚在人人看到班上那个喜欢用看政治来装逼，时而偷进我围脖来看看的女人 ，说不定这条你看操…… (BCC 微博)
+
+    \ex\label{ex:rel2}
+    % 大厅里坐着一些年轻人，他们是逛进来听听的爵士 乐迷。（BCC 为了告别的聚会 A:米兰·昆德拉 Y:UN）
+    \gll \objex{ta1men} \objex{shi4} [[\objex{guang4} \objex{jin4lai2} \obj{ting1-ting} \objex{de}] \objex{jue2shi4yue4-mi2}].\\
+    they be wander enter listen-listen \textsc{de} jazz-fan\\ \jambox{(BCC)}
+    \glt `They are jazz fans who wandered in to have a listen.'
+
+ \z
 
@@
 
-    \item On Page 20, the authors use the modification test (\citep{Dai1992} to argue that verb reduplication behaves like words rather than phrases.
+    \item On Page 20, the authors use the modification test \citep{Dai1992} to argue that verb reduplication behaves like words rather than phrases.
 Example (43) illustrates that adverbs cannot be inserted within a verb reduplication.
@@
     \noindent
-    \textbf{Answer:} The rationale of the test in (43) to insert an adverb in-between the reduplication is that a verb can be modified by an adverb but not an adjective as in (42).
-    In Mandarin Chinese, adverb modification is only permitted pre-verbally and not post-verbally, as illustrated in the example below (\ref{ex:adv}).
+    \textbf{Answer:} The rationale for inserting an adverb in-between the reduplication is that a verb can be modified by an adverb, hence the modification test.
+    In Mandarin Chinese, almost all adverbials are obligatorily pre-verbal \citep[50]{Ernst2014}, as illustrated in the example below (\ref{ex:adv}).
     \ea\label{ex:adv}
     \ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}\\
-    he quietly go-\textsc{pfv}\\
+    he quietly go-\textsc{pfv}.\\
     \glt `He quietly went away.'
     }
-    \ex[*]{\gll \objex{ta1} \objex{zou3-le} \objex{qiao1qiao1de}\\
+    \ex[*]{\gll \objex{ta1} \objex{zou3-le} \objex{qiao1qiao1de}.\\
     he go-\textsc{pfv} quietly\\
@@
     \z\z
-    Therefore, the general explanation for the ungrammaticality of \obj{kai1} \obj{tou1tou1de} \obj{men2} is that the adverb cannot occur after the verb.
-    This is not a problem in (43) as the adverb can, in principle, be interpreted as modifying the second verb.
-    \todo[inline]{YL: citation}
+    Therefore, the general explanation for the ungrammaticality of \obj{kai1} \obj{tou1tou1de} \obj{men2} `open secretly door' is that the adverb cannot occur after the verb.
+    This is not a problem for the test in (43), as the adverb can, in principle, be interpreted as modifying the second verb.
 

### 2025-06-13 replies-reviews2.tex
explain Tsai synsem mismatch

@@
 \textbf{Answer:} This passage is modified as follows: 
-``This analysis would result in a mismatch between syntax and semantics. 
-Even though \obj{le} and \obj{guo} both mark perfective aspects (Section 2.3.3, \citealt{Dai1997, XiaoMcEnery2004}),
-\obj{guo} is situated under Asp$_1$ while \obj{le} is under Asp$_2$, as can be seen from Figure 3.
-However, on the surface structure, both \obj{le} and \obj{guo} occur in the same position, directly following the verb.
-If we assume that the aspect markers are base-generated in different positions 
-and then move to the same position following the verb, 
-then there needs to be extra explanations given as to why \obj{zai4} occurs before the verb''.
-\todo[inline]{YL to do: check}
+``This analysis would result in a mismatch between syntax and semantics, 
+in the sense that the aspect markers that belong to the same semantic group do not occur in the same syntactic position. 
+Even though \obj{le}, \obj{guo} and reduplication all mark perfective aspects (Section 2.3.3, \citealt{Dai1997, XiaoMcEnery2004}),
+\obj{guo} is situated under Asp$_1$, while \obj{le} and reduplication are under Asp$_2$.
+Similarly, \obj{zai4} and \obj{zhe} are both imperfective aspects but also occur in different syntactic positions.
+The former is under Asp$_1$ while the latter is under Asp$_2$.''
+%However, on the surface structure, both \obj{le} and \obj{guo} occur in the same position, directly following the verb.
+%If we assume that the aspect markers are base-generated in different positions 
+%and then move to the same position following the verb, 
+%then there needs to be extra explanations given as to why \obj{zai4} occurs before the verb''.
+%\todo[inline]{YL to do: check}
 
@@
     % 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
-    \gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3} \objex{shi2} \objex{tiao2} \objex{wei1bo2}!\\
-    you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} some ten \textsc{clf} Weibo\\ \jambox{(BCC)}
+    \gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3}-\objex{shi2} \objex{tiao2} \objex{wei1bo2}!\\
+    you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} several-ten \textsc{clf} Weibo\\ \jambox{(BCC)}
     \glt `The government affairs Weibo account that you look at \ldots\, reposted dozens of Weibo posts.'

### 2025-06-14 replies-reviews2.tex
modify main paper according to reviewer replies

@@
 Instead, a footnote is added to Section 2.3.2 at the discussion on 
-the reduplication of non-volitional verbs in example (17): 
+the reduplication of non-volitional verbs in example (18) (example (17) in the previous draft): 
 ``A reviewer notes that verbs depicting events not controlled 
@@
  enable reduplication for these verbs. 
- It is also worth noting that the sentences in (17) 
+ It is also worth noting that the sentences in (18) 
  are not imperative, conditional or causative sentences. 
@@
 \noindent
-\textbf{Answer:} We modified footnote 11 as follows to make this point clearer: ``This applies except when \obj{yi2 xia4} `once' is used.
-Because of this, one reviewer suggests that the lost of the idiomatic interpretation may be attributed to the use of the numeral \obj{san1} `three' in (52b).
+\textbf{Answer:} We modified footnote 14 (footnote 11 in the previous draft) as follows to make this point clearer: ``This applies except when \obj{yi2 xia4} `once' is used.
+Because of this exception, one reviewer suggests that the lost of the idiomatic interpretation may be attributed to the use of the numeral \obj{san1} `three' in (52b).
 We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special,
@@
 \textbf{Answer:} We modified the passage as follows and added more examples to make it clearer: 
-``He observes that a minimal sentence, 
+``He observes the so-called incompleteness effect, namely that a minimal sentence, 
 which only contains a verb marked by \obj{zhe} `\textsc{dur}',
@@
 such as the sentence final particle \obj{le} 
- or a temporal adverbial like \obj{gang1cai2} `just now' (53). 
- In contrast, a minimal sentence with a verb marked by  \obj{zai4} `prog' or \obj{guo4}
- `\textsc{exp}'  and its arguments can stand alone (54).''
+or a temporal adverbial like \obj{gang1cai2} `just now' (51) . 
+In contrast, a minimal sentence with a verb marked by  \obj{zai4} `prog' or \obj{guo}
+`\textsc{exp}'  and its arguments can stand alone (52).''
 
@@
 
+  \citet[50]{Ernst2014} mentions that the only possible post-verbal adverbials are participant PPs (\textit{with somebody}),
+  manner or resultative V-de constructions as well as 
+  duration and frequency expressions.
+  (\ref{ex:VPinsert}) shows a case of inserting a frequency expression into a VP.
+  This suggests that it is, in principle, possible to insert adverbials into a VP.
+
+  \ea\label{ex:VPinsert}
+    \gll \objex{kai1}  \objex{san3} \objex{ci4} \objex{men2}\\
+    open three time door\\
+    \glt `open the door three times'
+  \z
+
     \item The application of MRS within the HPSG framework represents a central focus of this paper.

### 2025-06-14 chapters/ch02-Phenomenon.tex
modify main paper according to reviewer replies

@@
 		say-say\\ \jambox{AA}
+        \glt `say a little bit'
+
 		\ex \gll \objex{shuo1-yi-shuo1}\\
 		say-one-say\\ \jambox{A-\textit{yi}-A}
+        \glt `say a little bit'
+
 		\ex \gll \objex{shuo1-le-shuo1}\\
 		say-\textsc{pfv}-say\\ \jambox{A-\textit{le}-A}
+        \glt `said a little bit'
+
 		\ex \gll \objex{shuo1-le-yi-shuo1}\\
 		say-\textsc{pfv}-one-say\\ \jambox{A-\textit{le}-\textit{yi}-A}
+        \glt `said a little bit'
+
 		\ex \gll \objex{shuo1-shuo1-kan4}\\
 		say-say-look\\ \jambox{AA-\obj{kan4}}
+        \glt `try to say a little bit'
+
 		\ex \gll \objex{shuo1-kan4-kan4}\\
 		 say-look-look\\ \jambox{A-\obj{kan4}-\obj{kan4}\footnotemark}
+         \glt `try to say a little bit'
 		\z
@@
 		come-go-come-go\\ \jambox{ABAB}
+        \glt `communicate a little bit'
+
 		\ex \gll \objex{lai2-wang3-le-lai2-wang3}\\
 		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
+        \glt `communicated a little bit'
+
 		\ex \gll \objex{lai2-lai2-wang3-wang3}\\
 		come-come-go-go\\ \jambox{AABB}
+        \glt `coming and going'
 		\z
@@
 		tell-tell-lie\\ \jambox{AAB}
+        \glt `lie a little bit'
+
 		\ex \gll \objex{shuo1-yi-shuo1-huang3}\\
 		tell-one-tell-lie\\ \jambox{A-\textit{yi}-AB}
+        \glt `lie a little bit'
+
 		\ex \gll \objex{shuo1-le-shuo1-huang3}\\
 		tell-\textsc{pfv}-tell-lie\\ \jambox{A-\textit{le}-AB}
+        \glt `lied a little bit'        
 		\z
@@
 \citet{SuiHu2016} claim that the syntactic distribution of the deliminative reduplication is subject to the following constraints.
-First, it cannot appear in a relative clause without a modal verb, providing the contrast in (\ref{ex:rel-suihu}) as an example \citep[319]{SuiHu2016}.
+First, \citet[319, 332]{SuiHu2016} claim that reduplication
+ cannot appear in a relative clause without a modal verb 
+ or a verb with a modal or mood meaning, 
+ such as \obj{da3suan4} `plan', \obj{rang4} `let' and \obj{jiao4} `ask', 
+ providing the contrast in (\ref{ex:rel-suihu}) as an example.
 \ea\label{ex:rel-suihu}
@@
 \z\z
-This claim can be falsified by (\ref{ex:rel-ccl}) found in CCL.
+This claim can be falsified by corpora examples such as (\ref{ex:rel}),
+where reduplication occurs in relative clauses without modal or mood verbs.
 We thus consider the contrast in (\ref{ex:rel-suihu}) a matter of providing a proper context.
-\ea\label{ex:rel-ccl}
-\gll \objex{er2qie3} \objex{yan3-qian2} \objex{zhe4} \objex{[[ku3-liu2} \objex{ta1} \objex{zai4} \obj{tan2-tan} \objex{de]} \objex{ren2]} \ldots\\
-moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\\jambox{(CCL)}
-\glt `Moreover, this person in front of her who is trying hard to make her stay to discuss a bit more \ldots'
+%\ea\label{ex:rel-ccl}
+%\gll \objex{er2qie3} \objex{yan3-qian2} \objex{zhe4} \objex{[[ku3-liu2} \objex{ta1} \objex{zai4} \obj{tan2-tan} \objex{de]} \objex{ren2]} \ldots\\
+%moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\\jambox{(CCL)}
+%\glt `Moreover, this person in front of her who is trying hard to make her stay to discuss a bit more \ldots'
+%\z
+
+\ea\label{ex:rel}
+% 随便看看的粉丝	群 (BCC 微博)
+
+\ea\label{ex:rel1}
+% 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
+\gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3}-\objex{shi2} \objex{tiao2} \objex{wei1bo2}!\\
+you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} several-ten \textsc{clf} Weibo\\ \jambox{(BCC)}
+\glt `The government affairs Weibo account that you look at \ldots\, reposted dozens of Weibo posts.'
+
+% 大年初一参差光谷，初二去，初三去看看的店 （BCC 微博）
+
+% 像是习惯路过了不进去看看的店 。（BCC 微博）
+
+% 刚在人人看到班上那个喜欢用看政治来装逼，时而偷进我围脖来看看的女人 ，说不定这条你看操…… (BCC 微博)
+
+\ex\label{ex:rel2}
+% 大厅里坐着一些年轻人，他们是逛进来听听的爵士 乐迷。（BCC 为了告别的聚会 A:米兰·昆德拉 Y:UN）
+\gll \objex{ta1men} \objex{shi4} [[\objex{guang4} \objex{jin4lai2} \obj{ting1-ting} \objex{de}] \objex{jue2shi4yue4-mi2}].\\
+they be wander enter listen-listen \textsc{de} jazz-fan\\ \jambox{(BCC)}
+\glt `They are jazz fans who wandered in to have a listen.'
+
+\z  
 \z
@@
 \ea \label{ex:redup-neg}
-\ea \gll \objex{wei4shen2me} \objex{wo3} \objex{bu4} \objex{kan4} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4} \ldots\\
-why I not look he other aspect \textsc{de} progress\\
-\glt `Why don't I look at his progress in other aspects?'
-\ex \gll  \objex{wei4shen2me} \objex{wo3} \objex{bu4} \obj{kan4-kan} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4}\ldots\\
-why I not look-look he other aspect \textsc{de} progress \\ \jambox{({CCL})}
-\glt `Why don't I look a little bit at his progress in other aspects?'
-\z\z
+%\ea \gll \objex{wei4shen2me} \objex{wo3} \objex{bu4} \objex{kan4} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4} \ldots\\
+%why I not look he other aspect \textsc{de} progress\\
+%\glt `Why don't I look at his progress in other aspects?'
+%\ex \gll  \objex{wei4shen2me} \objex{wo3} \objex{bu4} \obj{kan4-kan} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4}\ldots\\
+%why I not look-look he other aspect \textsc{de} progress \\ \jambox{({CCL})}
+%\glt `Why don't I look a little bit at his progress in other aspects?'
+\ea\label{ex:neg1}
+% 你们只知道责备人家，全不想想自己。(CCL 1910s\1916\文学\小说笔记\1916_5 向恺然 留东外史.txt)
+\gll \objex{ni3-men} \objex{zhi3} \objex{zhi1dao4} \objex{ze2bei4} \objex{ren2jia1}, \objex{quan2} \objex{bu4} \obj{xiang3-xiang} \objex{zi4ji3}.\\
+you-\textsc{pl} only know blame others at.all not think-think self\\ \jambox{(CCL)}
+\glt `You only blame others, not thinking about yourselves at all.'
+
+% 曾孝一听，登时无名火起，说怎么着，他欺侮我的孩子，可以，也不打听打听，我们家人多，非先去把他家拆个土平，把周家小老婆子，拉在十字路口儿，非撕了他不行。(CCL 1910s\191x\文学\191x_estimated 爱新觉罗·勋锐 评讲聊斋.txt)
+
+% 吊膀子是你的生性使然，你自己曾对我说过，你见了少年生得好的女人，若不转转念头，你心中便像有什么事放不下似的。(CCL 1910s\1916\文学\小说笔记\1916_5 向恺然 留东外史.txt)
+
+\ex\label{ex:neg2}
+% 所谓职业的读书者，譬如学生因为升学，教员因为要讲功课，不翻翻书，就有些危险的就是。(CCL 1920s\1928\文学\1928 鲁迅 而已集.txt)
+\gll \objex{jiao4yuan2} \ldots\, \objex{bu4} \obj{fan1-fan1} \objex{shu1}, \objex{jiu4} \objex{you3xie1} \objex{wei1xian3} \objex{de} \objex{jiu4} \objex{shi4}.\\
+lecturer {} not flip-flip book just somewhat dangerous \textsc{de} just be\\ \jambox{(CCL)}
+\glt `If lecturers do not read books, then it is a bit dangerous.'
+
+\ex\label{ex:neg3}
+% 花儿匠简直不管事了，你看，什么东西也不收拾收拾。(CCL 	1930s\1932\文学\1932 张恨水 金粉世家.txt)
+\gll \objex{hua1erjiang4} \objex{jian3zhi2} \objex{bu4} \objex{guan3} \objex{shi4} \objex{le}, \ldots\, \objex{shen2me} \objex{dong1xi} \objex{ye3} \objex{bu4} \obj{shou1shi-shou1shi}.\\
+florist at.all not care thing \textsc{ptc} {} what thing also not tidy-tidy\\ \jambox{(CCL)}
+\glt `The florist did not care about anything at all, did not tidy up anything.'
+
+\z
+\z
 
@@
 \glt `I want to highlight two important interconnected outcomes.'
+\z\z
+
+\noindent
+One reviewer suggests that \citeauthor{SuiHu2016}'s (\citeyear[322]{SuiHu2016}) claim only holds true for accomplishments, not activities.
+Since a quantized object only make accomplishments but not activities telic, 
+the acceptability of (\ref{ex:quantobj}) is expected 
+(more on the semantics of reduplication will be discussed in \sectref{sec:sem}).
+However, we also find examples of reduplicated accomplishments followed by quantized objects in CCL and BCC, as shown in (\ref{ex:qobj}).
+\ea\label{ex:qobj}
+% 吃?吃三种?局，一是吃口味，一是吃氛围，一是吃免费。(CCL 2010s\201x\网络语料\微博\weibo_062.txt)
+\ea\label{ex:qobj1}
+% 其实他一直想写写两位老师 （CCL 2010s\201x\网络语料\微信公众号\Wechat_123.txt）
+\gll \objex{qi2shi2} \objex{ta1} \objex{yi4zhi2} \objex{xiang3} \obj{xie3-xie3} \objex{liang3} \objex{wei4} \objex{lao3shi1} \ldots\\
+actually he always want write-write two \textsc{clf} teacher\\ \jambox{(CCL)}
+\glt `Actually, he has always wanted to write a bit about two teachers.'
+
+\ex\label{ex:qobj2}% 男人跟男人的沟通比较快，打打球、喝喝两 杯就行了。（BCC 微博）
+\gll \objex{nan2ren2} \objex{gen1} \objex{nan2ren2} \objex{de} \objex{gou1tong1} \objex{bi3jiao4} \objex{kuai4}, \ldots\, \obj{he1-he1} \objex{liang3} \objex{bei1} \objex{jiu4} \objex{xing2} \objex{le}.\\
+man and man \textsc{de} communication relatively fast {} drink-drink two cup just ok \textsc{ptc}\\ \jambox{(BCC)}
+\glt `The communication between men is relatively fast, \ldots\, they just need to drink two cups together.'
+
+% 可我还是壮着胆子想写写一 个同行。 （BCC 人民日报1996）
+%农民们就卖卖五样东西，大酱、葱、煎饼、鸡蛋、苞米。（CCL 2010s\201x\网络语料\微信公众号\Wechat_157.txt）
 \z\z
@@
 But \citet[381--382]{Zhu1998} lists a number of non\hyp{}volitional predicates that can be reduplicated.
-We found the examples shown in (\ref{ex:nonvol}) in {CCL} where non\nobreakdash-vo\-li\-tion\-al verbs \obj{wei3qu1} `feel wronged', \obj{ren4-xing4} `be willful' and \obj{diao4} `drop' are reduplicated.
+We found the examples shown in (\ref{ex:nonvol}) in {CCL} where non\nobreakdash-vo\-li\-tion\-al verbs \obj{wei3qu1} `feel wronged', \obj{ren4-xing4} `be willful' and \obj{diao4} `drop' are reduplicated.\footnote{
+A reviewer notes that verbs depicting events not controlled 
+by an agent sometimes can undergo reduplication, 
+especially in imperative, conditional, or causative sentences. 
+It is worthwhile to delve into why such sentence structures
+enable reduplication for these verbs. 
+It is also worth noting that the sentences in (\ref{ex:nonvol}) 
+are not imperative, conditional or causative sentences. 
+This shows that non-volitional verbs can also be reduplicated
+outside of the aforementioned sentence structures
+}
 
@@
 
-The reduplication does not seem to cancel the \textit{telos} of achievements.
-Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
-\ea
-\ea[]{\label{ex:teloa}% 一块... 到附近市场买买东西 (CCL)
-    \gll \objex{yi2kuai4} \ldots\, \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\ldots\\
-    together {} arrive nearby market buy-buy thing\\\jambox{(CCL)}
-    \glt `(We) together \ldots\, went to the market nearby to buy some things.'}
-
-\ex[]{\label{ex:telob}% 两天后到附近市场买买东西
-    \gll \objex{liang3} \objex{tian1} \objex{hou4} \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}.\\
-    two day later arrive nearby market buy-buy thing\\
-    \glt `Two days later, (we) went to the market nearby to buy some things.}
-
-\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
-    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}.\\
-    arrive nearby market buy-buy thing two day\\
-    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
-\z\z
-The following continuation that cancels the \textit{telos} is also infelicitous (\ref{ex:telod}).
-\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
-\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}.\\
-arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
-\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
-\z
-These tests suggest that the reduplicated verbs are indeed achievements,
-rather than being used as activities.
+%The reduplication does not seem to cancel the \textit{telos} of achievements.
+%Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
+%\ea
+%\ea[]{\label{ex:teloa}% 一块... 到附近市场买买东西 (CCL)
+%    \gll \objex{yi2kuai4} \ldots\, \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\ldots\\
+%    together {} arrive nearby market buy-buy thing\\\jambox{(CCL)}
+%    \glt `(We) together \ldots\, went to the market nearby to buy some things.'}
+
+%\ex[]{\label{ex:telob}% 两天后到附近市场买买东西
+%    \gll \objex{liang3} \objex{tian1} \objex{hou4} \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}.\\
+%    two day later arrive nearby market buy-buy thing\\
+%    \glt `Two days later, (we) went to the market nearby to buy some things.}
+
+%\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
+%    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}.\\
+%    arrive nearby market buy-buy thing two day\\
+%    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
+%\z\z
+%The following continuation that cancels the \textit{telos} is also infelicitous (\ref{ex:telod}).
+%\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
+%\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}.\\
+%arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
+%\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
+%\z
+%These tests suggest that the reduplicated verbs are indeed achievements,
+%rather than being used as activities.
 
@@
 
-\citet[Ch. 4]{XiaoMcEnery2004} consider \obj{le}, \obj{guo4} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
-The perfective aspect marker \obj{le} is compatible with reduplication while the experiential aspect marker \obj{guo4} is not.
+\citet[Ch. 4]{XiaoMcEnery2004} consider \obj{le}, \obj{guo} and reduplication to indicate perfective aspects, as they all view the situation as an inseparable whole.
+The perfective aspect marker \obj{le} is compatible with reduplication while the experiential aspect marker \obj{guo} is not.
 \citet[128--131]{XiaoMcEnery2004} state that \obj{le} has the semantic feature of dynamicity, since it ``can focus on both heterogeneous internal structures and changing points'' \citep[129]{XiaoMcEnery2004}.
@@
 It can also co\hyp{}occur with a situation with a change at a certain time point, such as getting to know in (\ref{ex:know}).
+As shown in \sectref{sec:core-sem}, reduplication can also express
+dynamicity of both a time point and a time period, 
+just like \obj{le} illustrated here. 
+Therefore, \obj{le} is compatible with reduplication.
 
@@
 \z
-\obj{Le} is compatible with the reduplication, because its dynamicity can relate to not only the termination or instantiation of an event (a point of change), but also the process of the situation, just like that of the reduplication (see \sectref{sec:core-sem}).
+%\obj{Le} is compatible with the reduplication, because its dynamicity can relate to not only the termination or instantiation of an event (a point of change), but also the process of the situation, just like that of the reduplication (see \sectref{sec:core-sem}).
 
@@
 
-A reviewer also notes that the reduplication appears frequently in imperative (example \ref{ex:redup-achi-stat1}) and conditional sentences (\ref{ex:cond}) as well as causative sentences with \obj{rang4}\slash\obj{jiao4}\slash\obj{shi3} `let/let/make' (examples \ref{ex:xiangxin}, \ref{ex:xiang}, \ref{ex:redup-achi-stat5}).
-\ea\label{ex:cond}
-\gll \objex{ni3} \objex{yao4shi4} \objex{gei3} \objex{wo3} \obj{zhi3-zhi} \objex{Li3-jia1} \objex{de} \objex{men2}, \objex{wo3} \objex{yuan4} \objex{gei3} \objex{ni3} \objex{gui4xia4}\\
-you if give I point-point Li-family \textsc{de} door I be.willing.to give you kneel.down\\\jambox{\citep[157]{XiaoMcEnery2004}}
-\glt `If you point at the door of Li's for me, I am willing to kneel down for you.'
-\z
-This can  be attributed to the holistic semantics of reduplication (see \sectref{sec:core-sem}).
+%A reviewer also notes that the reduplication appears frequently in imperative (example \ref{ex:redup-achi-stat1}) and conditional sentences (\ref{ex:cond}) as well as causative sentences with \obj{rang4}\slash\obj{jiao4}\slash\obj{shi3} `let/let/make' (examples \ref{ex:xiangxin}, \ref{ex:xiang}, \ref{ex:redup-achi-stat5}).
+%\ea\label{ex:cond}
+%\gll \objex{ni3} \objex{yao4shi4} \objex{gei3} \objex{wo3} \obj{zhi3-zhi} \objex{Li3-jia1} \objex{de} \objex{men2}, \objex{wo3} \objex{yuan4} \objex{gei3} \objex{ni3} \objex{gui4xia4}\\
+%you if give I point-point Li-family \textsc{de} door I be.willing.to give you kneel.down\\\jambox{\citep[157]{XiaoMcEnery2004}}
+%\glt `If you point at the door of Li's for me, I am willing to kneel down for you.'
+%\z
+%This can  be attributed to the holistic semantics of reduplication (see \sectref{sec:core-sem}).
 %Due to its unique features compared to the perfective aspect marker \obj{le} and the experiential aspect marker \obj{guo4},
-As illustrated in \sectref{sec:aspM}, \obj{le} expresses a situation being realized,
-while \obj{guo4} conveys a situation already experienced,
-and thus, both rarely occur in future situations.
-The use of reduplication does not have these constraints.
-This makes the reduplication the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
-This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts,
-which are frequently used to describe future situations.
+%As illustrated in \sectref{sec:aspM}, \obj{le} expresses a situation being realized,
+%while \obj{guo4} conveys a situation already experienced,
+%and thus, both rarely occur in future situations.
+%The use of reduplication does not have these constraints.
+%This makes the reduplication the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
+%This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts,
+%which are frequently used to describe future situations.
 
@@
 For instance, the \obj{-able} derivation in English is a productive morphological process.
-Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.
+Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.\footnote{
+We do not claim reduplication to be either inflection or derivation.
+}
 %the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
@@
 (\ref{ex:modVV}) is ungrammatical whether the AdvP is interpreted to modify the first or the second verb.
-This shows that it has nothing to do with the relative position of the verb and the AdvP.
+This shows that it has nothing to do with the relative position of the verb and the AdvP.\footnote{
+A reviewer questions the rationale for inserting an adverb within the reduplication,
+since an adverb also cannot be inserted into a VP consisting of a verb and its object, as shown below in (\ref{ex:vp}).
+
+\ea[*]{\label{ex:vp}
+\gll \objex{kai1} \objex{qiao1qiao1de} \objex{men2}\\
+open quietly door\\
+}
+\z
+
+\noindent
+The ungrammaticality of (\ref{ex:vp}) can be explained by the fact that almost all Mandarin Chinese adverbials are obligatorily pre-verbal \citep[50]{Ernst2014}, as illustrated in the example below in (\ref{ex:zouadv}).
+\ea\label{ex:zouadv}
+\ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}\\
+    he quietly go-\textsc{pfv}.\\
+    \glt `He quietly went away.'
+}
+\ex[*]{\gll \objex{ta1} \objex{zou3-le} \objex{qiao1qiao1de}.\\
+    he go-\textsc{pfv} quietly\\
+}
+\z\z
+
+\citet[50]{Ernst2014} mentions that the only possible post-verbal adverbials are participant PPs (\textit{with somebody}),
+manner or resultative V-de constructions as well as 
+duration and frequency expressions.
+(\ref{ex:inVCPa}) shows a case of inserting a frequency expression into a VP.
+This suggests that it is possible to insert adverbials into a VP.
+
+This  word order constraint is not a problem for the test in (\ref{ex:modVV}), as the adverb can, in principle, be interpreted as modifying the second verb.
+}
+
 \ea[*]{\label{ex:modVV} %看偷偷地看
@@
 %开门两次
-\ea \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
+\ea\label{ex:inVCPa} \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
 open door three time\\
@@
 Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as \textit{reduplication}) in other languages
-than syntactic reduplication (below as \textit{repetition}; \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
+than syntactic reduplication (below as \textit{repetition}; \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).\footnote{
+We do not claim that the syntactic analyses of reduplication discussed in \sectref{sec:prev} consider verbal reduplication in Mandarin Chinese to be syntactic repetition.
+}
 \citet[35--36]{Gil2005} considers non-iconicity and having only two (but not more) copies as sufficient but not necessary conditions for reduplication.

### 2025-06-14 chapters/ch04-Previous.tex
answered most reviewer comments
modify main paper according to reviewer replies

@@
 Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.\footnote{
-One reviewer suggests that the loss of the idiomatic meaning in (\ref{ex:clf-idiom}) but not in (\ref{ex:redup-idiom}) may be attributed to the use of the numeral \obj{san1} `three' in (\ref{ex:clf-idiom}),
-because if \obj{san1} \obj{xia3} `three times' is replaced with \obj{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
+This applies except when \obj{yi2} \obj{xia4} `once' is used. 
+Because of this exception, one reviewer suggests that the loss of the idiomatic meaning in (\ref{ex:clf-idiom}) 
+but not in (\ref{ex:redup-idiom}) may be attributed to the use of the numeral \obj{san1} `three' in (\ref{ex:clf-idiom}),
+because if \obj{san1} \obj{xia4} `three times' is replaced with \obj{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
 We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special, 
@@
 However, as shown in \sectref{sec:Aktionsarten}, the reduplication of states and achievements is unusual but not impossible.
-This suggests that the reduced acceptability of reduplicated achievement and stative verbs is semantic rather than structural. 
-Their use is possible in specific contexts and should not be ruled out syntactically.
+This suggests that the reduced acceptability of reduplicated achievement and stative verbs is \textit{semantic} rather than \textit{structural}. 
+Their use is possible in specific contexts and should not be ruled out \textit{syntactically}.
 Consequently, this proposal does not seem to offer an appropriate account for  reduplication.
@@
  \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
-He observes that  \obj{zhe} `\textsc{prog}', \obj{le} `\textsc{pfv}' and \obj{wan2} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}),
-while \obj{zai4} `\textsc{dur}' and \obj{guo4} `\textsc{exp}' can occur without further information (\ref{ex:complete}).
+ He observes the so-called incompleteness effect, namely that a minimal sentence, 
+ which only contains a verb marked by \obj{zhe} `\textsc{dur}',
+ \obj{le} `\textsc{pfv} or \obj{wan2} \textsc{compl} 
+ and its arguments, 
+ seems incomplete without further sentential elements 
+ such as the sentence final particle \obj{le} 
+ or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}) . 
+ In contrast, a minimal sentence with a verb marked by  \obj{zai4} `prog' or \obj{guo}
+ `\textsc{exp}'  and its arguments can stand alone (\ref{ex:complete}).
 
@@
  \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan4} fan *(le).\\
- Xiaoli eat-\textsc{prog}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
+ Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
  \glt `Xiaoli is eating/ate/finished eating the meal.'
@@
 \ea\label{ex:complete}
-\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo4}.\\
-Xiaoli just.now \textsc{dur} cry/cry-\textsc{exp}\\
+\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo}.\\
+Xiaoli just.now \textsc{prog} cry/cry-\textsc{exp}\\
 \glt `Xiaoli was crying/cried just now.'
 \z
-He thus proposed three aspect positions under TP.
-\obj{zai4} and \obj{guo4} reside under Asp$_1$, while \obj{zhe} and \obj{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \obj{wan2} can only occur with certain types of predicate.
+He thus proposed three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
+while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{
+    \citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that 
+    \obj{wan2} can only occur with certain types of predicate.
      This differentiation does not play a role for our purpose and will not be further discussed here.}
@@
 
-Turning to reduplication, it cannot occur without additional information as well (\ref{ex:redup-tsai}).
+Turning to reduplication, a minimal sentence with reduplication also seems incomplete (\ref{ex:redup-tsai}).
 Based on this, the reduplicant should reside under Asp$_2$, as illustrated in \figref{tree:redupasp}.
@@
 
-This analysis would result in a mismatch between syntax and semantics. 
-Even though \obj{le}, \obj{guo4} and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
-\obj{guo4} is situated under Asp$_1$ while \obj{le} and the reduplication are under Asp$_2$, as can be seen from \figref{tree:redupasp}.
+This analysis would result in a mismatch between syntax and semantics, 
+in the sense that the aspect markers that belong to the same semantic group do not occur in the same syntactic position. 
+Even though \obj{le} `\textsc{pfv}', \obj{guo} `\textsc{exp}' and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
+\obj{guo} `\textsc{exp}' is situated under Asp$_1$, while \obj{le} `\textsc{pfv}' and reduplication are under Asp$_2$.
+Similarly, \obj{zai4} `\textsc{prog}' and \obj{zhe} `\textsc{dur}' are both imperfective aspects but also occur in different syntactic positions.
 

### 2025-06-16 chapters/ch01-Intro.tex
check main text before sec 2.3

--- 2024-09-30 chapters/ch01-Intro.tex
@@
 The data in this paper was drawn from several sources.
-In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} and the BCC corpus \citep{BCC} was also consulted.
+In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}; \citealt{Zhanetal2003, Zhanetal2019}) and the BCC corpus \citep{BCC} were also consulted.
 Further, examples from novels and plays written by native speakers were considered.

### 2025-06-16 chapters/ch02-Phenomenon.tex
check main text before sec 2.3

@@
 This shows that the former is less common than the latter.
-(\ref{ex:Akankan}) is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
+(\ref{ex:Akankan}) below is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
 \ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
 \gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
-just follow-\textsc{prog} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
+just follow-\textsc{dur} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
 \glt `Let's just follow the north wind, try and see if we can block the sand!'
@@
 \ex\label{ex:forms-di} for disyllabic verbs: \obj{lai2-wang3} come-go `come and go/communicate'
-		\ea \gll \objex{lai2-wang3-lai2-wang3}\\
+		\ea\label{ex:forms-dia} \gll \objex{lai2-wang3-lai2-wang3}\\
 		come-go-come-go\\ \jambox{ABAB}
@@
 
-		\ex \gll \objex{lai2-wang3-le-lai2-wang3}\\
+		\ex\label{ex:forms-dib} \gll \objex{lai2-wang3-le-lai2-wang3}\\
 		come-go-\textsc{pfv}-come-go\\ \jambox{AB-\textit{le}-AB}
@@
 
-		\ex \gll \objex{lai2-lai2-wang3-wang3}\\
+		\ex\label{ex:forms-dic} \gll \objex{lai2-lai2-wang3-wang3}\\
 		come-come-go-go\\ \jambox{AABB}
@@
 namely that the event happens for a short duration or to a small extent. 
-By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress. 
+By contrast, AABB expresses an increasing meaning, which indicates a repetition or an action in progress
+(compare (\ref{ex:forms-dia}) and (\ref{ex:forms-dic})). 
 \citet[Sec.\,3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
@@
 
-\ex[*]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \objex{tao3lun4-tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
+\ex[*]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \obj{tao3lun4-tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
     this \textsc{clf} question everybody still need.to discuss-discuss one while/several time\\}
@@
 \ea\label{ex:redup-asp}
-\ea[]{ \gll \objex{wo3} \objex{kan4-le/guo4/zhe} \objex{zhe4} \objex{ben3} \objex{shu1}\\
+\ea[]{ \gll \objex{wo3} \objex{kan4-le/guo/zhe} \objex{zhe4} \objex{ben3} \objex{shu1}\\
 I read-\textsc{pfv/exp/dur} this \textsc{clf} book\\
@@
 }
-\ex[*]{ \gll \objex{wo3} \objex{kan4-kan4-le/guo4/zhe} \objex{zhe4} \objex{ben3} \objex{shu1}\\
+\ex[*]{ \gll \objex{wo3} \obj{kan4-kan4-le/guo/zhe} \objex{zhe4} \objex{ben3} \objex{shu1}\\
     I read-read-\textsc{pfv/exp/dur} this \textsc{clf} book\\
@@
 % 所谓职业的读书者，譬如学生因为升学，教员因为要讲功课，不翻翻书，就有些危险的就是。(CCL 1920s\1928\文学\1928 鲁迅 而已集.txt)
-\gll \objex{jiao4yuan2} \ldots\, \objex{bu4} \obj{fan1-fan1} \objex{shu1}, \objex{jiu4} \objex{you3xie1} \objex{wei1xian3} \objex{de} \objex{jiu4} \objex{shi4}.\\
+\gll \objex{jiao4yuan2} \ldots\, \objex{bu4} \obj{fan1-fan} \objex{shu1}, \objex{jiu4} \objex{you3xie1} \objex{wei1xian3} \objex{de} \objex{jiu4} \objex{shi4}.\\
 lecturer {} not flip-flip book just somewhat dangerous \textsc{de} just be\\ \jambox{(CCL)}
@@
 \ex\label{ex:qobj2}% 男人跟男人的沟通比较快，打打球、喝喝两 杯就行了。（BCC 微博）
-\gll \objex{nan2ren2} \objex{gen1} \objex{nan2ren2} \objex{de} \objex{gou1tong1} \objex{bi3jiao4} \objex{kuai4}, \ldots\, \obj{he1-he1} \objex{liang3} \objex{bei1} \objex{jiu4} \objex{xing2} \objex{le}.\\
+\gll \objex{nan2ren2} \objex{gen1} \objex{nan2ren2} \objex{de} \objex{gou1tong1} \objex{bi3jiao4} \objex{kuai4}, \ldots\, \obj{he1-he} \objex{liang3} \objex{bei1} \objex{jiu4} \objex{xing2} \objex{le}.\\
 man and man \textsc{de} communication relatively fast {} drink-drink two cup just ok \textsc{ptc}\\ \jambox{(BCC)}
@@
 \ea\label{ex:zouadv}
-\ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}\\
-    he quietly go-\textsc{pfv}.\\
+\ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}.\\
+    he quietly go-\textsc{pfv}\\
     \glt `He quietly went away.'
@@
 duration and frequency expressions.
-(\ref{ex:inVCPa}) shows a case of inserting a frequency expression into a VP.
+(\ref{ex:inVCPb}) shows a case of inserting a frequency expression into a VP.
 This suggests that it is possible to insert adverbials into a VP.
@@
 
-\ex  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
+\ex\label{ex:inVCPb}  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
 open three time door\\

### 2025-06-17 replies-reviews2.tex
check main text before sec 2.4

@@
 \textbf{Answer:} This passage is revised as follows 
-and moved before example (28) to directly follow the passage before: 
+and moved before example (27) ((28) in the previous version of the draft) to directly follow the passage before: 
 ``As shown in Section 2.3.1, reduplication can also express

### 2025-06-17 chapters/ch02-Phenomenon.tex
check main text before sec 2.4

@@
   \ex\label{ex:redup-dyn-look}
-    \gll  \objex{Wu2} \objex{Xu4mang2} \objex{kan4-le-kan4} \objex{zuo4-an4} \objex{shi2} \objex{liu2xia4} de \objex{jiao3yin1} \ldots\\
+    \gll  \objex{Wu2} \objex{Xu4mang2} \obj{kan4-le-kan4} \objex{zuo4-an4} \objex{shi2} \objex{liu2xia4} de \objex{jiao3yin1} \ldots\\
     Wu Xumang look-\textsc{pfv}-look commit-crime when leave \textsc{de} footprint\\ \jambox{\citep[158]{XiaoMcEnery2004}}
@@
 \ex\label{ex:xiangxin}%谁让我来相信相信 (CCL)
-\gll \objex{shei2} \objex{rang4} \objex{wo3} \objex{lai2} \objex{xiang1xin4-xiang1xin4}\\
+\gll \objex{shei2} \objex{rang4} \objex{wo3} \objex{lai2} \obj{xiang1xin4-xiang1xin4}\\
 who let I come believe-believe\\\jambox{(CCL)}
@@
   \ea\label{ex:cry}
-    \gll \objex{wei4ci3}, \objex{Deng4} \objex{Li4jun1} \objex{shang1xin1} \objex{de} \objex{ku1-le} \objex{san1} \objex{tian1}.\\
-    for.this Deng Lijun sadly \textsc{de} cry-\textsc{pfv} three day\\ \jambox{\citep[129]{XiaoMcEnery2004}}
+    \gll \objex{wei4ci3}, \objex{Deng4} \objex{Li4jun1} \objex{shang1xin1de}  \objex{ku1-le} \objex{san1} \objex{tian1}.\\
+    for.this Deng Lijun sadly  cry-\textsc{pfv} three day\\ \jambox{\citep[129]{XiaoMcEnery2004}}
     \glt `For this reason, Deng Lijun cried sadly for three days.'
@@
 
-In comparison, the experiential aspect marker \obj{guo4} cannot co\hyp{}occur with a reduplicated verb, 
+In comparison, the experiential aspect marker \obj{guo} cannot co\hyp{}occur with a reduplicated verb, 
 because its dynamicity attributes to an ``experiential change'' \citep[148]{XiaoMcEnery2004}, 
 namely that a situation has been experienced historically and that ``the final state of the situation no longer obtains'' at the reference time \citep[144]{XiaoMcEnery2004}. 
-Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \obj{guo4} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
+Compare (\ref{ex:guo-dyn}) and (\ref{ex:le-dyn}), \obj{guo} in (\ref{ex:guo-dyn}) suggests a change out of the state of being a soldier, 
 whereas \obj{le} in (\ref{ex:le-dyn}) conveys a change into the state of being a soldier \citep[149]{XiaoMcEnery2004}.
@@
   \ea\label{ex:guo-dyn}
-    \gll \objex{ta1} \objex{dang1-guo4} \objex{bing1}.\\
+    \gll \objex{ta1} \objex{dang1-guo} \objex{bing1}.\\
     he serve.as-\textsc{exp} soldier\\ \jambox{\citep[149]{XiaoMcEnery2004}}
@@
 \z
-It is clear that \obj{guo4} only indicates a change at the termination of a situation and cannot express the dynamicity within a situation.
+It is clear that \obj{guo} only indicates a change at the termination of a situation and cannot express the dynamicity within a situation.
 Hence, it is incompatible with the semantics of the reduplication.

### 2025-06-17 replies-reviews2.tex
check all main text, adapt example and page numbers in reviewer replies 2 to the newest version

@@
 \noindent
-\textbf{Answer:} We modified footnote 14 (footnote 11 in the previous draft) as follows to make this point clearer: ``This applies except when \obj{yi2 xia4} `once' is used.
-Because of this exception, one reviewer suggests that the lost of the idiomatic interpretation may be attributed to the use of the numeral \obj{san1} `three' in (52b).
+\textbf{Answer:} We modified footnote 15 (footnote 11 in the previous draft) as follows to make this point clearer: ``This applies except when \obj{yi2 xia4} `once' is used.
+Because of this exception, one reviewer suggests that the lost of the idiomatic interpretation may be attributed to the use of the numeral \obj{san1} `three' in (50b) (52b in the previous draft).
 We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special,
@@
 \noindent
-\textbf{Answer:} As we explained in our previous reply, 
+\textbf{Answer:} As we explained in our previous reply and also in Section 2.3, 
 verb classes are determined solely based on 
@@
 \noindent
-\textbf{Answer:} Yes, and this is also addressed in our analysis in Section 4.
-\todo[inline]{YL to do: add page number}
+\textbf{Answer:} Yes, and this is also addressed in our analysis in Section 4, p. 40.
+%\todo[inline]{YL to do: add page number}
 
@@
     Therefore, the general explanation for the ungrammaticality of \obj{kai1} \obj{tou1tou1de} \obj{men2} `open secretly door' is that the adverb cannot occur after the verb.
-    This is not a problem for the test in (43), as the adverb can, in principle, be interpreted as modifying the second verb.
+    This is not a problem for the test in (41) (43 in the previous draft), as the adverb can, in principle, be interpreted as modifying the second verb.
 

### 2025-06-17 chapters/ch02-Phenomenon.tex
check all main text, adapt example and page numbers in reviewer replies 2 to the newest version

@@
 \ea[]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \objex{tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
-this \textsc{clf} question everybody still need.to discuss one while/several time\\
+this \textsc{clf} question everybody still need.to discuss one while/several \textsc{clf}\\
 \glt `As for this question, everybody still needs to discuss it for a while/several times.'}
@@
 \ex[*]{\gll \objex{zhe4} \objex{ge4} \objex{wen4ti2} \objex{da4jia1} \objex{hai2} \objex{yao4} \obj{tao3lun4-tao3lun4} \objex{yi2} \objex{hui4er}/\objex{ji3} \objex{ci4}.\\
-    this \textsc{clf} question everybody still need.to discuss-discuss one while/several time\\}
+    this \textsc{clf} question everybody still need.to discuss-discuss one while/several \textsc{clf}\\}
 %    \glt `As for this question, everybody still needs to discuss it for a while/several times.'}
@@
 \ea\label{ex:AABB-input}
-  \ea \gll \objex{duo3-shan3} $\rightarrow$ \obj{duo3}-\obj{duo3}-\obj{shan3}-\obj{shan2}\\
+  \ea \gll \objex{duo3-shan3} $\rightarrow$ \obj{duo3}-\obj{duo3}-\obj{shan3}-\obj{shan3}\\
   hide-dodge {} hide-hide-dodge-dodge\\ \jambox{\citep[88]{Xie2020}}
@@
 \ea\label{ex:yaohuang} %我趁机从大货车以及左边的轿车车门上贴肤而过，	摇摇晃晃了	几下
-\ea[]{\gll \objex{wo3} \ldots\, \obj{yao2-yao2-huang4-huang3-le} \objex{ji3} \objex{xia4} \ldots\\
+\ea[]{\gll \objex{wo3} \ldots\, \obj{yao2-yao2-huang4-huang4-le} \objex{ji3} \objex{xia4} \ldots\\
 I {} shake-shake-sway-sway-\textsc{pfv} several time\\\jambox{(CCL)}
@@
 \ea\label{ex:inVCPa} \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
-open door three time\\
+open door three \textsc{clf}\\
 \glt `open the door three times'
@@
 \ex\label{ex:inVCPb}  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
-open three time door\\
+open three \textsc{clf} door\\
 \glt `open the door three times'

### 2025-06-17 chapters/ch05-Analysis.tex
check all main text, adapt example and page numbers in reviewer replies 2 to the newest version

@@
 \ex\label{ex:AByiAB-li}
-\gll \objex{fei1chang2} \objex{yan2su3} de \objex{ba3} \objex{jin4shi4} \objex{yan3jing4} \obj{duan1zheng4-le-yi-duan1zheng4}.\footnotemark\\
+\gll \objex{fei1chang2} \objex{yan2su4} de \objex{ba3} \objex{jin4shi4} \objex{yan3jing4} \obj{duan1zheng4-le-yi-duan1zheng4}.\footnotemark\\
 very seriously \textsc{de} \textsc{ba} nearsighted glasses straighten-\textsc{pfv}-one-straighten\\
@@
 \ex 
-\gll \objex{dan4shi4} \objex{dui4} \objex{fa1} \objex{mei2} \objex{fa1}-\objex{guo4} \objex{he2ge2-zheng4}, \objex{yi3jing1} \objex{shuo1} \objex{bu4} \objex{qing1} le, \objex{xu1yao4} \obj{cha2-yi-cha2-kan4}.\\
+\gll \objex{dan4shi4} \objex{dui4} \objex{fa1} \objex{mei2} \objex{fa1}-\objex{guo} \objex{he2ge2-zheng4}, \objex{yi3jing1} \objex{shuo1} \objex{bu4} \objex{qing1} le, \objex{xu1yao4} \obj{cha2-yi-cha2-kan4}.\\
 but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}

### 2025-06-18 replies-reviews2.tex
added more on MRS

--- 2025-06-14 replies-reviews2.tex
@@
     \noindent
-    \textbf{Answer:}
-    \todo[inline]{Stefan, say something}
+    \textbf{Answer:} We added references and particularly mentioned that MRS is also used in other
+    theoretical work and in computational implementations like the Grammar Matrix and CoreGram and
+    we pointed the reader to the HPSG handbook, which has a section on MRS in the chapter on
+    sematnics. We also point to Müller's forthcoming textbook that contains a chapter introducing MRS.
 

### 2025-06-18 chapters/ch05-Analysis.tex
added more on MRS

--- 2024-09-30 chapters/ch05-Analysis.tex
@@
 using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
+MRS is one instance of underspecified semantics as is currently used in theoretical and
+computational work in HPSG (\citealt[Section~6]{KR2024a}, \citealt[Section~3]{BFO2002a-u},
+\citealt[Section~4.4]{MuellerCoreGram}, \citealt[Chapter~5]{MuellerLehrbuch4}). The advantage of
+such types of semantics is that scope relations can be left underspecified. This way it is avoided
+that large numbers of analyses are assigned to single sentences. Instead sentences are paired with
+underspecified semantic representations from which various readings can be derived.
 MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
 represented by statements of domination. This allows for elegant ways to underspecify scope. The
-details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005}. In
+details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005},
+\citet[Section~6]{KR2024a} or for the use of MRS in a grammar of German to \citet[Chapter~5]{MuellerLehrbuch4}. In
 what follows, we will present the elementary predications with the features assumed in MRS, but leave

### 2025-06-18 chapters/ch04-Previous.tex

@@
 \ea\label{ex:clf}
-\gll \objex{mei2} \objex{che3} \objex{guo4} \objex{yi2} \objex{ci4} \objex{huang3}\\
-not tell \textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
+\gll \objex{mei2} \objex{che3}-\objex{guo} \objex{yi2} \objex{ci4} \objex{huang3}\\
+not tell-\textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
 \glt `haven't told lie once'
@@
 \gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
-she look-\textsc{pfv} his face one time\\\jambox{(CCL)}
+she look-\textsc{pfv} his face one \textsc{clf}\\\jambox{(CCL)}
 \glt `She took a look at his face.'
@@
 \gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
-he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
+he {} just look-\textsc{pfv} glass one \textsc{clf} glass just break-\textsc{pfv}\\\jambox{(CCL)}
 \glt `He just took a look at the glass and the glass just broke.'
@@
  or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}) . 
- In contrast, a minimal sentence with a verb marked by  \obj{zai4} `prog' or \obj{guo}
+ In contrast, a minimal sentence with a verb marked by  \obj{zai4} `\textsc{prog}' or \obj{guo}
  `\textsc{exp}'  and its arguments can stand alone (\ref{ex:complete}).
@@
 \ea\label{ex:incomplete}
- \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan4} fan *(le).\\
+ \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan42} fan *(le).\\
  Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
@@
 \z
-He thus proposed three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
+He thus propose three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
 while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{
@@
   [...
-    [AspP$_1$ (outer aspect) [Asp$_1$\\zai/guo]
+    [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
       [\textit{v}P [\textit{v}]
-        [AspP$_2$ (middle aspect) [Asp$_2$\\zhe/le]
-          [VP [V-Asp$_3$ (inner aspect)\\wan]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe/le}]
+          [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
           ]
@@
         [...
-        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo4}]
+        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
         [\textit{v}P [\textit{v}]

### 2025-06-18 chapters/ch04-Previous.tex
some typos

@@
  such as the sentence final particle \obj{le} 
- or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}) . 
+ or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}). 
  In contrast, a minimal sentence with a verb marked by  \obj{zai4} `\textsc{prog}' or \obj{guo}
@@
 \z
-He thus propose three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
+He thus proposes three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
 while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{

### 2025-07-24 chapters/ch02-Phenomenon.tex

@@
 I have.to listen-look-look your condition then say\\\jambox{(BCC)}
-\glt `I'll have to listen to your conditions first before talking about it/ deciding.'
+\glt `I'll have to listen to your conditions first before talking about it\slash deciding.'
 \z
@@
  \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compare the AA, ABAB and AABB forms of reduplication 
-and found a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin. 
+and find a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin.
 Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 

### 2025-07-24 chapters/ch04-Previous.tex

@@
  which only contains a verb marked by \obj{zhe} `\textsc{dur}',
- \obj{le} `\textsc{pfv} or \obj{wan2} \textsc{compl} 
+ \obj{le} `\textsc{pfv}' or \obj{wan2} `\textsc{compl}' 
  and its arguments, 
@@
 \ea\label{ex:incomplete}
- \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan42} fan *(le).\\
+ \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan2} \objex{fan4} *(le).\\
  Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\

### 2025-07-24 main.tex
added analysis as unary branching tree, addressed issues pointed out by reviewers
fixed typos, formulations

@@
 \input{localcommands}
+\input{localhyphenation}
+
+%\newtoggle{draft}\togglefalse{draft}
+\newtoggle{draft}\toggletrue{draft}
 
@@
 
-\rightrunning{An HPSG account for deliminative verbal reduplication in Mandarin Chinese} % Short title
+\rightrunning{Deliminative verbal reduplication in Mandarin Chinese} % Short title
 
@@
 We provide a detailed description of the phenomenon.
-After discussing reduplication’s interaction with verb classes and aspect markers, we argue that it is better analyzed as a morphological rather than a syntactic process.
+After discussing reduplication's interaction with verb classes and aspect markers, we argue that it is better analyzed as a morphological rather than a syntactic process.
 We put forward a lexical rule for verbal reduplication in Mandarin Chinese, and the different forms of reduplication are captured in an inheritance hierarchy.

### 2025-07-29 chapters/ch01-Intro.tex
added more on MRS
shortened the bibliography

@@
 It contributes more empirical evidence and 
-offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, HPSGHandbook}) to this phenomenon 
+offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, HPSGHandbook-2}) to this phenomenon 
 using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}) as the semantic representation formalism.
-This new account avoids the problems of previous approaches and
+This new account of reduplication avoids the problems of previous approaches and
 explains more forms of deliminative verbal reduplication in Mandarin Chinese.

### 2025-07-30 replies-reviews2.tex
some typos
shortened the bibliography
move parts to appendix

@@
 
+\bigskip
 \noindent
@@
     we pointed the reader to the HPSG handbook, which has a section on MRS in the chapter on
-    sematnics. We also point to Müller's forthcoming textbook that contains a chapter introducing MRS.
+    sematnics. We also point to Müller's forthcoming textbook that contains a chapter introducing
+    MRS.
 
 \end{enumerate}
+
+\section{Shortening}
+Since our manuscript exceeded the word limit of the journal, we moved the following parts into the appendices:
+\begin{itemize}
+    \item The analysis based on \citet{Tsai2008} (p.
+25--27 in the last version of the manuscript), because \citet{YangWei2017} did not spell out the exact analysis, but only suggested that reduplication can be analyzed as an aspect marker in the aspectual system proposed by \citet{Tsai2008}.
+The analysis presented here is inferef by us based on \citet{Tsai2008}.
+
+    \item The possible historical and phonological explanations for only \obj{yi} and \obj{le} appearing in between reduplication (footnote 17 in the last version of the manuscript).
+\end{itemize}
 

### 2025-07-30 chapters/appendix.tex
move parts to appendix

--- 2025-06-17 chapters/ch05-Analysis.tex
@@
-\section{A new HPSG analysis}\label{sec:analysis}
+\section{Analysis based on the aspectual system by \citet{Tsai2008}}\label{app:tsai}
 
-In this section, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
-using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
-MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
-represented by statements of domination. This allows for elegant ways to underspecify scope. The
-details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005}. In
-what follows, we will present the elementary predications with the features assumed in MRS, but leave
-out handle constraints to keep things simple.
+\citet[229]{YangWei2017} claim that reduplication can be analyzed as an aspect marker 
+following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+ \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
+He observes the so-called incompleteness effect, namely that a minimal sentence, 
+which only contains a verb marked by \obj{zhe} `\textsc{dur}',
+\obj{le} `\textsc{pfv}' or \obj{wan2} `\textsc{compl}' 
+and its arguments, 
+seems incomplete without further sentential elements 
+such as the sentence final particle \obj{le} 
+or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}). 
+In contrast, a minimal sentence with a verb marked by  \obj{zai4} `\textsc{prog}' or \obj{guo}
+`\textsc{exp}'  and its arguments can stand alone (\ref{ex:complete}).
 
-Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
-organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
-reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
-structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
-\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
-input verb with the possibility to have further phonological material in between.  \etag{} indicates
-an underspecified list which could be empty or not.\footnote{%
-The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
-follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
-notation, since we think this is more
-precise than simply using three dots.}
-A delimitative relation is appended to the
-\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
-argument (\textsc{arg0}, \ldots, \textsc{arg3} are feature names for arguments. The values are
-indices or events similar to variables in normal predicate logic.). The list of relations contains so-called elementary predications. There is no complicated
-embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
-label can be used as an argument of another relation or in scope constraints, which are not provided
-here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
-elementary predication that is considered the top-most one in the \relsl. Other elementary
-predications may share the label or have arguments with labels of other elementary predications. We
-will discuss an example below when we discuss the perfective lexical rule.
-The label of the output \iboxb{2} is identified with the label of the input and with the
-label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
-relations can be added at the beginning of the \textsc{rels} list to allow for the additional
-perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
-perfective will be elaborated on in the following paragraphs.
+\ea\label{ex:incomplete}
+\gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan2} \objex{fan4} *(le).\\
+Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
+\glt `Xiaoli is eating/ate/finished eating the meal.'
+\z
 
-\eas
-\type{verbal-reduplication-lr} \impl\\
-%\scalebox{.9}{%
-    \avm{
-        [
-        phon & \1 $\oplus$ \etag $\oplus$ \1\\
-        synsem & [ loc\textbar cont [ ltop & \2 \\
-        ind  & \3 ] ]\\
-        rels & \etag $\oplus$ \4 $\oplus$ < [\type*{delimitative-rel}\\
-        lbl & \2\\
-        arg0 & \3 ] > \smallskip\\
-        lex-dtr & [phon \1\\
-        synsem\textbar loc & [cat  & [ head & verb ] \\
-        cont & [ ltop & \2\\
-        ind  & \3 ]]\\
-        rels \4 ] ]
-}
-%}
-\label{avm:redup}
-\zs
+\ea\label{ex:complete}
+\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo}.\\
+Xiaoli just.now \textsc{prog} cry/cry-\textsc{exp}\\
+\glt `Xiaoli was crying/cried just now.'
+\z
+He thus proposes three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
+while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{
+    \citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that 
+    \obj{wan2} can only occur with certain types of predicate.
+    This differentiation does not play a role for our purpose and will not be further discussed here.}
 
-To account for the variations in the phonology of the reduplication as well as 
-the combination with the phonology and semantics of the perfective aspect marker \textit{le}, 
-the type hierarchy of lexical rules in \figref{fig:typehi} is put forward. 
 \begin{figure}
     \centering
-    \scalebox{.9}{\begin{forest}
-        type hierarchy
-        [,phantom
-        [,phantom
-        [verbal-reduplication-lr,name=verbal-reduplicaiton-lr
-        [non-perfective-reduplicaiton-lr
-        [a-a-lr]
-        [a-yi-a-lr]]
-        [,identify=!r211]]]
-        [aspect-marking-lr
-        [perfective-lr
-        [perfective-reduplicaiton-lr%,edge to=verbal-reduplicaiton-lr
-        [a-le-yi-a-lr]
-        [a-le-a-lr]]
-        [v-le-lr]]
-        [durative-lr]
-        [\ldots]]]
+    \begin{forest}
+        [TP [T]
+        [...
+        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
+        [\textit{v}P [\textit{v}]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe/le}]
+        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
+        ]
+        ]
+        ]
+        ]
+        ]
+        ]
     \end{forest}
-}
-    \caption{Type hierarchy for lexical rules of verbal reduplication and \textit{le}}
-    \label{fig:typehi}
+    \caption{Structure of the aspectual system in Mandarin Chinese according to \citet[683]{Tsai2008}}
+    \label{tree:tsai}
 \end{figure}
-Apart from the type \type{perfective-reduplication-lr}, 
-which adds the inherited perfective relation, 
-there is a subtype \type{non-perfective-reduplication-lr}, 
-which does not add further relations. 
-Hence, what is \etag in the \textsc{rels} list in (\ref{avm:redup}) is the empty list in (\ref{avm:nonperf}):
-\ea\label{avm:nonperf}
-\type{non-perfective-verbal-reduplication-lr} \impl\\
-%\scalebox{.9}{%
-    \avm{
-        [
-        rels & \1 $\oplus$ < [ ] > \smallskip\\
-        lex-dtr & [ rels \1 ] ]
-    }
-%}
-\z
-The \textsc{rels} list of the output of the lexical rule is the \textsc{rels} list of
-the daughter \iboxb{1} plus a list with one element. 
-Since this element is specified in the supertype, it is not specified in (\ref{avm:nonperf}) again.
 
-\type{non-perfective-verbal-reduplication-lr} has \type{aa-lr} and \type{a-yi-a-lr} as direct subtypes.
-(\ref{avm:AA}) and (\ref{avm:AyiA}) show \type{aa-lr} and \type{a-yi-a-lr}, respectively.
-As subtypes of \type{ver\-bal\hyp{}re\-dup\-li\-ca\-tion\hyp{}lr} illustrated in (\ref{avm:redup}), 
-both inherit the constraints on the \textsc{lex-dtr} and on the semantics of the output, 
-and because of (\ref{avm:nonperf}), no extra material is appended to the \textsc{rels} value of the input verb
-and the list containing the \type{delimitative-rel}.
- In addition to the inherited constraints,
-\type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
-\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is the empty list, 
-whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:
+Turning to reduplication, a minimal sentence with reduplication also seems incomplete (\ref{ex:redup-tsai}).
+Based on this, the reduplicant should reside under Asp$_2$, as illustrated in \figref{tree:redupasp}.
 
-\ea\label{avm:constr-AA}
-Constraints on lexical rules of type \type{aa-lr} and \type{a-yi-a-lr}:
-%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
- \ea   \type{aa-lr} \impl \\%& 
-  %  \scalebox{.9}{%
-        \avm{
-            [phon & \1 $\oplus$ \1\\
-            lex-dtr & [phon & \1] ]
-    }
-%} %& 
-\ex	\type{a-yi-a-lr} \impl\\
- %    \scalebox{.9}{%
-        \avm{
-            [phon & \1 $\oplus$ \phonliste{ yi } $\oplus$ \1\\
-            lex-dtr & [phon & \1] ]
-    }
-%}
-%\end{tabular}
+\ea\label{ex:redup-tsai}
+\ea[*] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}\\
+    he laugh-laugh\\}
+\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}\\
+    he laugh-\textsc{pfv}-laugh\\
+    \glt `He laughed a little.'}
+\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}, \objex{bu4} \objex{shuo1hua4}\\
+    he laugh-laugh not speak\\
+    \glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
 \z
@@
 
-\noindent
-The lexical rules with all inherited constraints are given in (\ref{avm:AA}) and (\ref{avm:AyiA}):
+\begin{figure}
+    \centering
+    \begin{forest}
+        [TP [T]
+        [...
+        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
+        [\textit{v}P [\textit{v}]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe}/\obj{le}/reduplication]
+        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
+        ]
+        ]
+        ]
+        ]
+        ]
+        ]
+    \end{forest}
+    \caption{Position of reduplication according to the aspectual system in \citet{Tsai2008}}
+    \label{tree:redupasp}
+\end{figure}
 
-\ea\label{avm:AA}
-The AA lexical rule with all constraints inherited from the supertypes:\\
-%\scalebox{.9}{%
-    \avm{
-        [\type*{aa-lr}\\
-        phon & \1 $\oplus$ \1\\
-        synsem & [ loc\textbar cont [ ltop & \2 \\
-        ind  & \3 ] ]\\
-        rels & \4 $\oplus$ < [\type*{delimitative-rel}\\
-        lbl & \2\\
-        arg0 & \3 ] >\\
-        lex-dtr & [phon & \1\\
-        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
-            cont & [ ltop & \2\\
-            ind  & \3 ]]}\\
-        rels & \4]
-        ]
-}
-%}
-\z
+This analysis would result in a mismatch between syntax and semantics, 
+in the sense that the aspect markers that belong to the same semantic group do not occur in the same syntactic position. 
+Even though \obj{le} `\textsc{pfv}', \obj{guo} `\textsc{exp}' and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
+\obj{guo} `\textsc{exp}' is situated under Asp$_1$, while \obj{le} `\textsc{pfv}' and reduplication are under Asp$_2$.
+Similarly, \obj{zai4} `\textsc{prog}' and \obj{zhe} `\textsc{dur}' are both imperfective aspects but also occur in different syntactic positions.
 
-%\newpage
-\ea\label{avm:AyiA}
-The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:\\
-%\scalebox{.9}{%
-    \avm{
-        [\type*{a-yi-a-lr}\\
-        phon & \1  $\oplus$ \phonliste{ yi } $\oplus$ \1\\
-        synsem & [ loc\textbar cont [ ltop & \2 \\
-        ind  & \3 ] ]\\
-        rels &  \4 $\oplus$ < [\type*{delimitative-rel}\\
-        lbl & \2\\
-        arg0 & \3 ] >\\
-        lex-dtr & [phon & \1\\
-        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
-            cont & [ ltop & \2\\
-            ind  & \3 ]]}\\
-        rels & \4]
-        ]
-}
-%}
-\z
-
-\type{v-le-lr} is a direct subtype of the \type{perfective-lr}.
-\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}
-and has two subtypes, \type{a-le-yi-a-lr} and \type{a-le-a-lr} itself.
-\type{verbal-reduplication-lr} is already presented in (\ref{avm:redup}). 
-We now turn to the constraints on \type{perfective-lr} and its subtypes.
-
-\citet[246]{MuellerLipenkova2013} propose the perfective lexical rule given in (\ref{avm:pfv-old}), 
-adapted to the formalization adopted in the current paper.
-It takes a verb as \textsc{lex-dtr}
-and appends \phonliste{ le } to its phonology.
-Further, it accounts for the change in semantics by appending the \textsc{rels} value of the input verb to a \type{perfective-rel}.
-
-\ea\label{avm:pfv-old}
-Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
-%\scalebox{.9}{%
-    \avm{
-        [\type*{perfective-lr}\\
-        phon & \1 \+ \phonliste{ le }\\
-        \punk{synsem\textbar loc\textbar cont}{ [ ltop & \2\\
-            ind & \3 ]}\\ 
-        rels & <[\type*{perfective-rel}\\
-        lbl  & \2\\
-        arg0 & \3\\
-        arg1 & \4]> \,\+\, \5\smallskip\\
-        lex-dtr & [phon & \1\\
-        \punk{synsem\textbar loc}{[cat & [ head & verb]\\
-            cont & [ ltop & \4\\
-            ind & \3]]}\\
-        rels & \5]
-        ]
-}
-%}
-\z
-The event variables \iboxb{3} of the input and the output verb are shared. 
-The \textsc{ltop} of the output of the lexical rule \iboxb{2} is the label of the perfective relation, 
-and this relation scopes over the embedded verb. 
-The handle of the embedded verb \iboxb{4} is the argument of the \type{perfective-rel}.
-
-The lexical rule suggested in (\ref{avm:pfv-old}) only explains simple perfective aspect marking with \textit{le}, 
-where \textit{le} immediately follows the verb.
-But it cannot account for the perfective aspect marking of a reduplicated verb,
- as \textit{le} does not occur after the reduplication, 
-nor can \textit{le} be reduplicated together with the verb.
-It can only appear between the verb and the reduplicant.
-In order to accommodate \textit{le} marking for both simple and reduplicated verbs, 
-a general perfective lexical rule as in (\ref{avm:pfv-new}) and 
-a subtype \type{v-le-lr} as in (\ref{avm:vle}) are posited here.
-Besides adding a \type{perfective-rel} in the \textsc{rels} list of the output as in (\ref{avm:pfv-old}), 
-the \type{perfective-lr} in (\ref{avm:pfv-new}) allows an underspecified list to be appended at the end of the \textsc{rels} list.
-The \textsc{phon} value of the output makes it possible for further phonological material to occur both before and after \phonliste{ le }.
-
-\ea\label{avm:pfv-new}
-Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
-%\scalebox{.9}{%
-    \avm{
-        [\type*{perfective-lr}\\
-        phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
-        \punk{synsem\textbar loc \textbar cont}{ [ltop & \2\\
-            ind  & \3]}\\ 
-        rels & <[\type*{perfective-rel}\\
-        lbl  & \2\\
-        arg0 & \3\\
-        arg1 & \4 ]> $\oplus$ \5 $\oplus$ \etag\smallskip\\
-        lex-dtr & [%phon & \1\\
-        \punk{synsem\textbar loc}{[cat & [ head & verb ]\\
-            cont & [ ltop & \4\\
-            ind  & \3]]}\\
-        rels & \5]
-        ]
-}
-%}
-\z
-
-\type{v-le-lr} with all inherited constraints as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
-and that nothing else comes after \phonliste{ le }.
-Furthermore, no other list can be appended at the end of the \textsc{rels} list of the output anymore.
-This corresponds to the proposal of \citet[246]{MuellerLipenkova2013} shown in (\ref{avm:pfv-old}), 
-which accounts for the simple perfective marking of verbs.
-
-%\newpage
-\ea\label{avm:vle}
-Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
-%\scalebox{.9}{%
-    \avm{
-        [\type*{v-le-lr}\\
-        phon & \1 $\oplus$ \phonliste{ le }\\
-        \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
-        rels & <[\type*{perfective-rel}\\
-        lbl  & \2\\
-        arg0 & \3\\
-        arg1 & \4]> $\oplus$ \5\smallskip\\
-        lex-dtr & [phon & \1\\
-        synsem\textbar loc \textbar cat  & [ head & verb\\
-        cont & [ltop & \4\\
-        ind & \3]]\\
-        rels & \5]]
-}
-%}
-\z
-
-\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}.
-The \textsc{phon} value of the output reduplicates the phonology of the input verb and states that there is \phonliste{ le } in between, 
-as well as potentially further phonological material.
-The \textsc{rels} list of the output appends the \type{delimitative-rel} to the \type{perfective-rel} and the \textsc{rels} value of the input verb.
-The arguments of both \type{perfective-rel} and \type{delimitative-rel} share the event index of the
-input verb \iboxb{3} to ensure that they apply to the same event denoted by the input verb. 
-The label of the \type{delimitative-rel} and the input verb are identified (\type{delimitative-rel} is a modifier) 
-and this shared label is embedded under the \type{perfective-rel}.
-
-\ea\label{avm:pfv-redup}
-Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
-constraints inherited from \type{perfective-lr} and \type{verbal-redu\-pli\-ca\-tion-lr}:\\
-%\resizebox{\linewidth}{!}{
- %   \scalebox{.9}{%
-        \avm{
-            [\type*{perfective-reduplication-lr}\\
-            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
-            \punk{synsem\textbar loc\textbar cont\textbar ltop}{ \2}\\ 
-            rels & <[\type*{perfective-rel}\\
-            lbl & \2\\
-            arg0 & \3\\
-            arg1 & \4]>
-            $\oplus$ \5 $\oplus$
-            <[\type*{delimitative-rel}\\
-            lbl  & \4\\
-            arg0 & \3]>\\
-            lex-dtr & [phon & \1\\
-            synsem\textbar loc & [cat  & [ head & verb ]\\
-            cont & [ ltop & \4\\
-            ind  & \3]]\\
-            rels & \5]
-            ]
-    }
-%}
-    %}
-\z
-For example %(\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as
- (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
-where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
-\ea\label{ex-he-tasted-the-soup-a-little-bit2}
-    \gll \objex{ta1} \obj{chang2}-\obj{le}-\obj{chang2} \objex{tang1}.\\
-    he taste-\textsc{pfv}-taste soup\\
-    \glt `He tasted the soup a little bit.'
- \z
-\ea\label{ex:mrs-soup}
-h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
-\z
-So the delimitative relation is treated as an adjunct to the main relation of the verb, 
-and the perfective relation scopes over both the main relation and the delimitative relation.
-
-Two subtypes of \type{perfective-reduplication-lr} are posited:
-\type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} %as in (\ref{avm:AleyiA}) 
-and \type{a-le-a-lr}, as shown in (\ref{avm:AleA}). %(\ref{avm:AleA}).
-They take over the semantic change to the input from \type{perfective\hyp{}reduplication\hyp{}lr}, but specify the \textsc{phon} value differently.
-Specifically, \type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} specifies the middle phonological material as
-\phonliste{ le, yi }, while \type{a-le-a} specifies it as \phonliste{ le } only.\footnote{
-A reviewer wants to know what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
-He/she states that this aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
+\section{\obj{yi} and \obj{le}}\label{app:hist}
+A reviewer suggests that 
+the fact that only  \obj{yi} and \obj{le}  can appear in between reduplication 
+seems somewhat arbitrary, 
+and it is not evident why certain elements are permissible while others are not.
+We think that there might be historical and phonological reasons.
 
@@
 
-The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
-}
-
-\ea\label{avm:AleA}
-%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
-\ea    %\scalebox{.9}{%
-        \type{a-le-yi-a-lr} \impl\\
-        \avm{
-            [%\type*{a-le-yi-a-lr}\\
-            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
-            lex-dtr & [phon & \1
-            ]
-            ]
-    }
-%}%&
-\ex   % \scalebox{.9}{%
-\label{avm:a-le-a-lr}
-    \type{a-le-a-lr} \impl\\
-        \avm{
-            [%\type*{a-le-a-lr}\\
-            phon & \1 \+ \phonliste{ le } \+ \1\\
-            lex-dtr & [phon & \1
-            ]
-            ]
-    }
-%}
-%\end{tabular}
-\z
-\z
-
-The analysis of (\ref{ex-he-tasted-the-soup-a-little-bit2}) is shown in tree format in
-Figure~\ref{fig-he-tasted-the-soup-a-little-bit}. The \textsc{lex-dtr} is the daughter in the tree.
-\begin{figure}[htbp]
-\centering
-\begin{forest}
-[        \avm{
-            [\type*{a-le-a-lr}\\
-            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \1\\
-            synsem\textbar loc & [ cat  & [ head  & verb\\
-                                            spr   & < NP$_{\6}$ >\\
-                                            comps & < NP$_{\7}$ > ]\\
-                                   cont & [ ltop & \2\\
-                                            ind  & \ibox{3} ]] \\
-            rels & <[\type*{perfective-rel}\\
-            lbl & \2\\
-            arg0 & \3\\
-            arg1 & \4]> $\oplus$ \5 $\oplus$
-            <[\type*{delimitative-rel}\\
-            lbl  & \4\\
-            arg0 & \3]> ]
-    }
-[\avm{ [phon & \1 \phonliste{ chang2 }\\
-       synsem\textbar loc & [cat  & [ head  & verb\\
-                                      spr   & < NP$_{\6}$ >\\
-                                      comps & < NP$_{\7}$ > ]\\
-                             cont & [ ltop & \4\\
-                                      ind  & \3]]\\
-        rels & \5 < [\type{taste}\\
-                     lbl  & \4\\
-                     arg0 & \3\\
-                     arg1 & \6\\
-                     arg2 & \7 ] > ]
-}]]
-\end{forest}
-
-\caption{Analysis of \obj{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
-\end{figure}
-
-The figure shows how the lexical item for \obj{chang2} `to taste' is inserted as a daughter into
-the \type{a-le-a-lr} lexical rule. The arguments of \obj{chang2} `to taste' are represented within the \spr and
-the \compsl (see \citealt{GSag2000a-u} for English) and the respective argument NPs are linked to the
-arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
-the stimulus. See \citet{DKW2021a} for more on linking. The part of speech of the lexical item
-(\type{verb}) and the valence information is carried over from the daughter to the mother
-unchanged. The semantic contribution of the daughter verb, the value of \ibox{5}, is inserted into
-the \relsl of the mother as it was specified in the constraints on the type
-\type{perfective-reduplication-lr} in (\ref{avm:pfv-redup}). The \textsc{phon} value of the mother
-is the concatentation of \obj{chang2}, \obj{le} and \obj{chang2}, as specified in the constraint
-on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \obj{chang2-le-chang2} then
-combines with its object forming a VP. This VP is combined with the subject resulting in a complete
-verbal projection, a sentence. \obj{chang2-le-chang2} behaves in the same way as the simple \obj{chang2}.
-
-Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
-they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
-as long as the input verb is disyllabic.
-Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
-Although these forms are considered unacceptable by some authors \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}},
-\citet[269]{Fan1964} and \citet[143]{Sui2018} consider AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognize that these two forms are rare.
-Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin %(12th to 20th centuries)
- (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.
-
-\settowidth\jamwidth{(CCL)}
-
-\begin{sloppypar}
-\ea\label{ex:ABleyiAB}
-\ea\label{ex:AByiAB-lu}
-\gll \objex{ni3} \objex{yu3} \objex{wo3} \obj{zheng3li3-yi-zheng3li3}.\footnotemark\\
-you let me arrange-one-arrange\\
-\glt `Let me arrange it a little bit!'
-\footnotetext{\obj{Yuan2qu3} \obj{xuan3}: \obj{Lu3zhai1lang2} \textit{[Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
-
-\ex\label{ex:AByiAB-pu}
-\gll \objex{ni3} \obj{da3ting1-yi-da3ting1}.\footnotemark\\
-you inquire-one-inquire\\
-\glt `Inquire about it a little bit!'
-\footnotetext{\obj{Yuan2} \obj{Ming2} \obj{juan4}: \obj{Piao2tong1shi4} \textit{[Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
-
-\ex\label{ex:AByiAB-rou1}
-\gll \objex{ge4} \objex{ge4} \objex{dian3-tou2} \obj{wei1xiao4-yi-wei1xiao4}.\footnotemark\\
-\textsc{clf} \textsc{clf} nod-head smile-one-smile\\
-\glt `Each one nodded his head and smiled a little bit.'
-\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
-
-\ex\label{ex:AByiAB-rou2}
-\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3}-\obj{le-yi}-\obj{ming2xiang3}.\footnotemark\\
-he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\
-\glt `He smiled a little bit and meditated a little bit.'
-\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
-
-\ex\label{ex:AByiAB-li}
-\gll \objex{fei1chang2} \objex{yan2su4} de \objex{ba3} \objex{jin4shi4} \objex{yan3jing4} \obj{duan1zheng4-le-yi-duan1zheng4}.\footnotemark\\
-very seriously \textsc{de} \textsc{ba} nearsighted glasses straighten-\textsc{pfv}-one-straighten\\
-\glt `[He] very seriously straightened the nearsighted glasses quickly.'
-\footnotetext{\objex{Li3}, \objex{Jie2ren2}. 1962. \obj{Da4} \obj{bo1} \textit{[Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
-
-\ex\label{ex:ABleyiAB-ccl}
-\gll \objex{ji3duo1} \objex{san3luan4}-zhe de \objex{chuan2} \objex{li3} de \objex{deng1guang1}, \objex{ye3} \objex{hu1yin1hu1mie4} de \obj{bian4huan4-le-yi-bian4huan4} \objex{wei4zhi}.\\
-many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
-\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
-\z
-\z
-\end{sloppypar}
-
-This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
-The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
-Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.\footnote{
-One reviewer suggests that given that AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}),
-these rare occurrences can be seen as relics of this usage.
-}
-
-AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} can also be accounted for by the lexical rules proposed in this section.
-They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
-Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
-    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.\,2]{Her1996}; \citeyear[Sec.\,3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
-    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
-}
-AA-\obj{kan4} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \obj{kan4} `look',
-whereas A-\obj{kan4}-\obj{kan4} is the compound of a monosyllabic verb (A) and the reduplication of \obj{kan4} `look'.
-A-\obj{yi}-A-\obj{kan4} is also possible, though rare, presumably also due to its length.
-An inquiry in CCL found 55 hits of A-\obj{yi}-A-\obj{kan4}.
-A sample is listed in (\ref{ex:AyiAkan}).
-
-\begin{sloppypar}
-\ea\label{ex:AyiAkan}
-\ea
-\gll \objex{te4yi4} \objex{gong1neng2} de \objex{yan2jiu1zhe3}-men \objex{bu4fang2} \objex{ru2ci3} \obj{shi4-yi-shi4-kan4} \ldots\\
-special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
-\glt `Researchers of special power may as well have a try as such and see \ldots'
-
-\ex 
-\gll \objex{dan4shi4} \objex{dui4} \objex{fa1} \objex{mei2} \objex{fa1}-\objex{guo} \objex{he2ge2-zheng4}, \objex{yi3jing1} \objex{shuo1} \objex{bu4} \objex{qing1} le, \objex{xu1yao4} \obj{cha2-yi-cha2-kan4}.\\
-but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
-\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'
-
-\ex
-\gll \objex{rang4} \objex{wo3} \objex{lai2} \obj{cai1-yi-cai1-kan4}.\\
-let I come guess-one-guess-look\\ \jambox{({CCL})}
-\glt `Let me have a guess.'
-
-\ex
-\gll \objex{da4-lao3ban3}-men \objex{yao4} \obj{deng3-yi-deng3-kan4}\\
-big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
-\glt `Big bosses need to wait a little bit and see.'
-
-\ex
-\gll \objex{fu1ren2} \objex{ni3} \objex{dao4} \obj{shu3-yi-shu3-kan4}, \objex{zhe4} \objex{zhu1} \objex{hua1} de \objex{hua1duo3} \objex{gong4} \objex{you3} \objex{ji3} \objex{zhong3} \objex{yan2se4}.\\
-madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
-\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
-\z
-\z
-Due to the prominent tentative, trying meaning of AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4}, they are not compatible with the perfective aspect marker \obj{le} semantically,
-as one usually cannot try something that is already realized.
-Thus, structures such as  A\hyp{}\obj{le}\hyp{}A\hyp{}\obj{kan4} and A\hyp{}\obj{kan4\hyp{}le\hyp{}kan4} are considered pragmatically infelicitous.
-\end{sloppypar}
-
-The current analysis provides a unified account for all forms of delimitative verbal reduplication in Mandarin Chinese.
-Like in \citet{FanSongBond2015}, \textit{yi} is handled as a phonological element which does not make any contribution to the semantics,
-and an inheritance hierarchy is used to capture the commonalities among different forms of reduplication.
-But the present proposal also reflects the connection between the reduplication and aspect marking via multiple inheritance.
-This account makes use of a semantic mechanism, which correctly rules out aspect marking with forms other than \textit{le}.
-By providing a semantic explanation, this mechanism seems less \textit{ad hoc} than the one used in \citet{FanSongBond2015}, which simply assumed that the reduplication cannot combine with aspect information.
-The present approach also has a broader coverage of the forms of verbal reduplication than the one in \citet{FanSongBond2015}.
-Furthermore, all the forms are derivable from the lexical rules proposed here, so that there is no need to resort to irregular lexicon entries, and the productivity of these forms is correctly captured.
-In sum, the analysis proposed in this paper possesses greater explanatory power and resolves the
-problems of previous studies.
-
-%      <!-- Local IspellDict: en_US-w_accents -->
+%The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.

### 2025-07-30 chapters/ch02-Phenomenon.tex
move parts to appendix

@@
 and find a number of differences between the AA, ABAB forms compared to the AABB form in terms of their semantics, productivity, syntactic distribution and origin.
-Specifically, \citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 
+Specifically, \citet[277]{Fan1964} proposes that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
+while AABB developed from the reiterative rhetoric from Old Chinese. 
+\citet[17--18]{Arcodiaetal2014}, \citet[144]{MelloniBasciano2018} and \citet[90]{Xie2020} identify that AA and ABAB have a diminishing meaning, 
 namely that the event happens for a short duration or to a small extent. 
@@
 (compare (\ref{ex:forms-dia}) and (\ref{ex:forms-dic})). 
-\citet[Sec.\,3.1]{Xie2020} also finds that AA and ABAB have relatively high productivity, 
-whereas the productivity of AABB is low. 
-She further shows that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
-\citet[277]{Fan1964} proposes that AA, ABAB originated from the verb-measure word combination from Middle Chinese, 
-while AABB developed from the reiterative rhetoric from Old Chinese. 
+%\citet[Sec.\,3.1]{Xie2020} also 
+%finds that AA and ABAB have relatively high productivity, 
+%whereas the productivity of AABB is low. 
+%She further shows that AABB is generally correlated with the lack of a postverbal object, but the direct object remains present when a transitive verb undergoes AA or ABAB patterns of reduplication. 
+\citet[Sec.\,3.1]{Xie2020} also finds a number of differences between AA, ABAB vs. AABB forms, which we will discuss in detail in \sectref{sec:word}.
 These differences seem to suggest that there is a fundmental difference between these two groups of verbal reduplication. 

### 2025-07-30 chapters/ch04-Previous.tex
move parts to appendix

--- 2025-06-18 chapters/ch04-Previous.tex
@@
 due to the delimitative aspectual meaning of reduplication. 
-\citet{Travis1999, Travis2000} also analyzes the reduplication in Tagalog as an imperfective aspect marker.
+%\citet{Travis1999, Travis2000} also analyzes the reduplication in Tagalog as an imperfective aspect marker.
 
@@
 
- \citet[229]{YangWei2017} endorse the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
- \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
- He observes the so-called incompleteness effect, namely that a minimal sentence, 
- which only contains a verb marked by \obj{zhe} `\textsc{dur}',
- \obj{le} `\textsc{pfv} or \obj{wan2} \textsc{compl} 
- and its arguments, 
- seems incomplete without further sentential elements 
- such as the sentence final particle \obj{le} 
- or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}). 
- In contrast, a minimal sentence with a verb marked by  \obj{zai4} `\textsc{prog}' or \obj{guo}
- `\textsc{exp}'  and its arguments can stand alone (\ref{ex:complete}).
+ \citet[229]{YangWei2017} endorse the analysis of  reduplication as an aspect marker 
+ following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+\citet{YangWei2017} did not spell out the exact analysis.
+We infer the analysis for reduplication based on \citet{Tsai2008},
+ and show in Appendix~\ref{app:tsai} that \citeauthor{Tsai2008}'s (\citeyear{Tsai2008}) system 
+ has a syntax-semantics mismatch problem.
 
-\ea\label{ex:incomplete}
- \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan42} fan *(le).\\
- Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
- \glt `Xiaoli is eating/ate/finished eating the meal.'
-\z
-
-\ea\label{ex:complete}
-\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo}.\\
-Xiaoli just.now \textsc{prog} cry/cry-\textsc{exp}\\
-\glt `Xiaoli was crying/cried just now.'
-\z
-He thus proposes three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
-while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{
-    \citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that 
-    \obj{wan2} can only occur with certain types of predicate.
-     This differentiation does not play a role for our purpose and will not be further discussed here.}
-
-\begin{figure}
-\centering
-\begin{forest}
-[TP [T]
-  [...
-    [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
-      [\textit{v}P [\textit{v}]
-        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe/le}]
-          [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
-          ]
-        ]
-      ]
-    ]
-  ]
-]
-\end{forest}
-\caption{Structure of the aspectual system in Mandarin Chinese according to \citet[683]{Tsai2008}}
-\label{tree:tsai}
-\end{figure}
-
-Turning to reduplication, a minimal sentence with reduplication also seems incomplete (\ref{ex:redup-tsai}).
-Based on this, the reduplicant should reside under Asp$_2$, as illustrated in \figref{tree:redupasp}.
-
-\ea\label{ex:redup-tsai}
-\ea[*] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}\\
-he laugh-laugh\\}
-\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}\\
-he laugh-\textsc{pfv}-laugh\\
-\glt `He laughed a little.'}
-\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}, \objex{bu4} \objex{shuo1hua4}\\
-he laugh-laugh not speak\\
-\glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
-\z
-\z
-
-\begin{figure}
-    \centering
-    \begin{forest}
-        [TP [T]
-        [...
-        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
-        [\textit{v}P [\textit{v}]
-        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe}/\obj{le}/reduplication]
-        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
-        ]
-        ]
-        ]
-        ]
-        ]
-        ]
-    \end{forest}
-    \caption{Position of reduplication according to the aspectual system in \citet{Tsai2008}}
-    \label{tree:redupasp}
-\end{figure}
-
-This analysis would result in a mismatch between syntax and semantics, 
-in the sense that the aspect markers that belong to the same semantic group do not occur in the same syntactic position. 
-Even though \obj{le} `\textsc{pfv}', \obj{guo} `\textsc{exp}' and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
-\obj{guo} `\textsc{exp}' is situated under Asp$_1$, while \obj{le} `\textsc{pfv}' and reduplication are under Asp$_2$.
-Similarly, \obj{zai4} `\textsc{prog}' and \obj{zhe} `\textsc{dur}' are both imperfective aspects but also occur in different syntactic positions.
-
-In sum, both analyses of the reduplicant as an aspect modifier do not seem to be convincing.
+%In sum, both analyses of the reduplicant as an aspect modifier do not seem to be convincing.
 

### 2025-07-30 chapters/ch05-Analysis.tex
move parts to appendix

@@
 A reviewer wants to know what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
-He/she states that this aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
-
-\obj{le} `\textsc{pfv}' marks the perfective aspect.
-The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in Section~\ref{sec:aspM}.
-
-As for \obj{yi} `one', its use stems from the historical development of delimitative verbal reduplication but is synchronically opac.
-\citet[13--15]{Zhang2000} shows that delimitative verbal reduplication originates from the ``V + numeral + verbal classifier'' phrase,
-where the verbal classifier is borrowed from a verb of the same form, as shown in (\ref{ex:hist1}) from \obj{Song4dai4} \obj{juan4}: \obj{Xu1tang2} \obj{He2shang} \obj{yu3lu4} \textit{[The Song dynasty volume: Quotations from Abbot Xutang]} p.
-387 as cited in \citet[12]{Zhang2000}.
-\ea\label{ex:hist1}
-%明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
-\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{lian2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\\
-Ming again yell Qi also yell Ming in.succession yell two yell Qi thus bow\\
-\glt `Ming yelled again. Qi yelled too. Ming yelled twice. Qi thus bowed.'
-\z
-Here the numeral refers to the actual number of the action taking place
-and can be any number.
-This evolved into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
-but simply conveys that the action happens in a short period of time or for only few times. 
-Consider (\ref{ex:hist2}) from \obj{Song4dai4} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p.
-519 as cited in \citet[13]{Zhang2000}.
-\ea\label{ex:hist2}
-%且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
-\gll \objex{qie3} \obj{xie1-yi-xie1} \objex{le}, \objex{qu4} \objex{zuo4} \objex{di4}.\\
-just rest-one-rest \textsc{ptc} go sit ground\\
-\glt `(Let me) just take a rest and go sit on the ground.'
-\z
-In this case, \obj{yi1} `one' cannot be replaced by other numerals.
-Since V-\obj{yi}-V does not express the actual number of the action anymore,
-it became possible to delete the \obj{yi1} `one',
-hence the use of the VV (or AA) form, too.
-
-Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
-This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure
-and is only there as a historical remnant.
-In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds
-
-Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little/few',
-there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
-In Mandarin Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
-where the \obj{li} is fixed and also does not bear any meaning.
-\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
-and the second syllable in A-\obj{li}-AB occupies an unstressed position.
-We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
-This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
-But a phonological account is out of the scope of this paper and has to be left for further research.
-
-The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
+The possible historical and phonological reasons are discussed in Appendix~\ref{app:hist}.
+In this analysis, the subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
 }
@@
 arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
-the stimulus. See \citet{DKW2021a} for more on linking. The part of speech of the lexical item
+the stimulus. See \citet{DKW2024a} for more on linking. The part of speech of the lexical item
 (\type{verb}) and the valence information is carried over from the daughter to the mother

### 2025-11-07 replies-reviews3.tex
reply some 3rd round reviews

%% -*- coding:utf-8 -*-
\documentclass[fleqn,twoside]{article}

\usepackage[
style = langsci-unified,
backend = biber,
natbib = true,
]{biblatex}
\addbibresource{Bib.bib}

\usepackage{xcolor}
\definecolor{lsDOIGray}{cmyk}{0,0,0,0.45}

\usepackage{csquotes}

\input{localpackages}
\input{localcommands}
%\usepackage{fontspec}

%\newtoggle{draft}\togglefalse{draft}
\newtoggle{draft}\toggletrue{draft}

%\usepackage{hyperref}
%\hypersetup{colorlinks=false, pdfborder={0 0 0}}

%\usepackage{unified-biblatex}

%\let\citew\citealp
%\newcommand{\page}{}
%\bibliography{Bib,bib-abbr,biblio}

%\usepackage{langsci-forest-setup}

%\usepackage{german}%

%\selectlanguage{USenglish}

%\usepackage{abbrev,merkmalstruktur,article-ex,makros.2e,mycommands,eng-date,my-xspace}
%\usepackage{my-gb4e-article}

%\usepackage{soul}

%\usepackage{forest}

\let\citew\cite

\newcommand{\is}[1]{}

\begin{document}
\noindent
{\large\bf Replies to 3rd round of reviews of \emph{Deliminative verbal reduplication in Mandarin Chinese}}\\

\bigskip
\noindent
Dear editors,\\

\noindent
Thank you very much again for the positive reviews. The following text is a repetition of the points the
reviewer raised and an explanation of how we addressed open issues.

\begin{enumerate}

\item p. 6--7, example (11). While example (11b) is acceptable, (11a) does not sound natural. It would be advisable to consult additional native speakers to confirm its acceptability.

\item p. 8, example (14b). In the English translation, it is unclear why the meaning `a bit' is associated with `dangerous' instead of `read.' Clarification or correction may be needed.

\textbf{Answer:} The translation `a bit dangerous' comes from \obj{you3xie1} \obj{wei1xian3} in the original sentence. We changed the translation to `If lectures do not read a bit of books, then it is somewhat dangerous' to avoid confusion.

\item p. 9, lines 1--6. ``In sum, we consider that the reduplication has a similar syntactic distribution as an unreduplicated verb, and the incompatibility of the reduplication with duration and frequency phrases as well as aspect markers other than \textit{le} can be explained semantically, as we will show in the next section.''

The author(s) stated that reduplication has a similar syntactic distribution to an unreduplicated verb. While some examples support this claim, previous studies have documented distributional restrictions in particular environments. It would be useful to briefly comment on potential sources of these different observations.

\textbf{Answer: } In p. 6--8, we discussed some distributional restrictions claimed in previous studies and used examples to show that reduplication has a broader distribution than previously assumed.

\item p. 19, lines 33--35. ``Tense inflections in English such as -ed change neither the category nor the valency of the input verb.''

The author(s) used the English past tense marker ed as an example of a morphological process that does not change the category or valency of the verb. However, in generative syntax, tense is typically introduced by a functional projection, and ed is viewed as a surface- level morphological realization. Therefore, it may be worth considering whether ed is the most appropriate example, especially as an example of a morphological process.

\todo[inline]{Stefan, say something.}

\item p. 20, lines 16--20. Example (38) is intended to demonstrate that \textit{le} can be inserted between V-\obj{gei3}. However, since the verb \obj{ji4} `send' can be used independently without \obj{gei3} (e.g., ``\obj{wo3} \obj{ji4} \obj{le} \obj{yi4} \obj{xiang1} \obj{ping2guo3} (\obj{gei3} \obj{ta1})'' `I sent a box of apples (to her)'), the insertion of \textit{le} may reflect the separability of an optional prepositional phrase, rather than a property of the V-\obj{gei3} unit. Thus, this example may not sufficiently support the claim.

\textbf{Answer: } The \obj{ji4-gei3} example is suggested by another reviewer, as \citet[1282]{Her2006} claims that the V-\obj{gei3} sequence forms a single lexical item. \citegen{Her2006} analysis cannot be elaborated here.

\item p. 21, example (41) and footnote [10]. Footnote [10] is helpful in explaining the purpose of using example (41). The author(s) mentioned that ``This word order constraint is not a problem for the test in (41), as the adverb can, in principle, be interpreted as modifying the second verb'' (line 44--45). However, the use of an adverb to modify the second occurrence in a reduplicated verb appears problematic, as the second occurrence is typically not analyzed as a syntactic head or the main part/verb of the reduplication (as evidenced by the acceptability
of \obj{kan4} \obj{le} \obj{kan4} but not \obj{kan4} \obj{kan4} \obj{le}). This raises concerns about whether (41), as a diagnostic test, presents a reliable example, where the adverb is used to modify the second occurrence.

\textbf{Answer: } non-head can be modified too.

\item p. 24, example (47b). The author(s) suggested that verb reduplications differ from verb classifier phrases based on their separability. While example (46) convincingly demonstrates that a verb classifier phrase can be separated, the claim that reduplications do not allow such separations may be overstated. Corpus data from the BCC show expressions such as (i) ``\obj{deng3} \obj{wo3} \obj{yi} \obj{deng3}'' `wait for me a bit,' (ii) ``\obj{kan4} \obj{shu1} \obj{yi} \obj{kan4}'' `read a book for a bit,' (iii) ``\obj{kan4} \obj{ta1} \obj{yi} \obj{kan4}'' `take a look at him' do occur. This means that separation is possible in certain cases, even if limited.

\end{enumerate}

{\sloppy
\printbibliography[heading=subbibliography,notkeyword=this]
}
\end{document}

%      <!-- Local IspellDict: en_US-w_accents -->

### 2025-11-10 replies-reviews3.tex
reply more 3rd round reviews

@@
 
+\textbf{Answer: } We found this example in the BCC corpus. 
+We asked 10 native speakers from different regions in Mainland China. 
+All found the sentence weird at first glace, but considered that the acceptability can be greatly improved 
+by adding more information to support the use of reduplication, such as \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{zheng4wu4wei1bo2} `the government affairs Weibo account that you look at \textit{casually}'.
+Three of them further insist on the use of a demonstrative: \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{na4} \obj{ge4} \obj{zheng4wu4wei1bo2} `\textit{that} government affairs Weibo account that you look at \textit{casually}'.
+These still constitute cases where reduplication occurs in relative clauses without modal or mood verbs 
+and thus strengthen our claim.
+We added this judgment information in a footnote.
+
 \item p. 8, example (14b). In the English translation, it is unclear why the meaning `a bit' is associated with `dangerous' instead of `read.' Clarification or correction may be needed.
@@
 \citegen{Her2006} analysis cannot be elaborated here.
+In any case, we analyze \obj{le} as a morphological element and do not consider \obj{le}-insertion as a violation of lexical integrity.
 
@@
 
-\textbf{Answer: } non-head can be modified too.
+\textbf{Answer: } The modification test examines whether a subpart of a word or phrase can be individually modified or not.
+In a phrase, non-head elements can also be modified individually.
+For example, in a noun phrase \obj{yi1} \obj{duo3} \obj{mei3li4de} \obj{hua1} `a beautiful flower', the adjective \obj{mei3li4de} is not the head of the whole phrase,
+but it can still be modified by an adverb:  \obj{yi1} \obj{duo3} \obj{fei1chang2} \obj{mei3li4de} \obj{hua1} `a \textit{very} beautiful flower'.
+The fact that the second occurrence in a reduplicated verb cannot be modified suggests that the reduplication forms a lexical unit.
 
@@
 This means that separation is possible in certain cases, even if limited.
+
+\textbf{Answer: } At the time of writing this revision, BCC is unfortunately down.
+We searched the CCL corpus and found some examples of \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him'.
+These texts are either written before the 1990s or written to imitate Old Mandarin (e.g. in fictions based in an ancient Chinese setting).
+Our native speaker informants said that they can understand these expressions, 
+but these expressions sound antiquated,
+and they will not use them in their daily life.
+They also completely reject A-\obj{yi}-A being separated by complex noun phrases, such as *\obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{deng3} `wait for that person a bit',  *\obj{kan4} \obj{na4} \obj{duo3} \obj{hua1} \obj{yi} \obj{kan4} `take a look at that flower'.
+In contrast, the verbal classifier counterparts are totally acceptable: \obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{xia4} `wait for that person a bit',  \obj{kan4} \obj{na4} \obj{duo3} \obj{hua1} \obj{yi} \obj{xia4} `take a look at that flower'.
+Furthermore, AA cannot be separated *\obj{deng3} \obj{wo3} \obj{deng3} `wait for me a bit',  *\obj{kan4} \obj{ta1} \obj{kan4} `take a look at him'.
+Considering that reduplication developed from verbs being borrowed as verbal classifiers \citep{Zhang2000},
+we can consider cases such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' to be in the process of grammaticalization.
+We added a footnote on this.
 

### 2025-11-10 chapters/ch02-Phenomenon.tex
reply some 3rd round reviews
reply more 3rd round reviews

@@
 % 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
-\gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3}-\objex{shi2} \objex{tiao2} \objex{wei1bo2}!\\
+\gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3}-\objex{shi2} \objex{tiao2} \objex{wei1bo2}!\footnotemark\\
 you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} several-ten \textsc{clf} Weibo\\ \jambox{(BCC)}
@@
 \z
+\footnotetext[]{We found this sentence in the BCC corpus, but one reviewer finds it unnatural.
+    We asked 10 native speakers from different regions in Mainland China. 
+    All found the sentence weird at first glace, but considered that the acceptability can be greatly improved 
+    by adding more information to support the use of reduplication, such as \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{zheng4wu4wei1bo2} `the government affairs Weibo account that you look at \textit{casually}'.
+    Three of them further insist on the use of a demonstrative: \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{na4} \obj{ge4} \obj{zheng4wu4wei1bo2} `\textit{that} government affairs Weibo account that you look at \textit{casually}'.
+    These still constitute cases where reduplication occurs in relative clauses without modal or mood verbs 
+    and thus strengthen our claim.}
 
@@
 lecturer {} not flip-flip book just somewhat dangerous \textsc{de} just be\\ \jambox{(CCL)}
-\glt `If lecturers do not read books, then it is a bit dangerous.'
+\glt `If lecturers do not read a bit of books, then it is somewhat dangerous.'
 

### 2025-11-11 replies-reviews3.tex
modify reviewer replies and modify paper accordingly

@@
 and they will not use them in their daily life.
-They also completely reject A-\obj{yi}-A being separated by complex noun phrases, such as *\obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{deng3} `wait for that person a bit',  *\obj{kan4} \obj{na4} \obj{duo3} \obj{hua1} \obj{yi} \obj{kan4} `take a look at that flower'.
-In contrast, the verbal classifier counterparts are totally acceptable: \obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{xia4} `wait for that person a bit',  \obj{kan4} \obj{na4} \obj{duo3} \obj{hua1} \obj{yi} \obj{xia4} `take a look at that flower'.
+They also completely rejected A-\obj{yi}-A being separated by complex noun phrases, such as *\obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{deng3} `wait for that person a bit',  *\obj{kan4} \obj{ta1de} \obj{lian3} \obj{yi} \obj{kan4} `take a look at his face'.
+In contrast, the verbal classifier counterparts are totally acceptable: \obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{xia4} `wait for that person a bit',  \obj{kan4} \obj{ta1de} \obj{lian3} \obj{yi} \obj{xia4} `take a look his face'.
 Furthermore, AA cannot be separated *\obj{deng3} \obj{wo3} \obj{deng3} `wait for me a bit',  *\obj{kan4} \obj{ta1} \obj{kan4} `take a look at him'.
-Considering that reduplication developed from verbs being borrowed as verbal classifiers \citep{Zhang2000},
-we can consider cases such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
-and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' to be in the process of grammaticalization.
+Considering that reduplication developed from verbs being borrowed as verbal classifiers (\citealt{Zhang2000}, see also Appendix B)
+we consider cases such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' to be in the process of grammaticalization and thus not a form of reduplication we study here.
 We added a footnote on this.

### 2025-11-11 chapters/ch04-Previous.tex
modify reviewer replies and modify paper accordingly

@@
 First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.\footnote{
+  \label{fn:vclpron}
 One reviewer notes that the objects that can be placed in between the verbal classifier phrase is usually limited to pronouns and proper nouns.
@@
 %This is not necessarily a syntactic constraint
+See also footnote~\ref{fn:vnv}.
 
-Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
-the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+%Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
+%the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+}
+$^,$
+\footnote{
+   \label{fn:vnv}
+A reviewer points out that there are examples such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' in corpora,
+where A-\obj{yi}-A seems to be separated by pronouns like \obj{wo3} `I' or \obj{ta1} `he'.
+We searched the CCL corpus, and the texts containing such expressions are either written before the 1990s 
+or written to imitate Old Mandarin (e.g. in fictions based in an ancient Chinese setting).
+Our native speaker informants said that they can understand these expressions, 
+but these expressions sound antiquated,
+and they will not use them in their daily life.
+They also completely rejected A-\obj{yi}-A being separated by complex noun phrases, such as *\obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{deng3} `wait for \textit{that person} a bit',  *\obj{kan4} \obj{ta1de} \obj{lian3} \obj{yi} \obj{kan4} `take a look at \textit{his face}'.
+In contrast, the verbal classifier counterparts are totally acceptable: \obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{xia4} `wait for that person a bit',  \obj{kan4} \obj{ta1de} \obj{lian3} \obj{yi} \obj{xia4} `take a look his face' (see also footnote~\ref{fn:vclpron}).
+Furthermore, AA cannot be separated even by pronouns: *\obj{deng3} \obj{wo3} \obj{deng3} `wait for me a bit',  *\obj{kan4} \obj{ta1} \obj{kan4} `take a look at him'.
+Considering that reduplication developed from verbs being borrowed as verbal classifiers (\citealt{Zhang2000}, see also Appendix~\ref{app:hist} for a short discussion on the historical development of reduplication),
+we consider cases such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' to be in the process of grammaticalization and thus not a form of reduplication we study here.
 }

### 2025-11-11 chapters/ch02-Phenomenon.tex
modify reviewer replies and modify paper accordingly
last changes replaced English tense inflection by German adjective inflection

@@
 \glt `The government affairs Weibo account that you look at \ldots\, reposted dozens of Weibo posts.'
-
-% 大年初一参差光谷，初二去，初三去看看的店 （BCC 微博）
-
-% 像是习惯路过了不进去看看的店 。（BCC 微博）
-
-% 刚在人人看到班上那个喜欢用看政治来装逼，时而偷进我围脖来看看的女人 ，说不定这条你看操…… (BCC 微博)
-
-\ex\label{ex:rel2}
-% 大厅里坐着一些年轻人，他们是逛进来听听的爵士 乐迷。（BCC 为了告别的聚会 A:米兰·昆德拉 Y:UN）
-\gll \objex{ta1men} \objex{shi4} [[\objex{guang4} \objex{jin4lai2} \obj{ting1-ting} \objex{de}] \objex{jue2shi4yue4-mi2}].\\
-they be wander enter listen-listen \textsc{de} jazz-fan\\ \jambox{(BCC)}
-\glt `They are jazz fans who wandered in to have a listen.'
-
-\z  
-\z
-\footnotetext[]{We found this sentence in the BCC corpus, but one reviewer finds it unnatural.
+\footnotetext{We found this sentence in the BCC corpus, but one reviewer finds it unnatural.
     We asked 10 native speakers from different regions in Mainland China. 
@@
     and thus strengthen our claim.}
+% 大年初一参差光谷，初二去，初三去看看的店 （BCC 微博）
+
+% 像是习惯路过了不进去看看的店 。（BCC 微博）
+
+% 刚在人人看到班上那个喜欢用看政治来装逼，时而偷进我围脖来看看的女人 ，说不定这条你看操…… (BCC 微博)
+
+\ex\label{ex:rel2}
+% 大厅里坐着一些年轻人，他们是逛进来听听的爵士 乐迷。（BCC 为了告别的聚会 A:米兰·昆德拉 Y:UN）
+\gll \objex{ta1men} \objex{shi4} [[\objex{guang4} \objex{jin4lai2} \obj{ting1-ting} \objex{de}] \objex{jue2shi4yue4-mi2}].\\
+they be wander enter listen-listen \textsc{de} jazz-fan\\ \jambox{(BCC)}
+\glt `They are jazz fans who wandered in to have a listen.'
+
+\z  
+\z
 
@@
 
-However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
-For instance, the \obj{-able} derivation in English is a productive morphological process.
-Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.\footnote{
+However, a morphological process can be productive, and it does not necessarily change the part of
+speech label or valency of the input. For instance, the \obj{-able} derivation in English is a productive morphological process.
+The adjective inflection in languages like German does change neither the part of speech nor the
+valency of the adjectival stem.\footnote{
 We do not claim reduplication to be either inflection or derivation.
 }
+% $^,$\footnote{A reviewer pointed out that tense inflection is assumed to live under the category T or
+%   Infl in theories within the framework of Government \& Binding \citep{Chomsky81a}. HPSG follows
+%   the lexicalist view according to which single morphemes are not syntactic objects. See
+%   Müller (\citeyear{MuellerGermanic}, \citeyear{MuellerLFGTAG}) on functional projections. 
+% }
 %the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
@@
 %Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.
+
+%      <!-- Local IspellDict: en_US-w_accents -->

### 2025-11-16 main.tex
move parts to appendix
weitere Kürzungen in Bib.bib
final editing, added references to TRALE and implementation. Moved all sections into one file. Added patch to get brackets in example numbers. Used most recent style files from CUP. Changed bibtex items to use unicode.

@@
-\documentclass[%
-%anonym,
-% times,
- %referee,
- %doublespacing,
- ]{lin}
+% \documentclass[%
+% %anonym,
+% % times,
+%  %referee,
+%  %doublespacing,
+%  ]{lin}
+\documentclass[a4paper]{CUP-JNL-LIN}%[ruler,draftrules]
+
+\articletype{RESEARCH ARTICLE}
+\jname{Journal of Linguistics}
+\jyear{2027}
+\jvol{0}
+%\jissue{1}
+\jdoi{10.1017/\ldots}
+
+\copyrightline{\textcopyright\ The Author(s) 2025. This is an Open Access article,
+distributed under the terms of the Creative Commons Attribution licence (http://creativecommons.org/licenses/by/4.0/),
+which permits unrestricted re-use, distribution, and reproduction in any medium, provided the original work is properly cited.}
 
@@
 
-%\leftrunning{Yanru Lu \& Stefan Müller}  % Short author list
+\begin{Frontmatter}
+\title{Deliminative verbal reduplication in Mandarin Chinese}
 
-\rightrunning{Deliminative verbal reduplication in Mandarin Chinese} % Short title
+\author[1]{Yanru Lu\corresp{\email{yanru.lu@hu-berlin.de}}}%\orcid{0000-0002-5915-7315}
+\author[1]{Stefan Müller\corresp{\email{st.mueller@hu-berlin.de}}}%\orcid{0000-0003-4413-5313}
 
-\title{Deliminative verbal reduplication in Mandarin Chinese}
+\authormark{Yanru Lu \& Stefan Müller}
+
+\address[1]{\orgname{Humboldt-Universität zu Berlin, Institute for German language and linguistics},
+  \orgaddress{\street{Unter den Linden 6}, \postcode{D-10099 Berlin}, \country{Germany}}}
+
+\received{08 July 2023}
+\revised{01 August 2025}
+\accepted{14 November 2025}
 
@@
 
-\maketitle
-
-\begin{abstract}
+\abstract{
 The current study presents an HPSG analysis for deliminative verbal reduplication in Mandarin Chinese.
@@
 This analysis covers all forms of deliminative verbal reduplication in Mandarin Chinese and has none of the shortcomings of previous analyses.
+}
 \keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}
-\end{abstract}
 
-\input{chapters/ch01-Intro}
+\end{Frontmatter}
 
-\input{chapters/ch02-Phenomenon}
+% \input{chapters/ch01-Intro}
 
-%\input{chapters/ch03-Theory}
+% \input{chapters/ch02-Phenomenon}
 
-\input{chapters/ch04-Previous}
+% %\input{chapters/ch03-Theory}
 
-\input{chapters/ch05-Analysis}
+% \input{chapters/ch04-Previous}
 
-\input{chapters/ch06-Conclusion}
+% \input{chapters/ch05-Analysis}
+
+% \input{chapters/ch06-Conclusion}
+
+% \appendix
+% \input{chapters/appendix}
+
+\input{reduplication-include}
 
@@
 \end{document}
+
+19866 Words mit anhang
+18850 ohne Anhang
+
+18761 ohne Anhang mit reduzierter Bib
+
+15172 ohne Anhang und Strichen von AVMs

### 2025-11-16 reduplication-include.tex
final editing, added references to TRALE and implementation. Moved all sections into one file. Added patch to get brackets in example numbers. Used most recent style files from CUP. Changed bibtex items to use unicode.

--- 2025-11-11 chapters/ch02-Phenomenon.tex
@@
+%% -*- coding:utf-8 -*-
+\section{Introduction}\label{sec:intro}
+
+In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g.
+\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}).
+This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
+    in the example sentences will be set in italics.}
+Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while''.
+
+\ea\label{ex:redup-ex} 
+	\ea
+	\gll \objex{qing3} \objex{ni3} \objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
+	please you taste this \textsc{clf} dish\\
+	\glt `Please taste this dish.'
+
+	\ex
+	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\obj{chang} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
+	please you taste-taste this \textsc{clf} dish\\
+	\glt `Please taste this dish a little bit.' 
+	\z
+\z
+
+The current study tries to determine a suitable formal and unified analysis for the structure of verbal reduplication in Mandarin Chinese.
+It contributes more empirical evidence and 
+offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, HPSGHandbook-2}) to this phenomenon 
+using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}) as the semantic representation formalism.
+This new account of reduplication avoids the problems of previous approaches and
+explains more forms of deliminative verbal reduplication in Mandarin Chinese.
+
+This paper is organized as follows: 
+after this introduction, we will present in \sectref{sec:phen} the forms and syntactic distribution as well as the semantics of verbal reduplication in Mandarin Chinese. 
+Importantly, we restrict the object of this study to the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le}-\textit{yi}-A, ABAB and AB-\textit{le}-AB forms of verbal reduplication in Mandarin Chinese.
+We will also discuss in this section, with the help of corpus data, the question of whether the reduplication is better analyzed as a morphological or a syntactic process.
+In \sectref{sec:prev}, we will discuss the advantages and drawbacks of previous approaches. 
+\sectref{sec:analysis} will present a new {HPSG} account for verbal reduplication in Mandarin Chinese.
+Finally,  \sectref{sec:conclu} will conclude the paper.
+
+The data in this paper was drawn from several sources.
+In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}; \citealt{Zhanetal2003, Zhanetal2019}) and the BCC corpus \citep{BCC} were also consulted.
+Further, examples from novels and plays written by native speakers were considered.
+Corpus data provides natural and contextualized examples, and contains a variation of linguistic properties \citep[921]{MM2009a}.
+This can help us discover relevant constraints that can otherwise go unnoticed through
+introspection.
+
 \section{The phenomenon}\label{sec:phen}
@@
 
+\section{Previous analyses}\label{sec:prev}
+
+Previous analyses on the reduplication in Mandarin Chinese and in other languages can be classified
+into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect modifier (\sectref{sec:asp}), and
+as a special reduplication construction (\sectref{sec:construc}).\footnote{The term \textit{construction} is used here in its general sense, not in the sense of Construction Grammar.} 
+This section will review these analyses and will discuss their advantages and shortcomings.
+
+%%%%%%%%%%%
+\subsection{The reduplication as a verbal classifier phrase}\label{sec:clf}
+
+\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyze the reduplication in Mandarin Chinese
+as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
+The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
+A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \obj{ci4} in (\ref{ex:clf}).
+
+%\settowidth\jamwidth{(Chomsky, 1957: 15)}
+\ea\label{ex:clf}
+\gll \objex{mei2} \objex{che3}-\objex{guo} \objex{yi2} \objex{ci4} \objex{huang3}\\
+not tell-\textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
+\glt `haven't told lie once'
+\z
+
+In this analysis, the first element in the reduplication is the actual verb, 
+the second element is a verbal classifier borrowed from a verb, 
+and \obj{yi} `one' is an optional pseudo-numeral that only has an abstract `a little bit' meaning.
+The analysis is syntactic.
+
+The parallel between the reduplication and a verbal classifier phrase is obvious. 
+Both the reduplication and the verbal classifier phrase serve to quantify the duration or the extent of a situation. 
+A reduplication structure can often be paraphrased into a verbal classifier phrase such as \obj{yi2} \obj{xia4} `once, a while', \obj{yi2} \obj{hui4} `a while', as illustrated in (\ref{ex:redup-clf}).
+
+\ea\label{ex:redup-clf}
+	\ea \gll \obj{deng3}-\obj{deng3} \objex{wo3}.\\
+		wait-wait I\\
+		\glt `Wait for me a little bit.'
+	\ex \gll \objex{deng3} \objex{wo3} \objex{yi2} \objex{xia4}.\\
+	wait I one \textsc{clf}\\
+	\glt `Wait for me a little while.'
+	\z
+\z
+
+However, there are several arguments suggesting that the reduplication cannot be analyzed the same way as a verbal classifier phrase.
+First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.\footnote{
+  \label{fn:vclpron}
+One reviewer notes that the objects that can be placed in between the verbal classifier phrase is usually limited to pronouns and proper nouns.
+We found some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
+\ea%她看了他的脸一下。(CCL)
+\gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
+she look-\textsc{pfv} his face one \textsc{clf}\\\jambox{(CCL)}
+\glt `She took a look at his face.'
+
+\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
+\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
+he {} just look-\textsc{pfv} glass one \textsc{clf} glass just break-\textsc{pfv}\\\jambox{(CCL)}
+\glt `He just took a look at the glass and the glass just broke.'
+\z
+We think it has to do with the length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
+%This is not necessarily a syntactic constraint
+See also footnote~\ref{fn:vnv}.
+
+%Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
+%the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
+}
+$^,$
+\footnote{\label{fn:vnv}%
+A reviewer points out that there are examples such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' in corpora,
+where A-\obj{yi}-A seems to be separated by pronouns like \obj{wo3} `I' or \obj{ta1} `he'.
+We searched the CCL corpus, and the texts containing such expressions are either written before the 1990s 
+or written to imitate Old Mandarin (e.g. in fictions based in an ancient Chinese setting).
+Our native speaker informants said that they can understand these expressions, 
+but these expressions sound antiquated,
+and they will not use them in their daily life.
+They also completely rejected A-\obj{yi}-A being separated by complex noun phrases, such as *\obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{deng3} `wait for \textit{that person} a bit',  *\obj{kan4} \obj{ta1de} \obj{lian3} \obj{yi} \obj{kan4} `take a look at \textit{his face}'.
+In contrast, the verbal classifier counterparts are totally acceptable: \obj{deng3} \obj{na4} \obj{ren2} \obj{yi} \obj{xia4} `wait for that person a bit',  \obj{kan4} \obj{ta1de} \obj{lian3} \obj{yi} \obj{xia4} `take a look his face' (see also footnote~\ref{fn:vclpron}).
+Furthermore, AA cannot be separated even by pronouns: *\obj{deng3} \obj{wo3} \obj{deng3} `wait for me a bit',  *\obj{kan4} \obj{ta1} \obj{kan4} `take a look at him'.
+Considering that reduplication developed from verbs being borrowed as verbal classifiers (\citealt{Zhang2000}, see also Appendix~\ref{app:hist} for a short discussion on the historical development of reduplication),
+we consider cases such as \obj{deng3} \obj{wo3} \obj{yi} \obj{deng3} `wait for me a bit'
+and \obj{kan4} \obj{ta1} \obj{yi} \obj{kan4} `take a look at him' to be in the process of grammaticalization and thus not a form of reduplication we study here.
+}
+
+\ea\label{ex:clf-sep}
+  \ea \gll \objex{ni3} \objex{deng3} \objex{yi2} \objex{xia4} \objex{Zhang1san1}!\\
+   you wait one \textsc{clf} Zhangsan\\
+   \glt `Wait for Zhangsan for a while!'
+  \ex \gll \objex{ni3} \objex{deng3} \objex{Zhang1san1} \objex{yi2} \objex{xia4}!\\
+   you wait Zhangsan one \textsc{clf}\\
+   \glt `Wait for Zhangsan for a while!'
+\z
+\z
+
+\ea\label{ex:redup-sep}
+  \ea[]{\gll \objex{ni3} \obj{deng3}-\obj{yi}-\obj{deng3} \objex{Zhang1san1}!\\
+   you wait-one-wait Zhangsan\\
+   \glt `Wait for Zhangsan a little bit!'}
+  \ex[*]{\gll \objex{ni3} \obj{deng3} \objex{Zhang1san1} \obj{yi} \obj{deng3}!\\
+  you wait Zhangsan one wait\\}
+\z
+\z
+
+Second, unlike verbal classifiers (\ref{ex:clf-num}), the \obj{yi} ‘one’ in A-\obj{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.
+
+\ea\label{ex:clf-num}
+  \ea \gll \objex{ta1} \objex{pai1}-le \objex{wo3} \objex{yi2} \objex{xia4}.\\
+   he pat-\textsc{pfv} I one \textsc{clf}\\
+   \glt `He patted me once.'
+   \ex \gll \objex{ta1} \objex{pai1}-le \objex{wo3} \objex{liang3} \objex{xia4}.\\
+    he pat-\textsc{pfv} I two \textsc{clf}\\
+    \glt `He patted me twice.'
+\z
+\z
+
+\ea\label{ex:redup-num}
+  \ea[]{\gll \objex{ta1} \obj{pai1}-\obj{le}-\obj{yi}-\obj{pai1} \objex{wo3}.\\
+   he pat-\textsc{pfv}-one-pat I\\
+   \glt `He patted me a little bit.'}
+   \ex[*]{\gll \objex{ta1} \obj{pai1}-\obj{le}-\obj{liang3}-\obj{pai1} \objex{wo3}.\\
+   he pat-\textsc{pfv}-two-pat I\\}
+\z
+\z
+
+Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.\footnote{
+This applies except when \obj{yi2} \obj{xia4} `once' is used. 
+Because of this exception, one reviewer suggests that the loss of the idiomatic meaning in (\ref{ex:clf-idiom}) 
+but not in (\ref{ex:redup-idiom}) may be attributed to the use of the numeral \obj{san1} `three' in (\ref{ex:clf-idiom}),
+because if \obj{san1} \obj{xia4} `three times' is replaced with \obj{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
+We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special, 
+but it is \obj{yi2} \obj{xia4} `once' that is special.
+We can replace \obj{san1} `three' with any number above two,
+and the distinction still exist.
+But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
+We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
+In this case, it is easy to interpret \obj{yi2} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
+but as duration adverbials as a whole,
+thus differing them from ``actual'' verbal classifier phrases with other numerals.
+}
+
+\ea
+  \ea\label{ex:idiom}
+  \gll \objex{bao4} \objex{fo2}-\objex{jiao3}\\
+  clasp Buddha-foot\\
+   \glt Literal: `clasp the Buddha's foot'\\
+   Idiomatic: `make a last-minute effort'
+
+   \ex\label{ex:clf-idiom}
+   \gll \objex{ta1} \objex{kao3shi4} \objex{qian2} \objex{bao4}-le \objex{san3} \objex{xia4} \objex{fo2}-\objex{jiao3}.\\
+   he exam before clasp-\textsc{pfv} three \textsc{clf} Buddha-foot\\
+   \glt `He clasped the Buddha's foot three times before the exam.' (idiomatic reading unavailable)
+
+   \ex\label{ex:redup-idiom}
+   \gll \objex{ta1} \objex{kao3shi4} \objex{qian2} \obj{bao4}-\obj{le}-\obj{bao4} \objex{fo2}-\objex{jiao3}.\\
+   he exam before clasp-\textsc{pfv}-clasp Buddha-foot\\
+   \glt Literal: `He clasped the Buddha's foot a little bit before the exam.'\\
+   Idiomatic: `He made a bit of a last-minute effort before the exam.'
+\z
+\z
+
+Based on these observations, it seems inappropriate to view the reduplication as a kind of verbal classifier phrase.
+
+%%%%%%%%%%%
+\subsection{The reduplicant as an aspect modifier}\label{sec:asp}
+
+A number of studies consider the reduplication to be an element that modifies the aspectual properties of the base verb \citep{Arcodiaetal2014, BascianoMelloni2017, YangWei2017} 
+due to the delimitative aspectual meaning of reduplication. 
+%\citet{Travis1999, Travis2000} also analyzes the reduplication in Tagalog as an imperfective aspect marker.
+
+ %%%%%%
+%Arcodiaetal2014, BascianoMelloni2017
+
+ \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} analyze the reduplication within the
+framework of First Phase Syntax \citep{Ramchand2008}.
+\citet{Ramchand2008} proposes that an event is comprised of the following phrases: 
+the causative subevent (\textit{init}P), the process subevent (\textit{proc}P) and the result subevent (\textit{res}P), which are ordered hierarchically, as illustrated in \figref{tree:ramchand}.\footnote{
+The present study does not argue for a {NP} or a {DP} analysis and simply takes over the illustration provided in the cited papers.}
+Dynamic and volitional verbs have the features [init proc] and are therefore located under \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.
+Achievement verbs possess the feature [res] and reside under \textit{res}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}. 
+Stative verbs do not contain a \textit{proc}P \citep[152]{BascianoMelloni2017}.
+
+\begin{figure}
+ \centering
+\begin{forest}
+[\textit{init}P (causing projection) [DP$_3$\\subject of `cause']
+  [ [init]
+    [\textit{proc}P (process projection)
+      [DP$_2$\\subject of `process']
+      [[\textit{proc}]
+        [\textit{res}P (result projection)
+        [DP$_1$\\subject of `result']
+          [[\textit{res}] [XP]
+          ]
+        ]
+      ] ]
+    ]
+  ]
+\end{forest} 
+\caption{Event structure according to \citet[193]{Ramchand2008}}
+\label{tree:ramchand}
+\end{figure}
+
+\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assume that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
+and that the second element is the copy of the verb, which resides in the complement position of \textit{proc} and serves as an event delimiter.
+Since the second element occupies the same syntactic position as \textit{res}P, it should have complementary distribution with \textit{res}P
+and should thus be incompatible with achievement verbs because of their [res] feature.
+Furthermore, if \textit{proc}P does not exist in the event, as in the case of states, there should be no place for the reduplication either.
+
+This analysis correctly predicts that the reduplication of achievement verbs and stative verbs is not as easily acceptable as that of dynamic and volitional verbs (marked by [init, proc] features).
+
+However, as shown in \sectref{sec:Aktionsarten}, the reduplication of states and achievements is unusual but not impossible.
+This suggests that the reduced acceptability of reduplicated achievement and stative verbs is \textit{semantic} rather than \textit{structural}. 
+Their use is possible in specific contexts and should not be ruled out \textit{syntactically}.
+Consequently, this proposal does not seem to offer an appropriate account for  reduplication.
+
+ %%%%%%
+ %YangWei2017, Tsai2008
+
+ \citet[229]{YangWei2017} endorse the analysis of  reduplication as an aspect marker 
+ following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+\citet{YangWei2017} did not spell out the exact analysis.
+We infer the analysis for reduplication based on \citet{Tsai2008},
+ and show in Appendix~\ref{app:tsai} that \citeauthor{Tsai2008}'s (\citeyear{Tsai2008}) system 
+ has a syntax-semantics mismatch problem.
+
+%In sum, both analyses of the reduplicant as an aspect modifier do not seem to be convincing.
+
+%%%%%%%%%%%%
+\subsection{Reduplication construction}\label{sec:construc}
+
+%The following section discusses previous literature which proposed a special construction for the reduplication.
+
+ %%%%%%%
+%Ghomeshietal2004
+
+%\citet{Ghomeshietal2004} provided an analysis within the theoretical framework of Parallel Architecture \citep{Jackendoff1997, Jackendoff2002} for Contrastive Reduplication (CRs) in English like (\ref{ex:salad}),\footnote{Capitalization indicates contrastive intonation.}
+%as shown in Figure~\ref{ghomeshi-cr}.\footnote{{P} = phonological unit, {P/E/S CTR} = prototypical/extreme/salient contrast, XP$^{min}$ = XP without its specifier} 
+%They postulated a new syntactic category {CR}$^{syn}$ to incorporate the reduplicant.
+%It has the semantics of {P/E/S CTR} and an empty phonological content that copies from the phonology of the base it applies to.
+%According to their observations, the base can be an X (e.g. \textit{SALAD-salad}) or an XP$^{min}$ (e.g. \textit{OVER-THE-HILL-over-the-hill}).
+%In Figure~\ref{ghomeshi-cr}, {CR}$^{syn}$ is coindexed with the first {P}, 
+%which is in turn coindexed with the phonology of X/XP$^{min}$ (P$_k$). 
+%{CR}$^{syn}$ is coindexed with the semantics of {P/E/S CTR}, 
+%which modifies the semantics of  X/XP$^{min}$ (Z$_k$).
+%\ea\label{ex:salad}
+%I make the tuna salad, and you make the \textit{SALAD-salad}.
+%\z
+%\begin{figure}[h!]
+%\centering
+%\begin{multicols}{3}
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Phonology\\
+%\vspace{15pt}
+%P$_{j, k}$ P$_k$
+%\end{center}
+%\end{minipage}
+%\columnbreak
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Syntax\\
+%\begin{forest}
+%for tree = {inner sep = 0pt,
+%	s sep = 1pt,
+%	anchor=children last,
+%    	align=center}
+%[X/XP$^{min}$
+% [CR$^{syn}$$_j$]
+% [X/XP$^{min}$$_k$]
+%]
+%\end{forest}
+%\end{center}
+%\end{minipage}
+%\columnbreak
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Semantics
+%\[
+%\begin{bmatrix}
+%Z_{k}\\
+%\begin{bmatrix}
+%P/E/S\\
+%CTR
+%\end{bmatrix}_{\!j}
+%\end{bmatrix}
+%\]
+%\end{center}
+%\end{minipage}
+%\end{multicols}
+%\caption{Analysis for {CR}s in English according to \citet[344]{Ghomeshietal2004}}
+%\label{ghomeshi-cr}
+%\end{figure}
+
+%Applying this to the reduplication in Mandarin Chinese, the structure should be something like \figref{ghomeshi-cn}.\footnote{{DELIM} = delimitative}\textsuperscript{,}\footnote{
+%Although the reduplication in Mandarin Chinese does not have a contrastive meaning, 
+%we preserve the notation of CR$^{syn}$ in \citet{Ghomeshietal2004} here to simply refer to the reduplicant.}
+%The base verb is coindexed with its phonology and its semantics `look'. 
+%The phonology of the reduplicant is coindexed with the phonology of the verb.
+%The reduplicant is coindexed with the delimiative semantics
+%and modifies the semantics of the base verb.
+%The base verb and the reduplicant combine to a V.\footnote{In English, it makes sense to assume CR$^{syn}$ to be a syntactic unit, because the base can be XP$^{min}$ (e.g.
+\textit{OVER-THE-HILL-over-the-hill}).
+%But for Mandarin Chinese, the base can only be V.
+%As \citet[353]{Ghomeshietal2004} wrote: ``when applying to its smallest scope, X inside of a word, it has the feel of other things that attach there, i.e., morphological affixes''.
+%It seems that it suffices to assume the reduplication in Mandarin Chinese to be a morphological phenomenon (cf. \sectref{sec:word}).
+%We continue to call the second column ``syntax'' to preserve the consistency of the notations.
+%}
+%We draw the head on the left because all analyses mentioned above considered the first element in the reduplication to be the actual verb and the second element the reduplicant, 
+%but this analysis itself does not forbid the head to be on the right side.
+
+%\begin{figure}[h!]
+%\centering
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Phonology\\
+%\begin{forest}
+%[P$_{j}$ [kan]] 
+%\end{forest}
+%\begin{forest}
+%[P$_{j, k}$ [kan]]
+%\end{forest}
+%\end{center}
+%\end{minipage}
+%\columnbreak
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Syntax\\
+%\begin{forest}
+%[V
+% [V$_j$]
+% [CR$^{syn}$$_k$]
+%]
+%\end{forest}
+%\end{center}
+%\end{minipage}
+%\columnbreak
+%\begin{minipage}[t]{.3\linewidth}
+%\begin{center}
+%Semantics
+%\[
+%\begin{bmatrix}
+%\begin{bmatrix}
+%DELIM\\([LOOK]_{j})
+%\end{bmatrix}_{\!k}\\
+%\end{bmatrix}
+%\]
+%\end{center}
+%\end{minipage}
+%\caption{Analysis for AA following \citet{Ghomeshietal2004}}
+%\label{ghomeshi-cn}
+%\end{figure}
+
+%As for the other forms of reduplication, A-\textit{le}-A can be viewed as two compositional processes \mbox{[[[A] -\textit{le}] -A]}.
+%Furthermore, the \textit{yi} in A-\textit{yi}-A and A-\textit{le}-\textit{yi}-A can simply be viewed as a dangling phonological unit. 
+%In this case, \phonliste{ yi } is neither coindexed with a syntactic unit nor with a semantic one.
+
+%This analysis correctly captures the fact that the addition of \textit{yi} does not change the syntactic and semantic behavior of the reduplication.
+%It also provides a formal account for the phonology of the reduplication.
+%Nevertheless, by assuming a construction specially for the reduplication, this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese, unlike the affixation analyses described in \sectref{sec:asp}.
+
+ %%%%%%%%%%%%%%
+ %FanSongBond2015
+
+\citet*{FanSongBond2015} provide a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
+They consider reduplication to be a morphological process and model it via lexical rules.
+They provide the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
+and further propose \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
+as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.\footnote{%
+  Note that the format in which the lexical rule is given is not the input--output format usually
+  used for lexical rules in HPSG. Instead it is depicted as a unary branching phrase structure
+  rule: the input is the daughter on the right-hand side of the rule. The output is the mother on
+  the left-hand side. The view of lexical rules as unary branching rules is adopted in most current work on
+  lexical rules \citep{BC99a,Meurers2001a} despite the notation that is commonly assumed.
+
+  \textsc{hook} is a technical feature for sharing information. \textsc{ltop} and \textsc{lbl} will
+  be explained in Section~\ref{sec:analysis} below.
+}
+For them, the reduplication functions as an intensifier predicate, as represented in the \textsc{predicate (pred)} in the \textsc{constructional-content (c-cont)}.
+The \type{intensifier\_x\_rel} has two subtypes: \type{redup\_up\_x\_rel} for the amplifiying meaning of adjectival reduplication and \type{redup\_down\_x\_rel} for the delimitative meaning of verbal reduplication.
+The orthography is handled separately.
+The AABB form for adjectives and the ABAB form for verbs, as well as the AAB form for V-O compounds, are handled as irregular derivation forms.
+
+\ea\label{avm:fsb-redup}
+\avm{
+[\type*{redup-type}\\
+cat\textbar head & \1\\
+val & \2\\
+cont & \3 \normalfont \textsc{hook} [ltop & \4\\
+			ind & \5]\\
+c-cont & <[\type*{event-rel}\\
+		pred & intensifier\_x\_rel\\
+		lbl & \4\\
+		arg1 & \5]>
+]
+}
+$\to$
+\avm{
+[cat\textbar head & \1\\
+val & \2\\
+cont & \3
+]
+}
+\z
+
+\ea\label{avm:fsb-redup-a}
+\avm{
+[\type*{redup-a-lr $\subset$ redup-type}\\
+cat\textbar head & adjective\\
+val & [spr <>]\\
+c-cont & <[pred & redup\_up\_x\_rel]>
+]
+}\\
+\textsc{orthography}: A $\to$ AA; (irregular AB $\to$ AABB)
+\z
+
+\ea\label{avm:fsb-redup-v}
+\avm{
+[\type*{redup-v-lr $\subset$ redup-type}\\
+cat\textbar head & verb\\
+cont\textbar hook & [aspect & non-aspect]\\
+c-cont & <[pred & redup\_down\_x\_rel]>
+]
+}\\
+\textsc{orthography}: A $\to$ AA; A $\to$ A-\textit{yi}-A; (irregular AB $\to$ ABAB)
+\z
+
+This approach provides a unified account for adjectival and verbal reduplication.
+Their commonalities are captured by inheritance hierarchies of the intensifier predicates and the lexical rules.
+In the case of verbal reduplication, A-\textit{yi}-A is analyzed as an alternative orthographical form of AA.
+This correctly captured the intuition that AA and A-\textit{yi}-A express the same meaning and only differ from each other phonologically/orthographically (see \sectref{sec:core-sem}).
+
+Nevertheless, this analysis has some shortcomings.
+To begin with, since the combination with aspect markers is completely forbidden, it is impossible for this approach to account for A\hyp{}\textit{le}\hyp{}A.
+Moreover, as verbal reduplication is  considered to express a delimitative aspectual meaning,
+it seems unconvincing to assume that there is no aspect information in its semantics.
+We consider a semantic explanation as described in  \sectref{sec:aspM} to be more reasonable for ruling out aspect markers other than \textit{le}.
+Furthermore, this account can only deal with monosyllabic reduplication and handles ABAB and AAB as irregular forms, for the reason that ABAB and AAB reduplication of AB verbs ``are not very productive in Chinese'' \citep[102]{FanSongBond2015}.
+This is not true. 
+\citet[33]{Xing2000stat}, \citet[161]{BascianoMelloni2017}, \citet[329]{MelloniBasciano2018} and  \citet[Sec.\,3.1]{Xie2020}  all consider both AA and ABAB to be productive,
+and \citet[36]{Xing2000stat} concludes that AAB is productive as well.
+Thus, these forms should not be handled as  irregular forms, but should be derivable by lexical rules.
+
+The shortcomings of previous analyses lead us to propose a new analysis on verbal reduplication with {HPSG}, 
+that formalizes the phonology of the reduplication, resolves the problem of \textit{yi} and preserves the generalization on aspect marking, 
+as we will elaborate in \sectref{sec:analysis}.
+
+\section{A new HPSG analysis}\label{sec:analysis}
+
+In this section, we suggest a new lexical-rule-based analysis of aspect marking and reduplication
+using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
+MRS is one instance of underspecified semantics as is currently used in theoretical and
+computational work in HPSG (\citealt[Section~6]{KR2024a}, \citealt[Section~3]{BFO2002a-u},
+\citealt[Section~4.4]{MuellerCoreGram}, \citealt[Chapter~5]{MuellerLehrbuch4}). The advantage of
+such types of semantics is that scope relations can be left underspecified. This way it is avoided
+that large numbers of analyses are assigned to single sentences. Instead sentences are paired with
+underspecified semantic representations from which various readings can be derived.
+MRS uses lists of elementary predications that are connected via pointers. Scope constraints are
+represented by statements of domination. This allows for elegant ways to underspecify scope. The
+details cannot be discussed here. The interested reader is referred to \citet{Copestakeetal2005},
+\citet[Section~6]{KR2024a} or for the use of MRS in a grammar of German to \citet[Chapter~5]{MuellerLehrbuch4}. In
+what follows, we will present the elementary predications with the features assumed in MRS, but leave
+out handle constraints to keep things simple.
+
+Like \citet{FanSongBond2015}, we assume lexical rules for reduplication. Our lexical rules are
+organized in an inheritance network. \textit{verbal-reduplication-lr} is the most general type for
+reduplication lexical rules in this network and the implicational constraint in (\ref{avm:redup}) shows the constraints on all
+structures of type \textit{verbal-reduplication-lr}. Such structures take a verb as
+\textsc{lexical-daughter (lex-dtr)}.  The output reduplicates the \textsc{phonology (phon)} of the
+input verb with the possibility to have further phonological material in between.  \etag{} indicates
+an underspecified list which could be empty or not.\footnote{%
+The \etag is equivalent to a tag with a number with the difference that \etag is never shared. We
+follow Müller (\citeyear[161]{Mueller2002b}, \citeyear[294]{Mueller2003e}) and elsewhere in using this
+notation, since we think this is more
+precise than simply using three dots.}
+A delimitative relation is appended to the
+\textsc{relations (rels)} value of the input verb, and it takes the event index of the input verb \iboxb{3} as
+argument (\textsc{arg0}, \ldots, \textsc{arg3} are feature names for arguments. The values are
+indices or events similar to variables in normal predicate logic.). The list of relations contains so-called elementary predications. There is no complicated
+embedding of relations. Instead each elementary predication comes with a label (\textsc{lbl}). The
+label can be used as an argument of another relation or in scope constraints, which are not provided
+here to keep things simple. The feature \textsc{ltop} points to the local top. This is the
+elementary predication that is considered the top-most one in the \relsl. Other elementary
+predications may share the label or have arguments with labels of other elementary predications. We
+will discuss an example below when we discuss the perfective lexical rule.
+The label of the output \iboxb{2} is identified with the label of the input and with the
+label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
+relations can be added at the beginning of the \textsc{rels} list to allow for the additional
+perfective meaning in A-\textit{le}-A and A-\textit{le}-\textit{yi}-A.  The combination with the
+perfective will be elaborated on in the following paragraphs.
+
+\eas
+\type{verbal-reduplication-lr} \impl\\
+%\scalebox{.9}{%
+    \avm{
+        [
+        phon & \1 $\oplus$ \etag $\oplus$ \1\\
+        synsem & [ loc\textbar cont [ ltop & \2 \\
+        ind  & \3 ] ]\\
+        rels & \etag $\oplus$ \4 $\oplus$ < [\type*{delimitative-rel}\\
+        lbl & \2\\
+        arg0 & \3 ] > \smallskip\\
+        lex-dtr & [phon \1\\
+        synsem\textbar loc & [cat  & [ head & verb ] \\
+        cont & [ ltop & \2\\
+        ind  & \3 ]]\\
+        rels \4 ] ]
+}
+%}
+\label{avm:redup}
+\zs
+
+To account for the variations in the phonology of the reduplication as well as 
+the combination with the phonology and semantics of the perfective aspect marker \textit{le}, 
+the type hierarchy of lexical rules in \figref{fig:typehi} is put forward. 
+\begin{figure}
+    \centering
+    \scalebox{.9}{\begin{forest}
+        type hierarchy
+        [,phantom
+        [,phantom
+        [verbal-reduplication-lr,name=verbal-reduplicaiton-lr
+        [non-perfective-reduplicaiton-lr
+        [a-a-lr]
+        [a-yi-a-lr]]
+        [,identify=!r211]]]
+        [aspect-marking-lr
+        [perfective-lr
+        [perfective-reduplicaiton-lr%,edge to=verbal-reduplicaiton-lr
+        [a-le-yi-a-lr]
+        [a-le-a-lr]]
+        [v-le-lr]]
+        [durative-lr]
+        [\ldots]]]
+    \end{forest}
+}
+    \caption{Type hierarchy for lexical rules of verbal reduplication and \textit{le}}
+    \label{fig:typehi}
+\end{figure}
+Apart from the type \type{perfective-reduplication-lr}, 
+which adds the inherited perfective relation, 
+there is a subtype \type{non-perfective-reduplication-lr}, 
+which does not add further relations. 
+Hence, what is \etag in the \textsc{rels} list in (\ref{avm:redup}) is the empty list in (\ref{avm:nonperf}):
+\ea\label{avm:nonperf}
+\type{non-perfective-verbal-reduplication-lr} \impl\\
+%\scalebox{.9}{%
+    \avm{
+        [
+        rels & \1 $\oplus$ < [ ] > \smallskip\\
+        lex-dtr & [ rels \1 ] ]
+    }
+%}
+\z
+The \textsc{rels} list of the output of the lexical rule is the \textsc{rels} list of
+the daughter \iboxb{1} plus a list with one element. 
+Since this element is specified in the supertype, it is not specified in (\ref{avm:nonperf}) again.
+
+\type{non-perfective-verbal-reduplication-lr} has \type{aa-lr} and \type{a-yi-a-lr} as direct subtypes.
+(\ref{avm:AA}) and (\ref{avm:AyiA}) show \type{aa-lr} and \type{a-yi-a-lr}, respectively.
+As subtypes of \type{ver\-bal\hyp{}re\-dup\-li\-ca\-tion\hyp{}lr} illustrated in (\ref{avm:redup}), 
+both inherit the constraints on the \textsc{lex-dtr} and on the semantics of the output, 
+and because of (\ref{avm:nonperf}), no extra material is appended to the \textsc{rels} value of the input verb
+and the list containing the \type{delimitative-rel}.
+ In addition to the inherited constraints,
+\type{aa-lr} and \type{a-yi-a-lr} specify the phonology of the output differently.
+\type{aa-lr} determines that the \etag between the two phonological copies in (\ref{avm:redup}) is the empty list, 
+whereas \type{a-yi-a-lr} specifies this list of phonological material as \phonliste{ yi }:
+
+\ea\label{avm:constr-AA}
+Constraints on lexical rules of type \type{aa-lr} and \type{a-yi-a-lr}:
+%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
+ \ea   \type{aa-lr} \impl \\%& 
+  %  \scalebox{.9}{%
+        \avm{
+            [phon & \1 $\oplus$ \1\\
+            lex-dtr & [phon & \1] ]
+    }
+%} %& 
+\ex	\type{a-yi-a-lr} \impl\\
+ %    \scalebox{.9}{%
+        \avm{
+            [phon & \1 $\oplus$ \phonliste{ yi } $\oplus$ \1\\
+            lex-dtr & [phon & \1] ]
+    }
+%}
+%\end{tabular}
+\z
+\z
+
+\noindent
+The lexical rules with all inherited constraints are given in (\ref{avm:AA}) and (\ref{avm:AyiA}):
+
+\ea\label{avm:AA}
+The AA lexical rule with all constraints inherited from the supertypes:\\
+%\scalebox{.9}{%
+    \avm{
+        [\type*{aa-lr}\\
+        phon & \1 $\oplus$ \1\\
+        synsem & [ loc\textbar cont [ ltop & \2 \\
+        ind  & \3 ] ]\\
+        rels & \4 $\oplus$ < [\type*{delimitative-rel}\\
+        lbl & \2\\
+        arg0 & \3 ] >\\
+        lex-dtr & [phon & \1\\
+        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
+            cont & [ ltop & \2\\
+            ind  & \3 ]]}\\
+        rels & \4]
+        ]
+}
+%}
+\z
+
+%\newpage
+\ea\label{avm:AyiA}
+The A-\textit{yi}-A lexical rule with all constraints inherited from the supertypes:\\
+%\scalebox{.9}{%
+    \avm{
+        [\type*{a-yi-a-lr}\\
+        phon & \1  $\oplus$ \phonliste{ yi } $\oplus$ \1\\
+        synsem & [ loc\textbar cont [ ltop & \2 \\
+        ind  & \3 ] ]\\
+        rels &  \4 $\oplus$ < [\type*{delimitative-rel}\\
+        lbl & \2\\
+        arg0 & \3 ] >\\
+        lex-dtr & [phon & \1\\
+        \punk{synsem\textbar loc}{[cat  & [ head & verb ]\\
+            cont & [ ltop & \2\\
+            ind  & \3 ]]}\\
+        rels & \4]
+        ]
+}
+%}
+\z
+
+\type{v-le-lr} is a direct subtype of the \type{perfective-lr}.
+\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}
+and has two subtypes, \type{a-le-yi-a-lr} and \type{a-le-a-lr} itself.
+\type{verbal-reduplication-lr} is already presented in (\ref{avm:redup}). 
+We now turn to the constraints on \type{perfective-lr} and its subtypes.
+
+\citet[246]{MuellerLipenkova2013} propose the perfective lexical rule given in (\ref{avm:pfv-old}), 
+adapted to the formalization adopted in the current paper.
+It takes a verb as \textsc{lex-dtr}
+and appends \phonliste{ le } to its phonology.
+Further, it accounts for the change in semantics by appending the \textsc{rels} value of the input verb to a \type{perfective-rel}.
+
+\ea\label{avm:pfv-old}
+Perfective lexical rule adapted from \citet[246]{MuellerLipenkova2013}:\\
+%\scalebox{.9}{%
+    \avm{
+        [\type*{perfective-lr}\\
+        phon & \1 \+ \phonliste{ le }\\
+        \punk{synsem\textbar loc\textbar cont}{ [ ltop & \2\\
+            ind & \3 ]}\\ 
+        rels & <[\type*{perfective-rel}\\
+        lbl  & \2\\
+        arg0 & \3\\
+        arg1 & \4]> \,\+\, \5\smallskip\\
+        lex-dtr & [phon & \1\\
+        \punk{synsem\textbar loc}{[cat & [ head & verb]\\
+            cont & [ ltop & \4\\
+            ind & \3]]}\\
+        rels & \5]
+        ]
+}
+%}
+\z
+The event variables \iboxb{3} of the input and the output verb are shared. 
+The \textsc{ltop} of the output of the lexical rule \iboxb{2} is the label of the perfective relation, 
+and this relation scopes over the embedded verb. 
+The handle of the embedded verb \iboxb{4} is the argument of the \type{perfective-rel}.
+
+The lexical rule suggested in (\ref{avm:pfv-old}) only explains simple perfective aspect marking with \textit{le}, 
+where \textit{le} immediately follows the verb.
+But it cannot account for the perfective aspect marking of a reduplicated verb,
+ as \textit{le} does not occur after the reduplication, 
+nor can \textit{le} be reduplicated together with the verb.
+It can only appear between the verb and the reduplicant.
+In order to accommodate \textit{le} marking for both simple and reduplicated verbs, 
+a general perfective lexical rule as in (\ref{avm:pfv-new}) and 
+a subtype \type{v-le-lr} as in (\ref{avm:vle}) are posited here.
+Besides adding a \type{perfective-rel} in the \textsc{rels} list of the output as in (\ref{avm:pfv-old}), 
+the \type{perfective-lr} in (\ref{avm:pfv-new}) allows an underspecified list to be appended at the end of the \textsc{rels} list.
+The \textsc{phon} value of the output makes it possible for further phonological material to occur both before and after \phonliste{ le }.
+
+\ea\label{avm:pfv-new}
+Type constraints on the type \type{perfective-lr} from which other subtypes inherit:\\
+%\scalebox{.9}{%
+    \avm{
+        [\type*{perfective-lr}\\
+        phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
+        \punk{synsem\textbar loc \textbar cont}{ [ltop & \2\\
+            ind  & \3]}\\ 
+        rels & <[\type*{perfective-rel}\\
+        lbl  & \2\\
+        arg0 & \3\\
+        arg1 & \4 ]> $\oplus$ \5 $\oplus$ \etag\smallskip\\
+        lex-dtr & [%phon & \1\\
+        \punk{synsem\textbar loc}{[cat & [ head & verb ]\\
+            cont & [ ltop & \4\\
+            ind  & \3]]}\\
+        rels & \5]
+        ]
+}
+%}
+\z
+
+\type{v-le-lr} with all inherited constraints as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
+and that nothing else comes after \phonliste{ le }.
+Furthermore, no other list can be appended at the end of the \textsc{rels} list of the output anymore.
+This corresponds to the proposal of \citet[246]{MuellerLipenkova2013} shown in (\ref{avm:pfv-old}), 
+which accounts for the simple perfective marking of verbs.
+
+%\newpage
+\ea\label{avm:vle}
+Structure of type \type{v-le-lr} with constraints inherited from \type{perfective-lr}:\\
+%\scalebox{.9}{%
+    \avm{
+        [\type*{v-le-lr}\\
+        phon & \1 $\oplus$ \phonliste{ le }\\
+        \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
+        rels & <[\type*{perfective-rel}\\
+        lbl  & \2\\
+        arg0 & \3\\
+        arg1 & \4]> $\oplus$ \5\smallskip\\
+        lex-dtr & [phon & \1\\
+        synsem\textbar loc \textbar cat  & [ head & verb\\
+        cont & [ltop & \4\\
+        ind & \3]]\\
+        rels & \5]]
+}
+%}
+\z
+
+\type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}.
+The \textsc{phon} value of the output reduplicates the phonology of the input verb and states that there is \phonliste{ le } in between, 
+as well as potentially further phonological material.
+The \textsc{rels} list of the output appends the \type{delimitative-rel} to the \type{perfective-rel} and the \textsc{rels} value of the input verb.
+The arguments of both \type{perfective-rel} and \type{delimitative-rel} share the event index of the
+input verb \iboxb{3} to ensure that they apply to the same event denoted by the input verb. 
+The label of the \type{delimitative-rel} and the input verb are identified (\type{delimitative-rel} is a modifier) 
+and this shared label is embedded under the \type{perfective-rel}.
+
+\ea\label{avm:pfv-redup}
+Perfective and reduplication combined: type \type{perfective-reduplication-lr} with
+constraints inherited from \type{perfective-lr} and \type{verbal-redu\-pli\-ca\-tion-lr}:\\
+%\resizebox{\linewidth}{!}{
+ %   \scalebox{.9}{%
+        \avm{
+            [\type*{perfective-reduplication-lr}\\
+            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \etag $\oplus$ \1\\
+            \punk{synsem\textbar loc\textbar cont\textbar ltop}{ \2}\\ 
+            rels & <[\type*{perfective-rel}\\
+            lbl & \2\\
+            arg0 & \3\\
+            arg1 & \4]>
+            $\oplus$ \5 $\oplus$
+            <[\type*{delimitative-rel}\\
+            lbl  & \4\\
+            arg0 & \3]>\\
+            lex-dtr & [phon & \1\\
+            synsem\textbar loc & [cat  & [ head & verb ]\\
+            cont & [ ltop & \4\\
+            ind  & \3]]\\
+            rels & \5]
+            ]
+    }
+%}
+    %}
+\z
+For example %(\ref{ex-he-tasted-the-soup-a-little-bit}), repeated here as
+ (\ref{ex-he-tasted-the-soup-a-little-bit2}), we get the  MRS representation in (\ref{ex:mrs-soup}),
+where h1 and h2 correspond to the handles \ibox{2} and \ibox{4} and e1 to the event variable \ibox{3}:
+\ea\label{ex-he-tasted-the-soup-a-little-bit2}
+    \gll \objex{ta1} \obj{chang2}-\obj{le}-\obj{chang2} \objex{tang1}.\\
+    he taste-\textsc{pfv}-taste soup\\
+    \glt `He tasted the soup a little bit.'
+ \z
+\ea\label{ex:mrs-soup}
+h1 \sliste{ h1:perfective(e1,h2), h2:taste(e1,he,soup), h2:delimitative(e1) }
+\z
+So the delimitative relation is treated as an adjunct to the main relation of the verb, 
+and the perfective relation scopes over both the main relation and the delimitative relation.
+
+Two subtypes of \type{perfective-reduplication-lr} are posited:
+\type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} %as in (\ref{avm:AleyiA}) 
+and \type{a-le-a-lr}, as shown in (\ref{avm:AleA}). %(\ref{avm:AleA}).
+They take over the semantic change to the input from \type{perfective\hyp{}reduplication\hyp{}lr}, but specify the \textsc{phon} value differently.
+Specifically, \type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} specifies the middle phonological material as
+\phonliste{ le, yi }, while \type{a-le-a} specifies it as \phonliste{ le } only.\footnote{
+A reviewer wants to know what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
+The possible historical and phonological reasons are discussed in Appendix~\ref{app:hist}.
+In this analysis, the subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
+}
+
+\ea\label{avm:AleA}
+%\begin{tabular}{@{}l@{\hspace{2cm}}l@{}}
+\ea    %\scalebox{.9}{%
+        \type{a-le-yi-a-lr} \impl\\
+        \avm{
+            [%\type*{a-le-yi-a-lr}\\
+            phon & \1 \+ \phonliste{ le, yi } \+ \1\\
+            lex-dtr & [phon & \1
+            ]
+            ]
+    }
+%}%&
+\ex   % \scalebox{.9}{%
+\label{avm:a-le-a-lr}
+    \type{a-le-a-lr} \impl\\
+        \avm{
+            [%\type*{a-le-a-lr}\\
+            phon & \1 \+ \phonliste{ le } \+ \1\\
+            lex-dtr & [phon & \1
+            ]
+            ]
+    }
+%}
+%\end{tabular}
+\z
+\z
+
+The analysis of (\ref{ex-he-tasted-the-soup-a-little-bit2}) is shown in tree format in
+Figure~\ref{fig-he-tasted-the-soup-a-little-bit}. The \textsc{lex-dtr} is the daughter in the tree.
+\begin{figure}[htb]
+\centering
+\begin{forest}
+[        \avm{
+            [\type*{a-le-a-lr}\\
+            phon & \1 $\oplus$ \phonliste{ le } $\oplus$ \1\\
+            synsem\textbar loc & [ cat  & [ head  & verb\\
+                                            spr   & < NP$_{\6}$ >\\
+                                            comps & < NP$_{\7}$ > ]\\
+                                   cont & [ ltop & \2\\
+                                            ind  & \ibox{3} ]] \\
+            rels & <[\type*{perfective-rel}\\
+            lbl & \2\\
+            arg0 & \3\\
+            arg1 & \4]> $\oplus$ \5 $\oplus$
+            <[\type*{delimitative-rel}\\
+            lbl  & \4\\
+            arg0 & \3]> ]
+    }
+[\avm{ [phon & \1 \phonliste{ chang2 }\\
+       synsem\textbar loc & [cat  & [ head  & verb\\
+                                      spr   & < NP$_{\6}$ >\\
+                                      comps & < NP$_{\7}$ > ]\\
+                             cont & [ ltop & \4\\
+                                      ind  & \3]]\\
+        rels & \5 < [\type{taste}\\
+                     lbl  & \4\\
+                     arg0 & \3\\
+                     arg1 & \6\\
+                     arg2 & \7 ] > ]
+}]]
+\end{forest}
+
+\caption{Analysis of \obj{chang2-le-chang2} taste-\textsc{pfv}-taste `taste the soup a little bit'}\label{fig-he-tasted-the-soup-a-little-bit}
+\end{figure}
+
+The figure shows how the lexical item for \obj{chang2} `to taste' is inserted as a daughter into
+the \type{a-le-a-lr} lexical rule. The arguments of \obj{chang2} `to taste' are represented within the \spr and
+the \compsl (see \citealt{GSag2000a-u} for English) and the respective argument NPs are linked to the
+arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
+the stimulus. See \citet{DKW2024a} for more on linking. The part of speech of the lexical item
+(\type{verb}) and the valence information is carried over from the daughter to the mother
+unchanged. The semantic contribution of the daughter verb, the value of \ibox{5}, is inserted into
+the \relsl of the mother as it was specified in the constraints on the type
+\type{perfective-reduplication-lr} in (\ref{avm:pfv-redup}). The \textsc{phon} value of the mother
+is the concatentation of \obj{chang2}, \obj{le} and \obj{chang2}, as specified in the constraint
+on \type{a-le-a-lr} in (\ref{avm:a-le-a-lr}). The resulting unit \obj{chang2-le-chang2} then
+combines with its object forming a VP. This VP is combined with the subject resulting in a complete
+verbal projection, a sentence. \obj{chang2-le-chang2} behaves in the same way as the simple \obj{chang2}.
+
+Since the above-described lexical rules do not constrain the number of syllables of the input verb, but simply reduplicate its phonology  as a whole,
+they can also account for the ABAB and the AB-\textit{le}-AB forms of reduplication,
+as long as the input verb is disyllabic.
+Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
+Although these forms are considered unacceptable by some authors \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}},
+\citet[269]{Fan1964} and \citet[143]{Sui2018} consider AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognize that these two forms are rare.
+Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin %(12th to 20th centuries)
+ (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.
+
+\settowidth\jamwidth{(CCL)}
+
+\begin{sloppypar}
+\ea\label{ex:ABleyiAB}
+\ea\label{ex:AByiAB-lu}
+\gll \objex{ni3} \objex{yu3} \objex{wo3} \obj{zheng3li3-yi-zheng3li3}.\footnotemark\\
+you let me arrange-one-arrange\\
+\glt `Let me arrange it a little bit!'
+\footnotetext{\obj{Yuan2qu3} \obj{xuan3}: \obj{Lu3zhai1lang2} \textit{[Selected Yuanqu: Luzhailang]}, as cited in \citet[15]{Zhang2000}}
+
+\ex\label{ex:AByiAB-pu}
+\gll \objex{ni3} \obj{da3ting1-yi-da3ting1}.\footnotemark\\
+you inquire-one-inquire\\
+\glt `Inquire about it a little bit!'
+\footnotetext{\obj{Yuan2} \obj{Ming2} \obj{juan4}: \obj{Piao2tong1shi4} \textit{[Yuan and Ming volume: Piaotongshi]}, 308, as cited in \citet[15]{Zhang2000}}
+
+\ex\label{ex:AByiAB-rou1}
+\gll \objex{ge4} \objex{ge4} \objex{dian3-tou2} \obj{wei1xiao4-yi-wei1xiao4}.\footnotemark\\
+\textsc{clf} \textsc{clf} nod-head smile-one-smile\\
+\glt `Each one nodded his head and smiled a little bit.'
+\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
+
+\ex\label{ex:AByiAB-rou2}
+\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3}-\obj{le-yi}-\obj{ming2xiang3}.\footnotemark\\
+he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\
+\glt `He smiled a little bit and meditated a little bit.'
+\footnotetext{\objex{Rou2}, \objex{Shi2}. 1975. \obj{Rou2} \obj{Shi2} \obj{xiao3shuo1} \obj{xuan3ji2} \textit{[Selected novels of Roushi]}, 31. Beijing: People's Literature Publishing House.}
+
+\ex\label{ex:AByiAB-li}
+\gll \objex{fei1chang2} \objex{yan2su4} de \objex{ba3} \objex{jin4shi4} \objex{yan3jing4} \obj{duan1zheng4-le-yi-duan1zheng4}.\footnotemark\\
+very seriously \textsc{de} \textsc{ba} nearsighted glasses straighten-\textsc{pfv}-one-straighten\\
+\glt `[He] very seriously straightened the nearsighted glasses quickly.'
+\footnotetext{\objex{Li3}, \objex{Jie2ren2}. 1962. \obj{Da4} \obj{bo1} \textit{[Great wave]}, 3rd band, 171. Beijing: The Writers Publishing House.}
+
+\ex\label{ex:ABleyiAB-ccl}
+\gll \objex{ji3duo1} \objex{san3luan4}-zhe de \objex{chuan2} \objex{li3} de \objex{deng1guang1}, \objex{ye3} \objex{hu1yin1hu1mie4} de \obj{bian4huan4-le-yi-bian4huan4} \objex{wei4zhi}.\\
+many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
+\glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
+\z
+\z
+\end{sloppypar}
+
+This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
+The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
+Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.\footnote{
+One reviewer suggests that given that AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}),
+these rare occurrences can be seen as relics of this usage.
+}
+
+AAB, A-\textit{yi}-AB, A-\textit{le}-AB, AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4} can also be accounted for by the lexical rules proposed in this section.
+They can be analyzed as compounds consisting of a reduplicated monosyllabic verb and another element.
+Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
+    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.\,2]{Her1996}; \citeyear[Sec.\,3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
+    Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.
+}
+AA-\obj{kan4} can be regarded as the compound of a reduplicated monosyllabic verb (A) and the verb \obj{kan4} `look',
+whereas A-\obj{kan4}-\obj{kan4} is the compound of a monosyllabic verb (A) and the reduplication of \obj{kan4} `look'.
+A-\obj{yi}-A-\obj{kan4} is also possible, though rare, presumably also due to its length.
+An inquiry in CCL found 55 hits of A-\obj{yi}-A-\obj{kan4}.
+A sample is listed in (\ref{ex:AyiAkan}).
+
+\begin{sloppypar}
+\ea\label{ex:AyiAkan}
+\ea
+\gll \objex{te4yi4} \objex{gong1neng2} de \objex{yan2jiu1zhe3}-men \objex{bu4fang2} \objex{ru2ci3} \obj{shi4-yi-shi4-kan4} \ldots\\
+special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
+\glt `Researchers of special power may as well have a try as such and see \ldots'
+
+\ex 
+\gll \objex{dan4shi4} \objex{dui4} \objex{fa1} \objex{mei2} \objex{fa1}-\objex{guo} \objex{he2ge2-zheng4}, \objex{yi3jing1} \objex{shuo1} \objex{bu4} \objex{qing1} le, \objex{xu1yao4} \obj{cha2-yi-cha2-kan4}.\\
+but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
+\glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'
+
+\ex
+\gll \objex{rang4} \objex{wo3} \objex{lai2} \obj{cai1-yi-cai1-kan4}.\\
+let I come guess-one-guess-look\\ \jambox{({CCL})}
+\glt `Let me have a guess.'
+
+\ex
+\gll \objex{da4-lao3ban3}-men \objex{yao4} \obj{deng3-yi-deng3-kan4}\\
+big-boss-\textsc{pl} need wait-one-wait-look\\ \jambox{(CCL)}
+\glt `Big bosses need to wait a little bit and see.'
+
+\ex
+\gll \objex{fu1ren2} \objex{ni3} \objex{dao4} \obj{shu3-yi-shu3-kan4}, \objex{zhe4} \objex{zhu1} \objex{hua1} de \objex{hua1duo3} \objex{gong4} \objex{you3} \objex{ji3} \objex{zhong3} \objex{yan2se4}.\\
+madam you just count-one-count-look this \textsc{clf} flower \textsc{de} blossom in.total have how.many \textsc{clf} color\\ \jambox{(CCL)}
+\glt `Madam, just try to count and see how many colors the blossom of this flower has in total.'
+\z
+\z
+Due to the prominent tentative, trying meaning of AA-\obj{kan4} and A-\obj{kan4}-\obj{kan4}, they are not compatible with the perfective aspect marker \obj{le} semantically,
+as one usually cannot try something that is already realized.
+Thus, structures such as  A\hyp{}\obj{le}\hyp{}A\hyp{}\obj{kan4} and A\hyp{}\obj{kan4\hyp{}le\hyp{}kan4} are considered pragmatically infelicitous.
+\end{sloppypar}
+
+The current analysis provides a unified account for all forms of delimitative verbal reduplication in Mandarin Chinese.
+Like in \citet{FanSongBond2015}, \textit{yi} is handled as a phonological element which does not make any contribution to the semantics,
+and an inheritance hierarchy is used to capture the commonalities among different forms of reduplication.
+But the present proposal also reflects the connection between the reduplication and aspect marking via multiple inheritance.
+This account makes use of a semantic mechanism, which correctly rules out aspect marking with forms other than \textit{le}.
+By providing a semantic explanation, this mechanism seems less \textit{ad hoc} than the one used in \citet{FanSongBond2015}, which simply assumed that the reduplication cannot combine with aspect information.
+The present approach also has a broader coverage of the forms of verbal reduplication than the one in \citet{FanSongBond2015}.
+Furthermore, all the forms are derivable from the lexical rules proposed here, so that there is no need to resort to irregular lexicon entries, and the productivity of these forms is correctly captured.
+In sum, the analysis proposed in this paper possesses greater explanatory power and resolves the
+problems of previous studies.
+
+\section{Conclusions}\label{sec:conclu}
+
+The current study provides a new HPSG account for delimitative verbal reduplication in Mandarin Chinese.
+We present empirical evidence that reduplication is possible with all verb classes.
+We give a semantic explanation for the incompatibility of reduplication with aspect markers other than \obj{le}.
+We argue that reduplication is better analyzed as a morphological rather than a syntactic process.
+We model reduplication as a lexical rule,
+and the different forms of reduplication are captured in an inheritance hierarchy using underspecified lists.
+The interaction between verbal reduplication and aspect marking is handled by multiple inheritance.
+This analysis is compatible with both mono- and disyllabic verbs, 
+so that all productive forms of reduplication are derivable by lexical rules.
+The analysis is implemented as part of a computer-processable grammar of Mandarin Chinese.
+The analysis is implemented as part of the CoreGram project \citep{MuellerCoreGram} in a Chinese
+grammar \citep{MuellerLipenkova2013} in the TRALE system \citep{MeurersEtAl2002, Penn2004}.
+
+\section{Acknowledgements}
+
+We are really grateful for the comments of several reviewers of the Journal of Linguistics and of
+the HPSG 2021 conference. We also thank Elizabeth Pankratz for comments on an earlier version of
+this paper. This work was supported by a grant of the DFG to the project SFB 1412 A04.
+
+\appendix
+
+\section{Analysis based on the aspectual system by \citet{Tsai2008}}\label{app:tsai}
+
+\citet[229]{YangWei2017} claim that reduplication can be analyzed as an aspect marker 
+following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
+ \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
+He observes the so-called incompleteness effect, namely that a minimal sentence, 
+which only contains a verb marked by \obj{zhe} `\textsc{dur}',
+\obj{le} `\textsc{pfv}' or \obj{wan2} `\textsc{compl}' 
+and its arguments, 
+seems incomplete without further sentential elements 
+such as the sentence final particle \obj{le} 
+or a temporal adverbial like \obj{gang1cai2} `just now' (\ref{ex:incomplete}). 
+In contrast, a minimal sentence with a verb marked by  \obj{zai4} `\textsc{prog}' or \obj{guo}
+`\textsc{exp}'  and its arguments can stand alone (\ref{ex:complete}).
+
+\ea\label{ex:incomplete}
+\gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan2} \objex{fan4} *(le).\\
+Xiaoli eat-\textsc{dur}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
+\glt `Xiaoli is eating/ate/finished eating the meal.'
+\z
+
+\ea\label{ex:complete}
+\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo}.\\
+Xiaoli just.now \textsc{prog} cry/cry-\textsc{exp}\\
+\glt `Xiaoli was crying/cried just now.'
+\z
+He thus proposes three aspect positions under TP. \obj{zai4} `\textsc{prog}' and \obj{guo} `\textsc{exp}' reside under Asp$_1$, 
+while \obj{zhe} `\textsc{dur}' and \obj{le} `\textsc{pfv}' under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{
+    \citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that 
+    \obj{wan2} can only occur with certain types of predicate.
+    This differentiation does not play a role for our purpose and will not be further discussed here.}
+
+\begin{figure}
+    \centering
+    \begin{forest}
+        [TP [T]
+        [...
+        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
+        [\textit{v}P [\textit{v}]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe/le}]
+        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
+        ]
+        ]
+        ]
+        ]
+        ]
+        ]
+    \end{forest}
+    \caption{Structure of the aspectual system in Mandarin Chinese according to \citet[683]{Tsai2008}}
+    \label{tree:tsai}
+\end{figure}
+
+Turning to reduplication, a minimal sentence with reduplication also seems incomplete (\ref{ex:redup-tsai}).
+Based on this, the reduplicant should reside under Asp$_2$, as illustrated in \figref{tree:redupasp}.
+
+\ea\label{ex:redup-tsai}
+\ea[*] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}\\
+    he laugh-laugh\\}
+\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}\\
+    he laugh-\textsc{pfv}-laugh\\
+    \glt `He laughed a little.'}
+\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}, \objex{bu4} \objex{shuo1hua4}\\
+    he laugh-laugh not speak\\
+    \glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
+\z
+\z
+
+\begin{figure}
+    \centering
+    \begin{forest}
+        [TP [T]
+        [...
+        [AspP$_1$ (outer aspect) [Asp$_1$\\\obj{zai4/guo}]
+        [\textit{v}P [\textit{v}]
+        [AspP$_2$ (middle aspect) [Asp$_2$\\\obj{zhe}/\obj{le}/reduplication]
+        [VP [V-Asp$_3$ (inner aspect)\\\obj{wan2}]
+        ]
+        ]
+        ]
+        ]
+        ]
+        ]
+    \end{forest}
+    \caption{Position of reduplication according to the aspectual system in \citet{Tsai2008}}
+    \label{tree:redupasp}
+\end{figure}
+
+This analysis would result in a mismatch between syntax and semantics, 
+in the sense that the aspect markers that belong to the same semantic group do not occur in the same syntactic position. 
+Even though \obj{le} `\textsc{pfv}', \obj{guo} `\textsc{exp}' and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
+\obj{guo} `\textsc{exp}' is situated under Asp$_1$, while \obj{le} `\textsc{pfv}' and reduplication are under Asp$_2$.
+Similarly, \obj{zai4} `\textsc{prog}' and \obj{zhe} `\textsc{dur}' are both imperfective aspects but also occur in different syntactic positions.
+
+\section{\obj{yi} and \obj{le}}\label{app:hist}
+
+A reviewer suggests that the fact that only  \obj{yi} and \obj{le}  can appear in between reduplication 
+seems somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.
+We think that there might be historical and phonological reasons.
+
+\obj{le} `\textsc{pfv}' marks the perfective aspect.
+The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in Section~\ref{sec:aspM}.
+
+As for \obj{yi} `one', its use stems from the historical development of delimitative verbal reduplication but is synchronically opac.
+\citet[13--15]{Zhang2000} shows that delimitative verbal reduplication originates from the ``V + numeral + verbal classifier'' phrase,
+where the verbal classifier is borrowed from a verb of the same form, as shown in (\ref{ex:hist1}) from \obj{Song4dai4} \obj{juan4}: \obj{Xu1tang2} \obj{He2shang} \obj{yu3lu4} \textit{[The Song dynasty volume: Quotations from Abbot Xutang]} p.
+387 as cited in \citet[12]{Zhang2000}.
+\ea\label{ex:hist1}
+%明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
+\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{lian2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\\
+Ming again yell Qi also yell Ming in.succession yell two yell Qi thus bow\\
+\glt `Ming yelled again. Qi yelled too. Ming yelled twice. Qi thus bowed.'
+\z
+Here the numeral refers to the actual number of the action taking place
+and can be any number.
+This evolved into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
+but simply conveys that the action happens in a short period of time or for only few times. 
+Consider (\ref{ex:hist2}) from \obj{Song4dai4} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p.
+519 as cited in \citet[13]{Zhang2000}.
+\ea\label{ex:hist2}
+%且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
+\gll \objex{qie3} \obj{xie1-yi-xie1} \objex{le}, \objex{qu4} \objex{zuo4} \objex{di4}.\\
+just rest-one-rest \textsc{ptc} go sit ground\\
+\glt `(Let me) just take a rest and go sit on the ground.'
+\z
+In this case, \obj{yi1} `one' cannot be replaced by other numerals.
+Since V-\obj{yi}-V does not express the actual number of the action anymore,
+it became possible to delete the \obj{yi1} `one',
+hence the use of the VV (or AA) form, too.
+
+Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
+This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure
+and is only there as a historical remnant.
+In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds
+
+Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little/few',
+there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
+In Mandarin Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
+where the \obj{li} is fixed and also does not bear any meaning.
+\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
+and the second syllable in A-\obj{li}-AB occupies an unstressed position.
+We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
+This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
+But a phonological account is out of the scope of this paper and has to be left for further research.
+
+%The subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
+
 %      <!-- Local IspellDict: en_US-w_accents -->

### 2025-11-16 main.tex
Einrückungen nach Beispielen weg und Beispiele in Fußnoten mit (i), (ii) usw. Das macht eigentlich langsci-gb4e automatisch. Das scheint aber inkompatibel mit den CUP-Klassen zu sein.

@@
 
-\author[1]{Yanru Lu\corresp{\email{yanru.lu@hu-berlin.de}}}%\orcid{0000-0002-5915-7315}
-\author[1]{Stefan Müller\corresp{\email{st.mueller@hu-berlin.de}}}%\orcid{0000-0003-4413-5313}
+\author[1]{Yanru Lu 0000-0002-5915-7315\corresp{\email{yanru.lu@hu-berlin.de}}}%\orcid{0000-0002-5915-7315}
+\author[1]{Stefan Müller 0000-0003-4413-5313\corresp{\email{st.mueller@hu-berlin.de}}}%\orcid{0000-0003-4413-5313}
 

### 2025-11-16 reduplication-include.tex
Einrückungen nach Beispielen weg und Beispiele in Fußnoten mit (i), (ii) usw. Das macht eigentlich langsci-gb4e automatisch. Das scheint aber inkompatibel mit den CUP-Klassen zu sein.

@@
 
-\ea\label{ex:redup-ex} 
-	\ea
+\eal
+\label{ex:redup-ex} 
+\ex
 \gll \objex{qing3} \objex{ni3} \objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
@@
 \glt `Please taste this dish a little bit.' 
-	\z
-\z
-
+\zl
+
+\noindent
 The current study tries to determine a suitable formal and unified analysis for the structure of verbal reduplication in Mandarin Chinese.
@@
 
-\settowidth\jamwidth{AB-\textit{le}-AB}
-
-\ea\label{ex:forms-mono} for monosyllabic verbs: \obj{shuo1} `say'
+\settowidth{\jamwidth}{AB-\textit{le}-AB}
+
+\ea\label{ex:forms-mono}for monosyllabic verbs: \obj{shuo1} `say'
 \ea \gll \objex{shuo1-shuo}\\ 
@@
          \glt `try to say a little bit'
-		\z
+\zl
 \footnotetext{One reviewer points out that this form is not acceptable for him/her.
@@
 This shows that the former is less common than the latter.
-(\ref{ex:Akankan}) below is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
-\ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
+%(\ref{ex:Akankan}) 
+(i) below is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
+\begin{exe}
+\exi{(i)}\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
 \gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
@@
 This suggests that A-\obj{kan4-kan4} is acceptable for and used by at least some Mainland Chinese Mandarin speakers as well.
-\ea %那么，你倒说看看 ，你会有什么样的改变\ldots \jambox{(BCC)}
+\begin{exe} %那么，你倒说看看 ，你会有什么样的改变\ldots \jambox{(BCC)}
+\exi{(ii)}
 \gll \objex{na4me}, \objex{ni3} \objex{dao4} \obj{shuo1-kan4-kan4}, \objex{ni3} \objex{hui4} \objex{you3} \objex{shen2meyang4de} \objex{gai3bian4}\ldots\\
@@
 
-\ex %我得听看看你的条件再说\ldots \jambox{(BCC)}
+\exi{(iii)} %我得听看看你的条件再说\ldots \jambox{(BCC)}
 \gll \objex{wo3} \objex{dei3} \obj{ting1-kan4-kan4} \objex{ni3de} \objex{tiao2jian4} \objex{zai4} \objex{shuo1}\ldots\\
@@
 
-\ex\label{ex:forms-di} for disyllabic verbs: \obj{lai2-wang3} come-go `come and go/communicate'
+\ea\label{ex:forms-di} for disyllabic verbs: \obj{lai2-wang3} come-go `come and go/communicate'
 \ea\label{ex:forms-dia} \gll \objex{lai2-wang3-lai2-wang3}\\
@@
         \glt `coming and going'
-		\z
-
-\ex\label{ex:forms-vo} for V-O compounds: \obj{shuo1-huang3} tell-lie `lie'
+\zl
+
+\ea\label{ex:forms-vo} for V-O compounds: \obj{shuo1-huang3} tell-lie `lie'
 \ea \gll \objex{shuo1-shuo1-huang3}\\
@@
         \glt `lied a little bit'        
-		\z
-\z
-
+\zl
+
+\noindent
 \citet{Fan1964}, \citet{Arcodiaetal2014}  and \citet{Xie2020} compare the AA, ABAB and AABB forms of reduplication 
@@
 
+\noindent
 \citet{SuiHu2016} claim that the syntactic distribution of the deliminative reduplication is subject to the following constraints.
@@
 
+\noindent
 Secondly, \citet[319]{SuiHu2016} show that the reduplication cannot co-occur with a duration or a frequency phrase (\ref{ex:durfreq}).
@@
 
+\noindent
 Finally, \citet[322]{SuiHu2016} claim that a reduplicated verb cannot combine with a quantized object.
@@
 
+\noindent
 In sum, we consider that the reduplication has a similar syntactic distribution as an unreduplicated verb,
@@
 
+\noindent
 The semantics of A-\textit{le}-A can be deduced compositionally from its structure. 
@@
 
+\noindent
 It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
@@
 \settowidth\jamwidth{\citep[155]{XiaoMcEnery2004}}
-
 \ea
@@
 
+\noindent
 However, examples such as (\ref{ex:redup-achi-stat4}) can be found where \obj{bing4} `be sick' is reduplicated.
@@
 
+\noindent
 As a reviewer points out, \citet[Sec.\,3.3]{Tham2013} considers  \obj{bing4} `be sick' to be a basic change of state (COS) verb, i.e. `become sick'.
@@
 
+\noindent
 On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
@@
 
+\noindent
 One might argue that even in the examples above, dynamic rather than stative meaning is conveyed.
@@
 
+\noindent
 However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat5}) can be found.
@@
 
+\noindent
 The examples presented in this section show that although the reduplication does have a tendency to interact with volitional verbs and with activities and semelfactives due to its dynamic meaning, 
@@
 \settowidth\jamwidth{\citep[129]{XiaoMcEnery2004}}
-
 \ea
@@
 
+\noindent
 In comparison, the experiential aspect marker \obj{guo} cannot co\hyp{}occur with a reduplicated verb, 
@@
 
+\noindent
 The output of AA and ABAB does not change the grammatical category of the input (verb), but the output of AABB could have other categories such as adverb (\ref{ex:AABBadv}) or adjective (\ref{ex:AABBadj}).
@@
 
+\noindent
 AA and ABAB do not change the valency of the input verb, but AABB makes a transitive verb intransitive (\ref{ex:trans}).
@@
 
+\noindent
 The two groups also have different input and output constraints.
@@
 
+\noindent
 However, a morphological process can be productive, and it does not necessarily change the part of
@@
 
+\noindent
 In respond to this, we found counter-examples that show \obj{le} insertion in between V-\obj{gei3} (\ref{ex:Vgei}) as well as \obj{guan1-xin1} `close-heart, care for' (\ref{ex:guanxin}) is possible.
@@
 
+\noindent
 In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provide psycholinguistic evidence),
@@
 A reviewer questions the rationale for inserting an adverb within the reduplication,
-since an adverb also cannot be inserted into a VP consisting of a verb and its object, as shown below in (\ref{ex:vp}).
-
-\ea[*]{\label{ex:vp}
+since an adverb also cannot be inserted into a VP consisting of a verb and its object, as shown below in (i).%(\ref{ex:vp}).
+\begin{exe}
+\exi{(i)}[*]{\label{ex:vp}
 \gll \objex{kai1} \objex{qiao1qiao1de} \objex{men2}\\
@@
 \noindent
-The ungrammaticality of (\ref{ex:vp}) can be explained by the fact that almost all Mandarin Chinese adverbials are obligatorily pre-verbal \citep[50]{Ernst2014}, as illustrated in the example below in (\ref{ex:zouadv}).
-\ea\label{ex:zouadv}
+The ungrammaticality of (i)
+%(\ref{ex:vp}) 
+can be explained by the fact that almost all Mandarin Chinese adverbials are obligatorily pre-verbal \citep[50]{Ernst2014}, as illustrated in the example below in (ii).%(\ref{ex:zouadv}).
+\begin{exe}\label{ex:zouadv}
+\exi{(ii)}
 \ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}.\\
@@
 
+\noindent
 \citet[50]{Ernst2014} mentions that the only possible post-verbal adverbials are participant PPs (\textit{with somebody}),
@@
 
+\noindent
 Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
@@
 
+\noindent
 In this analysis, the first element in the reduplication is the actual verb, 
@@
 
+\noindent
 However, there are several arguments suggesting that the reduplication cannot be analyzed the same way as a verbal classifier phrase.
@@
 We found some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
-\ea%她看了他的脸一下。(CCL)
+\begin{exe}%她看了他的脸一下。(CCL)
+\exi{(i)}
 \gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
@@
 
-\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
+\exi{(ii)}%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
 \gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
@@
 
+\noindent
 Second, unlike verbal classifiers (\ref{ex:clf-num}), the \obj{yi} ‘one’ in A-\obj{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.
@@
 
+\noindent
 Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.\footnote{
@@
 
+\noindent
 Based on these observations, it seems inappropriate to view the reduplication as a kind of verbal classifier phrase.
@@
 
+\noindent
 This approach provides a unified account for adjectival and verbal reduplication.
@@
 
+\noindent
 To account for the variations in the phonology of the reduplication as well as 
@@
 
+\noindent
 \type{v-le-lr} is a direct subtype of the \type{perfective-lr}.
@@
 
+\noindent
 \type{v-le-lr} with all inherited constraints as given in (\ref{avm:vle}) inherits from \type{perfective-lr} and specifies that the first element in the output \textsc{phon} list is identified with the \textsc{phon} value of the input verb
@@
 
+\noindent
 \type{perfective-reduplication-lr} inherits from both \type{verbal-reduplication-lr} and \type{per\-fec\-tive\hyp{}lr}.
@@
 
+\noindent
 The analysis of (\ref{ex-he-tasted-the-soup-a-little-bit2}) is shown in tree format in
@@
 
+\noindent
 This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
@@
 
+\noindent
 This analysis would result in a mismatch between syntax and semantics, 

### 2025-11-18 Comments/replies-reviews3.tex
final changes for JL

--- 2025-11-11 replies-reviews3.tex
@@
 The author(s) used the English past tense marker ed as an example of a morphological process that does not change the category or valency of the verb.
-However, in generative syntax, tense is typically introduced by a functional projection, and ed is viewed as a surface- level morphological realization.
+However, in generative syntax, tense is typically introduced by a functional projection, and ed is viewed as a surface-level morphological realization.
 Therefore, it may be worth considering whether ed is the most appropriate example, especially as an example of a morphological process.
 
-\todo[inline]{Stefan, say something.}
+\textbf{Answer: } We replaced the example by adjectival inflection in German.
 
@@
 
-\textbf{Answer: } The \obj{ji4-gei3} example is suggested by another reviewer, as \citet[1282]{Her2006} claims that the V-\obj{gei3} sequence forms a single lexical item. 
+\textbf{Answer: } The \obj{ji4-gei3} example was suggested by another reviewer, as \citet[1282]{Her2006} claims that the V-\obj{gei3} sequence forms a single lexical item. 
 \citegen{Her2006} analysis cannot be elaborated here.

### 2025-11-18 reduplication-include.tex
final changes for JL

@@
 \settowidth\jamwidth{\citep[83]{Li1998}}
-\begin{sloppypar}
+%\begin{sloppypar}
 \ea\label{ex:syn-vi} Intransitive verb:
@@
 \ex\label{ex:syn-svc} In a Serial Verb Construction (SVC):
-		\ea \gll \objex{ta1} \ldots\, \objex{qing3} \objex{shi1fu} \objex{bang1mang2} \objex{kan4} \objex{na3li3} \objex{chu1-le} \objex{wen4ti1}.\\
+\ea 
+\gll \objex{ta1} \ldots\, \objex{qing3} \objex{shi1fu} \objex{bang1mang2} \objex{kan4} \objex{na3li3} \objex{chu1-le} \objex{wen4ti1}.\\
      she {}  ask master help look where come.out-\textsc{pfv} problem\\
 \glt `She \ldots\, asked the master to help have a look at where went wrong.'
-		\ex \gll \objex{ta1} \ldots\, \objex{qing3} \objex{shi1fu} \objex{bang1mang2} \obj{kan4-kan} \objex{na3li3} \objex{chu1-le} \objex{wen4ti1}.\\
+\ex 
+\gll \objex{ta1} \ldots\, \objex{qing3} \objex{shi1fu} \objex{bang1mang2} \obj{kan4-kan} \objex{na3li3} \objex{chu1-le} \objex{wen4ti1}.\\
      she {} ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
 \glt `She \ldots\, asked the master to help have a quick look at where went wrong.'
-		\z
-\z
-
-\end{sloppypar}
+\zl
+
+%\end{sloppypar}
 
@@
 
-\ea\label{ex:rel}
+\eal\label{ex:rel}
 % 随便看看的粉丝	群 (BCC 微博)
 
-\ea\label{ex:rel1}
+\ex\label{ex:rel1}
 % 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
@@
 \glt `They are jazz fans who wandered in to have a listen.'
-
-\z  
-\z
+\zl
 
@@
 But (\ref{ex:redup-neg}) shows that this is not the case.
-\ea \label{ex:redup-neg}
+\eal \label{ex:redup-neg}
 %\ea \gll \objex{wei4shen2me} \objex{wo3} \objex{bu4} \objex{kan4} \objex{ta1} \objex{qi2ta1} \objex{fang1mian4} de \objex{jin4bu4} \ldots\\
@@
 %\glt `Why don't I look a little bit at his progress in other aspects?'
-\ea\label{ex:neg1}
 % 你们只知道责备人家，全不想想自己。(CCL 1910s\1916\文学\小说笔记\1916_5 向恺然 留东外史.txt)
+\ex\label{ex:neg1}
 \gll \objex{ni3-men} \objex{zhi3} \objex{zhi1dao4} \objex{ze2bei4} \objex{ren2jia1}, \objex{quan2} \objex{bu4} \obj{xiang3-xiang} \objex{zi4ji3}.\\
@@
 \glt `The florist did not care about anything at all, did not tidy up anything.'
-
-\z
-\z
+\zl
 
@@
 However, examples in (\ref{ex:quantobj}) prove otherwise.
-\ea\label{ex:quantobj}
-\ea\gll \objex{ta1} \ldots\, \obj{kan4-kan} \objex{san1} \objex{ge4} \objex{ren2} \objex{he2} \objex{na4} \objex{liang4} \objex{che1zi} \dots\\
+\eal\label{ex:quantobj}
+\ex
+\gll \objex{ta1} \ldots\, \obj{kan4-kan} \objex{san1} \objex{ge4} \objex{ren2} \objex{he2} \objex{na4} \objex{liang4} \objex{che1zi} \dots\\
 he {} look-look three \textsc{clf} person and that \textsc{clf} car\\\jambox{(CCL)}
@@
 
-\ex \gll \objex{wo3} \objex{xiang3} \objex{zhuo2zhong4} \obj{shuo1-shuo} \objex{liang2} \objex{ge4} \objex{hu4xiang1} \objex{lian2xi4-zhe} \objex{de} \objex{zhong4yao4} \objex{cheng2guo3}: \ldots\\
+\ex 
+\gll \objex{wo3} \objex{xiang3} \objex{zhuo2zhong4} \obj{shuo1-shuo} \objex{liang2} \objex{ge4} \objex{hu4xiang1} \objex{lian2xi4-zhe} \objex{de} \objex{zhong4yao4} \objex{cheng2guo3}: \ldots\\
 I want emphasize say-say two \textsc{clf} each.other connect-\textsc{dur} \textsc{de} important outcome\\
 \glt `I want to highlight two important interconnected outcomes.'
-\z\z
+\zl
 
@@
 However, we also find examples of reduplicated accomplishments followed by quantized objects in CCL and BCC, as shown in (\ref{ex:qobj}).
-\ea\label{ex:qobj}
+\eal\label{ex:qobj}
 % 吃?吃三种?局，一是吃口味，一是吃氛围，一是吃免费。(CCL 2010s\201x\网络语料\微博\weibo_062.txt)
-\ea\label{ex:qobj1}
+\ex\label{ex:qobj1}
 % 其实他一直想写写两位老师 （CCL 2010s\201x\网络语料\微信公众号\Wechat_123.txt）
@@
 %农民们就卖卖五样东西，大酱、葱、煎饼、鸡蛋、苞米。（CCL 2010s\201x\网络语料\微信公众号\Wechat_157.txt）
-\z\z
+\zl
 
@@
 
-\ea
-  \ea\label{ex:le-dyn-look}
+\eal
+\ex\label{ex:le-dyn-look}
 \gll \objex{Wu2} \objex{Xu4mang2} \objex{kan4-le} \objex{zuo4-an4} \objex{shi2} \objex{liu2xia4} de \objex{jiao3yin1} \ldots\\ 
@@
 \glt `Wu Xumang looked a little bit at the footprint left when the crime was committed.'
-  \z
-\z
+\zl
 
@@
 \begin{sloppypar}
-\ea\label{ex:nonvol}
-\ea
+\eal\label{ex:nonvol}
+\ex
 \gll \objex{ke3shi4} \objex{xian4mu4jin1}, \objex{da4jia1} \objex{ye3} \objex{zhi3hao3} \obj{wei3qu1-wei3qu1} le.\\
@@
 \glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
-\z
-\z
+\zl
 \end{sloppypar}
@@
 
-\settowidth\jamwidth{\citep[155]{XiaoMcEnery2004}}
-\ea
-\ea[?]
-{\gll \objex{ta1} \obj{bing4-bing} \objex{jiu4} \objex{hao3} le.\\
-he be.sick-be.sick then well \textsc{ptc}\\ \jambox{\citep[155]{XiaoMcEnery2004}}
-Intended: `He was sick for a little while and then got well.'}\label{ex:redup-stat}
-
-\ex[]
-{\gll \objex{ta1} \obj{kan4}-\obj{le}-\obj{kan4} \objex{na4} \objex{chang3} \objex{bi3sai4}.\\
+%\settowidth{\jamwidth}{\citep[155]{XiaoMcEnery2004}}
+\eal
+\ex[?]{\label{ex:redup-stat}
+\gll \objex{ta1} \obj{bing4-bing} \objex{jiu4} \objex{hao3} le.\\
+     he be.sick-be.sick then well \textsc{ptc}\\ \hfill{\citep[155]{XiaoMcEnery2004}}
+\glt Intended: `He was sick for a little while and then got well.'}
+\ex[]{\label{ex:redup-actV}
+\gll \objex{ta1} \obj{kan4}-\obj{le}-\obj{kan4} \objex{na4} \objex{chang3} \objex{bi3sai4}.\\
       he watch-\textsc{pfv}-watch that \textsc{clf} competition\\
-\glt `He watched that competition for a little while.' \\}\label{ex:redup-actV}
-
-\ex[]
-{\gll \objex{ta1} \obj{ke2sou4-ke2sou4} \objex{jiu4} \objex{hao3} le.\\
+\glt `He watched that competition for a little while.'}
+\ex[]{\label{ex:redup-semel}
+\gll \objex{ta1} \obj{ke2sou4-ke2sou4} \objex{jiu4} \objex{hao3} le.\\
      he cough-cough then well \textsc{ptc}\\
-\glt `He coughed a little bit and then got well.'}\label{ex:redup-semel}
-\z
-\z
+\glt `He coughed a little bit and then got well.'}
+\zl
 
@@
 \ea\label{ex:redup-achi-stat4}
-\gll \objex{wo3} \objex{zhen1} \objex{xiang3} \obj{bing4-yi-bing4}, \objex{xie1} \objex{ta1} \objex{ge} \objex{shi2} \objex{tian1} \objex{ban4} \objex{yue4}.\\
+\gll \objex{wo3} \objex{zhen1} \objex{xiang3} \obj{bing4-yi-bing4}, \objex{xie1} \objex{ta1}
+\objex{ge} \objex{shi2} \objex{tian1} \objex{ban4} \objex{yue4}.\\
 I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
@@
 \exi{(i)}
+\ea
 \gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
@@
 
-\exi{(ii)}%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
+\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
 \gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
@@
 \glt `He just took a look at the glass and the glass just broke.'
-\z
+\zl
 We think it has to do with the length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.

### 2025-11-18 reduplication.tex
final changes for JL

--- 2025-11-16 main.tex
@@
+%% -*- coding:utf-8 -*-
 % \documentclass[%
@@
 %  ]{lin}
-\documentclass[a4paper]{CUP-JNL-LIN}%[ruler,draftrules]
 
-\articletype{RESEARCH ARTICLE}
-\jname{Journal of Linguistics}
-\jyear{2027}
-\jvol{0}
-%\jissue{1}
-\jdoi{10.1017/\ldots}
+% The new styles break the alignment of \glt from gb4e if jambox is used.
+%\documentclass[a4paper]{article}%[ruler,draftrules]
+\documentclass[a4paper]{scrartcl}
 
-\copyrightline{\textcopyright\ The Author(s) 2025. This is an Open Access article,
-distributed under the terms of the Creative Commons Attribution licence (http://creativecommons.org/licenses/by/4.0/),
-which permits unrestricted re-use, distribution, and reproduction in any medium, provided the original work is properly cited.}
+%\copyrightline{\textcopyright\ The Author(s) 2025. This is an Open Access article,
+%distributed under the terms of the Creative Commons Attribution licence (http://creativecommons.org/licenses/by/4.0/),
+%which permits unrestricted re-use, distribution, and reproduction in any medium, provided the original work is properly cited.}
+
+\RequirePackage{amsmath} % loaded by JL
 
@@
 
-\begin{Frontmatter}
-\title{Deliminative verbal reduplication in Mandarin Chinese}
+\title{{\large\normalfont To appear: Journal of Linguistics, 2027, vol.\ 63}\\~\\
+Deliminative verbal reduplication in Mandarin Chinese}
 
-\author[1]{Yanru Lu\corresp{\email{yanru.lu@hu-berlin.de}}}%\orcid{0000-0002-5915-7315}
-\author[1]{Stefan Müller\corresp{\email{st.mueller@hu-berlin.de}}}%\orcid{0000-0003-4413-5313}
+\author{Yanru Lu \& Stefan Müller\\Humboldt-Universität zu Berlin}
 
-\authormark{Yanru Lu \& Stefan Müller}
-
-\address[1]{\orgname{Humboldt-Universität zu Berlin, Institute for German language and linguistics},
-  \orgaddress{\street{Unter den Linden 6}, \postcode{D-10099 Berlin}, \country{Germany}}}
-
-\received{08 July 2023}
-\revised{01 August 2025}
-\accepted{14 November 2025}
-
-% \author[1]{\givenname{Yanru} \surname{Lu}}
-% \address[1]
-% {%
-%   \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
-%   \addr{Unter den Linden 6}, % Street 
-%   \addr{D-10099 Berlin}, % Postcode etc
-%   \cnty{Germany}  % Country
-%   \email{yanru.lu@hu-berlin.de} % email
-% }
-
-% \author[2]{\givenname{Stefan} \surname{Müller}}
-% \address[2]
-% {%
-%   \inst{Humboldt-Universität zu Berlin}, % Institution name should be in \inst
-%   \addr{Unter den Linden 6}, % Street 
-%   \addr{D-10099 Berlin}, % Postcode etc
-%   \cnty{Germany}  % Country
-%   \email{st.mueller@hu-berlin.de} % email
-% }
+\maketitle
 
@@
 }
-\keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}
-
-\end{Frontmatter}
+%\keywords{verbal reduplication, Mandarin Chinese, HPSG, Minimal Recursion Semantics}
 

### 2025-11-19 reduplication-include.tex
use biblatex now to get mass citations. biblatex gets the separation right (, instead of ;) and also the punctuation after the name.

@@
 
-In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g.
-\citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}).
+In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \parencites[e.g.][204--205]{Chao1968}[232]{LiThompson1981}[14]{Li1996}[70]{Dai1997}[382--383]{Zhu1998}[420--421]{Xing2000}[48]{Chen2001}[288]{Tsao2001}[11--12]{Yang2003}[Sec.\,4.3]{XiaoMcEnery2004}.
 This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
@@
 
-The reduplication has a \textit{delimitativeness} meaning (e.g.\ \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec.\,4.3]{XiaoMcEnery2004}).
+The reduplication has a \textit{delimitativeness} meaning \parencites[e.g.][204--205]{Chao1968}[232]{LiThompson1981}[14]{Li1996}[70]{Dai1997}[382--383]{Zhu1998}[420--421]{Xing2000}[48]{Chen2001}[288]{Tsao2001}[11--12]{Yang2003}[Sec.\,4.3]{XiaoMcEnery2004}.
 To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
-and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
-Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \citeauthor{Smith1991} (\citeyear[356]{Smith1991}; \citeyear[199--120]{Smith1994}), \citet[14]{Li1996} and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
+and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \parencites[14]{Li1996}[149--150]{XiaoMcEnery2004}.
+Besides delimitativeness, \citet[204]{Chao1968}, \citet[276]{Fan1964}, \textcites[356]{Smith1991}[199--120]{Smith1994}, \citet[14]{Li1996}, and \citet[290--291]{Tsao2001} suggest that the reduplication signifies \textit{tentativeness}, which can be used
 ``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
@@
 
-The semantics of the reduplication has the properties of transitoriness,  holisticity  and dynamicity \citetext{\citealp[70--79]{Dai1997}; \citealp[155--159]{XiaoMcEnery2004}}.
+The semantics of the reduplication has the properties of transitoriness,  holisticity  and dynamicity \parencites[70--79]{Dai1997}[155--159]{XiaoMcEnery2004}.
 It presents the situation as a  transitory and non\hyp{}decomposable whole.
@@
 
-The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \citetext{\citealp[83--84]{Li1998}; \citealp[114--115]{Chen2005}}.
-This is  because the reduplication already contains a quantity meaning \citetext{\citealp[84]{Li1998}; \citealp[114--115]{Chen2005}}, namely a short duration or a small extent,
-which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}; \citealt[333]{SuiHu2016}).
+The reduplication is incompatible with an expression that quantifies the duration or the extent of the event expressed in the sentence (\ref{ex:syn-quan}) \parencites[83--84]{Li1998}[114--115]{Chen2005}.
+This is  because the reduplication already contains a quantity meaning \parencites[84]{Li1998}[114--115]{Chen2005}, namely a short duration or a small extent,
+which cannot be measured on a concrete scale \parencites[155]{XiaoMcEnery2004}[333]{SuiHu2016}.
 This results from the properties of reduplication rather than the verb itself,
@@
 %And inflections of tense in German do not change the valency of the input verb.
-Further, if \obj{le} is considered to be a morphological element (e.g.\ \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
+Further, if \obj{le} is considered to be a morphological element \parencites[e.g.][101--102]{Huangetal2009}[246]{MuellerLipenkova2013}, the insertion of \obj{le} does not have to be viewed as a syntactic
 process either.
@@
 \noindent
-In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provide psycholinguistic evidence),
+In any case, since reduplication is not compounding (\cites[149--150]{Sui2018}{GaoEtAl2021} provide psycholinguistic evidence),
 and the patterns discussed here constitute a different process than the AABB pattern
@@
 Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as \textit{reduplication}) in other languages
-than syntactic reduplication (below as \textit{repetition}; \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).\footnote{
+than syntactic reduplication (below as \textit{repetition}; \cites[31]{Gil2005}[1--2]{Forza2016}).\footnote{
 We do not claim that the syntactic analyses of reduplication discussed in \sectref{sec:prev} consider verbal reduplication in Mandarin Chinese to be syntactic repetition.
@@
 The present study does not argue for a {NP} or a {DP} analysis and simply takes over the illustration provided in the cited papers.}
-Dynamic and volitional verbs have the features [init proc] and are therefore located under \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.
-Achievement verbs possess the feature [res] and reside under \textit{res}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}. 
+Dynamic and volitional verbs have the features [init proc] and are therefore located under \textit{init} and \textit{proc}  \parencites[24]{Arcodiaetal2014}[147]{BascianoMelloni2017}.  
+Achievement verbs possess the feature [res] and reside under \textit{res}  \parencites[24]{Arcodiaetal2014}[147]{BascianoMelloni2017}. 
 Stative verbs do not contain a \textit{proc}P \citep[152]{BascianoMelloni2017}.
@@
 Notice that  the lexical rules above also produce AB-\textit{yi}-AB and AB\hyp{}\textit{le}\hyp{}\textit{yi}\hyp{}AB for disyllabic input verbs.
-Although these forms are considered unacceptable by some authors \citetext{\citealp[30]{LiThompson1981}; \citealp[275--276]{Hong1999};  \citealp[160]{BascianoMelloni2017}; \citealp[239]{YangWei2017}},
+Although these forms are considered unacceptable by some authors \parencites[30]{LiThompson1981}[275--276]{Hong1999}[160]{BascianoMelloni2017}[239]{YangWei2017}, 
 \citet[269]{Fan1964} and \citet[143]{Sui2018} consider AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognize that these two forms are rare.
@@
 This suggests that  even though AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB might be degraded, they are not ungrammatical \textit{per se}.
-The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \citetext{\citealp[274]{Fan1964}; \citealp[15]{Zhang2000}; \citealp[239]{YangWei2017}; \citealp[143]{Sui2018}}, but we argue that it is not an issue of grammaticality.
+The reason for this degradedness is probably phonological, since AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB contain too many syllables \parencites[274]{Fan1964}[15]{Zhang2000}[239]{YangWei2017}[143]{Sui2018}, but we argue that it is not an issue of grammaticality.
 Thus, they can still be produced via the lexical rules posited above, but are ruled out or degraded due to a general phonological constraint.\footnote{
-One reviewer suggests that given that AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}),
-these rare occurrences can be seen as relics of this usage.
+One reviewer suggests that given that AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB were
+possible in previous stages of the language
+\parencites[see][15]{Zhang2000}[160--161]{BascianoMelloni2017}, these rare occurrences can be seen as relics of this usage.
 }
@@
 Specifically, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can be considered as the compound of a reduplicated monosyllabic verb (A) and a noun (B).\footnote{
-    \citet[64--65]{Huang1984} and \citeauthor{Her1996} (\citeyear[Sec.\,2]{Her1996}; \citeyear[Sec.\,3.1]{Her2010}) argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
+    \citet[64--65]{Huang1984} and \textcites[Sec.\,2]{Her1996}[Sec.\,3.1]{Her2010} argue that some of these V-O combinations are compounds, some are phrases, and some have dual status (both compounds and phrases).
     Following this approach, AAB, A-\textit{yi}-AB and A-\textit{le}-AB can (also) be considered as the phrasal combination of a reduplicated verb and its object.

### 2025-12-28 reduplication-include.tex
changes from online proofreading

@@
 It contributes more empirical evidence and 
-offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, HPSGHandbook-2}) to this phenomenon 
+offers a novel analysis of this phenomenon in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, HPSGHandbook-2})  
 using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}) as the semantic representation formalism.
@@
      she {}  ask master help look where come.out-\textsc{pfv} problem\\
-\glt `She \ldots\, asked the master to help have a look at where went wrong.'
+\glt `She \ldots\, asked the master to help have a look at where the problem was.'
 \ex 
@@
      she {} ask master help look-look where come.out-\textsc{pfv} problem\\ \jambox{({CCL})}
-\glt `She \ldots\, asked the master to help have a quick look at where went wrong.'
+\glt `She \ldots\, asked the master to help have a quick look at where the problem was.'
 \zl
@@
 \ea\label{ex:rel-suihu}
-\ea[]{ \gll {[[\objex{tong2xue2-men}} \objex{tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
-student-\textsc{pl} discuss \textsc{de} this \textsc{clf} question very important\\
+\ea[]{
+\gll {[[\objex{tong2xue2-men}} \objex{tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
+      \hphantom{[[}student-\textsc{pl} discuss \textsc{de} this \textsc{clf} question very important\\
 \glt `The question that the students discussed is very important.'}
 
-\ex[*]{ \gll {[[\objex{tong2xue2-men}} \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
-student-\textsc{pl} discuss-discuss \textsc{de} this \textsc{clf} question very important\\}
+\ex[*]{ 
+\gll {[[\objex{tong2xue2-men}} \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
+      \hphantom{[[}student-\textsc{pl} discuss-discuss \textsc{de} this \textsc{clf} question very important\\}
 %\glt `The question that the students discussed is very important.'}
 
-\ex[]{ \gll {[[\objex{tong2xue2-men}} \objex{xu1yao4} (\objex{zai4}) \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
-    student-\textsc{pl} need again discuss-discuss \textsc{de} this \textsc{clf} question very important\\
+\ex[]{
+\gll {[[\objex{tong2xue2-men}} \objex{xu1yao4} (\objex{zai4}) \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
+      \hphantom{[[}student-\textsc{pl} need again discuss-discuss \textsc{de} this \textsc{clf} question very important\\
 \glt `The question that the students need to discuss (again) is very important.'}
@@
     We asked 10 native speakers from different regions in Mainland China. 
-    All found the sentence weird at first glace, but considered that the acceptability can be greatly improved 
+    All found the sentence weird at first glance, but considered that the acceptability can be greatly improved 
     by adding more information to support the use of reduplication, such as \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{zheng4wu4wei1bo2} `the government affairs Weibo account that you look at \textit{casually}'.
@@
 \ex\label{ex:sheng}%我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
-\gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi}\ldots \\
+\gll \objex{wo2men} \objex{nv3ren2} [\ldots] \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1}
+\objex{hai2zi} [\ldots] \\
 we women {} only can give.birth.to-give.birth.to child\\\jambox{(BCC)}
@@
 let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
-\glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
+\glt `Let her have a try at giving birth to a child and then she will know the bittersweetness of being a mother.'
 \z
@@
 \ea\label{ex:guanxin}%许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
-\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-}\obj{xin1}.\\
+\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-}\objex{xin1}.\\
 many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\\jambox{(CCL)}
@@
 Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
-This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in between.
+Expansion is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in between.
 \ea\label{ex:inVCP}%开两次门
@@
 \z\z
-For reduplication, this is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
+For reduplication, expansion is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
 \ea\label{ex:inVV}
@@
 \z\z
-The above two tests seem to indicate a lexical analysis for reduplication.
+The above two tests indicate a lexical analysis for reduplication.
 
@@
 
-In sum, we maintain that verbal reduplication in Mandarin Chinese is better off analyzed as a morphological phenomenon.
+In sum, we maintain that verbal reduplication in Mandarin Chinese is better analyzed as a morphological phenomenon.
 
@@
 
-Previous analyses on the reduplication in Mandarin Chinese and in other languages can be classified
+Previous analyses of the reduplication in Mandarin Chinese and in other languages can be classified
 into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect modifier (\sectref{sec:asp}), and
@@
   \label{fn:vclpron}
-One reviewer notes that the objects that can be placed in between the verbal classifier phrase is usually limited to pronouns and proper nouns.
+One reviewer notes that the objects that can be placed in between the verbal classifier phrase are usually limited to pronouns and proper nouns.
 We found some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
@@
 We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
-In this case, it is easy to interpret \obj{yi2} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
+In this case, it is easy to interpret \obj{yi2} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of actions taking place,
 but as duration adverbials as a whole,
-thus differing them from ``actual'' verbal classifier phrases with other numerals.
+thus distinguishing hem from ``actual'' verbal classifier phrases with other numerals.
 }
@@
 \noindent
-Based on these observations, it seems inappropriate to view the reduplication as a kind of verbal classifier phrase.
+Based on these observations, it seems inappropriate to view reduplication as involving a kind of verbal classifier phrase.
 
@@
 \citet{YangWei2017} did not spell out the exact analysis.
-We infer the analysis for reduplication based on \citet{Tsai2008},
+We worked out the analysis for reduplication based on \citet{Tsai2008},
  and show in Appendix~\ref{app:tsai} that \citeauthor{Tsai2008}'s (\citeyear{Tsai2008}) system 
@@
 using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}). %, as proposed in \citet{LuMueller2021}.
-MRS is one instance of underspecified semantics as is currently used in theoretical and
+MRS is an instance of underspecified semantics as is currently used in theoretical and
 computational work in HPSG (\citealt[Section~6]{KR2024a}, \citealt[Section~3]{BFO2002a-u},
@@
 The label of the output \iboxb{2} is identified with the label of the input and with the
-label of the delimitative relation, hence \type{delimitative-rel} is treated as a modifier.  Further
+label of the delimitative relation, hence \type{delimitative-rel} is treated as an intersective modifier.  Further
 relations can be added at the beginning of the \textsc{rels} list to allow for the additional
@@
         phon & \etag $\oplus$ \phonliste{ le } $\oplus$ \etag\\
-        \punk{synsem\textbar loc \textbar cont}{ [ltop & \2\\
+        \punk{synsem\textbar loc\textbar cont}{ [ltop & \2\\
             ind  & \3]}\\ 
@@
         phon & \1 $\oplus$ \phonliste{ le }\\
-        \punk{synsem\textbar loc \textbar cont\textbar ltop}{ \2}\\ 
+        \punk{synsem\textbar loc\textbar cont\textbar ltop}{ \2}\\ 
         rels & <[\type*{perfective-rel}\\
@@
         lex-dtr & [phon & \1\\
-        synsem\textbar loc \textbar cat  & [ head & verb\\
+        synsem\textbar loc\textbar cat  & [ head & verb\\
         cont & [ltop & \4\\
@@
 input verb \iboxb{3} to ensure that they apply to the same event denoted by the input verb. 
-The label of the \type{delimitative-rel} and the input verb are identified (\type{delimitative-rel} is a modifier) 
-and this shared label is embedded under the \type{perfective-rel}.
+The label of the \type{delimitative-rel} and the input verb are identified (\type{delimitative-rel}
+is an intersective modifier) and this shared label is embedded under the \type{perfective-rel}.
 
@@
 \z
-So the delimitative relation is treated as an adjunct to the main relation of the verb, 
+So the delimitative relation is treated as an intersective modifier to the main relation of the verb, 
 and the perfective relation scopes over both the main relation and the delimitative relation.
@@
 and \type{a-le-a-lr}, as shown in (\ref{avm:AleA}). %(\ref{avm:AleA}).
-They take over the semantic change to the input from \type{perfective\hyp{}reduplication\hyp{}lr}, but specify the \textsc{phon} value differently.
+They inherit the semantic change to the input from \type{perfective\hyp{}reduplication\hyp{}lr}, but specify the \textsc{phon} value differently.
 Specifically, \type{a\hyp{}le\hyp{}yi\hyp{}a\hyp{}lr} specifies the middle phonological material as
@@
 A reviewer wants to know what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements.
-The possible historical and phonological reasons are discussed in Appendix~\ref{app:hist}.
+The possible historical and phonological reasons for \emph{yi} and \emph{le} being the phonological elements left
+in the reduplication structure are discussed in Appendix~\ref{app:hist}.
 In this analysis, the subtypes of \type{verbal-reduplication-lr} (\ref{avm:AyiA}, \ref{avm:AleA}) prevent phonological materials other than \phonliste{ le } and \phonliste{ yi } from appearing in between the reduplication by specifying what can appear in the \etag list and what not.
@@
 the \type{a-le-a-lr} lexical rule. The arguments of \obj{chang2} `to taste' are represented within the \spr and
-the \compsl (see \citealt{GSag2000a-u} for English) and the respective argument NPs are linked to the
+the \compsl (see \citealt[23]{GSag2000a-u} for English) and the respective argument NPs are linked to the
 arguments of \type{taste}: the subject is \textsc{arg1}, the agent, and the object is \textsc{arg2},
@@
 \citet[269]{Fan1964} and \citet[143]{Sui2018} consider AB-\textit{yi}-AB and AB-\textit{le}-\textit{yi}-AB to be possible, even though they both recognize that these two forms are rare.
-Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Early Mandarin %(12th to 20th centuries)
+Indeed, a few examples of AB\hyp{}\emph{yi}\hyp{}AB and AB\hyp{}\emph{le}\hyp{}\emph{yi}\hyp{}AB in Old Mandarin %(12th to 20th centuries)
  (\ref{ex:AByiAB-lu}--\subref{ex:AByiAB-pu}) and Modern Mandarin (\ref{ex:AByiAB-rou1}--\subref{ex:ABleyiAB-ccl}) were found.
@@
 \gll \objex{ji3duo1} \objex{san3luan4}-zhe de \objex{chuan2} \objex{li3} de \objex{deng1guang1}, \objex{ye3} \objex{hu1yin1hu1mie4} de \obj{bian4huan4-le-yi-bian4huan4} \objex{wei4zhi}.\\
-many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-chang position\\ \jambox{(CCL)}
+many scattered-\textsc{dur} \textsc{de} boat in \textsc{de} light also flicker \textsc{de} change-\textsc{pfv}-one-change position\\ \jambox{(CCL)}
 \glt `Many scattered lights in the boats also changed their positions a little bit, flickering.'
@@
 \ea
-\gll \objex{te4yi4} \objex{gong1neng2} de \objex{yan2jiu1zhe3}-men \objex{bu4fang2} \objex{ru2ci3} \obj{shi4-yi-shi4-kan4} \ldots\\
+\gll \objex{te4yi4} \objex{gong1neng2} de \objex{yan2jiu1zhe3}-men \objex{bu4fang2} \objex{ru2ci3} \obj{shi4-yi-shi4-kan4} [\ldots]\\
 special power \textsc{de} researcher-\textsc{pl} may.as.well such try-one-try-look\\ \jambox{(CCL)}
@@
 \gll \objex{dan4shi4} \objex{dui4} \objex{fa1} \objex{mei2} \objex{fa1}-\objex{guo} \objex{he2ge2-zheng4}, \objex{yi3jing1} \objex{shuo1} \objex{bu4} \objex{qing1} le, \objex{xu1yao4} \obj{cha2-yi-cha2-kan4}.\\
-but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-chek-look\\ \jambox{(CCL)}
+but about issue not issue-\textsc{exp} conformity-certificate already say not clealy \textsc{ptc} need check-one-check-look\\ \jambox{(CCL)}
 \glt `But one already cannot say it clearly anymore, whether a certificate of conformity is issued or not. One needs to have a check and see.'
@@
 and the second syllable in A-\obj{li}-AB occupies an unstressed position.
-We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
+We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupy an unstressed position.
 This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.

### 2025-12-30 reduplication-include.tex
fix typo esp in figure 3 (fig-he-tasted-the-soup-a-little-bit)

@@
     }
-[\avm{ [phon & \1 \phonliste{ chang2 }\\
+[\avm{ [phon & \1 \phonliste{ \obj{chang2} }\\
        synsem\textbar loc & [cat  & [ head  & verb\\
@@
 \ex\label{ex:AByiAB-rou2}
-\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, you \obj{ming2xiang3}-\obj{le-yi}-\obj{ming2xiang3}.\footnotemark\\
+\gll \objex{ta1} \obj{wei1xiao4-le-yi-wei1xiao4}, \objex{you4} \obj{ming2xiang3}-\obj{le-yi}-\obj{ming2xiang3}.\footnotemark\\
 he smile-\textsc{pfv}-one-smile and meditate-\textsc{pfv}-one-meditate\\
@@
 Similarly, \obj{zai4} `\textsc{prog}' and \obj{zhe} `\textsc{dur}' are both imperfective aspects but also occur in different syntactic positions.
+We prefer a uniform treatment.
 
